### 2011-05-12 ms.tex
Added the 'first' draft of the paper

\documentclass[12pt,manuscript]{aastex}
%%\documentclass[twocolumn]{emulateapj}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{nkarlsson@physics.umn.edu}
\newcommand{\expval}[1]{\left\langle #1 \right\rangle}
\newcommand{\RA}[3]{#1$^{\mathrm{h}}$#2$^{\mathrm{m}}$#3$^{\mathrm{s}}$}
\newcommand{\Dec}[3]{#1$^{\circ}$#2\arcmin#3\arcsec}

\shorttitle{Coma Cluster Observations with VERITAS}
\shortauthors{VERITAS collaboration}

\begin{document}

%\title{VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
\author{N. Karlsson\altaffilmark{1,2}, M. Pohl\altaffilmark{3,4}}
\affil{(the VERITAS collaboration)} 
%%\email{nkarlsson@physics.umn.edu}
\and
\author{C. Pfrommer\altaffilmark{5,6},
A. Pinzke\altaffilmark{7}}

\altaffiltext{1}{Corresponding author: N. Karlsson, nkarlsson@physics.umn.edu}
\altaffiltext{2}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
\altaffiltext{3}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
\altaffiltext{4}{ Institut fu\"r Physik und Astronomie, Universita\"t Potsdam, 14476 Potsdam-Golm, Germany}
\altaffiltext{5}{Heidelberg Institute	for Theoretical	Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
\altaffiltext{6}{Canadian Institute for Theoretical Astrophysics, University of Toronto, Toronto, ON, M5S 3H8, Canada}
\altaffiltext{7}{University of California, Santa Barbara, CA 93106}

%%\journalinfo{The Astrophysical Journal}
%%\submitted{preprint}

\begin{abstract}
Theoretical models of galaxy clusters suggest they may be sources of very high-energy (VHE) gamma-ray emission. Observations of radio halos and relics in clusters indicate populations of relativistic electrons and positrons, which are either injected into the intra-cluster medium and accelerated by turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with the intra-cluster gas. Those interactions would also produce gamma rays through the decay of neutral pions. Reported here are observations of the Coma cluster of galaxies with the VERITAS array of imaging Cherenkov telescopes. The observations were made between March and May 2008. Radio observations at 1.41 GHz taken with the Green Bank Telescope and X-ray observations with the ROSAT All-Sky survey was used to a priori select regions of interest in the field of view. No significant VHE gamma-ray emission from the Coma cluster was detected by VERITAS. Flux upper limits at the 99\% confidence level were obtained for the cluster core, both as a point source and a mildly extended source centered at the cluster core, and for a select few other cluster members. The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields in the cluster. The cosmic-ray pressure is... The observations imply a lower limit on the intra-cluster magnetic field of X$\mu$G. Finally, a constraint on the dark matter annihilation cross section is derived, $\expval{\sigma v}=$.
\end{abstract}

%\keywords{cosmic rays: interactions --- galaxies --- galaxy clusters -- VHE}
\keywords{cosmic rays --- gamma rays: observations --- gamma rays: VHE --- galaxies: clusters: general --- galaxies: clusters: individual: Coma (ACO 1656)}

\section{Introduction}
Clusters of galaxies are the largest observable structures in the Universe, with typical diameters of several Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. These gravitationally bound objects have formed on increasingly larger scales during the evolution of the Universe through the process of cosmic structure formation \citep{article:Voit:2005}. Although most of the cluster mass comes from large amounts of dark matter embedded in a cluster, as indicated by cluster dynamics and weak gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}, gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass. Individual galaxies contribute only a small amount (about 5\%) to the cluster mass. The ICM gas mass also comprise a significant fraction of the observable (baryonic) matter in the Universe.

The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.][]{article:Petrosian:2001}. Heating of this plasma is thought to come primarily from collisionless structure-formation shocks, due to accretion and merger processes. Such shocks and turbulences in the ICM gas and magnetic fields also provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} provide further indications of relativistic particle populations in clusters, although the interpretation of these observations have been disputed \citep[see, e.g.][]{article:Wik_etal:2009}.

Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration in the ICM is an efficent process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected. The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{Charged pions decay to muons/antimuons which subsequently decay to electrons/positrons.} and the neutral pion to gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$) and the sheer size of a cluster, CR hadrons will be confined in the cluster on very long timescales \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.

Depending on the CR energy density, quantified by the fraction of energy in CRs to the thermal energy in a cluster, $\eta=\expval{ E_{\mathrm{CR}}/E_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected. This fraction could plausibly be as large as 50\% \citep{article:Ryu_etal:2003}, but a much smaller fraction of only a few percent is required in order to produce a gamma-ray flux observable with current generation gamma-ray telescopes.

Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example cosmic microwave background (CMB) photons, on ultra-relativistic leptons. Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.

While several observations of clusters of galaxies have been made with satellite-borne and ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.  Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several galaxy clusters in the MeV to GeV band. Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009, article:Aleksic_etal:2010}.

The Coma cluster of galaxies (ACO 1656) is one of the most thouroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}. Located at a distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest and also one of the most massive clusters \citep[$M \sim 10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}. It hosts both a giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested that the relic is an infall shock. Extended soft X-ray (SXR) emission is evident from the ROSAT All-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo. As such it is a natural candidate for gamma-ray observations. In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with its constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.

\section{Observations and Analysis}
The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an altitude of 1268 m a.s.l. at the Fred Lawrence Whipple Observatory in southern Arizona (31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes is equipped with a 499 pixel camera covering a 3.5$^{\circ}$ field of view. The array, completed in the spring of 2007, is designed to detect gamma-ray emission from astrophysical objects in the energy range from 100 GeV to more than 30 TeV. The energy resolution is about 15\% and the angular resolution (68\% containment) is about 0.1$^{\circ}$ per event at 1 TeV. The sensitivity of the array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009. The move had no impact on the Coma cluster data set.}

The Coma cluster was observed with VERITAS between March and May in 2008 with all four telescopes fully operational. The total exposure amounts to 18.6 hours of quality-selected live time, i.e. time periods of astronomical darkness, clear sky conditions and without technical problems with the array. The center of the Coma cluster was tracked in \emph{wobble} mode, where the expected source location is offset from the center of the field of view, to allow for simultaneous background estimation \citep{article:Formin_etal:1994}. All of the observations were made in a small range of zenith angles averaging $\sim 21^{\circ}$.

The data analysis was performed following the standard VERITAS procedures described in \citet{inproc:Cogan_etal:2007} and \citet{inproc:Daniel_etal:2007}. Prior to event reconstruction and selection, all shower images are calibrated and cleaned. Showers are then reconstructed for events with at least two contributing telescope images that pass the following quality selection criteria: more than four participating pixels in the camera, number of photoelectrons in the image is larger than 75, and the distance from the image centroid to the center of the camera is less than $1.43^{\circ}$. These quality selection criteria impose an energy threshold\footnote{Defined as$\ldots$} of about 220 GeV. In addition, events for which only images from the two closest-spaced telescopes\footnote{In the array configuration prior to summer 2009, two telescopes had a separation of only 35 m.} survive quality selection are rejected, as they introduce an irreducible high background rate, due to local muons, degrading the instrument sensitivity \citep{article:MaierKnapp:2007}.

Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters \citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images \citep{inproc:Hillas:1985}. The gamma-hadron separation cuts used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level) and a photon index of -2.4 using data taken on the Crab Nebula during the same epoch and are termed \emph{standard} cuts. Because the VHE gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about -2.3, these standard cuts are suitable.

The Coma cluster is a complex region with many plausible sites for gamma-ray emission.

The ring background model \citep{article:Aharonian_etal:2001} was used to produce skymaps of the VERITAS excess over the field of view. The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess.

%The observed radio halo and thermal X-ray emission in the Coma cluster suggest that the VHE gamma-ray emission should have a similar spatial extension.

\begin{figure*}
\begin{center}
\scalebox{0.5}{\plotone{f1a.eps}}
\scalebox{0.5}{\plotone{f1b.eps}}
\end{center}
\caption{Skymaps.}
\label{fig:skymaps}
\end{figure*}

\section{Results and Discussion}
No significant excess was detected with VERITAS in the Coma cluster.
A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} and assuming Gaussian background.

\begin{deluxetable}{lccccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{Flux upper limits for regions of interest in the Coma galaxy cluster}
\tablehead{
\colhead{Source} &
\colhead{RA} &
\colhead{Dec} &
\colhead{RoI} &
\colhead{Excess} &
\colhead{Significance\tablenotemark{a}} &
\multicolumn{2}{c}{Flux U.L.\tablenotemark{b}}\\
\colhead{} & \colhead{[J2000]} & \colhead{[J2000]} & \colhead{[deg]} & \colhead{[counts]} & \colhead{[$\sigma$]} & \multicolumn{2}{c}{[$10^{-8}$ ph. m$^{-2}$ s$^{-1}$]}}
\startdata
Core & \RA{12}{59}{48.7} & Dec{27}{58}{50.0} & 0 & 17 & 0.84 & 2.62 & (1.3\%)\\
& & & 0.2 & -41 & -1.0 & 1.7 & (0.87\%)\\
& & & 0.4 & -26 & -0.30 & 4.5 & (2.3\%)\\
NGC 4889 & \RA{13}{00}{08.13} & \Dec{+27}{58}{37.03} & 0 & 3 & 0.14 & 2.09 & (1.1\%)\\
NGC 4874 & \RA{12}{59}{35.71} & \Dec{+27}{57}{33.37} & 0 & -14 & -0.71 & 1.42 & (0.72\%)\\
NGC 4921 & \RA{13}{01}{26.12} & \Dec{+27}{53}{09.59} & 0 & -4 & -0.23 & 1.89 & (0.96\%)
\enddata
\tablenotetext{a}{Statistical significance calculated according to \citet{article:LiMa:1983}}
\tablenotetext{b}{99\% confidence level upper limit calculated according to \citet{article:Rolke:2005} above an energy threshold of 220 GeV. Values in parentheses are the corresponding fluxes in percent of the steady Crab nebula flux.}
\label{table:results}
\end{deluxetable}

\section{Conclusions}
VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.

\acknowledgments
This research was supported by grants from the U.S. Department of Energy, the U.S. National Science Foundation, and the Smithsonian Institution, by NSERC in Canada, by Science Foundation Ireland, and by STFC in the UK. We acknowledge the excellent work of the technical support staff at the FLWO and the collaborating institutions in the construction and operation of the instrument.

%%Facilities: \facility{VERITAS}.

\bibliographystyle{apj}
\bibliography{refs}

\end{document}

### 2011-05-12 table_deluxe.tex
Added the 'first' draft of the paper

--- 2011-05-12 ms.tex
@@
-\documentclass[12pt,manuscript]{aastex}
-%%\documentclass[twocolumn]{emulateapj}
-
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand{\myemail}{nkarlsson@physics.umn.edu}
-\newcommand{\expval}[1]{\left\langle #1 \right\rangle}
-\newcommand{\RA}[3]{#1$^{\mathrm{h}}$#2$^{\mathrm{m}}$#3$^{\mathrm{s}}$}
-\newcommand{\Dec}[3]{#1$^{\circ}$#2\arcmin#3\arcsec}
-
-\shorttitle{Coma Cluster Observations with VERITAS}
-\shortauthors{VERITAS collaboration}
-
-\begin{document}
-
-%\title{VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
-\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
-\author{N. Karlsson\altaffilmark{1,2}, M. Pohl\altaffilmark{3,4}}
-\affil{(the VERITAS collaboration)} 
-%%\email{nkarlsson@physics.umn.edu}
-\and
-\author{C. Pfrommer\altaffilmark{5,6},
-A. Pinzke\altaffilmark{7}}
-
-\altaffiltext{1}{Corresponding author: N. Karlsson, nkarlsson@physics.umn.edu}
-\altaffiltext{2}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
-\altaffiltext{3}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
-\altaffiltext{4}{ Institut fu\"r Physik und Astronomie, Universita\"t Potsdam, 14476 Potsdam-Golm, Germany}
-\altaffiltext{5}{Heidelberg Institute	for Theoretical	Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
-\altaffiltext{6}{Canadian Institute for Theoretical Astrophysics, University of Toronto, Toronto, ON, M5S 3H8, Canada}
-\altaffiltext{7}{University of California, Santa Barbara, CA 93106}
-
-%%\journalinfo{The Astrophysical Journal}
-%%\submitted{preprint}
-
-\begin{abstract}
-Theoretical models of galaxy clusters suggest they may be sources of very high-energy (VHE) gamma-ray emission.
-Observations of radio halos and relics in clusters indicate populations of relativistic electrons and positrons, which are either injected into the intra-cluster medium and accelerated by turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with the intra-cluster gas.
-Those interactions would also produce gamma rays through the decay of neutral pions.
-Reported here are observations of the Coma cluster of galaxies with the VERITAS array of imaging Cherenkov telescopes.
-The observations were made between March and May 2008.
-Radio observations at 1.41 GHz taken with the Green Bank Telescope and X-ray observations with the ROSAT All-Sky survey was used to a priori select regions of interest in the field of view.
-No significant VHE gamma-ray emission from the Coma cluster was detected by VERITAS.
-Flux upper limits at the 99\% confidence level were obtained for the cluster core, both as a point source and a mildly extended source centered at the cluster core, and for a select few other cluster members.
-The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields in the cluster.
-The cosmic-ray pressure is...
-The observations imply a lower limit on the intra-cluster magnetic field of X$\mu$G.
-Finally, a constraint on the dark matter annihilation cross section is derived, $\expval{\sigma v}=$.
-\end{abstract}
-
-%\keywords{cosmic rays: interactions --- galaxies --- galaxy clusters -- VHE}
-\keywords{cosmic rays --- gamma rays: observations --- gamma rays: VHE --- galaxies: clusters: general --- galaxies: clusters: individual: Coma (ACO 1656)}
-
-\section{Introduction}
-Clusters of galaxies are the largest observable structures in the Universe, with typical diameters of several Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$.
-These gravitationally bound objects have formed on increasingly larger scales during the evolution of the Universe through the process of cosmic structure formation \citep{article:Voit:2005}.
-Although most of the cluster mass comes from large amounts of dark matter embedded in a cluster, as indicated by cluster dynamics and weak gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}, gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass.
-Individual galaxies contribute only a small amount (about 5\%) to the cluster mass.
-The ICM gas mass also comprise a significant fraction of the observable (baryonic) matter in the Universe.
-
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.][]{article:Petrosian:2001}.
-Heating of this plasma is thought to come primarily from collisionless structure-formation shocks, due to accretion and merger processes.
-Such shocks and turbulences in the ICM gas and magnetic fields also provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}.
-Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}.
-Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} provide further indications of relativistic particle populations in clusters, although the interpretation of these observations have been disputed \citep[see, e.g.][]{article:Wik_etal:2009}.
-
-Galaxy clusters have for many years been proposed as sources of gamma rays.
-If shock acceleration in the ICM is an efficent process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected.
-The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM.
-Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{Charged pions decay to muons/antimuons which subsequently decay to electrons/positrons.} and the neutral pion to gamma rays.
-Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$) and the sheer size of a cluster, CR hadrons will be confined in the cluster on very long timescales \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.
-
-Depending on the CR energy density, quantified by the fraction of energy in CRs to the thermal energy in a cluster, $\eta=\expval{ E_{\mathrm{CR}}/E_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.
-This fraction could plausibly be as large as 50\% \citep{article:Ryu_etal:2003}, but a much smaller fraction of only a few percent is required in order to produce a gamma-ray flux observable with current generation gamma-ray telescopes.
-
-Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example cosmic microwave background (CMB) photons, on ultra-relativistic leptons.
-Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.
-
-While several observations of clusters of galaxies have been made with satellite-borne and ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
-Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several galaxy clusters in the MeV to GeV band.
-Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009, article:Aleksic_etal:2010}.
-
-The Coma cluster of galaxies (ACO 1656) is one of the most thouroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}.
-Located at a distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest and also one of the most massive clusters \citep[$M \sim 10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}.
-It hosts both a giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
-It has been suggested that the relic is an infall shock.
-Extended soft X-ray (SXR) emission is evident from the ROSAT All-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo.
-As such it is a natural candidate for gamma-ray observations.
-In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with its constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
-
-\section{Observations and Analysis}
-The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an altitude of 1268 m a.s.l.
-at the Fred Lawrence Whipple Observatory in southern Arizona (31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W).
-Each of the telescopes is equipped with a 499 pixel camera covering a 3.5$^{\circ}$ field of view.
-The array, completed in the spring of 2007, is designed to detect gamma-ray emission from astrophysical objects in the energy range from 100 GeV to more than 30 TeV.
-The energy resolution is about 15\% and the angular resolution (68\% containment) is about 0.1$^{\circ}$ per event at 1 TeV.
-The sensitivity of the array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009.
-The move had no impact on the Coma cluster data set.}
-
-The Coma cluster was observed with VERITAS between March and May in 2008 with all four telescopes fully operational.
-The total exposure amounts to 18.6 hours of quality-selected live time, i.e.
-time periods of astronomical darkness, clear sky conditions and without technical problems with the array.
-The center of the Coma cluster was tracked in \emph{wobble} mode, where the expected source location is offset from the center of the field of view, to allow for simultaneous background estimation \citep{article:Formin_etal:1994}.
-All of the observations were made in a small range of zenith angles averaging $\sim 21^{\circ}$.
-
-The data analysis was performed following the standard VERITAS procedures described in \citet{inproc:Cogan_etal:2007} and \citet{inproc:Daniel_etal:2007}.
-Prior to event reconstruction and selection, all shower images are calibrated and cleaned.
-Showers are then reconstructed for events with at least two contributing telescope images that pass the following quality selection criteria: more than four participating pixels in the camera, number of photoelectrons in the image is larger than 75, and the distance from the image centroid to the center of the camera is less than $1.43^{\circ}$.
-These quality selection criteria impose an energy threshold\footnote{Defined as$\ldots$} of about 220 GeV.
-In addition, events for which only images from the two closest-spaced telescopes\footnote{In the array configuration prior to summer 2009, two telescopes had a separation of only 35 m.} survive quality selection are rejected, as they introduce an irreducible high background rate, due to local muons, degrading the instrument sensitivity \citep{article:MaierKnapp:2007}.
-
-Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters \citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images \citep{inproc:Hillas:1985}.
-The gamma-hadron separation cuts used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level) and a photon index of -2.4 using data taken on the Crab Nebula during the same epoch and are termed \emph{standard} cuts.
-Because the VHE gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about -2.3, these standard cuts are suitable.
-
-The Coma cluster is a complex region with many plausible sites for gamma-ray emission.
-
-The ring background model \citep{article:Aharonian_etal:2001} was used to produce skymaps of the VERITAS excess over the field of view.
-The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess.
-
-%The observed radio halo and thermal X-ray emission in the Coma cluster suggest that the VHE gamma-ray emission should have a similar spatial extension.
-
-\begin{figure*}
-\begin{center}
-\scalebox{0.5}{\plotone{f1a.eps}}
-\scalebox{0.5}{\plotone{f1b.eps}}
-\end{center}
-\caption{Skymaps.}
-\label{fig:skymaps}
-\end{figure*}
-
-\section{Results and Discussion}
-No significant excess was detected with VERITAS in the Coma cluster.
-A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} and assuming Gaussian background.
-
-\begin{deluxetable}{lccccccc}
+\begin{deluxetable*}{lccccccc}
 \tablecolumns{7}
@@
 \label{table:results}
-\end{deluxetable}
-
-\section{Conclusions}
-VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
-
-\acknowledgments
-This research was supported by grants from the U.S.
-Department of Energy, the U.S.
-National Science Foundation, and the Smithsonian Institution, by NSERC in Canada, by Science Foundation Ireland, and by STFC in the UK.
-We acknowledge the excellent work of the technical support staff at the FLWO and the collaborating institutions in the construction and operation of the instrument.
-
-%%Facilities: \facility{VERITAS}.
-
-\bibliographystyle{apj}
-\bibliography{refs}
-
-\end{document}
+\end{deluxetable*}

### 2011-05-17 ms.tex
Some minor changes to the manuscript

@@
 The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM.
-Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{Charged pions decay to muons/antimuons which subsequently decay to electrons/positrons.} and the neutral pion to gamma rays.
+Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron.} and the neutral pion to gamma rays.
 Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$) and the sheer size of a cluster, CR hadrons will be confined in the cluster on very long timescales \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.
@@
 \tablewidth{0pc}
-\tablecaption{Flux upper limits for regions of interest in the Coma galaxy cluster}
+\tablecaption{Flux upper limits for regions of interest in the Coma cluster of galaxies.}
 \tablehead{
@@
 \startdata
-Core & \RA{12}{59}{48.7} & Dec{27}{58}{50.0} & 0 & 17 & 0.84 & 2.62 & (1.3\%)\\
+Core & \RA{12}{59}{48.7} & \Dec{+27}{58}{50.0} & 0 & 17 & 0.84 & 2.62 & (1.3\%)\\
 & & & 0.2 & -41 & -1.0 & 1.7 & (0.87\%)\\
@@
 \tablenotetext{b}{99\% confidence level upper limit calculated according to \citet{article:Rolke:2005} above an energy threshold of 220 GeV.
-Values in parentheses are the corresponding fluxes in percent of the steady Crab nebula flux.}
+Values in parentheses are the corresponding fluxes in percent of the steady Crab Nebula flux.}
 \label{table:results}

### 2011-06-08 ms.tex
Minor changes, new skymaps and sections

@@
 It has been suggested that the relic is an infall shock.
-Extended soft X-ray (SXR) emission is evident from the ROSAT All-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo.
+Extended soft X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo.
 As such it is a natural candidate for gamma-ray observations.
@@
 time periods of astronomical darkness, clear sky conditions and without technical problems with the array.
-The center of the Coma cluster was tracked in \emph{wobble} mode, where the expected source location is offset from the center of the field of view, to allow for simultaneous background estimation \citep{article:Formin_etal:1994}.
+The center of the cluster was tracked in \emph{wobble} mode, where the expected source location is offset from the center of the field of view, to allow for simultaneous background estimation \citep{article:Formin_etal:1994}.
 All of the observations were made in a small range of zenith angles averaging $\sim 21^{\circ}$.
@@
 The gamma-hadron separation cuts used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level) and a photon index of -2.4 using data taken on the Crab Nebula during the same epoch and are termed \emph{standard} cuts.
-Because the VHE gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about -2.3, these standard cuts are suitable.
+Because the VHE gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about -2.3, these standard cuts are suitable for the analysis of the Coma cluster data set.
 
-The Coma cluster is a complex region with many plausible sites for gamma-ray emission.
-
-The ring background model \citep{article:Aharonian_etal:2001} was used to produce skymaps of the VERITAS excess over the field of view.
+The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs.
 The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess.
-
-%The observed radio halo and thermal X-ray emission in the Coma cluster suggest that the VHE gamma-ray emission should have a similar spatial extension.
+The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.
+Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:Coma:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.
 
@@
 \caption{Skymaps.}
-\label{fig:skymaps}
+\label{fig:Coma:skymaps}
 \end{figure*}
 
-\section{Results and Discussion}
+\section{Results}
 No significant excess was detected with VERITAS in the Coma cluster.
@@
 
+\section{Cosmic Rays}
+
+\section{Dark Matter}
+
 \section{Conclusions}

### 2011-06-13 ms.tex
Added theta^2 and sig dist plots and updated the skymaps

@@
 %%\documentclass[twocolumn]{emulateapj}
+
+\usepackage{lscape}
 
@@
 The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.
-Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:Coma:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.
+Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.
 
@@
 \begin{center}
-\scalebox{0.5}{\plotone{f1a.eps}}
-\scalebox{0.5}{\plotone{f1b.eps}}
+\scalebox{0.45}{\plotone{f1a.eps}}
+\scalebox{0.45}{\plotone{f1b.eps}}
 \end{center}
-\caption{Skymaps.}
-\label{fig:Coma:skymaps}
+\caption{\emph{Top}: Smoothed significance map of the Coma cluster calculated from the observed excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view.
+The excess counts were derived using a ring-ring background model \citep{article:Aharonian_etal:2001}.
+White contours show the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}.
+\emph{Bottom}: Same as above but with overlaid contours from point source subtracted GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010}.
+Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan) considered for the extended source analyses presented here.}
+\label{fig:skymaps}
 \end{figure*}
@@
 \section{Results}
-No significant excess was detected with VERITAS in the Coma cluster.
-A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} and assuming Gaussian background.
+No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS.
 
+A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} assuming a Gaussian background.
+Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean of zero and unit standard deviation.
+The results are listed in Table \ref{table:results}.
+
+\begin{figure*}
+\begin{center}
+\scalebox{1.0}{\plotone{f2.eps}}
+\end{center}
+\caption{$\theta^{2}$ distribution from VERITAS observations of the Coma cluster of galaxies.
+The points with error bars represent the ON-source data sample and and the filled area the background sample.
+Each bin represents an annulus around the Coma cluster core position.
+The data were derived from the ring-ring background model using a $0.2^{\circ}$ sampling radius.}
+\label{fig:thetasq}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\scalebox{1.0}{\plotone{f3.eps}}
+\end{center}
+\caption{Distribution of significance for Figure \ref{fig:skymaps} and a sampling radius of $0.2^{\circ}$.
+The line is a Gaussian fit to the data, with mean close to zero and almost unit standard deviation.}
+\label{fig:sigdist}
+\end{figure*}
+
+\begin{landscape}
 \begin{deluxetable}{lccccccc}
@@
 \end{deluxetable}
+\end{landscape}
 

### 2011-06-13 ms.tex
Some minor changes

@@
 Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.
+The skymaps were produced with a $0.2^{\circ}$ sampling radius.
+
+\section{Results}
+No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as illustrated by the $\theta^{2}$ distribution shown in  Figure \ref{fig:thetasq}.
+The $\theta^{2}$ distribution is a radial comparison of the ON-source event distribution with the estimated background.
+A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} assuming a Gaussian background.
+Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent of unity.
+The results are listed in Table \ref{table:results}.
+
+\section{Cosmic Rays}
+
+\section{Dark Matter}
+
+\section{Conclusions}
+VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
+
+\acknowledgments
+This research was supported by grants from the U.S.
+Department of Energy, the U.S.
+National Science Foundation, and the Smithsonian Institution, by NSERC in Canada, by Science Foundation Ireland, and by STFC in the UK.
+We acknowledge the excellent work of the technical support staff at the FLWO and the collaborating institutions in the construction and operation of the instrument.
+
+%%Facilities: \facility{VERITAS}.
+
+\bibliographystyle{apj}
+\bibliography{refs}
 
@@
 \end{figure*}
-
-\section{Results}
-No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS.
-
-A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} assuming a Gaussian background.
-Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean of zero and unit standard deviation.
-The results are listed in Table \ref{table:results}.
 
@@
 
-\section{Cosmic Rays}
-
-\section{Dark Matter}
-
-\section{Conclusions}
-VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
-
-\acknowledgments
-This research was supported by grants from the U.S.
-Department of Energy, the U.S.
-National Science Foundation, and the Smithsonian Institution, by NSERC in Canada, by Science Foundation Ireland, and by STFC in the UK.
-We acknowledge the excellent work of the technical support staff at the FLWO and the collaborating institutions in the construction and operation of the instrument.
-
-%%Facilities: \facility{VERITAS}.
-
-\bibliographystyle{apj}
-\bibliography{refs}
-
 \end{document}

### 2011-06-13 ms.tex
Some more text in the Analysis and Results sections

@@
 
-The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs.
+The Coma cluster is a very rich cluster of galaxies with many plausible sites for gamma-ray emission.
+The core region, the peripheral radio relic, as well as individual powerful cluster member galaxies.
+VERITAS has a large enough field of view to allow investigation of several of these scenarios.
+In this work the focus has been on the core region and three cluster members.
+The latter are treated as point sources in the analysis, whereas the core is treated as both a point source and a mildly extended source.
+The intrinsic source extension is assumed to be $0.2^{\circ}$ and $0.4^{\circ}$, based on the extension of the thermal soft X-ray emission from the core.
+
+The ring-ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs.
 The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess.
 The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.
-Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.
-The skymaps were produced with a $0.2^{\circ}$ sampling radius.
+Significance skymaps over the VERITAS field of view produced with a $0.2^{\circ}$ sampling radius are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.
 

### 2011-07-01 ms.tex
Some minor changes
New citations and some text about the RoI selection and updated tables

@@
 \altaffiltext{3}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
-\altaffiltext{4}{ Institut fu\"r Physik und Astronomie, Universita\"t Potsdam, 14476 Potsdam-Golm, Germany}
+\altaffiltext{4}{ Institut fu\"r Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm, Germany}
 \altaffiltext{5}{Heidelberg Institute	for Theoretical	Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
@@
 As such it is a natural candidate for gamma-ray observations.
-In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with its constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
+In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
 
-\section{Observations and Analysis}
+\section{VERITAS Observations and Analysis}
 The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an altitude of 1268 m a.s.l.
@@
 The intrinsic source extension is assumed to be $0.2^{\circ}$ and $0.4^{\circ}$, based on the extension of the thermal soft X-ray emission from the core.
+There is evidence of a recent merger event between the two central galaxies NGC 4889 and NGC 4874 \citep{article:Tribble:1993}.
+There is also evidence for an excess of non-thermal X-ray emission from these galaxies as well as the galaxy NGC 4921.
+Therefore, searches for point-like VHE gamma-ray emission have been conducted at the locations of these galaxies.
+The regions of interest considered in this work are summarized in Table \ref{table:roi}.
 
-The ring-ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs.
+The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs.
 The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess.
@@
 
+%%\section{Fermi-LAT Observations and Analysis}
+
 \section{Results}
@@
 The $\theta^{2}$ distribution is a radial comparison of the ON-source event distribution with the estimated background.
-A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} assuming a Gaussian background.
+It extends out to a radius of $0.42^{\circ}$ to cover all regions of interest considered in this work.
+A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke_etal:2005} assuming a Gaussian background.
+A lower bound of zero is imposed on the signal rate to handle the negative excesses seen for several of the regions of interest.
 Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent of unity.
-The results are listed in Table \ref{table:results}.
+
+Table \ref{table:results} lists the upper limits for the selected regions of interest tabulated in Table \ref{table:roi}.
+These upper-limit calculations depend on the gamma-ray spectrum, which in this work is assumed to be a power law with a spectral index $\alpha=-2.1, -2.3$, and $-2.5$.
+A power-law spectrum with index $\alpha=-1.5$ is also considered for the dark matter constraints.
 
@@
 
+\section{Constrainsts on Magnetic Fields}
+
 \section{Dark Matter}
 
-\section{Conclusions}
+\section{Discussion}
 VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
@@
 \end{center}
-\caption{\emph{Top}: Smoothed significance map of the Coma cluster calculated from the observed excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view.
-The excess counts were derived using a ring-ring background model \citep{article:Aharonian_etal:2001}.
+\caption{\emph{Left}: Smoothed significance map of the Coma cluster calculated from the observed excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view.
+The excess counts were derived using a ring background model \citep{article:Aharonian_etal:2001}.
 White contours show the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}.
-\emph{Bottom}: Same as above but with overlaid contours from point source subtracted GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010}.
+\emph{Right}: Same as above but with overlaid contours from point source subtracted GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010}.
 Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan) considered for the extended source analyses presented here.}
@@
 Each bin represents an annulus around the Coma cluster core position.
-The data were derived from the ring-ring background model using a $0.2^{\circ}$ sampling radius.}
+The data were derived from the ring background model using a $0.2^{\circ}$ sampling radius.}
 \label{fig:thetasq}
@@
 \begin{center}
-\scalebox{1.0}{\plotone{f3.eps}}
+\scalebox{0.75}{\plotone{f3.eps}}
 \end{center}
@@
 
-\begin{landscape}
-\begin{deluxetable}{lccccccc}
-\tablecolumns{7}
+\begin{deluxetable}{lcc}
+\tablecolumns{3}
 \tablewidth{0pc}
-\tablecaption{Flux upper limits for regions of interest in the Coma cluster of galaxies.}
+\tablecaption{Regions of interest in the Coma cluster field of view.
+The cluster core is considered both as a point source and a modestly extended source.
+Three central galaxies are also considered in point-source searches.
+The choice is based on evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the location of these galaxies.}
 \tablehead{
@@
 \colhead{RA} &
-\colhead{Dec} &
-\colhead{RoI} &
-\colhead{Excess} &
-\colhead{Significance\tablenotemark{a}} &
-\multicolumn{2}{c}{Flux U.L.\tablenotemark{b}}\\
-\colhead{} & \colhead{[J2000]} & \colhead{[J2000]} & \colhead{[deg]} & \colhead{[counts]} & \colhead{[$\sigma$]} & \multicolumn{2}{c}{[$10^{-8}$ ph. m$^{-2}$ s$^{-1}$]}}
+\colhead{Dec}}
 \startdata
-Core & \RA{12}{59}{48.7} & \Dec{+27}{58}{50.0} & 0 & 17 & 0.84 & 2.62 & (1.3\%)\\
-& & & 0.2 & -41 & -1.0 & 1.7 & (0.87\%)\\
-& & & 0.4 & -26 & -0.30 & 4.5 & (2.3\%)\\
-NGC 4889 & \RA{13}{00}{08.13} & \Dec{+27}{58}{37.03} & 0 & 3 & 0.14 & 2.09 & (1.1\%)\\
-NGC 4874 & \RA{12}{59}{35.71} & \Dec{+27}{57}{33.37} & 0 & -14 & -0.71 & 1.42 & (0.72\%)\\
-NGC 4921 & \RA{13}{01}{26.12} & \Dec{+27}{53}{09.59} & 0 & -4 & -0.23 & 1.89 & (0.96\%)
+Core & \RA{12}{59}{48.7} & \Dec{+27}{58}{50.0}\\
+NGC 4889 & \RA{13}{00}{08.13} & \Dec{+27}{58}{37.03}\\
+NGC 4874 & \RA{12}{59}{35.71} & \Dec{+27}{57}{33.37}\\
+NGC 4921 & \RA{13}{01}{26.12} & \Dec{+27}{53}{09.59}\\
 \enddata
-\tablenotetext{a}{Statistical significance calculated according to \citet{article:LiMa:1983}}
-\tablenotetext{b}{99\% confidence level upper limit calculated according to \citet{article:Rolke:2005} above an energy threshold of 220 GeV.
+\label{table:roi}
+\end{deluxetable}
+
+\begin{landscape}
+\begin{deluxetable}{lcccccccccccc}
+\tablecolumns{6}
+\tablewidth{0pc}
+\tablecaption{Flux upper limits for regions of interest in the Coma cluster of galaxies and surroundings.}
+\tablehead{
+\colhead{Source} & \colhead{RoI\tablenotemark{a} [deg]} & \colhead{$N_{S}$} & \colhead{S\tablenotemark{b} [$\sigma$]} &
+\multicolumn{6}{c}{Flux U.L.\tablenotemark{c}} &
+\multicolumn{3}{c}{Minimum gamma-ray flux\tablenotemark{d}}\\
+\colhead{} & \colhead{} & \colhead{} & \colhead{} & \multicolumn{2}{c}{$\alpha=-2.1$} &
+\multicolumn{2}{c}{$\alpha=-2.3$} &
+\multicolumn{2}{c}{$\alpha=-2.5$} &
+\colhead{$\alpha=-2.1$} &
+\colhead{$\alpha=-2.3$} &
+\colhead{$\alpha=-2.5$}}
+\startdata
+Core & 0 & 17 & 0.84 & 2.59 & (0.78\%) & 2.78 & (0.83\%) & 2.97 & (0.89\%) \\
+& 0.2 & -41 & -1.0 & 1.96 & (0.59\%)  & 2.09 & (0.63\%) & 2.21 & (0.66\%) \\
+& 0.4 & -26 & -0.30 & 4.44 & (1.3\%)  & 4.74 & (1.4\%) & 5.02 & (1.5\%)\\
+NGC 4889 & 0 & 3 & 0.14 & - & - & 1.85 & (0.55\%)  & - & - \\
+NGC 4874 & 0 & -14 & -0.71 & - & - &  1.51 & (0.45\%)  & - & - \\
+NGC 4921 & 0 & -4 & -0.23 & - & - &  2.41 & (0.72\%)  & - & -
+\enddata
+\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
+\tablenotetext{b}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
+\tablenotetext{c}{99\% confidence level upper limit in units of $10^{-8}$ ph.
+m$^{-2}$ s$^{-1}$ calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV.
 Values in parentheses are the corresponding fluxes in percent of the steady Crab Nebula flux.}
+\tablenotetext{d}{Minimum gamma-ray flux in units of $10^{-13}$ ph. cm$^{-2}$ s$^{-1}$ from the hadronic model described in the text.}
 \label{table:results}

### 2011-07-01 ms.tex
Temporaty plots for Xcr and DM annihilation cross section. Place holder for integrated spectrum plot.

@@
 
-%%\section{Fermi-LAT Observations and Analysis}
+\section{Fermi-LAT Observations and Analysis}
 
@@
 
+\begin{figure*}
+\begin{center}
+%\scalebox{1.0}{\plotone{f4.eps}}
+\end{center}
+\caption{Integral flux upper limits (this work, Table X) compared with simulated integrated spectra of VHE gamma-ray emission from the Coma cluster.}
+\label{fig:spectrum}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\scalebox{1.0}{\plotone{f5.eps}}
+\end{center}
+\caption{Cosmic-ray pressure, $X_{\mathrm{CR}}$, as a function of radial distance from the Coma cluster core.}
+\label{fig:xcr}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\scalebox{1.0}{\plotone{f6.eps}}
+\end{center}
+\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ calculated using the VERITAS data in this work.}
+\label{fig:dm}
+\end{figure*}
+
 \begin{deluxetable}{lcc}

### 2011-07-05 ms.tex
Fermi section added

@@
 \and
-\author{C. Pfrommer\altaffilmark{5,6},
+\author{S. Federici\altaffilmark{3,4}, C. Pfrommer\altaffilmark{5,6},
 A. Pinzke\altaffilmark{7}}
@@
 No significant VHE gamma-ray emission from the Coma cluster was detected by VERITAS.
-Flux upper limits at the 99\% confidence level were obtained for the cluster core, both as a point source and a mildly extended source centered at the cluster core, and for a select few other cluster members.
+Several emission regions are considered, including the cluster core as both unresolved (point-like) and spatially extended, and a select few cluster members.
+The flux upper limits at the 99\% confidence level measured are on the order of $2-5\times 10^{-8}$ ph.
+m$^{-2}$ s$^{-1}$, which is X times higher than the model-predicted minimum gamma-ray flux.
+
 The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields in the cluster.
-The cosmic-ray pressure is...
+The relative cosmic-ray pressure $X_{\mathrm{CR}}$ is.
 The observations imply a lower limit on the intra-cluster magnetic field of X$\mu$G.
@@
 
+A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a dark matter particle, e.g. a weakly interacting massive particle (WIMP).
+
 While several observations of clusters of galaxies have been made with satellite-borne and ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
@@
 Showers are then reconstructed for events with at least two contributing telescope images that pass the following quality selection criteria: more than four participating pixels in the camera, number of photoelectrons in the image is larger than 75, and the distance from the image centroid to the center of the camera is less than $1.43^{\circ}$.
-These quality selection criteria impose an energy threshold\footnote{Defined as$\ldots$} of about 220 GeV.
+These quality selection criteria impose an energy threshold\footnote{Defined as the energy corresponding to the maximum of the product function of the observed spectrum with the collection area} of about 220 GeV.
 In addition, events for which only images from the two closest-spaced telescopes\footnote{In the array configuration prior to summer 2009, two telescopes had a separation of only 35 m.} survive quality selection are rejected, as they introduce an irreducible high background rate, due to local muons, degrading the instrument sensitivity \citep{article:MaierKnapp:2007}.
@@
 
-The Coma cluster is a very rich cluster of galaxies with many plausible sites for gamma-ray emission.
-The core region, the peripheral radio relic, as well as individual powerful cluster member galaxies.
+The Coma cluster is a very rich cluster of galaxies with many plausible sites for gamma-ray emission: the core region, the peripheral radio relic, as well as individual powerful cluster member galaxies.
 VERITAS has a large enough field of view to allow investigation of several of these scenarios.
@@
 There is evidence of a recent merger event between the two central galaxies NGC 4889 and NGC 4874 \citep{article:Tribble:1993}.
-There is also evidence for an excess of non-thermal X-ray emission from these galaxies as well as the galaxy NGC 4921.
+There is also evidence for an excess of non-thermal X-ray emission from these galaxies as well as the galaxy NGC 4921 \citep{article:Neumann_etal:2003}.
 Therefore, searches for point-like VHE gamma-ray emission have been conducted at the locations of these galaxies.
@@
 
-The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs.
+The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs misinterpreted as gamma rays (the cuts described above reject more than 99\% of all CRs).
 The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess.
@@
 \section{Fermi-LAT Observations and Analysis}
+The Large Area Telescope (LAT) on board the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi}) has observed the Coma cluster in all-sky survey mode since its launch in June 2008.
+The \emph{Fermi}-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus very complimentary to the VERITAS obervations.
+\citet{article:Ackermann_etal:2010} reported on the search for gamma-ray emission from thirty-three galaxy clusters in the data from the first 18 months, including the Coma cluster, for which an upper limit of $4.58\times 10^{-9}$ ph.
+cm$^{-2}$ s$^{-1}$ in the 0.2 to 100 GeV energy band was reported.
+This limit is expected to improve as the exposure is increased.
+In this work an updated analysis which includes additional data taken during the period 2010 February 5 to 2011 June 10 is presented as a compliment to the VERITAS results.
+
+The analysis of this work follows the same procedure as described in detail in \citet{article:Abdo_etal:2009}.
+To eliminate albedo gamma rays from the Earth limb, a zenith angle cut of 105$^{\circ}$ is applied.
+The \emph{Fermi} Science Tools version v9r23p1 and Instrumental Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events calibrated ...) were used throughout this work.
+Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful.
+The 99\% confidence level flux upper limits in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission are tabulated in Table \ref{tabel:fermi}.
+The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$ and $2.5$.
 
@@
 Table \ref{table:results} lists the upper limits for the selected regions of interest tabulated in Table \ref{table:roi}.
-These upper-limit calculations depend on the gamma-ray spectrum, which in this work is assumed to be a power law with a spectral index $\alpha=-2.1, -2.3$, and $-2.5$.
-A power-law spectrum with index $\alpha=-1.5$ is also considered for the dark matter constraints.
+These upper-limit calculations depend on the gamma-ray spectrum, which in this work is assumed to be a power law with a spectral index $\alpha=2.1, 2.3$, and $2.5$.
 
@@
 White contours show the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}.
-\emph{Right}: Same as above but with overlaid contours from point source subtracted GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010}.
+\emph{Right}: Same as above but with overlaid contours from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where strong point sources have been subtracted.
 Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan) considered for the extended source analyses presented here.}
@@
 \caption{$\theta^{2}$ distribution from VERITAS observations of the Coma cluster of galaxies.
-The points with error bars represent the ON-source data sample and and the filled area the background sample.
+The points with error bars represent the ON-source data sample and the filled area is the estimated background due to cosmic rays.
 Each bin represents an annulus around the Coma cluster core position.
@@
 \tablewidth{0pc}
-\tablecaption{Regions of interest in the Coma cluster field of view.
-The cluster core is considered both as a point source and a modestly extended source.
-Three central galaxies are also considered in point-source searches.
-The choice is based on evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the location of these galaxies.}
+\tablecaption{Regions of interest in the Coma cluster field of view.}
 \tablehead{
@@
 \enddata
+\tablenotetext{a}{Note.
+The cluster core is considered both as a point source and a modestly extended source.
+Three central galaxies are also considered in point-source searches.
+The choice is based on evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the location of these galaxies.}
 \label{table:roi}
@@
 \multicolumn{3}{c}{Minimum gamma-ray flux\tablenotemark{d}}\\
-\colhead{} & \colhead{} & \colhead{} & \colhead{} & \multicolumn{2}{c}{$\alpha=-2.1$} &
-\multicolumn{2}{c}{$\alpha=-2.3$} &
-\multicolumn{2}{c}{$\alpha=-2.5$} &
-\colhead{$\alpha=-2.1$} &
-\colhead{$\alpha=-2.3$} &
-\colhead{$\alpha=-2.5$}}
+\colhead{} & \colhead{} & \colhead{} & \colhead{} & \multicolumn{2}{c}{$\alpha=2.1$} &
+\multicolumn{2}{c}{$\alpha=2.3$} &
+\multicolumn{2}{c}{$\alpha=2.5$} &
+\colhead{$\alpha=2.1$} &
+\colhead{$\alpha=2.3$} &
+\colhead{$\alpha=2.5$}}
 \startdata
@@
 \tablenotetext{c}{99\% confidence level upper limit in units of $10^{-8}$ ph.
-m$^{-2}$ s$^{-1}$ calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV.
-Values in parentheses are the corresponding fluxes in percent of the steady Crab Nebula flux.}
-\tablenotetext{d}{Minimum gamma-ray flux in units of $10^{-13}$ ph. cm$^{-2}$ s$^{-1}$ from the hadronic model described in the text.}
+m$^{-2}$ s$^{-1}$ calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
+\tablenotetext{d}{Minimum gamma-ray flux in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$ from the hadronic model described in the text.}
 \label{table:results}

### 2011-07-07 ms.tex
Added a nice table comment to source table and skeleton for Fermi results table
1st draft of CR and B analysis

@@
 \usepackage{lscape}
+
+\def\del#1{{}}
+%\def\del#1{{\bf (DELETED TEXT)}}
+\def\C#1{#1}
+%\def\C#1{{\bf #1}}
 
@@
 \newcommand{\Dec}[3]{#1$^{\circ}$#2\arcmin#3\arcsec}
+\newcommand{\rmn}{\mathrm}
+\newcommand{\CR}{\mathrm{CR}}
+\newcommand{\dps}{\displaystyle}
+\newcommand{\eps}{\varepsilon}
+\newcommand{\bra}{\langle}
+\newcommand{\ket}{\rangle}
 
@@
 \and
-\author{S. Federici\altaffilmark{3,4}, C. Pfrommer\altaffilmark{5,6},
+\author{S. Federici\altaffilmark{3,4}, C. Pfrommer\altaffilmark{1,5,6},
 A. Pinzke\altaffilmark{7}}
 
-\altaffiltext{1}{Corresponding author: N. Karlsson, nkarlsson@physics.umn.edu}
+\altaffiltext{1}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
 \altaffiltext{2}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
@@
 It hosts both a giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
-It has been suggested that the relic is an infall shock.
+It has been suggested that the relic is an infall shock \citep{1998A&A...332..395E} and succesively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{2008MNRAS.385.1211P,2008MNRAS.385.1242P,2009MNRAS.393.1073B, 2011ApJ...735...96S}.
 Extended soft X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo.
@@
 In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
+Throughout the analysis, we use a present day Hubble constant of $H_0 = 100 h \mbox{ km s}^{-1} \mbox{ Mpc}^{-1}$ with $h=0.7$.
 
@@
 
-\section{Constrainsts on Magnetic Fields}
+We decided to adopt a multifaceted approach to constrain the CR-to-thermal
+pressure distribution in Coma with these upper limits. That includes (1) an
+analytic model derived from cosmological hydrodynamical simulations of the
+formation of galaxy clusters, (2) a simplified multi-frequency analytical
+approach that assumes a constant CR-to-thermal energy density and a power-law
+spectrum in momentum, and (3) an approach that uses the observed luminosity of
+the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray
+flux in the hadronic model -- independent of the magnetic field distribution.
+This translates into a minimum CR pressure which, if challenged by tight
+gamma-ray limits/detections, enables scrutinizing the hadronic interaction model
+of the formation of giant radio halos.  Modelling the CR distribution through
+different techniques enable to bracket our ignorance about the underlying plasma
+physics that shape the CR distribution and hence reflect the Bayesian priors
+that are imposed on the modelling \citep[see][for a
+discussion]{2011arXiv1105.3240P}.
+
+\subsection{Simulation-based approach}
+
+We adopt the universal spectral and spatial gamma-ray model developed by
+\citet{2010MNRAS.409..449P} to estimate the emission from decaying neutral pions
+that dominates over the IC emission from primary and secondary electrons above
+100~MeV in clusters. Given a density profile as, e.g., inferred by cosmological
+simulations or X-ray observations, the analytic approach models the CR
+distribution and the associated radiative emission processes from radio to the
+gamma-ray band.  This formalism was derived from high resolution simulations of
+clusters of galaxies that included radiative hydrodynamics, star formation,
+supernova feedback, and followed CR physics using a novel formulation that trace
+the most important injection and loss processes self-consistently while
+accounting for the CR pressure in the equation of motion
+\citep{2006MNRAS.367..113P,2007A&A...473...41E,2008A&A...481...33J}.  The
+results are in line with earlier numerical results on some of the overall
+characteristics of the CR distribution and the associated radiative emission
+processes \citep{2000A&A...362..151D,2001ApJ...559...59M,2003MNRAS.342.1009M,
+  2007MNRAS.378..385P,2008MNRAS.385.1211P,2008MNRAS.385.1242P}, but for the
+first time is able to track the spectral evolution as a function of space while
+accounting for the non-linear feedback of such a population on the hydrodynamics
+in a high-resolution cosmological simulation of the formation of galaxy
+clusters.
+
+We note that the overall normalization of the CR and gamma-ray distribution
+scales with the maximum acceleration efficiency at structure formation shock
+waves. Following recent observations at supernova remnants
+\cite{2009Sci...325..719H} as well as theoretical studies
+\cite{2005ApJ...620...44K}, we adopt an optimistic but nevertheless realistic
+value of this parameter and assume that 50\% of the dissipated energy at strong
+shocks is injected into CRs while this efficiency rapidly decreases for weaker
+shocks \cite{2007A&A...473...41E}. Since the vast majority of internal formation
+shocks (merger and flow shocks) are weak shocks with Mach numbers $M\lesssim3$
+\citep[e.g.,][]{2003ApJ...593..599R,2006MNRAS.367..113P} they do not
+significantly contribute to the CR population in clusters. Instead, strong
+shocks during the formation epoch of clusters and strong accretion shocks at the
+present time (at the boundary of voids and filaments/super-cluster regions)
+dominate the injection of CRs which are adiabatically transported into clusters
+thereafter. Hence, these model predictions provide a plausible upper limit for
+the CR contribution from structure formation shocks in galaxy clusters which can
+be scaled down for a lower effective acceleration efficiency in the strong shock
+regime.  On the other hand, other possible CR sources such as AGN and starburst
+driven galactic winds have been neglected for simplicity which could in
+principle increase the expected gamma-ray yield from clusters by an unknown
+factor.
+
+There are additional limitations of the simulated physics in these cosmological
+simulations which only considered advective transport of CRs by turbulent gas
+motions which produces centrally enhanced profiles.  However, active CR
+transport such as CR diffusion and streaming tends to drive the CR radial
+profiles towards being flat, with equal CR number density everywhere. While the
+CR streaming is then usually larger than typical advection velocities and
+becomes comparable or lower than this only for periods with trans- and
+supersonic cluster turbulence during a cluster merger. As a consequence a
+bimodality of the CR spatial distribution results with merging (relaxed)
+clusters showing a centrally concentrated (flat) CR energy density profile
+\cite{2011A&A...527A..99E}.  This translates into a bimodality of the expected
+diffuse radio and gamma-ray emission of clusters, since more centrally
+concentrated CR will find higher target densities for hadronic CR proton
+interactions \cite{2011A&A...527A..99E}. As a result of this, relaxed clusters
+could have a reduced gamma-ray luminosity by up to a factor of five. The goal of
+this and other future work of seeking for gamma-ray emission from clusters is to
+constrain the acceleration physics and transport properties of CRs.
+
+We adopt the electron density profile for the Coma cluster that has been
+inferred from ROSAT X-ray observations \citep{1992A&A...259L..31B} and model the
+spatial and spectral distribution of CRs according to the (conservative) model
+by \citet{2010MNRAS.409..449P} that neglects the contribution of cluster
+galaxies. Figure ?? shows the expected spectrum of Coma, normalized to the total
+flux within the virial radius. Add {\em Fermi} results \ldots
+
+Figure~\ref{fig:xcr} shows the relative CR pressure, $X_\CR = \bra P_\CR
+\ket / \bra P_\rmn{th} \ket$ as a function of radial distance from the
+Coma cluster center (dashed lines). To compute the CR pressure, we assume a
+lower cutoff of the CR distribution of $P = 0.8\,m_\rmn{p} c^2$ as found in
+these simulations due to the high cooling rates at low CR energies that
+effectively thermalizes the low-energy, trans-relativistic CR population.  The
+relative CR pressure rises toward the outer regions due to CR acceleration being
+more efficient at the peripheral strong accretion shocks compared to weak
+central flow shocks and adiabatic compression of a composite of CRs and thermal
+gas disfavours the CR pressure relative to the thermal pressure due to the
+softer equation of state of CRs. The weak increase of $X_\CR$ toward the core is
+due to the comparably fast thermal cooling of gas which diminishes the thermal
+pressure support relative to that in CRs yielding to adiabatic compression of
+CRs.
+
+Table~\ref{table:constraints} shows the expected gamma-ray fluxes within the
+regions of interest. For the most constraining regions tested (within an
+aperture of radius 0.2$^\circ$), those are a factor of 7.2 below the inferred
+upper limits (see Table~\ref{table:results} and assuming a spectral index of
+$\alpha=2.3$ which matches the simulated one at energies $E=200$~GeV).  Hence we
+scale the averaged relative CR pressure, $X_\CR = \bra P_\CR \ket /
+\bra P_\rmn{th} \ket$ of our model by that factor, keep the spatial
+behavior and obtain an integrated limit of the relative CR pressure of
+$X_\CR<0.091$ within 0.2$^\circ$ that translates to a limit within the cluster
+virial radius of $X_\CR<0.13$ (solid lines of Figure~\ref{fig:xcr}).
+
+\subsection{Simplified analytical model}
+
+To complement the simulation-inspired analysis and to facilitate comparison with
+earlier analytical work, we repeat the data analysis with a simplified
+analytical model that assumes a power-law CR spectrum and a constant relative CR
+pressure, i.e., we adopt the {\em isobaric model of CRs}. Since a priori, the CR
+spectral index is unconstrained, we vary it within plausible ranges of
+$2.1<\alpha_\rmn{p}<2.5$. These spectral ranges are needed to explain the radio
+spectral index of the giant radio halo of Coma after accounting for the spectral
+steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich
+effect \citep{2004A&A...413...17P}\footnote[4]{Assuming a magnetic field of
+  1~$\mu$G, the CR protons responsible for the GHz radio emitting electrons have
+  an energy of $~100$~GeV and are $\sim$ 20 times less energetic than those CR
+  protons that are responsible for the 200 GeV $\gamma$-ray emission. This is
+  consistent with the concave curvature found in the universal CR spectrum
+  \citet{2010MNRAS.409..449P}.}.  Table~\ref{table:constraints} shows the
+resulting constraints on $X_\CR$ which range between 0.05 and 1, strongly
+depending on the assumed spectral index.
+
+Add {\em Fermi} results, critical spectral index \ldots
+
+\del{
+the limit for 0.2 deg and alpha_p = 2.3 is compatible with the simulation based
+one, X_CR < 0.1. However, there is currently a discrepancy in our assumptions
+about the lower energy cutoff of CRs: in the simulations we use P/mp c = 0.8 (as
+simulated) while I set this to 0 in my simplified (isobaric) model. The
+discrepancy can be understood as follows:
+*) in the isobaric model, we would have to normalize our $X_\CR$ by a factor of 2/3
+for an effective spectral index of ~ 2.4 (between GeV and 200 GeV) as inferred
+from the simulations (see Fig 1, CP & Ensslin 2004, A&A, 413, 17).
+*) In the simulation model, we have an increased pressure by this factor of 3/2
+(in comparison to a power law spectrum with alpha_TeV ~ 2.3 down to a cutoff in
+the normalized momentum of 0.8) due to the concave curvature of our spectrum.
+}
+
+\subsection{Minimum gamma-ray flux}
+
+For clusters that host radio halos we are able to derive a minimum $\gamma$-ray
+flux in the hadronic model of CR interactions. The idea is based on the fact
+that a stationary distribution of CR electrons loses all its energy to
+synchrotron radiation for strong magnetic fields ($B \gg B_\rmn{CMB} \simeq 3.2
+\mu$G) so that the ratio of $\gamma$-ray to synchrotron flux becomes independent
+of the spatial distribution of CRs and thermal gas \citep{2008MNRAS.385.1242P}.
+This can be easily seen by considering the pion decay induced $\gamma$-ray
+luminosity $L_\gamma$ and the synchrotron luminosity $L_\nu$ of a steady state
+distribution of CR electrons that has been generated by hadronic CR
+interactions,
+\begin{eqnarray}
+L_\gamma &=& A_\gamma \dps\int d V\, n_\CR n_\rmn{gas},\\
+\label{eq:Lnu}
+   L_\nu &=& A_\nu \dps\int d V\, n_\CR n_\rmn{gas} \frac{\dps
+    \eps_B^{(\alpha_\nu+1)/2}}{\dps\eps_\rmn{CMB}+\eps_B}\\
+  &\simeq&A_\nu \dps\int d V\, n_\CR n_\rmn{gas}\quad\rmn{for}~\eps_B \gg \eps_\rmn{CMB}.
+\end{eqnarray}
+Here $A_\gamma$ and $A_\nu$ are dimensional constants that depend on the
+hadronic physics of the interaction \citep{2008MNRAS.385.1211P,
+  2008MNRAS.385.1242P} and $\alpha_\nu\simeq 1$ is the observed synchrotron
+spectral index. Hence we can derive a minimum $\gamma$-ray flux in the hadronic
+model
+\begin{equation}
+  \label{eq:Fmin}
+  \mathcal{F}_{\gamma,\rmn{min}} = 
+  \frac{\dps A_\gamma}{\dps A_\nu}\frac{\dps L_\nu}{\dps 4\pi D_\rmn{lum}^2},
+\end{equation}
+where $L_\nu$ is the observed luminosity of the radio mini-halo and
+$D_\rmn{lum}$ denotes the luminosity distance to the respective cluster.
+Lowering the magnetic field would require an increase in the energy density of
+CR electrons to reproduce the observed synchrotron luminosity and thus increase
+the associated $\gamma$-ray flux.
+
+To derive a minimum gamma-ray flux that is comparable to the upper limits, we
+need to determined the radio flux within the corresponding angular regions. To
+this end, we fit the point source subtracted, azimuthally averaged radio halo
+profile at 1.38 GHz \citet{1997A&A...321...55D} with a $\beta$-model,
+\begin{equation}
+S_\nu (r_\bot)= S_0\, 
+\left[ 1 + \left( \frac{r_\bot}{r_{\rmn{c}}}\right)^2\right]
+^{-3\beta + 1/2},
+\label{beta}
+\end{equation}
+where $S_0 = 1.1 \times 10^{-3}\,\rmn{Jy\,arcmin}^{-2}$, $r_{\rmn{c}} = 450
+kpc$, and $\beta = 0.78$.  Within the error bars, this profile is consistent
+with 326 MHz-data taken by \citet{2001A&A...369..441G} when scaled with a radio
+spectral index of 1.15.
+
+The results for the minimum gamma-ray flux $F_{\rmn{min}}(>E=220~\rmn{GeV}$ and
+the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ are
+shown in Table~\ref{table:constraints}. Even in the most constraining case
+($\alpha=2.1$, $<0.2^\circ$), these are a factor of about 60 below the upper
+limits obtained in this work.
+
+Add {\em Fermi} results\ldots
+
+\section{Constraining the Magnetic Field}
+\label{sec:B}
+
+We have seen in the previous Section that we can obtain an absolute lower limit
+on the gamma-ray emission in the hadronic model by assuming high magnetic
+fields, $B>B_\rmn{CMB}$. Hence, we can turn this around by using our upper limit
+on the gamma-ray emission (and by extension on the CR pressure) to infer a lower
+limit on the magnetic field that is needed to explain the observed radio
+emission which, however, assumes the validity of the hadronic model. Lowering
+the gamma-ray constraint will tighten (increase) the magnetic field limit. Once
+this gets in conflict with magnetic field measurements by means of other
+methods, e.g., Faraday rotation measure (RM)\footnote{Generally, Faraday RM
+  of the magnetic field strength by, e.g., background sources through clusters
+  are degenerate with the magnetic coherence scale. Only a simultaneous
+  deprojection method that self-consistently solves for the magnetic power
+  spectrum is in principle able to break this degeneracy, however, require
+  high-quality data and picks up further complications when using embedded
+  sources within the cluster plasma, e.g., degeneracies with the assumed
+  projection angle of the jet \citep{2011A&A...529A..13K}.}, this would
+challenge the hadronic model of radio halos.  The method that we use to
+constrain the magnetic field inherits a dependence on the assumed spatial
+structure that we parametrize by
+\begin{equation}
+  \label{eq:B}
+  B(r) = B_0  \,\left(\frac{n_\rmn{e}(r)}{n_\rmn{e}(0)}\right)^{\alpha_B},
+\end{equation}
+as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD)
+simulations \citep[][and references therein]{2010A&A...513A..30B,
+  2011arXiv1107.0968B}. In fact, the magnetic field in the Coma cluster is among
+the best ones constrained due to its proximity that enables RM observations of
+seven radio-sources located at projected distances of 50 to 1500 kpc from the
+cluster center. The best fit model obtains $B_0 = 4.7^{+0.7}_{-0.8}\,\mu$G and
+$\alpha_B = 0.5^{+0.2}_{-0.1}$ \citep{2010A&A...513A..30B}.  We aim for
+constraining the central field strength, $B_0$, which depends on the magnetic
+decline, $\alpha_B$, that we vary (within reasonable ranges of
+$\Delta\alpha_B=0.2$ as suggested from the Faraday RM studies) to address this
+dependence. We proceed as follows:
+
+1) Given a model for the magnetic field, we determine the profile of the
+relative CR pressure, $X_\CR$, so that the hadronically produced CR electrons
+exactly matches the observed radio halo emission over the entire extent. To this
+end, we de-project the fit to the surface brightness profile (using an Abel
+integral equation, see Appendix of \citealt{2004A&A...413...17P}) yielding the
+radio emissivity,
+\begin{equation}
+  \label{eq:Coma:radio}
+  j_\nu (r) = \frac{S_0}{2\pi\, r_\rmn{c}}\, 
+  \frac{6\beta - 1}{\left(1 + r^2/r_\rmn{c}^2\right)^{3 \beta}}\,
+  \mathcal{B}\left(\frac{1}{2}, 3\beta\right)
+  = j_{\nu,0} \left(1 + r^2/r_\rmn{c}^2\right)^{-3 \beta},
+\end{equation}
+where $\mathcal{B}$ denotes the beta function. Using ``isobaric CR model'' of
+the formalism suggested by \citet{2004A&A...413...17P} to compute the secondary
+radio emission and imposing the boundary condition to reproduce the observed
+radio emission profile uniquely determines $X_\CR(r)$. One of those realizations
+for the relative CR energy density $\tilde{X}_\CR(r) = \eps_\CR (r) /
+\eps_\rmn{th} (r)$ and $\tilde{X}_B(r) = \eps_B (r) / \eps_\rmn{th} (r)$ is
+shown in Figure 2 (lower left panel) of \citet{2004MNRAS.352...76P} which also
+has the interesting property to represent the minimum energy configuration that
+is able to reproduce the radio emission in the hadronic model.\footnote{Note
+  that a central magnetic field of $3\,\mu$G corresponds in the Coma cluster to
+  a relative magnetic energy density of $\tilde{X}_B=0.005$. For a CR population
+  in clusters that have been accelerated in structure formation shocks the
+  relativistic limit $E_\CR/E_\rmn{th} = 2 \bra P_\CR \ket / \bra P_\rmn{th}
+  \ket$ is not applicable since the CR pressure is dominated by the
+  trans-relativistic regime. This implies a somewhat harder equation of state
+  for the CRs with a larger adiabatic index and yields the relation
+  $E_\CR/E_\rmn{th} = 1.6 \bra P_\CR \ket / \bra P_\rmn{th} \ket$.}  The shaded
+regions indicate the logarithmic curvature at the minimum, showing that only
+modest additional energy investment would be needed to move the system by a
+factor two away from this energetically least expensive state which needs not to
+be realized in Nature.  The realization of the minimum energy magnetic field
+corresponds to a magnetic decline of $\alpha_B\simeq0.3$ and is close to
+equipartition with the CR proton pressure (but not that of the resulting
+secondary CR electrons).  It is generically true for weak magnetic fields
+($B<B_\rmn{CMB}$) in the outer parts of the Coma halo that the product
+$X_\CR(r)X_B(r)$ has to increase by a factor of about 100 toward the radio halo
+periphery to account for the observed extent.  If we were to adopt a steeper
+magnetic decline such as $\alpha_B=0.5$ which produces a flat $X_B(r)$, the
+relative CR pressure would have to rise accordingly by a factor of 100.
+
+2) Given this realization for $X_\CR$, we compute the pion decay gamma-ray
+surface brightness profile, integrate the flux within a radius of $\{0.13, 0.2,
+0.4\}$ degree, and scale the CR profile in order to match the corresponding
+VERITAS upper limits.  This scaling factor, $X_{\CR,0}$, depends on the CR
+spectral index, $\alpha$, (assuming a power-law CR population for simplicity) and
+the radial decline of the magnetic field, $\alpha_B$.
+
+3) In the last step, we scale the secondary radio emission profile linearly
+with $X_{\CR,0}$ and solve for $B_0$ subject to the boundary condition to match
+the observed synchrotron profile. Note that for $B_0 \gg B_\rmn{CMB}$ and radio
+spectral index, $\alpha_\nu$, the solution would be degenerate according to
+Eqn.~(\ref{eq:Lnu}).
+
+Table~\ref{table:Bmin} shows the results on the lower limit of the central
+magnetic field that range from $B_0 = 0.4$ to $1.2\,\mu$G. There are a few
+interesting remarks in order.  (1) The hardest CR spectral indices are most
+constraining because of the tightest upper limits.  (2) For a steeper magnetic decline
+(larger $\alpha_B$), the CR number density needs to be larger to match the
+observed radio emission profiles which would yield a higher gamma-ray flux so
+that the upper limits are more constraining. This implies tighter lower limits for $B_0$.
+However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing
+magnetic field, is possibly too steep in the outer parts as it neglects the
+contributions from the turbulent dynamo in these dynamically active regions with
+large amounts of vorticity injection at corrugated structure formation shocks
+\citep[as observationally inferred for the first time
+by][]{2011ApJ...730...22P}.  (3) Interestingly, in all cases, we use the
+0.4$^\circ$ limit that is always most constraining for our choice of magnetic
+field configurations.  This is because we need a substantially increasing
+relative CR pressure profile to match the observed radio profiles (for a given
+magnetic realization); hence that CR realization produces a larger flux within
+0.4$^\circ$ in comparison to the ``isobaric CR model'' assumption ($X_\CR =
+\rmn{const.}$) for which the 0.2$^\circ$ upper limits are more constraining;
+hence the constraints on $B_0$ get better for the larger integration area.
+Physically, this can be achieved by considering (active) CR transport such as CR
+streaming which produces an increasing $X_\CR$-profile due to the larger
+available phase space in the outer cluster regions (or equivalently an
+incomplete turbulent pumping of CRs into the central regions).  Required
+streaming and turbulent pumping timescales match what is required to explain the
+observed radio halo bimodality when carefully considering the plasma physics in
+high-beta plasmas \citep{2011A&A...527A..99E}.
+
+As a final word, we note that the $X_\CR$-profiles always obey the energy
+condition, i.e., $P_\CR < P_\mathrm{th}$ over the entire range of the radio halo
+emission ($< 1$~Mpc) when assuming a central magnetic field of $B_0=3\,\mu$G
+that is at the lower 2-$\sigma$ interval bound inferred from Faraday RM
+\citep{2010A&A...513A..30B}. Typical values at 1 Mpc range from $X_\CR = 0.02$
+($\alpha_B=0.3$, $\alpha=2.1$) to $X_\CR = 1$ ($\alpha_B=0.7$,
+$\alpha=2.5$).\footnote{See Figure 3 in \citet{2004MNRAS.352...76P} for the
+  entire parameter range assuming minimum energy conditions and
+  \citet{2004A&A...413...17P}, Figure 7 for a parametrization as adopted in this
+  study.} We caution, however, that the minimum energy condition is violated at
+the outer radio halo boundary for the range of minimum magnetic field values
+inferred by this study.
 
@@
 VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
+
+Various approaches to model CR population and magnetic field distribution are
+complementary (so far just ideas, need to be formulated):
+\begin{itemize}
+\item simplified ``isobaric CR model'': simple and widely used in the
+  literature. A priori, physically not justified, old fashioned, should be
+  replaced by the approached below.
+\item simulation-based analytical approach: ``first principle approach'' that
+  predicts the CR and B distribution for a given set of assumptions. Powerful
+  since it only required the density profile as input, but limited in the
+  modeled physics (no active CR transport) that appears to be necessary to
+  explain the radio halo bimodality.
+\item pragmatic approach as employed in Sect.~\ref{sec:B}: model CR and B to
+  reproduce observed radio emission profile. Minimum energy conditions (or
+  equivalently equipartition arguments) represent a special case within this
+  approach. A priori, also physically not justified, but quite powerful as it
+  shows what the ``correct'' model has to achieve and can point into the
+  direction what the relevant physics has to deliever. Compare CR transport
+  vs. simulation inspired models
+\end{itemize}
 
@@
 \end{center}
-\caption{Cosmic-ray pressure, $X_{\mathrm{CR}}$, as a function of radial distance from the Coma cluster core.}
+\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}\bra P_\CR \ket / \bra
+  P_\rmn{th} \ket$, as a function of radial distance from the Coma cluster
+  center. Model predictions are shown by dashed lines \citep{2010MNRAS.409..449P}
+  while these are scaled to match the most constraining VERITAS upper limits
+  within 0.2$^\circ$ (solid). We compare differential $X_\CR$-profiles (red) to
+  integrated profiles $X_\CR(<R/R_\rmn{vir})$ (blue) which we use to compare to
+  the upper limits.}
 \label{fig:xcr}
@@
 
+\begin{landscape}
+\begin{deluxetable}{cccccccccccc}
+\tablecolumns{12}
+\tablewidth{0pc}
+\tablecaption{Constraints on relative CR pressure and magnetic fields for different regions of interest in the Coma cluster of galaxies.}
+\tablehead{
+\colhead{RoI\tablenotemark{a} [deg]} 
+    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
+    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
+    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
+    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
+& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+}
+\startdata
+0.13 & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
+0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
+0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16
+\enddata
+\tablenotetext{a}{Intrinsic source radius (in the point source case, the radius got replaced by the PSF radius).}
+
+\tablenotetext{b}{Differential gamma-ray flux $E^2 dF/dE$ at $E=220$~GeV in
+  units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic
+  model by \citet{2010MNRAS.409..449P}. }
+
+\tablenotetext{c}{Integrated gamma-ray flux $F(>E=220~\rmn{GeV})$ in units of
+  $10^{-9}$ ph. m$^{-2}$ s$^{-1}$ in the simulation-based analytical model by
+  \citet{2010MNRAS.409..449P}.}
+
+\tablenotetext{c}{Constraint on the relative CR pressure, $X_\CR = \bra P_\CR\ket /
+  \bra P_\rmn{th}\ket$ that was assumed to be constant throught the cluster; calculated
+  according to \citet{2004A&A...413...17P}.}
+
+\tablenotetext{e}{Minimum gamma-ray flux $F_{\rmn{min}}(>E=220~\rmn{GeV}$ in units of
+  $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
+
+\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ for energies
+  above $E=220~\rmn{GeV}$ of the hadronic model described in the text.}
+\label{table:constraints}
+\end{deluxetable}
+\end{landscape}
+
+\begin{deluxetable}{cccc}
+\tablecolumns{4}
+\tablewidth{0pc}
+\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma}
+\tablehead{
+\colhead{$\alpha_B$\tablenotemark{a}} &
+\multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$\tablenotemark{a}}\\
+\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+}
+\startdata
+0.3 & 0.61 & 0.51 & 0.43 \\
+0.5 & 0.82 & 0.68 & 0.58 \\
+0.7 & 1.19 & 0.98 & 0.83 
+\enddata
+\tablenotetext{a}{The parameters of the magnetic field are the magnetic decline,
+  $\alpha_B$, and the central field strength, $B_0$, which are defined by $B(r) = B_0
+  \,[n_\rmn{e}(r)/n_\rmn{e}(0)]^{\alpha_B}$.}
+\label{table:Bmin}
+\end{deluxetable}
+
 \end{document}

### 2011-07-08 ms.tex
more conflicts resolved
Changes

--- 2011-07-05 ms.tex
@@
 Several emission regions are considered, including the cluster core as both unresolved (point-like) and spatially extended, and a select few cluster members.
-The flux upper limits at the 99\% confidence level measured are on the order of $2-5\times 10^{-8}$ ph.
+The measured flux upper limits at the 99\% confidence level are on the order of $2-5\times 10^{-8}$ ph.
 m$^{-2}$ s$^{-1}$, which is X times higher than the model-predicted minimum gamma-ray flux.
@@
 %\keywords{cosmic rays: interactions --- galaxies --- galaxy clusters -- VHE}
-\keywords{cosmic rays --- gamma rays: observations --- gamma rays: VHE --- galaxies: clusters: general --- galaxies: clusters: individual: Coma (ACO 1656)}
+\keywords{cosmic rays --- gamma rays: observations --- gamma rays: VHE --- galaxies: clusters: general --- galaxies: clusters: individual: Coma (ACO 1656) --- dark matter}
 
@@
 \enddata
-\tablenotetext{a}{Note.
-The cluster core is considered both as a point source and a modestly extended source.
+\tablecomments{The cluster core is considered both as a point source and a modestly extended source.
 Three central galaxies are also considered in point-source searches.
@@
 
+\begin{deluxetable}{lcccccc}
+\tablecolumns{7}
+\tablewidth{0pc}
+\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core.}
+\tablehead{
+\colhead{Spatial model} & \multicolumn{6}{c}{Flux U.L.}
+}
+\startdata
+Point source & 1.73 & 1.81 & 0.487 & 0.526 & 0.627 & 0.635
+\enddata
+\end{deluxetable}
+
 \end{document}

### 2011-07-20 ms.tex
Edited citations to match

@@
 \altaffiltext{3}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
-\altaffiltext{4}{ Institut fu\"r Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm, Germany}
+\altaffiltext{4}{ Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm, Germany}
 \altaffiltext{5}{Heidelberg Institute	for Theoretical	Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
 \altaffiltext{6}{Canadian Institute for Theoretical Astrophysics, University of Toronto, Toronto, ON, M5S 3H8, Canada}
-\altaffiltext{7}{University of California, Santa Barbara, CA 93106}
+\altaffiltext{7}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
 
@@
 Theoretical models of galaxy clusters suggest they may be sources of very high-energy (VHE) gamma-ray emission.
-Observations of radio halos and relics in clusters indicate populations of relativistic electrons and positrons, which are either injected into the intra-cluster medium and accelerated by turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with the intra-cluster gas.
+Observations of radio halos and relics in clusters indicate populations of relativistic electrons, which are either injected into the intra-cluster medium and accelerated by turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with the intra-cluster gas.
 Those interactions would also produce gamma rays through the decay of neutral pions.
@@
 Several emission regions are considered, including the cluster core as both unresolved (point-like) and spatially extended, and a select few cluster members.
-The measured flux upper limits at the 99\% confidence level are on the order of $2-5\times 10^{-8}$ ph.
+The flux upper limits at the 99\% confidence level measured are on the order of $2-5\times 10^{-8}$ ph.
 m$^{-2}$ s$^{-1}$, which is X times higher than the model-predicted minimum gamma-ray flux.
@@
 %\keywords{cosmic rays: interactions --- galaxies --- galaxy clusters -- VHE}
-\keywords{cosmic rays --- gamma rays: observations --- gamma rays: VHE --- galaxies: clusters: general --- galaxies: clusters: individual: Coma (ACO 1656) --- dark matter}
+\keywords{cosmic rays --- gamma rays: observations --- gamma rays: VHE --- galaxies: clusters: general --- galaxies: clusters: individual: Coma (ACO 1656) --- dark matter --- magnetic fields}
 
@@
 It hosts both a giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
-It has been suggested that the relic is an infall shock \citep{1998A&A...332..395E} and succesively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{2008MNRAS.385.1211P,2008MNRAS.385.1242P,2009MNRAS.393.1073B, 2011ApJ...735...96S}.
+It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and succesively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
 Extended soft X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo.
@@
 In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
-Throughout the analysis, we use a present day Hubble constant of $H_0 = 100 h \mbox{ km s}^{-1} \mbox{ Mpc}^{-1}$ with $h=0.7$.
+Throughout the analysis, a present day Hubble constant of $H_0 = 100 h \mbox{ km s}^{-1} \mbox{ Mpc}^{-1}$ with $h=0.7$ has been used.
 
@@
 The Large Area Telescope (LAT) on board the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi}) has observed the Coma cluster in all-sky survey mode since its launch in June 2008.
-The \emph{Fermi}-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus very complimentary to the VERITAS obervations.
+The \emph{Fermi}-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus very complimentary to the VERITAS observations.
 \citet{article:Ackermann_etal:2010} reported on the search for gamma-ray emission from thirty-three galaxy clusters in the data from the first 18 months, including the Coma cluster, for which an upper limit of $4.58\times 10^{-9}$ ph.
@@
 To eliminate albedo gamma rays from the Earth limb, a zenith angle cut of 105$^{\circ}$ is applied.
-The \emph{Fermi} Science Tools version v9r23p1 and Instrumental Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events calibrated ...) were used throughout this work.
+The \emph{Fermi} Science Tools version v9r23p1 and Instrumental Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events calibrated  in flight) were used throughout this work.
 Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful.
@@
 
-\section{Cosmic Rays}
-
+\section{Gamma Rays Emission from Cosmic Rays}
 We decided to adopt a multifaceted approach to constrain the CR-to-thermal
@@
 that are imposed on the modelling \citep[see][for a
-discussion]{2011arXiv1105.3240P}.
+discussion]{article:PinzkePfrommerBergstrom}.
 
 \subsection{Simulation-based approach}
-
 We adopt the universal spectral and spatial gamma-ray model developed by
-\citet{2010MNRAS.409..449P} to estimate the emission from decaying neutral pions
+\citet{article:PinzkePfrommer:2010} to estimate the emission from decaying neutral pions
 that dominates over the IC emission from primary and secondary electrons above
@@
 accounting for the CR pressure in the equation of motion
-\citep{2006MNRAS.367..113P,2007A&A...473...41E,2008A&A...481...33J}.  The
+\citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007, article:JubelgasSpringelEnsslinPfrommer:2008}.  The
 results are in line with earlier numerical results on some of the overall
 characteristics of the CR distribution and the associated radiative emission
-processes \citep{2000A&A...362..151D,2001ApJ...559...59M,2003MNRAS.342.1009M,
-  2007MNRAS.378..385P,2008MNRAS.385.1211P,2008MNRAS.385.1242P}, but for the
+processes \citep{article:DolagEnsslin, article:MiniatiRyuKangJones:2001, article:Miniati:2003, article:Pfrommer_etal:2007, article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008}, but for the
 first time is able to track the spectral evolution as a function of space while
@@
 waves. Following recent observations at supernova remnants
-\cite{2009Sci...325..719H} as well as theoretical studies
-\cite{2005ApJ...620...44K}, we adopt an optimistic but nevertheless realistic
+\cite{article:Helder_etal:2009} as well as theoretical studies
+\cite{article:KandJones:2005}, we adopt an optimistic but nevertheless realistic
 value of this parameter and assume that 50\% of the dissipated energy at strong
 shocks is injected into CRs while this efficiency rapidly decreases for weaker
-shocks \cite{2007A&A...473...41E}. Since the vast majority of internal formation
+shocks \cite{article:EnsslinPfrommerSpringelJubelgas:2007}. Since the vast majority of internal formation
 shocks (merger and flow shocks) are weak shocks with Mach numbers $M\lesssim3$
-\citep[e.g.,][]{2003ApJ...593..599R,2006MNRAS.367..113P} they do not
+\citep[e.g.,][]{article:Ryu_etal:2003, article:PfrommerSpringelEnsslinJubelgas} they do not
 significantly contribute to the CR population in clusters. Instead, strong
@@
 clusters showing a centrally concentrated (flat) CR energy density profile
-\cite{2011A&A...527A..99E}.  This translates into a bimodality of the expected
+\cite{article:EnsslinPfrommerMiniatiSubramanian:2011}.  This translates into a bimodality of the expected
 diffuse radio and gamma-ray emission of clusters, since more centrally
 concentrated CR will find higher target densities for hadronic CR proton
-interactions \cite{2011A&A...527A..99E}. As a result of this, relaxed clusters
+interactions \cite{article:EnsslinPfrommerMiniatiSubramanian:2011}. As a result of this, relaxed clusters
 could have a reduced gamma-ray luminosity by up to a factor of five. The goal of
@@
 We adopt the electron density profile for the Coma cluster that has been
-inferred from ROSAT X-ray observations \citep{1992A&A...259L..31B} and model the
+inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the
 spatial and spectral distribution of CRs according to the (conservative) model
-by \citet{2010MNRAS.409..449P} that neglects the contribution of cluster
+by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster
 galaxies. Figure ?? shows the expected spectrum of Coma, normalized to the total
@@
 steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich
-effect \citep{2004A&A...413...17P}\footnote[4]{Assuming a magnetic field of
+effect \citep{article:PfrommerEnsslin:2004b}\footnote[4]{Assuming a magnetic field of
   1~$\mu$G, the CR protons responsible for the GHz radio emitting electrons have
@@
   protons that are responsible for the 200 GeV $\gamma$-ray emission. This is
-  consistent with the concave curvature found in the universal CR spectrum
-  \citet{2010MNRAS.409..449P}.}.  Table~\ref{table:constraints} shows the
+  consistent with the concave curvature found in the universal CR spectrum by
+  \citet{article:PinzkePfrommer:2010}.}.  Table~\ref{table:constraints} shows the
 resulting constraints on $X_\CR$ which range between 0.05 and 1, strongly
@@
 
-\del{
-the limit for 0.2 deg and alpha_p = 2.3 is compatible with the simulation based
-one, X_CR < 0.1. However, there is currently a discrepancy in our assumptions
-about the lower energy cutoff of CRs: in the simulations we use P/mp c = 0.8 (as
-simulated) while I set this to 0 in my simplified (isobaric) model. The
-discrepancy can be understood as follows:
-*) in the isobaric model, we would have to normalize our $X_\CR$ by a factor of 2/3
-for an effective spectral index of ~ 2.4 (between GeV and 200 GeV) as inferred
-from the simulations (see Fig 1, CP & Ensslin 2004, A&A, 413, 17).
-*) In the simulation model, we have an increased pressure by this factor of 3/2
-(in comparison to a power law spectrum with alpha_TeV ~ 2.3 down to a cutoff in
-the normalized momentum of 0.8) due to the concave curvature of our spectrum.
-}
+%the limit for 0.2 deg and alpha_p = 2.3 is compatible with the simulation based
+%one, X_CR < 0.1. However, there is currently a discrepancy in our assumptions
+%about the lower energy cutoff of CRs: in the simulations we use P/mp c = 0.8 (as
+%simulated) while I set this to 0 in my simplified (isobaric) model. The
+%discrepancy can be understood as follows:
+%*) in the isobaric model, we would have to normalize our $X_\CR$ by a factor of 2/3
+%for an effective spectral index of ~ 2.4 (between GeV and 200 GeV) as inferred
+%from the simulations \citep[see Fig 1 in][]{article:PfrommerEnsslin:2004}).
+%*) In the simulation model, we have an increased pressure by this factor of 3/2
+%(in comparison to a power law spectrum with alpha_TeV ~ 2.3 down to a cutoff in
+%the normalized momentum of 0.8) due to the concave curvature of our spectrum.
+%}
 
@@
 \mu$G) so that the ratio of $\gamma$-ray to synchrotron flux becomes independent
-of the spatial distribution of CRs and thermal gas \citep{2008MNRAS.385.1242P}.
+of the spatial distribution of CRs and thermal gas \citep{article:Pfrommer:2008}.
 This can be easily seen by considering the pion decay induced $\gamma$-ray
@@
 Here $A_\gamma$ and $A_\nu$ are dimensional constants that depend on the
-hadronic physics of the interaction \citep{2008MNRAS.385.1211P,
-  2008MNRAS.385.1242P} and $\alpha_\nu\simeq 1$ is the observed synchrotron
+hadronic physics of the interaction \citep{article:PfrommerEnsslinSpringel:2008,
+  article:Pfrommer:2008} and $\alpha_\nu\simeq 1$ is the observed synchrotron
 spectral index. Hence we can derive a minimum $\gamma$-ray flux in the hadronic
@@
 this end, we fit the point source subtracted, azimuthally averaged radio halo
-profile at 1.38 GHz \citet{1997A&A...321...55D} with a $\beta$-model,
+profile at 1.38 GHz \citep{article:Deiss_etal:1997} with a $\beta$-model,
 \begin{equation}
@@
 kpc$, and $\beta = 0.78$.  Within the error bars, this profile is consistent
-with 326 MHz-data taken by \citet{2001A&A...369..441G} when scaled with a radio
+with 326 MHz-data taken by \citet{article:Govoni_etal:2001} when scaled with a radio
 spectral index of 1.15.
@@
   sources within the cluster plasma, e.g., degeneracies with the assumed
-  projection angle of the jet \citep{2011A&A...529A..13K}.}, this would
+  projection angle of the jet \citep{article:KucharEnsslin:2011}.}, this would
 challenge the hadronic model of radio halos.  The method that we use to
@@
 as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD)
-simulations \citep[][and references therein]{2010A&A...513A..30B,
-  2011arXiv1107.0968B}. In fact, the magnetic field in the Coma cluster is among
+simulations \citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}. In fact, the magnetic field in the Coma cluster is among
 the best ones constrained due to its proximity that enables RM observations of
@@
 cluster center. The best fit model obtains $B_0 = 4.7^{+0.7}_{-0.8}\,\mu$G and
-$\alpha_B = 0.5^{+0.2}_{-0.1}$ \citep{2010A&A...513A..30B}.  We aim for
+$\alpha_B = 0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}.  We aim for
 constraining the central field strength, $B_0$, which depends on the magnetic
@@
 end, we de-project the fit to the surface brightness profile (using an Abel
-integral equation, see Appendix of \citealt{2004A&A...413...17P}) yielding the
+integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the
 radio emissivity,
@@
 where $\mathcal{B}$ denotes the beta function. Using ``isobaric CR model'' of
-the formalism suggested by \citet{2004A&A...413...17P} to compute the secondary
+the formalism suggested by \citet{article:PfrommerEnsslin:2004b} to compute the secondary
 radio emission and imposing the boundary condition to reproduce the observed
@@
 \eps_\rmn{th} (r)$ and $\tilde{X}_B(r) = \eps_B (r) / \eps_\rmn{th} (r)$ is
-shown in Figure 2 (lower left panel) of \citet{2004MNRAS.352...76P} which also
+shown in Figure 2 (lower left panel) of \citet{article:PfrommerEnsslin:2004a} which also
 has the interesting property to represent the minimum energy configuration that
@@
 \citep[as observationally inferred for the first time
-by][]{2011ApJ...730...22P}.  (3) Interestingly, in all cases, we use the
+by][]{article:PfrommerJones:2011}.  (3) Interestingly, in all cases, we use the
 0.4$^\circ$ limit that is always most constraining for our choice of magnetic
@@
 observed radio halo bimodality when carefully considering the plasma physics in
-high-beta plasmas \citep{2011A&A...527A..99E}.
+high-beta plasmas \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}.
 
@@
 that is at the lower 2-$\sigma$ interval bound inferred from Faraday RM
-\citep{2010A&A...513A..30B}. Typical values at 1 Mpc range from $X_\CR = 0.02$
+\citep{article:Bonafede_etal:2010}. Typical values at 1 Mpc range from $X_\CR = 0.02$
 ($\alpha_B=0.3$, $\alpha=2.1$) to $X_\CR = 1$ ($\alpha_B=0.7$,
-$\alpha=2.5$).\footnote{See Figure 3 in \citet{2004MNRAS.352...76P} for the
+$\alpha=2.5$).\footnote{See Figure 3 in \citet{article:PfrommerEnsslin:2004a} for the
   entire parameter range assuming minimum energy conditions and
-  \citet{2004A&A...413...17P}, Figure 7 for a parametrization as adopted in this
+  \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in this
   study.} We caution, however, that the minimum energy condition is violated at
@@
 \end{center}
-\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}\bra P_\CR \ket / \bra
-  P_\rmn{th} \ket$, as a function of radial distance from the Coma cluster
-  center. Model predictions are shown by dashed lines \citep{2010MNRAS.409..449P}
-  while these are scaled to match the most constraining VERITAS upper limits
-  within 0.2$^\circ$ (solid). We compare differential $X_\CR$-profiles (red) to
-  integrated profiles $X_\CR(<R/R_\rmn{vir})$ (blue) which we use to compare to
-  the upper limits.}
+\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a function of radial distance from the center of the Coma cluster.
+Model predictions are shown by dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining VERITAS upper limits within 0.2$^\circ$ (solid).
+We compare differential $X_\CR$-profiles (red) to integrated profiles $X_{\CR}(<R/R_{\rmn{vir}})$ (blue) which we use to compare to the upper limits.}
 \label{fig:xcr}
@@
 \end{center}
-\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ calculated using the VERITAS data in this work.}
+\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ as a function of the DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
 \label{fig:dm}
@@
 \begin{landscape}
-\begin{deluxetable}{lcccccccccccc}
-\tablecolumns{6}
+\begin{deluxetable}{lccccccccc}
+\tablecolumns{10}
 \tablewidth{0pc}
-\tablecaption{Flux upper limits for regions of interest in the Coma cluster of galaxies and surroundings.}
+\tablecaption{Flux upper limits for different regions of interest in the Coma cluster of galaxies and surroundings.}
 \tablehead{
 \colhead{Source} & \colhead{RoI\tablenotemark{a} [deg]} & \colhead{$N_{S}$} & \colhead{S\tablenotemark{b} [$\sigma$]} &
-\multicolumn{6}{c}{Flux U.L.\tablenotemark{c}} &
-\multicolumn{3}{c}{Minimum gamma-ray flux\tablenotemark{d}}\\
+\multicolumn{6}{c}{Flux U.L.\tablenotemark{c}} \\
 \colhead{} & \colhead{} & \colhead{} & \colhead{} & \multicolumn{2}{c}{$\alpha=2.1$} &
 \multicolumn{2}{c}{$\alpha=2.3$} &
-\multicolumn{2}{c}{$\alpha=2.5$} &
-\colhead{$\alpha=2.1$} &
-\colhead{$\alpha=2.3$} &
-\colhead{$\alpha=2.5$}}
+\multicolumn{2}{c}{$\alpha=2.5$}}
 \startdata
@@
 m$^{-2}$ s$^{-1}$ calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
-\tablenotetext{d}{Minimum gamma-ray flux in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$ from the hadronic model described in the text.}
 \label{table:results}
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on relative CR pressure and magnetic fields for different regions of interest in the Coma cluster of galaxies.}
+\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions.} 
 \tablehead{
@@
 \startdata
-0.13 & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
+0 & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
 0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
@@
 \enddata
-\tablenotetext{a}{Intrinsic source radius (in the point source case, the radius got replaced by the PSF radius).}
-
-\tablenotetext{b}{Differential gamma-ray flux $E^2 dF/dE$ at $E=220$~GeV in
-  units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic
-  model by \citet{2010MNRAS.409..449P}. }
-
-\tablenotetext{c}{Integrated gamma-ray flux $F(>E=220~\rmn{GeV})$ in units of
-  $10^{-9}$ ph. m$^{-2}$ s$^{-1}$ in the simulation-based analytical model by
-  \citet{2010MNRAS.409..449P}.}
-
-\tablenotetext{c}{Constraint on the relative CR pressure, $X_\CR = \bra P_\CR\ket /
-  \bra P_\rmn{th}\ket$ that was assumed to be constant throught the cluster; calculated
-  according to \citet{2004A&A...413...17P}.}
-
-\tablenotetext{e}{Minimum gamma-ray flux $F_{\rmn{min}}(>E=220~\rmn{GeV}$ in units of
-  $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
-
-\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ for energies
-  above $E=220~\rmn{GeV}$ of the hadronic model described in the text.}
+\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
+\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}. }
+\tablenotetext{c}{Integrated gamma-ray flux $F(>E=220~\mathrm{GeV}$) in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$ in the simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
+\tablenotetext{c}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$ that was assumed to be constant throught the cluster; calculated according to \citet{article:PfrommerEnsslin:2004b}.}
+\tablenotetext{e}{Minimum gamma-ray flux $F_{\rmn{min}}(>E=220~\mathrm{GeV}$) in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
+\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ for energies above $E=220~\rmn{GeV}$ of the hadronic model described in the text.}
 \label{table:constraints}
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma}
+\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma cluster.}
 \tablehead{
-\colhead{$\alpha_B$\tablenotemark{a}} &
-\multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$\tablenotemark{a}}\\
-\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
-}
+\colhead{$\alpha_{B}$} &
+\multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
+\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}}
 \startdata
@@
 \enddata
-\tablenotetext{a}{The parameters of the magnetic field are the magnetic decline,
-  $\alpha_B$, and the central field strength, $B_0$, which are defined by $B(r) = B_0
-  \,[n_\rmn{e}(r)/n_\rmn{e}(0)]^{\alpha_B}$.}
+\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
 \label{table:Bmin}

### 2011-07-21 ms.tex
Moved 'Results' to 'VERITAS Results' and before 'Fermi' section

@@
 \altaffiltext{3}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
-\altaffiltext{4}{ Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm, Germany}
+\altaffiltext{4}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm, Germany}
 \altaffiltext{5}{Heidelberg Institute	for Theoretical	Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
@@
 In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
-Throughout the analysis, a present day Hubble constant of $H_0 = 100 h \mbox{ km s}^{-1} \mbox{ Mpc}^{-1}$ with $h=0.7$ has been used.
+Throughout the analysis, a present day Hubble constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
 
@@
 
-\section{Fermi-LAT Observations and Analysis}
+\section{VERITAS Results}
+No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as illustrated by the $\theta^{2}$ distribution shown in Figure \ref{fig:thetasq}.
+The $\theta^{2}$ distribution is a radial comparison of the ON-source event distribution with the estimated background.
+It extends out to a radius of $0.42^{\circ}$ to cover all regions of interest considered in this work.
+A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke_etal:2005} assuming a Gaussian background.
+A lower bound of zero is imposed on the signal rate to handle the negative excesses seen for several of the regions of interest.
+Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent of unity.
+
+Table \ref{table:results} lists the upper limits for the selected regions of interest tabulated in Table \ref{table:roi}.
+These upper-limit calculations depend on the gamma-ray spectrum, which in this work is assumed to be a power law with a spectral index $\alpha=2.1, 2.3$, and $2.5$.
+
+\section{Fermi-LAT Analysis and Results}
 The Large Area Telescope (LAT) on board the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi}) has observed the Coma cluster in all-sky survey mode since its launch in June 2008.
@@
 Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful.
-The 99\% confidence level flux upper limits in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission are tabulated in Table \ref{tabel:fermi}.
+The 99\% confidence level flux upper limits in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission are tabulated in Table \ref{table:fermi}.
 The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$ and $2.5$.
-
-\section{Results}
-No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as illustrated by the $\theta^{2}$ distribution shown in Figure \ref{fig:thetasq}.
-The $\theta^{2}$ distribution is a radial comparison of the ON-source event distribution with the estimated background.
-It extends out to a radius of $0.42^{\circ}$ to cover all regions of interest considered in this work.
-A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke_etal:2005} assuming a Gaussian background.
-A lower bound of zero is imposed on the signal rate to handle the negative excesses seen for several of the regions of interest.
-Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent of unity.
-
-Table \ref{table:results} lists the upper limits for the selected regions of interest tabulated in Table \ref{table:roi}.
-These upper-limit calculations depend on the gamma-ray spectrum, which in this work is assumed to be a power law with a spectral index $\alpha=2.1, 2.3$, and $2.5$.
 
@@
 \enddata
+\label{table:fermi}
 \end{deluxetable}

### 2011-07-21 ms.tex
Fixed a typo

@@
 
-\section{Gamma Rays Emission from Cosmic Rays}
+\section{Gamma Ray Emission from Cosmic Rays}
 We decided to adopt a multifaceted approach to constrain the CR-to-thermal

### 2011-07-21 ms.tex
Fixed a typo

@@
 \section{Gamma Ray Emission from Cosmic Rays}
-We decided to adopt a multifaceted approach to constrain the CR-to-thermal
-pressure distribution in Coma with these upper limits. That includes (1) an
-analytic model derived from cosmological hydrodynamical simulations of the
-formation of galaxy clusters, (2) a simplified multi-frequency analytical
-approach that assumes a constant CR-to-thermal energy density and a power-law
-spectrum in momentum, and (3) an approach that uses the observed luminosity of
-the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray
-flux in the hadronic model -- independent of the magnetic field distribution.
-This translates into a minimum CR pressure which, if challenged by tight
-gamma-ray limits/detections, enables scrutinizing the hadronic interaction model
-of the formation of giant radio halos.  Modelling the CR distribution through
-different techniques enable to bracket our ignorance about the underlying plasma
-physics that shape the CR distribution and hence reflect the Bayesian priors
-that are imposed on the modelling \citep[see][for a
-discussion]{article:PinzkePfrommerBergstrom}.
+We decided to adopt a multifaceted approach to constrain the CR-to-thermal pressure distribution in Coma with these upper limits.
+That includes (1) an analytic model derived from cosmological hydrodynamical simulations of the formation of galaxy clusters, (2) a simplified multi-frequency analytical approach that assumes a constant CR-to-thermal energy density and a power-law spectrum in momentum, and (3) an approach that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray flux in the hadronic model -- independent of the magnetic field distribution.
+This translates into a minimum CR pressure which, if challenged by tight gamma-ray limits/detections, enables scrutinizing the hadronic interaction model of the formation of giant radio halos.
+Modelling the CR distribution through different techniques enable to bracket our ignorance about the underlying plasma
+physics that shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modelling \citep[see][for a discussion]{article:PinzkePfrommerBergstrom}.
 
 \subsection{Simulation-based approach}
-We adopt the universal spectral and spatial gamma-ray model developed by
-\citet{article:PinzkePfrommer:2010} to estimate the emission from decaying neutral pions
-that dominates over the IC emission from primary and secondary electrons above
-100~MeV in clusters. Given a density profile as, e.g., inferred by cosmological
-simulations or X-ray observations, the analytic approach models the CR
-distribution and the associated radiative emission processes from radio to the
-gamma-ray band.  This formalism was derived from high resolution simulations of
-clusters of galaxies that included radiative hydrodynamics, star formation,
-supernova feedback, and followed CR physics using a novel formulation that trace
-the most important injection and loss processes self-consistently while
-accounting for the CR pressure in the equation of motion
-\citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007, article:JubelgasSpringelEnsslinPfrommer:2008}.  The
-results are in line with earlier numerical results on some of the overall
-characteristics of the CR distribution and the associated radiative emission
-processes \citep{article:DolagEnsslin, article:MiniatiRyuKangJones:2001, article:Miniati:2003, article:Pfrommer_etal:2007, article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008}, but for the
-first time is able to track the spectral evolution as a function of space while
-accounting for the non-linear feedback of such a population on the hydrodynamics
-in a high-resolution cosmological simulation of the formation of galaxy
-clusters.
+We adopt the universal spectral and spatial gamma-ray model developed by \citet{article:PinzkePfrommer:2010} to estimate the emission from decaying neutral pions that dominates over the IC emission from primary and secondary electrons above 100 MeV in clusters.
+Given a density profile as, e.g., inferred by cosmological simulations or X-ray observations, the analytic approach models the CR distribution and the associated radiative emission processes from radio to the gamma-ray band.
+This formalism was derived from high resolution simulations of clusters of galaxies that included radiative hydrodynamics, star formation, supernova feedback, and followed CR physics by tracing the most important injection and loss processes self-consistently while accounting for the CR pressure in the equation of motion \citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007, article:JubelgasSpringelEnsslinPfrommer:2008}.
+The results are in line with earlier numerical results on some of the overall characteristics of the CR distribution and the associated radiative emission processes \citep{article:DolagEnsslin, article:MiniatiRyuKangJones:2001, article:Miniati:2003, article:Pfrommer_etal:2007, article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008}.
 
-We note that the overall normalization of the CR and gamma-ray distribution
-scales with the maximum acceleration efficiency at structure formation shock
-waves. Following recent observations at supernova remnants
-\cite{article:Helder_etal:2009} as well as theoretical studies
-\cite{article:KandJones:2005}, we adopt an optimistic but nevertheless realistic
-value of this parameter and assume that 50\% of the dissipated energy at strong
-shocks is injected into CRs while this efficiency rapidly decreases for weaker
-shocks \cite{article:EnsslinPfrommerSpringelJubelgas:2007}. Since the vast majority of internal formation
-shocks (merger and flow shocks) are weak shocks with Mach numbers $M\lesssim3$
-\citep[e.g.,][]{article:Ryu_etal:2003, article:PfrommerSpringelEnsslinJubelgas} they do not
-significantly contribute to the CR population in clusters. Instead, strong
-shocks during the formation epoch of clusters and strong accretion shocks at the
-present time (at the boundary of voids and filaments/super-cluster regions)
-dominate the injection of CRs which are adiabatically transported into clusters
-thereafter. Hence, these model predictions provide a plausible upper limit for
-the CR contribution from structure formation shocks in galaxy clusters which can
-be scaled down for a lower effective acceleration efficiency in the strong shock
-regime.  On the other hand, other possible CR sources such as AGN and starburst
-driven galactic winds have been neglected for simplicity which could in
-principle increase the expected gamma-ray yield from clusters by an unknown
-factor.
+We note that the overall normalization of the CR and gamma-ray distribution scales with the maximum acceleration efficiency at structure formation shock waves.
+Following recent observations at supernova remnants \citep{article:Helder_etal:2009} as well as theoretical studies \citep{article:KangJones:2005}, we adopt an optimistic but nevertheless realistic value of this parameter and assume that 50\% of the dissipated energy at strong shocks is injected into CRs while this efficiency rapidly decreases for weaker shocks.
+Since the vast majority of internal formation shocks (merger and flow shocks) are weak shocks with Mach numbers $M\lesssim3$ \citep[e.g.,][]{article:Ryu_etal:2003}, they do not significantly contribute to the CR population in clusters.
+Instead, strong shocks during the formation epoch of clusters and strong accretion shocks at the present time (at the boundary of voids and filaments/super-cluster regions) dominate the injection of CRs which are adiabatically transported through the cluster.
+Hence, these model predictions provide a plausible upper limit for the CR contribution from structure formation shocks in galaxy clusters which can be scaled with the effective acceleration efficiency.
+Other possible CR sources, such as AGN and starburst-driven galactic winds have been neglected for simplicity which could in principle increase the expected gamma-ray yield.
 
-There are additional limitations of the simulated physics in these cosmological
-simulations which only considered advective transport of CRs by turbulent gas
-motions which produces centrally enhanced profiles.  However, active CR
-transport such as CR diffusion and streaming tends to drive the CR radial
-profiles towards being flat, with equal CR number density everywhere. While the
-CR streaming is then usually larger than typical advection velocities and
-becomes comparable or lower than this only for periods with trans- and
-supersonic cluster turbulence during a cluster merger. As a consequence a
-bimodality of the CR spatial distribution results with merging (relaxed)
-clusters showing a centrally concentrated (flat) CR energy density profile
-\cite{article:EnsslinPfrommerMiniatiSubramanian:2011}.  This translates into a bimodality of the expected
-diffuse radio and gamma-ray emission of clusters, since more centrally
-concentrated CR will find higher target densities for hadronic CR proton
-interactions \cite{article:EnsslinPfrommerMiniatiSubramanian:2011}. As a result of this, relaxed clusters
-could have a reduced gamma-ray luminosity by up to a factor of five. The goal of
-this and other future work of seeking for gamma-ray emission from clusters is to
-constrain the acceleration physics and transport properties of CRs.
+There cosmological simulations only considered advective transport of CRs by turbulent gas motions which produces centrally enhanced profiles.
+However, other means of CR transport such as diffusion and streaming may flatten the CR radial profiles.
+It has been suggested that advection is dominant only during mergers \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}, in which case relaxed clusters could have a reduced gamma-ray luminosity by up to a factor of five compared with merging clusters.
+The goal of this and other future work of seeking for gamma-ray emission from clusters is to constrain the acceleration physics and transport properties of CRs.
 
-We adopt the electron density profile for the Coma cluster that has been
-inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the
-spatial and spectral distribution of CRs according to the (conservative) model
-by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster
-galaxies. Figure ?? shows the expected spectrum of Coma, normalized to the total
-flux within the virial radius. Add {\em Fermi} results \ldots
+We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster galaxies.
+Figure ??
+shows the expected spectrum of Coma, normalized to the total flux within the virial radius.
+[Add {\em Fermi} results]
 
-Figure~\ref{fig:xcr} shows the relative CR pressure, $X_\CR = \bra P_\CR
-\ket / \bra P_\rmn{th} \ket$ as a function of radial distance from the
-Coma cluster center (dashed lines). To compute the CR pressure, we assume a
-lower cutoff of the CR distribution of $P = 0.8\,m_\rmn{p} c^2$ as found in
-these simulations due to the high cooling rates at low CR energies that
-effectively thermalizes the low-energy, trans-relativistic CR population.  The
-relative CR pressure rises toward the outer regions due to CR acceleration being
-more efficient at the peripheral strong accretion shocks compared to weak
-central flow shocks and adiabatic compression of a composite of CRs and thermal
-gas disfavours the CR pressure relative to the thermal pressure due to the
-softer equation of state of CRs. The weak increase of $X_\CR$ toward the core is
-due to the comparably fast thermal cooling of gas which diminishes the thermal
-pressure support relative to that in CRs yielding to adiabatic compression of
-CRs.
+Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance from the Coma cluster center (dashed lines).
+To compute the CR pressure, we assume a low-energy cutoff of the CR distribution at $T = 0.8\,m_\rmn{p} c^2$ reflecting the high cooling rates at low CR energies.
+The relative CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the peripheral strong accretion shocks compared to weak central flow shocks.
+Adiabatic compression of a mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on account of the softer equation of state of CRs.
+The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas which diminishes the thermal support relative to that in CRs.
 
-Table~\ref{table:constraints} shows the expected gamma-ray fluxes within the
-regions of interest. For the most constraining regions tested (within an
-aperture of radius 0.2$^\circ$), those are a factor of 7.2 below the inferred
-upper limits (see Table~\ref{table:results} and assuming a spectral index of
-$\alpha=2.3$ which matches the simulated one at energies $E=200$~GeV).  Hence we
-scale the averaged relative CR pressure, $X_\CR = \bra P_\CR \ket /
-\bra P_\rmn{th} \ket$ of our model by that factor, keep the spatial
-behavior and obtain an integrated limit of the relative CR pressure of
-$X_\CR<0.091$ within 0.2$^\circ$ that translates to a limit within the cluster
-virial radius of $X_\CR<0.13$ (solid lines of Figure~\ref{fig:xcr}).
+Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest.
+For the most constraining regions tested (within an aperture of radius 0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits (see Table \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at energies $E=200$ GeV).
+Hence we scale the averaged relative CR pressure, $X_{\CR}$
+% = \bra P_\CR \ket /\bra P_\rmn{th} \ket$ 
+of our model by that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of $X_{\CR}<0.091$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of $X_\CR<0.13$ (solid lines of Figure \ref{fig:xcr}).
 
 \subsection{Simplified analytical model}
-
-To complement the simulation-inspired analysis and to facilitate comparison with
-earlier analytical work, we repeat the data analysis with a simplified
-analytical model that assumes a power-law CR spectrum and a constant relative CR
-pressure, i.e., we adopt the {\em isobaric model of CRs}. Since a priori, the CR
-spectral index is unconstrained, we vary it within plausible ranges of
-$2.1<\alpha_\rmn{p}<2.5$. These spectral ranges are needed to explain the radio
-spectral index of the giant radio halo of Coma after accounting for the spectral
-steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich
-effect \citep{article:PfrommerEnsslin:2004b}\footnote[4]{Assuming a magnetic field of
-  1~$\mu$G, the CR protons responsible for the GHz radio emitting electrons have
-  an energy of $~100$~GeV and are $\sim$ 20 times less energetic than those CR
-  protons that are responsible for the 200 GeV $\gamma$-ray emission. This is
-  consistent with the concave curvature found in the universal CR spectrum by
-  \citet{article:PinzkePfrommer:2010}.}.  Table~\ref{table:constraints} shows the
-resulting constraints on $X_\CR$ which range between 0.05 and 1, strongly
+To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}.
+Since a priori, the CR spectral index is unconstrained, we vary it within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$.
+This spectral range is compatible with the radio spectral index of the giant radio halo of Coma after accounting for the spectral
+steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.
+Table \ref{table:constraints} shows the resulting constraints on $X_\CR$ which range between 0.05 and 1, strongly
 depending on the assumed spectral index.
 
-Add {\em Fermi} results, critical spectral index \ldots
+[Add {\em Fermi} results, critical spectral index]
 
+%
+% This part was in \del{...} 
+%
 %the limit for 0.2 deg and alpha_p = 2.3 is compatible with the simulation based
@@
 \subsection{Minimum gamma-ray flux}
-
-For clusters that host radio halos we are able to derive a minimum $\gamma$-ray
-flux in the hadronic model of CR interactions. The idea is based on the fact
-that a stationary distribution of CR electrons loses all its energy to
-synchrotron radiation for strong magnetic fields ($B \gg B_\rmn{CMB} \simeq 3.2
-\mu$G) so that the ratio of $\gamma$-ray to synchrotron flux becomes independent
-of the spatial distribution of CRs and thermal gas \citep{article:Pfrommer:2008}.
-This can be easily seen by considering the pion decay induced $\gamma$-ray
-luminosity $L_\gamma$ and the synchrotron luminosity $L_\nu$ of a steady state
-distribution of CR electrons that has been generated by hadronic CR
-interactions,
-\begin{eqnarray}
-L_\gamma &=& A_\gamma \dps\int d V\, n_\CR n_\rmn{gas},\\
-\label{eq:Lnu}
-   L_\nu &=& A_\nu \dps\int d V\, n_\CR n_\rmn{gas} \frac{\dps
-    \eps_B^{(\alpha_\nu+1)/2}}{\dps\eps_\rmn{CMB}+\eps_B}\\
-  &\simeq&A_\nu \dps\int d V\, n_\CR n_\rmn{gas}\quad\rmn{for}~\eps_B \gg \eps_\rmn{CMB}.
-\end{eqnarray}
-Here $A_\gamma$ and $A_\nu$ are dimensional constants that depend on the
-hadronic physics of the interaction \citep{article:PfrommerEnsslinSpringel:2008,
-  article:Pfrommer:2008} and $\alpha_\nu\simeq 1$ is the observed synchrotron
-spectral index. Hence we can derive a minimum $\gamma$-ray flux in the hadronic
+For clusters that host radio halos we are able to derive a minimum gamma-ray flux in the hadronic model of CR interactions.
+The idea is based on the fact that a stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and thermal gas \citep{article:Voelk:1989, article:Pohl:1994}, in particular with $\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.
+Hence we can derive a minimum gamma-ray flux in the hadronic
 model
@@
 \label{eq:Fmin}
-  \mathcal{F}_{\gamma,\rmn{min}} = 
-  \frac{\dps A_\gamma}{\dps A_\nu}\frac{\dps L_\nu}{\dps 4\pi D_\rmn{lum}^2},
+\mathcal{F}_{\gamma,\rmn{min}} = \frac{\dps A_{\gamma}}{\dps A_{\nu}}\frac{\dps L_{\nu}}{\dps 4\pi D_{\rmn{lum}}^{2}},
 \end{equation}
-where $L_\nu$ is the observed luminosity of the radio mini-halo and
-$D_\rmn{lum}$ denotes the luminosity distance to the respective cluster.
-Lowering the magnetic field would require an increase in the energy density of
-CR electrons to reproduce the observed synchrotron luminosity and thus increase
-the associated $\gamma$-ray flux.
+where $L_{\nu}$ is the observed luminosity of the radio mini-halo and $D_{\rmn{lum}}$ denotes the luminosity distance to the respective cluster.
+Lowering the magnetic field would require an increase in the energy density of CR electrons to reproduce the observed synchrotron luminosity and thus increase the associated gamma-ray flux.
 
-To derive a minimum gamma-ray flux that is comparable to the upper limits, we
-need to determined the radio flux within the corresponding angular regions. To
-this end, we fit the point source subtracted, azimuthally averaged radio halo
-profile at 1.38 GHz \citep{article:Deiss_etal:1997} with a $\beta$-model,
+To derive a minimum gamma-ray flux that is comparable to the upper limits, we need to determined the radio flux within the corresponding angular regions.
+To this end, we fit the point-source subtracted, azimuthally averaged radio halo profile at 1.38 GHz \citep{article:Deiss_etal:1997} with a $\beta$-model,
 \begin{equation}
-S_\nu (r_\bot)= S_0\, 
-\left[ 1 + \left( \frac{r_\bot}{r_{\rmn{c}}}\right)^2\right]
-^{-3\beta + 1/2},
 \label{beta}
+ S_{\nu} (r_{\bot})= S_{0} \left[ 1 + \left( \frac{r_{\bot}}{r_{\rmn{c}}}\right)^{2}\right]^{-3\beta + 1/2},
 \end{equation}
-where $S_0 = 1.1 \times 10^{-3}\,\rmn{Jy\,arcmin}^{-2}$, $r_{\rmn{c}} = 450
-kpc$, and $\beta = 0.78$.  Within the error bars, this profile is consistent
-with 326 MHz-data taken by \citet{article:Govoni_etal:2001} when scaled with a radio
-spectral index of 1.15.
+where $S_{0} = 1.1 \times 10^{-3}\,\rmn{Jy\,arcmin}^{-2}$, $r_{\rmn{c}} = 450$ kpc, and $\beta = 0.78$.
+Within the error bars, this profile is consistent with 326-MHz data taken by \citet{article:Govoni_etal:2001} when scaled with a radio spectral index of 1.15.
 
-The results for the minimum gamma-ray flux $F_{\rmn{min}}(>E=220~\rmn{GeV}$ and
-the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ are
-shown in Table~\ref{table:constraints}. Even in the most constraining case
-($\alpha=2.1$, $<0.2^\circ$), these are a factor of about 60 below the upper
-limits obtained in this work.
+The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV}$ and the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ are shown in Table \ref{table:constraints}.
+Even in the most constraining case ($\alpha=2.1$, $<0.2^{\circ}$), these are a factor of about 60 below the upper limits obtained in this work.
 
-Add {\em Fermi} results\ldots
+[Add {\em Fermi} results]
 
@@
 \label{sec:B}
-
-We have seen in the previous Section that we can obtain an absolute lower limit
-on the gamma-ray emission in the hadronic model by assuming high magnetic
-fields, $B>B_\rmn{CMB}$. Hence, we can turn this around by using our upper limit
-on the gamma-ray emission (and by extension on the CR pressure) to infer a lower
-limit on the magnetic field that is needed to explain the observed radio
-emission which, however, assumes the validity of the hadronic model. Lowering
-the gamma-ray constraint will tighten (increase) the magnetic field limit. Once
-this gets in conflict with magnetic field measurements by means of other
-methods, e.g., Faraday rotation measure (RM)\footnote{Generally, Faraday RM
-  of the magnetic field strength by, e.g., background sources through clusters
-  are degenerate with the magnetic coherence scale. Only a simultaneous
-  deprojection method that self-consistently solves for the magnetic power
-  spectrum is in principle able to break this degeneracy, however, require
-  high-quality data and picks up further complications when using embedded
-  sources within the cluster plasma, e.g., degeneracies with the assumed
-  projection angle of the jet \citep{article:KucharEnsslin:2011}.}, this would
-challenge the hadronic model of radio halos.  The method that we use to
-constrain the magnetic field inherits a dependence on the assumed spatial
-structure that we parametrize by
+We have seen in the previous Section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B>B_\rmn{CMB}$.
+Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assumes the validity of the hadronic model.
+Lowering the gamma-ray constraint will tighten (increase) the magnetic field limit.
+Once this gets in conflict with magnetic field measurements by means of other methods, e.g., Faraday rotation measure (RM)\footnote{Generally, Faraday RM analysis of the magnetic-field strength by, e.g., background sources through clusters are degenerate with the magnetic coherence scale and may be biased by the unknown correlation between magnetic and density fluctuations.}, this would challenge the hadronic model of radio halos.
+The method that we use to constrain the magnetic field inherits a dependence on the assumed spatial structure that we parametrize by
 \begin{equation}
 \label{eq:B}
-  B(r) = B_0  \,\left(\frac{n_\rmn{e}(r)}{n_\rmn{e}(0)}\right)^{\alpha_B},
+B(r) = B_{0} \,\left(\frac{n_{\rmn{e}(r)}}{n_{\rmn{e}(0)}}\right)^{\alpha_B},
 \end{equation}
-as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD)
-simulations \citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}. In fact, the magnetic field in the Coma cluster is among
-the best ones constrained due to its proximity that enables RM observations of
-seven radio-sources located at projected distances of 50 to 1500 kpc from the
-cluster center. The best fit model obtains $B_0 = 4.7^{+0.7}_{-0.8}\,\mu$G and
-$\alpha_B = 0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}.  We aim for
-constraining the central field strength, $B_0$, which depends on the magnetic
-decline, $\alpha_B$, that we vary (within reasonable ranges of
-$\Delta\alpha_B=0.2$ as suggested from the Faraday RM studies) to address this
-dependence. We proceed as follows:
+as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD) simulations \citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}.
+In fact, the magnetic field in the Coma cluster is among the best constrained, because its proximity permits RM observations of
+seven radio-sources located at projected distances of 50 to 1500 kpc from the cluster center.
+The best-fit model obtains $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and $\alpha_{B} = 0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}.
+We aim for constraining the central field strength, $B_{0}$, which depends on the magnetic decline, $\alpha_{B}$, that we vary (within reasonable ranges of $\Delta\alpha_{B}=0.2$ as suggested from the Faraday RM studies) to address this dependence.
+We proceed as follows:
 
-1) Given a model for the magnetic field, we determine the profile of the
-relative CR pressure, $X_\CR$, so that the hadronically produced CR electrons
-exactly matches the observed radio halo emission over the entire extent. To this
-end, we de-project the fit to the surface brightness profile (using an Abel
-integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the
-radio emissivity,
+\begin{enumerate}
+\item Given a model for the magnetic field, we determine the profile of the relative CR pressure, $X_{\CR}$, so that the hadronically produced CR electrons exactly matches the observed radio halo emission over the entire extent.
+To this end, we de-project the fit to the surface brightness profile (using an Abel integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio emissivity,
 \begin{equation}
 \label{eq:Coma:radio}
-  j_\nu (r) = \frac{S_0}{2\pi\, r_\rmn{c}}\, 
-  \frac{6\beta - 1}{\left(1 + r^2/r_\rmn{c}^2\right)^{3 \beta}}\,
+j_{\nu} (r) = \frac{S_{0}}{2\pi\, r_{\rmn{c}}}\,
+\frac{6\beta - 1}{\left(1 + r^{2}/r_{\rmn{c}}^{2}\right)^{3 \beta}}\,
 \mathcal{B}\left(\frac{1}{2}, 3\beta\right)
-  = j_{\nu,0} \left(1 + r^2/r_\rmn{c}^2\right)^{-3 \beta},
+= j_{\nu,0} \left(1 + r^2/r_{\rmn{c}}^{2}\right)^{-3 \beta},
 \end{equation}
-where $\mathcal{B}$ denotes the beta function. Using ``isobaric CR model'' of
-the formalism suggested by \citet{article:PfrommerEnsslin:2004b} to compute the secondary
-radio emission and imposing the boundary condition to reproduce the observed
-radio emission profile uniquely determines $X_\CR(r)$. One of those realizations
-for the relative CR energy density $\tilde{X}_\CR(r) = \eps_\CR (r) /
-\eps_\rmn{th} (r)$ and $\tilde{X}_B(r) = \eps_B (r) / \eps_\rmn{th} (r)$ is
-shown in Figure 2 (lower left panel) of \citet{article:PfrommerEnsslin:2004a} which also
-has the interesting property to represent the minimum energy configuration that
-is able to reproduce the radio emission in the hadronic model.\footnote{Note
-  that a central magnetic field of $3\,\mu$G corresponds in the Coma cluster to
-  a relative magnetic energy density of $\tilde{X}_B=0.005$. For a CR population
-  in clusters that have been accelerated in structure formation shocks the
-  relativistic limit $E_\CR/E_\rmn{th} = 2 \bra P_\CR \ket / \bra P_\rmn{th}
-  \ket$ is not applicable since the CR pressure is dominated by the
-  trans-relativistic regime. This implies a somewhat harder equation of state
-  for the CRs with a larger adiabatic index and yields the relation
-  $E_\CR/E_\rmn{th} = 1.6 \bra P_\CR \ket / \bra P_\rmn{th} \ket$.}  The shaded
-regions indicate the logarithmic curvature at the minimum, showing that only
-modest additional energy investment would be needed to move the system by a
-factor two away from this energetically least expensive state which needs not to
-be realized in Nature.  The realization of the minimum energy magnetic field
-corresponds to a magnetic decline of $\alpha_B\simeq0.3$ and is close to
-equipartition with the CR proton pressure (but not that of the resulting
-secondary CR electrons).  It is generically true for weak magnetic fields
-($B<B_\rmn{CMB}$) in the outer parts of the Coma halo that the product
-$X_\CR(r)X_B(r)$ has to increase by a factor of about 100 toward the radio halo
-periphery to account for the observed extent.  If we were to adopt a steeper
-magnetic decline such as $\alpha_B=0.5$ which produces a flat $X_B(r)$, the
-relative CR pressure would have to rise accordingly by a factor of 100.
+where $\mathcal{B}$ denotes the beta function.
+Using ``isobaric CR model'' to compute the secondary radio emission profile uniquely determines $X_\CR(r)$.
+It is generically true for weak magnetic fields ($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$ has to increase by a factor of about 100 toward the radio halo periphery to account for the observed extent.
+If we were to adopt a steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative CR pressure would have to rise accordingly by a factor of 100.
 
-2) Given this realization for $X_\CR$, we compute the pion decay gamma-ray
-surface brightness profile, integrate the flux within a radius of $\{0.13, 0.2,
-0.4\}$ degree, and scale the CR profile in order to match the corresponding
-VERITAS upper limits.  This scaling factor, $X_{\CR,0}$, depends on the CR
-spectral index, $\alpha$, (assuming a power-law CR population for simplicity) and
-the radial decline of the magnetic field, $\alpha_B$.
+\item Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness profile, integrate the flux within a radius of $\{0.13, 0.2, 0.4\}$ degree, and scale the CR profile in order to match the corresponding VERITAS upper limits.
+This scaling factor, $X_{\CR,0}$, depends on the CR spectral index, $\alpha$, (assuming a power-law CR population for simplicity) and the radial decline of the magnetic field, $\alpha_{B}$.
 
-3) In the last step, we scale the secondary radio emission profile linearly
-with $X_{\CR,0}$ and solve for $B_0$ subject to the boundary condition to match
-the observed synchrotron profile. Note that for $B_0 \gg B_\rmn{CMB}$ and radio
-spectral index, $\alpha_\nu$, the solution would be degenerate according to
-Eqn.~(\ref{eq:Lnu}).
+\item In the last step, we scale the secondary radio emission profile linearly with $X_{\CR,0}$ and solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile.
+Note that for $B_{0} \gg B_{\rmn{CMB}}$ and radio spectral index, $\alpha_{\nu}$, the solution would be degenerate according to Eqn.
+(\ref{eq:Lnu}).
+\end{enumerate}
 

### 2011-07-21 ms.tex
Updated with Martin's edits

@@
 \label{sec:B}
-We have seen in the previous Section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B>B_\rmn{CMB}$.
+We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B>B_\rmn{CMB}$.
 Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assumes the validity of the hadronic model.
@@
 \item In the last step, we scale the secondary radio emission profile linearly with $X_{\CR,0}$ and solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile.
-Note that for $B_{0} \gg B_{\rmn{CMB}}$ and radio spectral index, $\alpha_{\nu}$, the solution would be degenerate according to Eqn.
-(\ref{eq:Lnu}).
+Note that for $B_{0} \gg B_{\rmn{CMB}}$ and radio spectral index, $\alpha_{\nu}$, the solution would be degenerate.
+% according to Eqn. (\ref{eq:Lnu}). 
 \end{enumerate}
 
-Table~\ref{table:Bmin} shows the results on the lower limit of the central
-magnetic field that range from $B_0 = 0.4$ to $1.2\,\mu$G. There are a few
-interesting remarks in order.  (1) The hardest CR spectral indices are most
-constraining because of the tightest upper limits.  (2) For a steeper magnetic decline
-(larger $\alpha_B$), the CR number density needs to be larger to match the
-observed radio emission profiles which would yield a higher gamma-ray flux so
-that the upper limits are more constraining. This implies tighter lower limits for $B_0$.
-However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing
-magnetic field, is possibly too steep in the outer parts as it neglects the
-contributions from the turbulent dynamo in these dynamically active regions with
-large amounts of vorticity injection at corrugated structure formation shocks
-\citep[as observationally inferred for the first time
-by][]{article:PfrommerJones:2011}.  (3) Interestingly, in all cases, we use the
-0.4$^\circ$ limit that is always most constraining for our choice of magnetic
-field configurations.  This is because we need a substantially increasing
-relative CR pressure profile to match the observed radio profiles (for a given
-magnetic realization); hence that CR realization produces a larger flux within
-0.4$^\circ$ in comparison to the ``isobaric CR model'' assumption ($X_\CR =
-\rmn{const.}$) for which the 0.2$^\circ$ upper limits are more constraining;
-hence the constraints on $B_0$ get better for the larger integration area.
-Physically, this can be achieved by considering (active) CR transport such as CR
-streaming which produces an increasing $X_\CR$-profile due to the larger
-available phase space in the outer cluster regions (or equivalently an
-incomplete turbulent pumping of CRs into the central regions).  Required
-streaming and turbulent pumping timescales match what is required to explain the
-observed radio halo bimodality when carefully considering the plasma physics in
-high-beta plasmas \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}.
+Table~\ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range from $B_{0} = 0.4$ to $1.2\,\mu$G.
+There are a few interesting remarks in order.
+(1) The hardest CR spectral indices are most constraining because of the tightest upper limits.
+(2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining.
+This implies tighter lower limits for $B_{0}$.
+However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions.
+(3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic field configurations.
+This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the constraints on $B_{0}$ get better for the larger integration area.
+Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.
 
-As a final word, we note that the $X_\CR$-profiles always obey the energy
-condition, i.e., $P_\CR < P_\mathrm{th}$ over the entire range of the radio halo
-emission ($< 1$~Mpc) when assuming a central magnetic field of $B_0=3\,\mu$G
-that is at the lower 2-$\sigma$ interval bound inferred from Faraday RM
-\citep{article:Bonafede_etal:2010}. Typical values at 1 Mpc range from $X_\CR = 0.02$
-($\alpha_B=0.3$, $\alpha=2.1$) to $X_\CR = 1$ ($\alpha_B=0.7$,
-$\alpha=2.5$).\footnote{See Figure 3 in \citet{article:PfrommerEnsslin:2004a} for the
-  entire parameter range assuming minimum energy conditions and
-  \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in this
-  study.} We caution, however, that the minimum energy condition is violated at
-the outer radio halo boundary for the range of minimum magnetic field values
-inferred by this study.
+As a final word, we note that the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo emission ($< 1$ Mpc) when assuming a central magnetic field of $B_{0}=3\,\mu$G that is at the lower 2-$\sigma$ interval bound inferred from Faraday RM
+\citep{article:Bonafede_etal:2010}. Typical values at 1 Mpc range from $X_{\CR} = 0.02$
+($\alpha_{B}=0.3$, $\alpha=2.1$) to $X_{\CR} = 1$ ($\alpha_{B}=0.7$,
+$\alpha=2.5$).\footnote{See Figure 3 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in this study.} We caution, however, that the minimum-energy condition is violated at the outer radio halo boundary for the range of minimum magnetic-field values inferred by this study.
 
@@
 
-Various approaches to model CR population and magnetic field distribution are
-complementary (so far just ideas, need to be formulated):
+Various approaches to model CR population and magnetic field distribution are complementary (so far just ideas, need to be formulated):
 \begin{itemize}
-\item simplified ``isobaric CR model'': simple and widely used in the
-  literature. A priori, physically not justified, old fashioned, should be
-  replaced by the approached below.
-\item simulation-based analytical approach: ``first principle approach'' that
-  predicts the CR and B distribution for a given set of assumptions. Powerful
-  since it only required the density profile as input, but limited in the
-  modeled physics (no active CR transport) that appears to be necessary to
-  explain the radio halo bimodality.
-\item pragmatic approach as employed in Sect.~\ref{sec:B}: model CR and B to
-  reproduce observed radio emission profile. Minimum energy conditions (or
-  equivalently equipartition arguments) represent a special case within this
-  approach. A priori, also physically not justified, but quite powerful as it
-  shows what the ``correct'' model has to achieve and can point into the
-  direction what the relevant physics has to deliever. Compare CR transport
-  vs. simulation inspired models
+\item simplified ``isobaric CR model'': simple and widely used in the literature. A priori, physically not justified, old fashioned, should be replaced by the approached below.
+\item simulation-based analytical approach: ``first principle approach'' that predicts the CR and B distribution for a given set of assumptions.
+Powerful since it only required the density profile as input, but limited in the modeled physics (no active CR transport) that appears to be necessary to explain the radio halo bimodality.
+\item pragmatic approach as employed in \S \ref{sec:B}: model CR and B to reproduce observed radio emission profile.
+Minimum energy conditions (or equivalently equipartition arguments) represent a special case within this approach.
+A priori, also physically not justified, but quite powerful as it shows what the ``correct'' model has to achieve and can point into the direction what the relevant physics has to deliever.
+Compare CR transport vs.
+simulation inspired models
 \end{itemize}

### 2011-07-22 ms.tex
Minor changes
Finished the Fermi-LAT result table; minor tweaks

@@
 %%\documentclass[twocolumn]{emulateapj}
-
-\usepackage{lscape}
 
@@
 
-\section{Dark Matter}
+\section{Emission from Dark Matter Annihilations}
 
@@
 \colhead{RA} &
-\colhead{Dec}}
+\colhead{Dec}
+}
 \startdata
@@
 
-\begin{landscape}
 \begin{deluxetable}{lccccccccc}
@@
 \tablecaption{Flux upper limits for different regions of interest in the Coma cluster of galaxies and surroundings.}
+\rotate
 \tablehead{
@@
 \multicolumn{2}{c}{$\alpha=2.3$} &
-\multicolumn{2}{c}{$\alpha=2.5$}}
+\multicolumn{2}{c}{$\alpha=2.5$}
+}
 \startdata
@@
 \end{deluxetable}
-\end{landscape}
 
-\begin{landscape}
 \begin{deluxetable}{cccccccccccc}
@@
 \tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions.} 
+\rotate
+\tabletypesize{\small}
 \tablehead{
@@
 \tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}. }
-\tablenotetext{c}{Integrated gamma-ray flux $F(>E=220~\mathrm{GeV}$) in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$ in the simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
-\tablenotetext{c}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$ that was assumed to be constant throught the cluster; calculated according to \citet{article:PfrommerEnsslin:2004b}.}
-\tablenotetext{e}{Minimum gamma-ray flux $F_{\rmn{min}}(>E=220~\mathrm{GeV}$) in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
-\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ for energies above $E=220~\rmn{GeV}$ of the hadronic model described in the text.}
+\tablenotetext{c}{Integrated gamma-ray flux above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$; simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
+\tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
+\tablenotetext{e}{Minimum gamma-ray flux in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
+\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$, for energies $E>220~\rmn{GeV}$ in the hadronic model described in the text.}
 \label{table:constraints}
 \end{deluxetable}
-\end{landscape}
 
@@
 \multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
-\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}}
+\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+}
 \startdata
@@
 \tablehead{
-\colhead{Spatial model} & \multicolumn{6}{c}{Flux U.L.}
+\colhead{Spatial model} & \multicolumn{3}{c}{S[$\sigma$]} & \multicolumn{3}{c}{Flux U.L.} \\
+\colhead{} & \colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} & 
+\colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} \\
+\hline
+\multicolumn{7}{c}{Spectral index $\alpha=2.1$ (fixed)}
 }
 \startdata
-Point source & 1.73 & 1.81 & 0.487 & 0.526 & 0.627 & 0.635
+Point source & 0.30 & 0 & 1.3 & 1.73 & 4.87 & 0.627 \\
+Disk, $r=0.2^{\circ}$ & 0.65 & 0.22 & 2.0 & 2.03 & 0.691 & 0.783 \\
+Disk, $r=0.4^{\circ}$ & 0.77 & 0.18 & 2.3 & 2.39 & 0.757 & 0.847 \\
+\cutinhead{Spectral index $\alpha=2.5$ (fixed)}
+Point source & 0.33 & 0 & 1.42 & 1.81 & 0.526 & 0.635 \\
+Disk, $r=0.2^{\circ}$ & 0.66 & 0.35 & 2.1 & 2.12 & 0.748 & 0.785 \\
+Disk, $r=0.4^{\circ}$ & 0.80 & 0.36 & 2.4 & 2.50 & 0.833 & 0.849 \\
 \enddata

### 2011-07-25 ms.tex
Some minor changes to text

@@
 
+\paragraph{rewrite this}
 Depending on the CR energy density, quantified by the fraction of energy in CRs to the thermal energy in a cluster, $\eta=\expval{ E_{\mathrm{CR}}/E_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.
@@
 
-A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a dark matter particle, e.g. a weakly interacting massive particle (WIMP).
+A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a dark matter particle, e.g.
+a weakly interacting massive particle (WIMP).
+This is particularly compelling because of the large amount of dark matter in a galaxy cluster.
 
@@
 Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful.
-The 99\% confidence level flux upper limits in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission are tabulated in Table \ref{table:fermi}.
+The 95\% confidence level flux upper limits in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission are tabulated in Table \ref{table:fermi}.
 The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$ and $2.5$.
@@
 \section{Gamma Ray Emission from Cosmic Rays}
-We decided to adopt a multifaceted approach to constrain the CR-to-thermal pressure distribution in Coma with these upper limits.
-That includes (1) an analytic model derived from cosmological hydrodynamical simulations of the formation of galaxy clusters, (2) a simplified multi-frequency analytical approach that assumes a constant CR-to-thermal energy density and a power-law spectrum in momentum, and (3) an approach that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray flux in the hadronic model -- independent of the magnetic field distribution.
+We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution in the Coma cluster with the VERITAS and \emph{Fermi}-LAT upper limits from this work.
+This approach includes (1) an analytic model derived from cosmological hydrodynamical simulations of the formation of galaxy clusters, (2) a simplified multi-frequency analytical approach that assumes a constant CR-to-thermal energy density and a power-law spectrum in momentum, and (3) an approach that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray flux in the hadronic model -- independent of the magnetic field distribution.
 This translates into a minimum CR pressure which, if challenged by tight gamma-ray limits/detections, enables scrutinizing the hadronic interaction model of the formation of giant radio halos.
@@
 We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster galaxies.
-Figure ??
-shows the expected spectrum of Coma, normalized to the total flux within the virial radius.
+Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius.
 [Add {\em Fermi} results]
@@
 For the most constraining regions tested (within an aperture of radius 0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits (see Table \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at energies $E=200$ GeV).
-Hence we scale the averaged relative CR pressure, $X_{\CR}$
+Hence we scale the averaged relative CR pressure %$X_{\CR}$
 % = \bra P_\CR \ket /\bra P_\rmn{th} \ket$ 

### 2011-07-25 ms.tex
Some minor changes to text

@@
 
-A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a dark matter particle, e.g.
-a weakly interacting massive particle (WIMP).
-This is particularly compelling because of the large amount of dark matter in a galaxy cluster.
+A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a dark matter particle, e.g. a weakly interacting massive particle (WIMP). 
+%This is particularly compelling because of the large amount of dark matter in a galaxy cluster.
 
@@
 Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful.
-The 95\% confidence level flux upper limits in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission are tabulated in Table \ref{table:fermi}.
+The \emph{Fermi}-LAT collaboration estimates the systematic uncertainties at 10 GeV to be around 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits at the 95\% confidence level in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}.
 The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$ and $2.5$.

### 2011-07-25 ms.tex
Some changes to DM paragraph in section 1. Other minor tweaks

@@
 The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields in the cluster.
-The relative cosmic-ray pressure $X_{\mathrm{CR}}$ is.
-The observations imply a lower limit on the intra-cluster magnetic field of X$\mu$G.
-Finally, a constraint on the dark matter annihilation cross section is derived, $\expval{\sigma v}=$.
+The relative cosmic-ray pressure $X_{\mathrm{CR}}$ is less than\ldots.
+The observations imply a lower limit on the intra-cluster magnetic field on the order of a $\mu$G depending on the magnetic decline and gamma-ray spectral index.
+Finally, a constraint on the thermally averaged product of the total self-annihilation cross section and the relative velocity of the dark-matter particles is derived, $\expval{\sigma v}\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}>X$ GeV/c$^{2}$.
 \end{abstract}
@@
 These gravitationally bound objects have formed on increasingly larger scales during the evolution of the Universe through the process of cosmic structure formation \citep{article:Voit:2005}.
-Although most of the cluster mass comes from large amounts of dark matter embedded in a cluster, as indicated by cluster dynamics and weak gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}, gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass.
+Although most of the cluster mass comes from large amounts of dark matter (DM) embedded in a cluster, as indicated by cluster dynamics and weak gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}, gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass.
 Individual galaxies contribute only a small amount (about 5\%) to the cluster mass.
@@
 
-\paragraph{rewrite this}
+\paragraph{Rewrite this paragraph!}
 Depending on the CR energy density, quantified by the fraction of energy in CRs to the thermal energy in a cluster, $\eta=\expval{ E_{\mathrm{CR}}/E_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.
@@
 
-A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a dark matter particle, e.g. a weakly interacting massive particle (WIMP). 
-%This is particularly compelling because of the large amount of dark matter in a galaxy cluster.
+A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM particle, e.g.
+a weakly interacting massive particle (WIMP).
+As already mentioned, about 80\% of the cluster mass is in the form of dark matter.
+Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the DM density along the line of sight, making clusters of galaxies potentially good candidates for DM searches.
 
@@
 As such it is a natural candidate for gamma-ray observations.
-In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
+
+In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, 
+together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
 Throughout the analysis, a present day Hubble constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
@@
 The sensitivity of the array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009.
-The move had no impact on the Coma cluster data set.}
+The move had no impact on the this data set.}
 
@@
 \tablehead{
-\colhead{Spatial model} & \multicolumn{3}{c}{S[$\sigma$]} & \multicolumn{3}{c}{Flux U.L.} \\
+\colhead{Spatial model} & \multicolumn{3}{c}{S[$\sigma$]\tablenotemark{a}} & \multicolumn{3}{c}{Flux U.L.\tablenotemark{b}} \\
 \colhead{} & \colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} & 
@@
 \enddata
+\tablenotetext{a}{Statistical significance.}
+\tablenotetext{b}{95\% confidence level upper limit in units of $10^{-10}$ ph. cm$^{-2}$ s$^{-1}$.}
 \label{table:fermi}
@@
 
+%\begin{deluxetable}{lccc}
+%\tablecolumns{4}
+%\tablewidth{0pc}
+%\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$.}
+%\tablehead{
+%\colhead{Channel} & RoI [deg] & $m_{\chi}$ [GeV] & $\expval{\sigma v}$ [cm$^{3}$ s$^{-1}$] \\
+%}
+%\startdata
+%W$^{+}$W$^{-}$ & & & \\
+%$b\bar{b}$ & & & \\
+%$\tau^{+}\tau^{-}$ & & & \\
+%\enddata
+%\tablecomments{Limits are for different integration regions and DM particle mass $m_{\chi}$ derived from %the VERITAS gamma-ray flux upper limits presented in this work.}
+%\end{deluxetable}
+
 \end{document}

### 2011-07-28 ms.tex
Added two tables for the DM results: astrophysical factors and <sigma v> limits

@@
 As already mentioned, about 80\% of the cluster mass is in the form of dark matter.
-Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the DM density along the line of sight, making clusters of galaxies potentially good candidates for DM searches.
+Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the DM density along the line of sight, making clusters of galaxies potentially good candidates for DM searches, despite their large distances.
 
@@
 \tablewidth{0pc}
-\tablecaption{Regions of interest in the Coma cluster field of view.}
+\tablecaption{Regions of interest in the Coma cluster field of view}
 \tablehead{
@@
 \tablewidth{0pc}
-\tablecaption{Flux upper limits for different regions of interest in the Coma cluster of galaxies and surroundings.}
+\tablecaption{VERITAS flux upper limits for different regions of interest in the Coma cluster of galaxies and surroundings}
 \rotate
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions.} 
-\rotate
+\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions} \rotate
 \tabletypesize{\small}
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma cluster.}
+\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma cluster}
 \tablehead{
@@
 \tablewidth{0pc}
-\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core.}
+\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core}
 \tablehead{
@@
 
-%\begin{deluxetable}{lccc}
-%\tablecolumns{4}
-%\tablewidth{0pc}
-%\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$.}
-%\tablehead{
-%\colhead{Channel} & RoI [deg] & $m_{\chi}$ [GeV] & $\expval{\sigma v}$ [cm$^{3}$ s$^{-1}$] \\
-%}
-%\startdata
-%W$^{+}$W$^{-}$ & & & \\
-%$b\bar{b}$ & & & \\
-%$\tau^{+}\tau^{-}$ & & & \\
-%\enddata
-%\tablecomments{Limits are for different integration regions and DM particle mass $m_{\chi}$ derived from %the VERITAS gamma-ray flux upper limits presented in this work.}
-%\end{deluxetable}
+\begin{deluxetable}{ccc}
+\tablecolumns{3}
+\tablewidth{0pc}
+\tablecaption{Astrophysical factors}
+\tablehead{
+\colhead{RoI [deg]} & $\expval{J}_{\rmn{signal}}$ [GeV$^{2}$ cm$^{-5}$ sr] & $\alpha\expval{J}_{\rmn{bkg}}$ [GeV$^{2}$ cm$^{-5}$ sr]
+}
+\startdata
+0 & $5.7\times 10^{16}$ & $1.3\times 10^{14}$ (negligible) \\
+0.2 & $8.1\times 10^{16}$ & $4.4\times 10^{14}$ ($<0.01\expval{J}_{\rmn{signal}}$, negligible) \\
+0.4 & $9.4\times 10^{16}$ & $1.3\times 10^{15}$ ($\simeq0.01\expval{J}_{\rmn{signal}}$, negligible)
+\enddata
+\tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background region (ring method) and is used to estimate the level of gamma-ray contamination from DM.}
+\end{deluxetable}
+
+\begin{deluxetable}{lccc}
+\tablecolumns{4}
+\tablewidth{0pc}
+\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$.}
+\tablehead{
+\colhead{Channel} & RoI [deg] & $m_{\chi}$ [GeV] & $\expval{\sigma v}$ [cm$^{3}$ s$^{-1}$]
+}
+\startdata
+W$^{+}$W$^{-}$ & 0 & 2000 & $1.1\times 10^{-20}$ \\
+& 0.2 & 1900 & $4.3\times 10^{-21}$ \\
+& 0.4 & 1900 & $8.4\times 10^{-21}$ \\
+$b\bar{b}$ & 0 & 3500 & $1.2\times 10^{-20}$ \\
+& 0.2 & 3400 & $4.4\times 10^{-21}$ \\
+& 0.4 & 3500 & $8.7\times 10^{-21}$ \\
+$\tau^{+}\tau^{-}$ & 0 & 670 & $2.4\times 10^{-21}$ \\
+& 0.2 & 650 & $9.1\times 10^{-22}$ \\
+& 0.4 & 660 & $1.8\times 10^{-21}$ \\
+\enddata
+\tablecomments{Limits are for different integration regions and DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
+\end{deluxetable}
 

### 2011-07-28 ms.tex
More DM related text

@@
 The flux upper limits at the 99\% confidence level measured are on the order of $2-5\times 10^{-8}$ ph.
-m$^{-2}$ s$^{-1}$, which is X times higher than the model-predicted minimum gamma-ray flux.
+m$^{-2}$ s$^{-1}$, which is two orders of magnitude higher than model-predicted minimum gamma-ray fluxes.
 
-The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields in the cluster.
-The relative cosmic-ray pressure $X_{\mathrm{CR}}$ is less than\ldots.
-The observations imply a lower limit on the intra-cluster magnetic field on the order of a $\mu$G depending on the magnetic decline and gamma-ray spectral index.
-Finally, a constraint on the thermally averaged product of the total self-annihilation cross section and the relative velocity of the dark-matter particles is derived, $\expval{\sigma v}\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}>X$ GeV/c$^{2}$.
+The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields and in the Coma cluster of galaxies.
+The relative cosmic-ray pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$, is \ldots.
+The observations imply a lower limit on the intra-cluster magnetic field on the order of a $\mu$G, depending on the magnetic decline and gamma-ray spectral index.
+Finally, a constraint on the thermally averaged product of the total self-annihilation cross section and the relative velocity of the dark-matter particles, $\expval{\sigma v}$, is derived and found to be $\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
 \end{abstract}
@@
 As already mentioned, about 80\% of the cluster mass is in the form of dark matter.
-Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the DM density along the line of sight, making clusters of galaxies potentially good candidates for DM searches, despite their large distances.
+Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the DM density along the line of sight, making clusters of galaxies potentially good candidates for DM searches.
+This despite their large distances compared to other common targets for DM searches, such as dwarf spheriodal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010, article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006, article:Aharonian_etal:2009b}.
 
@@
 Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several galaxy clusters in the MeV to GeV band.
-Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009, article:Aleksic_etal:2010}.
+Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
 
@@
 \section{Emission from Dark Matter Annihilations}
+When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated background.
+For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor no longer compensate for the increased count of background events and the signal-to-noise deteriorates.
 

### 2011-08-08 ms.tex
More DM edits
Fermi analysis for XCR and B limits added

@@
 \documentclass[12pt,manuscript]{aastex}
-%%\documentclass[twocolumn]{emulateapj}
+%\documentclass[twocolumn]{emulateapj}
 
@@
 \startdata
+\multicolumn{12}{l}{VERITAS constraints:}\\
 0    & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
 0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
-0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16
+0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
+\hline
+\multicolumn{12}{l}{{\em Fermi} constraints:}\\
+0    & -  & -  & 3.2 & - & 3.0 & ~~3.5 & - & ~~6.4 & 0.067 & 0.061 & 0.11 \\
+0.2  & -  & -  & 2.3 & - & 2.1 & ~~6.8 & - &  12.5 & 0.078 & 0.072 & 0.13 \\
+0.4  & -  & -  & 1.7 & - & 1.5 &  13.5 & - &  25.0 & 0.098 & 0.090 & 0.16 \\
 \enddata
@@
 \tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
-\tablenotetext{e}{Minimum gamma-ray flux in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
-\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$, for energies $E>220~\rmn{GeV}$ in the hadronic model described in the text.}
+\tablenotetext{e}{Minimum gamma-ray flux of the hadronic model described in the
+  text. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS) and
+  $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ {\em (Fermi)}.}
+\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ in the hadronic model described in the text.}
 \label{table:constraints}
@@
 
-\begin{deluxetable}{cccc}
+\begin{deluxetable}{ccccccc}
 \tablecolumns{4}
 \tablewidth{0pc}
-\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma cluster}
+\tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo}
 \tablehead{
-\colhead{$\alpha_{B}$} &
-\multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
-\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+ &
+\multicolumn{6}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
+ & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{{\em Fermi} constraints:} \\
+\colhead{$\alpha_{B}$}
+ & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+ & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
 }
 \startdata
-0.3 & 0.61 & 0.51 & 0.43 \\
-0.5 & 0.82 & 0.68 & 0.58 \\
-0.7 & 1.19 & 0.98 & 0.83 
+0.3 & 0.61 & 0.51 & 0.43 & 1.26 & - & ~~2.69 \\
+0.5 & 0.82 & 0.68 & 0.58 & 1.75 & - & ~~4.44 \\
+0.7 & 1.19 & 0.98 & 0.83 & 2.75 & - &  14.6~ 
 \enddata
@@
 \tablewidth{0pc}
-\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$.}
+\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$}
 \tablehead{

### 2011-08-30 ms.tex
Moved Fermi results table to come before constraints
Fermi analysis redone with 99% CL, text accordingly added in the main part and conclusions

@@
 Galaxy clusters have for many years been proposed as sources of gamma rays.
-If shock acceleration in the ICM is an efficent process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected.
+If shock acceleration in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected.
 The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM.
@@
 
-The Coma cluster of galaxies (ACO 1656) is one of the most thouroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}.
+The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}.
 Located at a distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest and also one of the most massive clusters \citep[$M \sim 10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}.
 It hosts both a giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
-It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and succesively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
+It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
 Extended soft X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo.
@@
 
-Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters \citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images \citep{inproc:Hillas:1985}.
+Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters \citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parametrized moment analysis of the shower images \citep{inproc:Hillas:1985}.
 The gamma-hadron separation cuts used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level) and a photon index of -2.4 using data taken on the Crab Nebula during the same epoch and are termed \emph{standard} cuts.
@@
 
-There cosmological simulations only considered advective transport of CRs by turbulent gas motions which produces centrally enhanced profiles.
+These cosmological simulations only considered advective transport of CRs by turbulent gas motions which produces centrally enhanced profiles.
 However, other means of CR transport such as diffusion and streaming may flatten the CR radial profiles.
@@
 Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius.
-[Add {\em Fermi} results]
+In our further analysis, we use the gamma-ray flux limits of {\em Fermi} in the energy interval of 1-3 GeV which are most constraining.
 
@@
 Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest.
-For the most constraining regions tested (within an aperture of radius 0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits (see Table \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at energies $E=200$ GeV).
-Hence we scale the averaged relative CR pressure %$X_{\CR}$
-% = \bra P_\CR \ket /\bra P_\rmn{th} \ket$ 
-of our model by that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of $X_{\CR}<0.091$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of $X_\CR<0.13$ (solid lines of Figure \ref{fig:xcr}).
+For the most constraining regions tested (within an aperture of radius 0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at energies $E=200$ GeV).
+Hence we scale the averaged relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of $X_{\CR}<0.091$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of $X_\CR<0.13$ (solid lines of Figure \ref{fig:xcr}).
+
+[Anders: add and discuss Fermi limits on XCR]
 
 \subsection{Simplified analytical model}
-To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}.
-Since a priori, the CR spectral index is unconstrained, we vary it within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$.
-This spectral range is compatible with the radio spectral index of the giant radio halo of Coma after accounting for the spectral
-steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.
-Table \ref{table:constraints} shows the resulting constraints on $X_\CR$ which range between 0.05 and 1, strongly
-depending on the assumed spectral index.
-
-[Add {\em Fermi} results, critical spectral index]
+To complement the simulation-inspired analysis and to facilitate comparison with
+earlier analytical work, we repeat the data analysis with a simplified
+analytical model that assumes a power-law CR spectrum and a constant relative CR
+pressure, i.e., we adopt the {\em isobaric model of CRs}. Since a priori, the CR
+spectral index is unconstrained, we vary it within plausible ranges of
+$2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the radio
+spectral index of the giant radio halo of Coma after accounting for the spectral
+steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich
+effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field
+  of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons
+  have an energy of $\sim100$ GeV and are $\sim$ 20 times less energetic than
+  those CR protons responsible for 200-GeV gamma-ray emission.}. Table
+\ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS
+flux upper limits strongly depend on $\alpha$ due to the comparably large lever
+arm from GeV energies (that dominate the CR pressure) to TeV-energies. The
+limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$
+between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5). The {\em
+  Fermi} limits depend only weakly on $\alpha$ and are most constraining for an
+aperture of 0.4$^{\circ}$.  The best limit on $X_\CR$ of 0.017 is achieved for
+$\alpha=2.3$.
 
@@
 For clusters that host radio halos we are able to derive a minimum gamma-ray flux in the hadronic model of CR interactions.
-The idea is based on the fact that a stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and thermal gas \citep{article:Voelk:1989, article:Pohl:1994}, in particular with $\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.
+The idea is based on the fact that a stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and thermal gas \citep{article:Voelk:1989, article:Pohl:1994, article:Pfrommer:2008}, in particular with $\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.
 Hence we can derive a minimum gamma-ray flux in the hadronic
@@
 \end{equation}
-where $L_{\nu}$ is the observed luminosity of the radio mini-halo and $D_{\rmn{lum}}$ denotes the luminosity distance to the respective cluster.
-Lowering the magnetic field would require an increase in the energy density of CR electrons to reproduce the observed synchrotron luminosity and thus increase the associated gamma-ray flux.
+where $L_{\nu}$ is the observed luminosity of the radio mini-halo,
+$D_{\rmn{lum}}$ denotes the luminosity distance to the respective cluster,
+$A_\gamma$ and $A_\nu$ are dimensional constants that depend on the hadronic
+physics of the interaction \citep{2008MNRAS.385.1211P,
+  2008MNRAS.385.1242P}. Lowering the magnetic field would require an increase in
+the energy density of CR electrons to reproduce the observed synchrotron
+luminosity and thus increase the associated gamma-ray flux.
 
-To derive a minimum gamma-ray flux that is comparable to the upper limits, we need to determined the radio flux within the corresponding angular regions.
+To derive a minimum gamma-ray flux that is comparable to the upper limits, we need to determine the radio flux within the corresponding angular regions.
 To this end, we fit the point-source subtracted, azimuthally averaged radio halo profile at 1.38 GHz \citep{article:Deiss_etal:1997} with a $\beta$-model,
@@
 
-The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV}$ and the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ are shown in Table \ref{table:constraints}.
-Even in the most constraining case ($\alpha=2.1$, $<0.2^{\circ}$), these are a factor of about 60 below the upper limits obtained in this work.
-
-[Add {\em Fermi} results]
+The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV})$ and the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ are shown in Table \ref{table:constraints}.
+Even in the most constraining cases, these are a factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$, $<0.2^{\circ}$) and a factor of about 20 below the {\em Fermi} upper limits (adopting $\alpha=2.3$, $<0.4^{\circ}$).
 
@@
 We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B>B_\rmn{CMB}$.
-Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assumes the validity of the hadronic model.
+Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assuming the validity of the hadronic model \cite{article:PfrommerEnsslin:2004a}.
 Lowering the gamma-ray constraint will tighten (increase) the magnetic field limit.
@@
 \begin{enumerate}
-\item Given a model for the magnetic field, we determine the profile of the relative CR pressure, $X_{\CR}$, so that the hadronically produced CR electrons exactly matches the observed radio halo emission over the entire extent.
+\item Given a model for the magnetic field, we determine the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced CR electrons exactly matches the observed radio halo emission over the entire extent.
 To this end, we de-project the fit to the surface brightness profile (using an Abel integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio emissivity,
@@
 where $\mathcal{B}$ denotes the beta function.
-Using ``isobaric CR model'' to compute the secondary radio emission profile uniquely determines $X_\CR(r)$.
 It is generically true for weak magnetic fields ($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$ has to increase by a factor of about 100 toward the radio halo periphery to account for the observed extent.
@@
 
-\item Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness profile, integrate the flux within a radius of $\{0.13, 0.2, 0.4\}$ degree, and scale the CR profile in order to match the corresponding VERITAS upper limits.
+\item Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness profile, integrate the flux within a radius of $(0.13, 0.2, 0.4)$ degree, and scale the CR profile in order to match the corresponding VERITAS/{\em Fermi} upper limits.
 This scaling factor, $X_{\CR,0}$, depends on the CR spectral index, $\alpha$, (assuming a power-law CR population for simplicity) and the radial decline of the magnetic field, $\alpha_{B}$.
@@
 \item In the last step, we scale the secondary radio emission profile linearly with $X_{\CR,0}$ and solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile.
-Note that for $B_{0} \gg B_{\rmn{CMB}}$ and radio spectral index, $\alpha_{\nu}$, the solution would be degenerate.
-% according to Eqn. (\ref{eq:Lnu}). 
+Note that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution would be degenerate.
 \end{enumerate}
 
-Table~\ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range from $B_{0} = 0.4$ to $1.2\,\mu$G.
-There are a few interesting remarks in order.
-(1) The hardest CR spectral indices are most constraining because of the tightest upper limits.
-(2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining.
-This implies tighter lower limits for $B_{0}$.
-However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions.
-(3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic field configurations.
-This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the constraints on $B_{0}$ get better for the larger integration area.
-Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.
+Table~\ref{table:Bmin} shows the results on the lower limit of the central
+magnetic field that range for the VERITAS limits from $B_{0} = 0.4$ to
+$1.2\,\mu$G and for the {\em Fermi} limits from $B_{0} = 1$ to $7\,\mu$G. Since
+these lower limits on $B_0$ are for most of the parameter space spanned by
+$\alpha_B$ and $\alpha$ below the values favored by Faraday RM, the hadronic
+model is still viable. The only exception is the parameter combination of
+$alpha_B=0.7$ and $\alpha=2.5$ which starts to be in (weak) tension with Faraday
+RM data. This indicates the power of future gamma-ray observations of Coma in
+constraining parameters of the hadronic model.
 
-As a final word, we note that the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo emission ($< 1$ Mpc) when assuming a central magnetic field of $B_{0}=3\,\mu$G that is at the lower 2-$\sigma$ interval bound inferred from Faraday RM
-\citep{article:Bonafede_etal:2010}. Typical values at 1 Mpc range from $X_{\CR} = 0.02$
-($\alpha_{B}=0.3$, $\alpha=2.1$) to $X_{\CR} = 1$ ($\alpha_{B}=0.7$,
-$\alpha=2.5$).\footnote{See Figure 3 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in this study.} We caution, however, that the minimum-energy condition is violated at the outer radio halo boundary for the range of minimum magnetic-field values inferred by this study.
+In addition there are a few interesting remarks in order. (1) For the VERITAS
+limits, the hardest CR spectral indices are most constraining because of the
+tightest upper limits. The opposite is true for the {\em Fermi} upper limits
+which probe the region around the pion decay bump characterized by a shape
+parameter that depends inversely on the CR spectral index
+\cite{article:PfrommerEnsslin:2004b}.  (2) For a steeper magnetic decline
+(larger $\alpha_{B}$), the CR number density needs to be larger to match the
+observed radio emission profiles which would yield a higher gamma-ray flux so
+that the upper limits are more constraining. This implies tighter lower limits
+for $B_{0}$. However, the largest choice of $\alpha_B=0.7$, which represents a
+flux-freezing magnetic field, is possibly too steep in the outer parts as it
+neglects the contributions from turbulent dynamos in these dynamically active
+regions with vorticity injection at corrugated structure formation shocks
+\cite{article:PfrommerJones:2011}. (3) Interestingly, in all cases, we use the
+0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic
+field configurations.  This is because we need a substantially increasing
+relative CR pressure profile to match the observed radio profiles (for a given
+magnetic realization); hence that CR realization produces a larger flux within
+0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} =
+\rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining;
+hence the constraints on $B_{0}$ get better for the larger integration
+area. Physically, this may be achieved by considering CR transport processes
+such as streaming which produces an increasing $X_{\CR}$-profile due to the
+larger available phase space in the outer cluster regions.
+
+As a final word, we note that the $X_{\CR}$ profiles always obey the energy
+condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio
+halo emission ($< 1$ Mpc) when assuming a central magnetic field of
+$B_{0}=3\,\mu$G that is at the lower 2-$\sigma$ interval bound inferred from
+Faraday RM \citep{article:Bonafede_etal:2010}.\footnote{Note that a central
+  magnetic field of $3\,\mu$G corresponds in the Coma cluster to a relative
+  magnetic energy density of $\tilde{X}_B=0.005$.} Typical values at 1 Mpc range
+from $X_{\CR} = 0.02$ ($\alpha_{B}=0.3$, $\alpha=2.1$) to $X_{\CR} = 1$
+($\alpha_{B}=0.7$, $\alpha=2.5$).\footnote{See Figure 3 in
+  \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming
+  minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7
+  for a parametrization as adopted in this study.} We caution, however, that the
+minimum-energy condition is violated at the outer radio halo boundary for the
+range of minimum magnetic-field values inferred by this study.
 
@@
 
-\section{Discussion}
+\section{Discussion and Conclusions}
 VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
 
-Various approaches to model CR population and magnetic field distribution are complementary (so far just ideas, need to be formulated):
-\begin{itemize}
-\item simplified ``isobaric CR model'': simple and widely used in the literature. A priori, physically not justified, old fashioned, should be replaced by the approached below.
-\item simulation-based analytical approach: ``first principle approach'' that predicts the CR and B distribution for a given set of assumptions.
-Powerful since it only required the density profile as input, but limited in the modeled physics (no active CR transport) that appears to be necessary to explain the radio halo bimodality.
-\item pragmatic approach as employed in \S \ref{sec:B}: model CR and B to reproduce observed radio emission profile.
-Minimum energy conditions (or equivalently equipartition arguments) represent a special case within this approach.
-A priori, also physically not justified, but quite powerful as it shows what the ``correct'' model has to achieve and can point into the direction what the relevant physics has to deliever.
-Compare CR transport vs.
-simulation inspired models
-\end{itemize}
+We employed various approaches to constrain the CR population and magnetic field
+distribution that are complementary in their assumptions and hence well suited
+in assessing underlying Bayesian priors in the models. (1) We use a simplified
+``isobaric CR model'' that is characterized by a constant CR-to-thermal pressure
+fraction and has a power-law momentum spectrum.  While this model is physically
+not justified a priory, it is simple and widely used in the literature and
+captures some aspects of more elaborate models such as (2) the simulation-based
+analytical approach of \citet{article:PinzkePfrommer:2010}. This is a ``first
+principle approach'' that predicts the CR distribution for a given set of
+assumptions (namely the physics that was simulated). It is powerful since it
+only requires the density profile as input due to the approximate universality
+of the CR distribution (when neglecting CR diffusion and streaming which
+appears, however, necessary to explain the radio halo bimodality). (3) We
+finally use a pragmatic approach which models the CR and magnetic distribution
+such as to reproduce the observed emission profile of the Coma radio halo. While
+this approach is also physically not justified, it is powerful as it shows what
+the ``correct'' model has to achieve and can point into the direction of the
+relevant physics.
+
+Within this pragmatic approach we employ two different directions. First,
+adopting a high magnetic field everywhere in the cluster ($B\gg B_\rmn{CMB}$)
+yields the minimum gamma-ray flux in the hadronic model of radio halos which we
+find to be a factor of 20 (60) below the most constraining flux upper limits of
+{\em Fermi} (VERITAS). Second, by matching the radio emission profile
+(i.e. fixing the radial CR profile for a given magnetic field model) and by
+requiring the pion-decay gamma-ray flux to match the flux upper limits
+(i.e. fixing the normalization of the CR distribution) we obtain lower limits on
+the magnetic field distribution under consideration. Our limits of the central
+magnetic field range from $B_{0} = 0.4$ to $1.2\,\mu$G (for VERITAS limits) and
+from $B_{0} = 1$ to $7\,\mu$G (for {\em Fermi} limits). Since these lower limits
+on $B_0$ are below the values favored by Faraday RM, the hadronic model is still
+viable.
+
+Using the most constraining VERITAS limits, we can constrain the CR-to-thermal
+pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray spectral
+index, $\alpha$, varying between 2.1 and 2.5).  The best {\em Fermi} flux limit
+constrains $X_\CR$ to be below 0.017 (for $\alpha=2.3$), only weakly depending
+on the assumed CR spectral index.
 
@@
 We acknowledge the excellent work of the technical support staff at the FLWO and the collaborating institutions in the construction and operation of the instrument.
+C.P.
+gratefully acknowledges financial support of the Klaus Tschira Foundation.
 
@@
 
-\begin{deluxetable}{cccccccccccc}
-\tablecolumns{12}
+\begin{deluxetable}{lccc}
+\tablecolumns{4}
 \tablewidth{0pc}
-\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions} \rotate
-\tabletypesize{\small}
+\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core}
 \tablehead{
-\colhead{RoI\tablenotemark{a} [deg]} 
-    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
-    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
-    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
-    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
-& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
-    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
-    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+                      & $1-3$ GeV & $3-10$ GeV & $10-30$ GeV\\
+\small{Spatial Model} & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}} (\small{Significance})\\
+\hline
+\multicolumn{4}{c}{\small{Spectral index $\alpha=2.1$}}
 }
 \startdata
-\multicolumn{12}{l}{VERITAS constraints:}\\
-0    & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
-0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
-0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
-\hline
-\multicolumn{12}{l}{{\em Fermi} constraints:}\\
-0    & -  & -  & 3.2 & - & 3.0 & ~~3.5 & - & ~~6.4 & 0.067 & 0.061 & 0.11 \\
-0.2  & -  & -  & 2.3 & - & 2.1 & ~~6.8 & - &  12.5 & 0.078 & 0.072 & 0.13 \\
-0.4  & -  & -  & 1.7 & - & 1.5 &  13.5 & - &  25.0 & 0.098 & 0.090 & 0.16 \\
+\small{Point Source} & 2.745 (0.302) & 0.965 (0.000) & 1.002 (1.313)\\
+\small{Disk: r = 0.2$^\circ$} & 3.066 (0.648) & 1.193 (0.218) & 1.165 (2.031)\\
+\small{Disk: r = 0.4$^\circ$} & 3.515 (0.768) & 1.297 (0.177) & 1.234 (2.349)\\
+\cutinhead{\small{Spectral index $\alpha=2.3$}}
+\small{Point Source} & 2.803 (0.317) & 0.992 (0.000) & 1.006 (1.371)\\
+\small{Disk: r = 0.2$^\circ$} & 3.130 (0.654) & 1.227 (0.286) & 1.166 (2.072)\\
+\small{Disk: r = 0.4$^\circ$} & 3.586 (0.787) & 1.341 (0.273) & 1.236 (2.380)\\
+\cutinhead{\small{Spectral index $\alpha=2.5$}}
+\small{Point Source} & 2.854 (0.333) & 1.016 (0.000) & 1.009 (1.424)\\
+\small{Disk: r = 0.2$^\circ$} & 3.184 (0.658) & 1.259 (0.349) & 1.167 (2.112)\\
+\small{Disk: r = 0.4$^\circ$} & 3.647 (0.804) & 1.381 (0.362) & 1.237 (2.408)\\
 \enddata
-\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
-\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}. }
-\tablenotetext{c}{Integrated gamma-ray flux above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$; simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
-\tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
-\tablenotetext{e}{Minimum gamma-ray flux of the hadronic model described in the
-  text. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS) and
-  $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ {\em (Fermi)}.}
-\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ in the hadronic model described in the text.}
-\label{table:constraints}
+\tablenotetext{a}{99\% confidence level upper limit in units of $10^{-10}$ ph. cm$^{-2}$ s$^{-1}$.}
+\label{table:fermi}
 \end{deluxetable}
 
-\begin{deluxetable}{ccccccc}
-\tablecolumns{4}
-\tablewidth{0pc}
-\tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo}
-\tablehead{
- &
-\multicolumn{6}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
- & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{{\em Fermi} constraints:} \\
-\colhead{$\alpha_{B}$}
- & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
- & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
-}
-\startdata
-0.3 & 0.61 & 0.51 & 0.43 & 1.26 & - & ~~2.69 \\
-0.5 & 0.82 & 0.68 & 0.58 & 1.75 & - & ~~4.44 \\
-0.7 & 1.19 & 0.98 & 0.83 & 2.75 & - &  14.6~ 
-\enddata
-\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
-\label{table:Bmin}
-\end{deluxetable}
-
+\del{
 \begin{deluxetable}{lcccccc}
@@
 \label{table:fermi}
+\end{deluxetable}
+}
+
+\begin{deluxetable}{cccccccccccc}
+\tablecolumns{12}
+\tablewidth{0pc}
+\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions} \rotate
+\tabletypesize{\small}
+\tablehead{
+\colhead{RoI\tablenotemark{a} [deg]} 
+    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
+    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
+    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
+    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
+& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+}
+\startdata
+\multicolumn{12}{c}{VERITAS constraints:}\\
+\hline
+0    & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
+0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
+0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
+\cutinhead{{\em Fermi} constraints:}
+0    & -    & -    & 5.2 & 3.5 & 4.7 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
+0.2  & 3.1  & 2.9  & 3.5 & 2.4 & 3.1 & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
+0.4  & 4.7  & 4.4  & 2.5 & 1.7 & 2.3 &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
+\enddata
+\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
+\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ from the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}: at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for Fermi.
+}
+\tablenotetext{c}{Integrated gamma-ray flux from the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph.
+m$^{-2}$ s$^{-1}$ for VERITAS and  above $E=1~\rmn{GeV}$ in units of $10^{-6}$ ph.
+m$^{-2}$ s$^{-1}$ for Fermi.}
+\tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
+\tablenotetext{e}{Minimum gamma-ray flux of the hadronic model described in the
+  text. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS) and
+  $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ {\em (Fermi)}.}
+\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ in the hadronic model described in the text.}
+\label{table:constraints}
+\end{deluxetable}
+
+\begin{deluxetable}{ccccccc}
+\tablecolumns{4}
+\tablewidth{0pc}
+\tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo}
+\tablehead{
+ &
+\multicolumn{6}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
+ & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{{\em Fermi} constraints:} \\
+\colhead{$\alpha_{B}$}
+ & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+ & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+}
+\startdata
+0.3 & 0.61 & 0.51 & 0.43 & 1.02 & 1.48 & 2.13 \\
+0.5 & 0.82 & 0.68 & 0.58 & 1.40 & 2.11 & 3.24 \\
+0.7 & 1.19 & 0.98 & 0.83 & 2.11 & 3.51 & 6.91 
+\enddata
+\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
+\label{table:Bmin}
 \end{deluxetable}

### 2011-08-30 ms.tex
introduction modified and enlarged

@@
 \and
-\author{S. Federici\altaffilmark{3,4}, C. Pfrommer\altaffilmark{1,5,6},
-A. Pinzke\altaffilmark{7}}
+\author{S. Federici\altaffilmark{3,4}, C. Pfrommer\altaffilmark{1,5},
+A. Pinzke\altaffilmark{6}}
 
@@
 \altaffiltext{5}{Heidelberg Institute	for Theoretical	Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
-\altaffiltext{6}{Canadian Institute for Theoretical Astrophysics, University of Toronto, Toronto, ON, M5S 3H8, Canada}
-\altaffiltext{7}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
+\altaffiltext{67}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
 
@@
 \section{Introduction}
-Clusters of galaxies are the largest observable structures in the Universe, with typical diameters of several Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$.
-These gravitationally bound objects have formed on increasingly larger scales during the evolution of the Universe through the process of cosmic structure formation \citep{article:Voit:2005}.
-Although most of the cluster mass comes from large amounts of dark matter (DM) embedded in a cluster, as indicated by cluster dynamics and weak gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}, gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass.
-Individual galaxies contribute only a small amount (about 5\%) to the cluster mass.
-The ICM gas mass also comprise a significant fraction of the observable (baryonic) matter in the Universe.
+Clusters of galaxies are the largest virialized objects in the Universe, with
+typical diameters of a few Mpc and masses on the order of $10^{14}$ to $10^{15}
+M_{\odot}$. According to the currently favored hierarchical model of cosmic
+structure formation, larger objects formed through successive mergers of smaller
+objects with galaxy clusters sitting a top this mass hierarchy \citep[see][for a
+review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark
+matter (DM), as indicated by galaxy dynamics and gravitational lensing
+\citep[][]{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the
+intra-cluster medium (ICM) contributes about 15\% of the total cluster mass and
+individual galaxies account for the remainder (about 5\%). The ICM gas mass also
+comprises a significant fraction of the observable (baryonic) matter in the
+Universe.
 
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.][]{article:Petrosian:2001}.
-Heating of this plasma is thought to come primarily from collisionless structure-formation shocks, due to accretion and merger processes.
-Such shocks and turbulences in the ICM gas and magnetic fields also provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}.
-Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}.
-Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} provide further indications of relativistic particle populations in clusters, although the interpretation of these observations have been disputed \citep[see, e.g.][]{article:Wik_etal:2009}.
+The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung
+radiation in the soft X-rays regime \citep[see,
+e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these
+temperatures primarily through collisionless structure-formation shocks that
+form as a result of the hierarchical merging and accretion processes. Such
+shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
+provide a means to efficiently accelerate particles \citep[see,
+e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters
+do indeed feature mega-parsec scale halos of non-thermal radio emission,
+indicative of a population of relativistic electrons and positrons (leptons) and
+magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Recent
+observations of possible non-thermal emission from clusters in the the extreme
+ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
+\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004,
+  article:Eckert_etal:2007} may provide further indications of relativistic
+particle populations in clusters, although the interpretation of these
+observations as non-thermal diffuse emission have been disputed on the basis of
+more sensitive observations \citep[see, e.g.,][]{2009ApJ...690..367A,
+  2010ApJ...725.1688A, article:Wik_etal:2009}.
 
-Galaxy clusters have for many years been proposed as sources of gamma rays.
-If shock acceleration in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected.
-The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM.
-Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron.} and the neutral pion to gamma rays.
-Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$) and the sheer size of a cluster, CR hadrons will be confined in the cluster on very long timescales \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.
+Galaxy clusters have for many years been proposed as sources of gamma rays. If
+shock acceleration in the ICM is an efficient process, a population of highly
+relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in
+the ICM is to be expected. The main energy-loss mechanism for CR hadrons at high
+energies is pion production through the interaction of CRs with nuclei in the
+ICM. Pions are short lived and decay; the charged pions to electrons and
+positrons,\footnote{A charged pion decays to a muon or antimuon, which
+  subsequently decay to an electron or positron as well as neutrinos.} and the
+neutral pion to gamma rays. Due to the low density of the ICM
+($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and
+the volume filling magnetic fields in the ICM, CR hadrons will be confined in
+the cluster on timescales comparable and longer than the Hubble time
+\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them
+to accumulate over time.  Depending on the CR pressure, quantified by the
+CR-to-thermal pressure fraction $X_\CR=\expval{
+  P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma
+rays can be expected.
 
-\paragraph{Rewrite this paragraph!}
-Depending on the CR energy density, quantified by the fraction of energy in CRs to the thermal energy in a cluster, $\eta=\expval{ E_{\mathrm{CR}}/E_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.
-This fraction could plausibly be as large as 50\% \citep{article:Ryu_etal:2003}, but a much smaller fraction of only a few percent is required in order to produce a gamma-ray flux observable with current generation gamma-ray telescopes.
+Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as
+well as the temperature decrement of the CMB in the direction of a galaxy
+cluster due to the Sunyaev-Zel'dovich effect which is proportional to the
+line-of-sight integral of the thermal electron pressure. This could then
+severely jeopardize the use of clusters to determine cosmological
+parameters. Comparing X-ray and optical potential profiles in the centers of
+galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that
+can be composed of CRs, magnetic fields or turbulence) relative to the thermal
+gas pressure \cite{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}. An analysis that
+compares spatially resolved weak gravitational lensing and hydrostatic X-ray
+masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic
+in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the
+mean density is 500 times the critical density -- suggesting again a substantial
+non-thermal pressure contribution on large scales
+\citep{2008MNRAS.384.1567M}. High-energy gamma-ray emission is a complementary
+method of constraining the pressure contribution of CRs that is most sensitive
+to the cluster core region. However, it assumes that the CR component is fully
+mixed with the ICM and almost insensitive in detecting a two-phase structure of
+CRs and the thermal ICM.  A fraction $X_\CR$ of only a few percent is required
+in order to produce a gamma-ray flux observable with current generation
+gamma-ray telescopes rendering this technique at least as sensitive as the
+dynamical and hydrostatic method (which are however more general in that they
+are sensitive to any non-thermal pressure component).
 
-Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example cosmic microwave background (CMB) photons, on ultra-relativistic leptons.
-Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.
+Gamma-ray emission can also be produced by Compton up-scattering of ambient
+photons, for example cosmic microwave background (CMB) photons, on
+ultra-relativistic leptons. Those leptons can either be secondaries from the
+above mentioned CR interactions or be injected into the ICM by powerful cluster
+members and be further accelerated by diffusive shock acceleration or turbulent
+reacceleration processes.
 
-A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM particle, e.g.
-a weakly interacting massive particle (WIMP).
-As already mentioned, about 80\% of the cluster mass is in the form of dark matter.
-Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the DM density along the line of sight, making clusters of galaxies potentially good candidates for DM searches.
-This despite their large distances compared to other common targets for DM searches, such as dwarf spheriodal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010, article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006, article:Aharonian_etal:2009b}.
+A third mechanism for gamma-ray production in a galaxy cluster is
+self-annihilation of a DM particle, e.g. a weakly interacting massive particle
+(WIMP). As already mentioned, about 80\% of the cluster mass is in the form of
+dark matter. Recent works \citep{article:EvansFerrerSarkar:2004,
+  article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM
+annihilations is expected to be proportional to the square of the DM density
+integrated along the line of sight, making clusters of galaxies potentially good
+candidates for DM searches \cite{article:PinzkePfrommerBergstrom2009,
+  2011ApJ...726L...6C}. This despite their large distances compared to other
+common targets for DM searches, such as dwarf spheroidal galaxies
+\citep{article:Strigari_etal:2007, article:Acciari_etal:2010,
+  article:Aliu_etal:2009} or the Galactic center
+\citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
+  article:Aharonian_etal:2009b}.
 
-While several observations of clusters of galaxies have been made with satellite-borne and ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
-Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several galaxy clusters in the MeV to GeV band.
-Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
+While several observations of clusters of galaxies have been made with
+satellite-borne and ground-based telescopes, a detection of gamma-ray emission
+from a cluster has yet to be made.  Observations with EGRET
+\citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi
+Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided
+upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$
+s$^{-1}$ for Fermi observations) for several galaxy clusters in the 100 MeV to GeV
+band. Upper limits on the VHE gamma-ray flux from a few select clusters,
+including the Coma cluster, have been provided by observations with ground-based
+imaging atmospheric Cherenkov telescopes
+\citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008,
+  article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
 
-The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}.
-Located at a distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest and also one of the most massive clusters \citep[$M \sim 10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}.
-It hosts both a giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
-It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
-Extended soft X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo.
-As such it is a natural candidate for gamma-ray observations.
+The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied
+clusters over all wavelengths \citep{article:Voges_etal:1999}. Located at a
+distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is
+one of the closest massive clusters \citep[$M \sim
+10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}. It hosts both
+a giant radio halo
+\citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral
+radio relic, which appears connected to the radio halo with a ``diffuse'' bridge
+\citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested
+that the relic is an infall shock \citep{article:Ensslin_etal:1998} and
+successively demonstrated by cosmological simulations that model the non-thermal
+emission processes \citep{article:PfrommerEnsslinSpringel:2008,
+  article:Pfrommer:2008, article:Battaglia_etal:2009,
+  article:Skillman_etal:2011}. Extended soft thermal X-ray (SXR) emission is
+evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band
+\citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton
+\citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with
+substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$
+of the total intracluster medium pressure \cite{2004A&A...426..387S}. As such it
+is a natural candidate for gamma-ray observations.
 

### 2011-09-01 ms.tex
typos in Fermi section fixed

@@
 Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful.
-The \emph{Fermi}-LAT collaboration estimates the systematic uncertainties at 10 GeV to be around 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits at the 95\% confidence level in the energy range 1-100 GeV, assuming both a unresolved, point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}.
-The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$ and $2.5$.
+The \emph{Fermi}-LAT collaboration estimates the systematic uncertainties at 10 GeV to be around 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}.
+The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and $2.5$.
 

### 2011-09-01 ms.tex
more typos fixed in the CR/B-analysis part

@@
 can be composed of CRs, magnetic fields or turbulence) relative to the thermal
-gas pressure \cite{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}. An analysis that
+gas pressure \citep{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}. An analysis that
 compares spatially resolved weak gravitational lensing and hydrostatic X-ray
@@
 integrated along the line of sight, making clusters of galaxies potentially good
-candidates for DM searches \cite{article:PinzkePfrommerBergstrom2009,
+candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009,
   2011ApJ...726L...6C}. This despite their large distances compared to other
@@
 substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$
-of the total intracluster medium pressure \cite{2004A&A...426..387S}. As such it
+of the total intracluster medium pressure \citep{2004A&A...426..387S}. As such it
 is a natural candidate for gamma-ray observations.
@@
 
-We note that the overall normalization of the CR and gamma-ray distribution scales with the maximum acceleration efficiency at structure formation shock waves.
+The overall normalization of the CR and gamma-ray distribution scales with the maximum acceleration efficiency at structure formation shock waves.
 Following recent observations at supernova remnants \citep{article:Helder_etal:2009} as well as theoretical studies \citep{article:KangJones:2005}, we adopt an optimistic but nevertheless realistic value of this parameter and assume that 50\% of the dissipated energy at strong shocks is injected into CRs while this efficiency rapidly decreases for weaker shocks.
@@
 However, other means of CR transport such as diffusion and streaming may flatten the CR radial profiles.
-It has been suggested that advection is dominant only during mergers \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}, in which case relaxed clusters could have a reduced gamma-ray luminosity by up to a factor of five compared with merging clusters.
+It has been suggested that advection is dominant only during mergers, in which case relaxed clusters could have a reduced gamma-ray luminosity by up to a factor of five compared with merging clusters \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}.
 The goal of this and other future work of seeking for gamma-ray emission from clusters is to constrain the acceleration physics and transport properties of CRs.
@@
 Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius.
-In our further analysis, we use the gamma-ray flux limits of {\em Fermi} in the energy interval of 1-3 GeV which are most constraining.
+In our further analysis, we use the gamma-ray flux limits of {\em Fermi} in the energy interval of 1--3 GeV which are most constraining as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.
 
-Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance from the Coma cluster center (dashed lines).
-To compute the CR pressure, we assume a low-energy cutoff of the CR distribution at $T = 0.8\,m_\rmn{p} c^2$ reflecting the high cooling rates at low CR energies.
+Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster center (dashed red lines) and contained within $R$ (dashed blue lines).
+To compute the CR pressure, we assume a low-momentum cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which reflects the high cooling rates at low CR energies.
 The relative CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the peripheral strong accretion shocks compared to weak central flow shocks.
@@
 \subsection{Simplified analytical model}
-To complement the simulation-inspired analysis and to facilitate comparison with
-earlier analytical work, we repeat the data analysis with a simplified
-analytical model that assumes a power-law CR spectrum and a constant relative CR
-pressure, i.e., we adopt the {\em isobaric model of CRs}. Since a priori, the CR
-spectral index is unconstrained, we vary it within plausible ranges of
-$2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the radio
-spectral index of the giant radio halo of Coma after accounting for the spectral
-steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich
-effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field
-  of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons
-  have an energy of $\sim100$ GeV and are $\sim$ 20 times less energetic than
-  those CR protons responsible for 200-GeV gamma-ray emission.}. Table
-\ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS
-flux upper limits strongly depend on $\alpha$ due to the comparably large lever
-arm from GeV energies (that dominate the CR pressure) to TeV-energies. The
-limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$
-between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5). The {\em
-  Fermi} limits depend only weakly on $\alpha$ and are most constraining for an
-aperture of 0.4$^{\circ}$.  The best limit on $X_\CR$ of 0.017 is achieved for
-$\alpha=2.3$.
+To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}.
+To be independent of additional assumptions and in line with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$.
+Since a priori, the CR spectral index is unconstrained, we vary it within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$.
+This spectral range is compatible with the radio spectral index of the giant radio halo of Coma after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and
+  are $\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.
+Table \ref{table:constraints} shows the resulting constraints on $X_\CR$.
+The VERITAS flux upper limits strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies.
+The limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5).
+The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of 0.4$^{\circ}$.
+The best limit on $X_\CR$ of 0.017 is achieved for $\alpha=2.3$.
 
@@
 The idea is based on the fact that a stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and thermal gas \citep{article:Voelk:1989, article:Pohl:1994, article:Pfrommer:2008}, in particular with $\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.
-Hence we can derive a minimum gamma-ray flux in the hadronic
-model
+Hence we can derive a minimum gamma-ray flux in the hadronic model
 \begin{equation}
@@
 \end{equation}
-where $L_{\nu}$ is the observed luminosity of the radio mini-halo,
-$D_{\rmn{lum}}$ denotes the luminosity distance to the respective cluster,
-$A_\gamma$ and $A_\nu$ are dimensional constants that depend on the hadronic
-physics of the interaction \citep{2008MNRAS.385.1211P,
-  2008MNRAS.385.1242P}. Lowering the magnetic field would require an increase in
-the energy density of CR electrons to reproduce the observed synchrotron
-luminosity and thus increase the associated gamma-ray flux.
+where $L_{\nu}$ is the observed luminosity of the radio mini-halo, $D_{\rmn{lum}}$ denotes the luminosity distance to the respective cluster, $A_\gamma$ and $A_\nu$ are dimensional constants that depend on the hadronic physics of the interaction \citep{article:Pfrommer:2008, Pfrommer_etal:2008}.
+Lowering the magnetic field would require an increase in the energy density of CR electrons to reproduce the observed synchrotron luminosity and thus increase the associated gamma-ray flux.
 
@@
 
-The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV})$ and the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ are shown in Table \ref{table:constraints}.
+The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV})$ and the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/\tilde{F}$ are shown in Table \ref{table:constraints}, where $F_\rmn{iso} = X_\CR\,\tilde{F}$ is the gamma-ray flux in the {\em isobaric model of CRs} introduced in the previous section.
 Even in the most constraining cases, these are a factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$, $<0.2^{\circ}$) and a factor of about 20 below the {\em Fermi} upper limits (adopting $\alpha=2.3$, $<0.4^{\circ}$).
@@
 We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B>B_\rmn{CMB}$.
-Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assuming the validity of the hadronic model \cite{article:PfrommerEnsslin:2004a}.
+Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assuming the validity of the hadronic model \citep{article:PfrommerEnsslin:2004a}.
 Lowering the gamma-ray constraint will tighten (increase) the magnetic field limit.
@@
 
-Table~\ref{table:Bmin} shows the results on the lower limit of the central
-magnetic field that range for the VERITAS limits from $B_{0} = 0.4$ to
-$1.2\,\mu$G and for the {\em Fermi} limits from $B_{0} = 1$ to $7\,\mu$G. Since
-these lower limits on $B_0$ are for most of the parameter space spanned by
-$\alpha_B$ and $\alpha$ below the values favored by Faraday RM, the hadronic
-model is still viable. The only exception is the parameter combination of
-$alpha_B=0.7$ and $\alpha=2.5$ which starts to be in (weak) tension with Faraday
-RM data. This indicates the power of future gamma-ray observations of Coma in
-constraining parameters of the hadronic model.
+Table~\ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range for the VERITAS limits from $B_{0} = 0.4$ to $1.2\,\mu$G and for the {\em Fermi} limits from $B_{0} = 1$ to $7\,\mu$G.
+Since these lower limits on $B_0$ are below the values favored by Faraday RM for most of the parameter space spanned by $\alpha_B$ and $\alpha$, the hadronic model is still viable.
+The only exception is the parameter combination of $\alpha_B=0.7$ and $\alpha=2.5$ which starts to be in (weak) tension with Faraday RM data.
+This indicates the power of future gamma-ray observations of Coma in constraining parameters of the hadronic model.
 
-In addition there are a few interesting remarks in order. (1) For the VERITAS
-limits, the hardest CR spectral indices are most constraining because of the
-tightest upper limits. The opposite is true for the {\em Fermi} upper limits
-which probe the region around the pion decay bump characterized by a shape
-parameter that depends inversely on the CR spectral index
-\cite{article:PfrommerEnsslin:2004b}.  (2) For a steeper magnetic decline
-(larger $\alpha_{B}$), the CR number density needs to be larger to match the
-observed radio emission profiles which would yield a higher gamma-ray flux so
-that the upper limits are more constraining. This implies tighter lower limits
-for $B_{0}$. However, the largest choice of $\alpha_B=0.7$, which represents a
-flux-freezing magnetic field, is possibly too steep in the outer parts as it
-neglects the contributions from turbulent dynamos in these dynamically active
-regions with vorticity injection at corrugated structure formation shocks
-\cite{article:PfrommerJones:2011}. (3) Interestingly, in all cases, we use the
-0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic
-field configurations.  This is because we need a substantially increasing
-relative CR pressure profile to match the observed radio profiles (for a given
-magnetic realization); hence that CR realization produces a larger flux within
-0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} =
-\rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining;
-hence the constraints on $B_{0}$ get better for the larger integration
-area. Physically, this may be achieved by considering CR transport processes
-such as streaming which produces an increasing $X_{\CR}$-profile due to the
-larger available phase space in the outer cluster regions.
+In addition there are a few interesting remarks in order.
+(1) For the VERITAS limits, the hardest CR spectral indices are most constraining because of the tightest upper limits.
+The opposite is true for the {\em Fermi} upper limits which probe the region around the pion decay bump characterized by a shape parameter that depends inversely on the CR spectral index \citep{article:PfrommerEnsslin:2004b}.
+(2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining.
+This implies tighter lower limits for $B_{0}$.
+However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions with vorticity injection at corrugated structure formation shocks
+\citep{article:PfrommerJones:2011}.
+(3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic field configurations.
+This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the constraints on $B_{0}$ get better for the larger integration area.
+Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.
 
-As a final word, we note that the $X_{\CR}$ profiles always obey the energy
-condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio
-halo emission ($< 1$ Mpc) when assuming a central magnetic field of
-$B_{0}=3\,\mu$G that is at the lower 2-$\sigma$ interval bound inferred from
-Faraday RM \citep{article:Bonafede_etal:2010}.\footnote{Note that a central
-  magnetic field of $3\,\mu$G corresponds in the Coma cluster to a relative
-  magnetic energy density of $\tilde{X}_B=0.005$.} Typical values at 1 Mpc range
-from $X_{\CR} = 0.02$ ($\alpha_{B}=0.3$, $\alpha=2.1$) to $X_{\CR} = 1$
-($\alpha_{B}=0.7$, $\alpha=2.5$).\footnote{See Figure 3 in
-  \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming
-  minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7
-  for a parametrization as adopted in this study.} We caution, however, that the
-minimum-energy condition is violated at the outer radio halo boundary for the
-range of minimum magnetic-field values inferred by this study.
+As a final word, we note that the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo emission ($< 1$ Mpc) when assuming a central magnetic field of $B_{0}=3\,\mu$G that is at the lower 2-$\sigma$ interval bound inferred from Faraday RM \citep{article:Bonafede_etal:2010}.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the Coma cluster to a relative magnetic energy density of $\tilde{X}_B=0.005$.} Typical values at 1 Mpc range from $X_{\CR} = 0.02$ ($\alpha_{B}=0.3$, $\alpha=2.1$) to $X_{\CR} = 1$ ($\alpha_{B}=0.7$, $\alpha=2.5$).\footnote{See Figure 3 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in this study.} We caution, however, that the minimum-energy condition is violated at the outer radio halo boundary for the range of minimum
+magnetic-field values inferred by this study.
 
@@
 
-We employed various approaches to constrain the CR population and magnetic field
-distribution that are complementary in their assumptions and hence well suited
-in assessing underlying Bayesian priors in the models. (1) We use a simplified
-``isobaric CR model'' that is characterized by a constant CR-to-thermal pressure
-fraction and has a power-law momentum spectrum.  While this model is physically
-not justified a priory, it is simple and widely used in the literature and
-captures some aspects of more elaborate models such as (2) the simulation-based
-analytical approach of \citet{article:PinzkePfrommer:2010}. This is a ``first
-principle approach'' that predicts the CR distribution for a given set of
-assumptions (namely the physics that was simulated). It is powerful since it
-only requires the density profile as input due to the approximate universality
-of the CR distribution (when neglecting CR diffusion and streaming which
-appears, however, necessary to explain the radio halo bimodality). (3) We
-finally use a pragmatic approach which models the CR and magnetic distribution
-such as to reproduce the observed emission profile of the Coma radio halo. While
-this approach is also physically not justified, it is powerful as it shows what
-the ``correct'' model has to achieve and can point into the direction of the
-relevant physics.
+We employed various approaches to constrain the CR population and magnetic field distribution that are complementary in their assumptions and hence well suited in assessing underlying Bayesian priors in the models.
+(1) We use a simplified ``isobaric CR model'' that is characterized by a constant CR-to-thermal pressure fraction and has a power-law momentum spectrum.
+While this model is physically not justified a priory, it is simple and widely used in the literature and captures some aspects of more elaborate models such as (2) the simulation-based analytical approach of \citet{article:PinzkePfrommer:2010}.
+This is a ``first principle approach'' that predicts the CR distribution for a given set of assumptions (namely the physics that was simulated).
+It is powerful since it only requires the density profile as input due to the approximate universality of the CR distribution (when neglecting CR diffusion and streaming which appears, however, necessary to explain the radio halo bimodality).
+(3) We finally use a pragmatic approach which models the CR and magnetic distribution such as to reproduce the observed emission profile of the Coma radio halo.
+While this approach is also physically not justified, it is powerful as it shows what the ``correct'' model has to achieve and can point into the direction of the relevant physics.
 
-Within this pragmatic approach we employ two different directions. First,
-adopting a high magnetic field everywhere in the cluster ($B\gg B_\rmn{CMB}$)
-yields the minimum gamma-ray flux in the hadronic model of radio halos which we
-find to be a factor of 20 (60) below the most constraining flux upper limits of
-{\em Fermi} (VERITAS). Second, by matching the radio emission profile
-(i.e. fixing the radial CR profile for a given magnetic field model) and by
-requiring the pion-decay gamma-ray flux to match the flux upper limits
-(i.e. fixing the normalization of the CR distribution) we obtain lower limits on
-the magnetic field distribution under consideration. Our limits of the central
-magnetic field range from $B_{0} = 0.4$ to $1.2\,\mu$G (for VERITAS limits) and
-from $B_{0} = 1$ to $7\,\mu$G (for {\em Fermi} limits). Since these lower limits
-on $B_0$ are below the values favored by Faraday RM, the hadronic model is still
-viable.
+Within this pragmatic approach we employ two different directions.
+First, adopting a high magnetic field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining flux upper limits of {\em Fermi} (VERITAS).
+Second, by matching the radio emission profile (i.e., fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR distribution) we obtain lower limits on the magnetic field distribution under consideration.
+Our limits of the central magnetic field range from $B_{0} = 0.4$ to $1.2\,\mu$G (for VERITAS gamma-ray flux limits) and from $B_{0} = 1$ to $7\,\mu$G (for {\em Fermi} gamma-ray flux limits).
+Since these lower limits on $B_0$ are below the values favored by Faraday RM, the hadronic model is still viable.
 
-Using the most constraining VERITAS limits, we can constrain the CR-to-thermal
-pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray spectral
-index, $\alpha$, varying between 2.1 and 2.5).  The best {\em Fermi} flux limit
-constrains $X_\CR$ to be below 0.017 (for $\alpha=2.3$), only weakly depending
-on the assumed CR spectral index.
+Using the most constraining VERITAS limits, we can constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray spectral index, $\alpha$, varying between 2.1 and 2.5).
+The best {\em Fermi} flux limit constrains $X_\CR$ to be below 0.017 (for $\alpha=2.3$), only weakly depending on the assumed CR spectral index.
 
@@
 Model predictions are shown by dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining VERITAS upper limits within 0.2$^\circ$ (solid).
-We compare differential $X_\CR$-profiles (red) to integrated profiles $X_{\CR}(<R/R_{\rmn{vir}})$ (blue) which we use to compare to the upper limits.}
+We compare differential $X_\CR$-profiles (red) to integrated profiles $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (blue) which we use to compare to the upper limits.}
 \label{fig:xcr}

### 2011-09-01 ms.tex
Minor change to last paragraph of the introduction

@@
 \section{Introduction}
-Clusters of galaxies are the largest virialized objects in the Universe, with
-typical diameters of a few Mpc and masses on the order of $10^{14}$ to $10^{15}
-M_{\odot}$. According to the currently favored hierarchical model of cosmic
-structure formation, larger objects formed through successive mergers of smaller
-objects with galaxy clusters sitting a top this mass hierarchy \citep[see][for a
-review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark
-matter (DM), as indicated by galaxy dynamics and gravitational lensing
-\citep[][]{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the
-intra-cluster medium (ICM) contributes about 15\% of the total cluster mass and
-individual galaxies account for the remainder (about 5\%). The ICM gas mass also
-comprises a significant fraction of the observable (baryonic) matter in the
-Universe.
+Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of a few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$.
+According to the currently favored hierarchical model of cosmic structure formation, larger objects formed through successive mergers of smaller
+objects with galaxy clusters sitting a top this mass hierarchy \citep[see][for a review]{article:Voit:2005}.
+Most of the mass of a cluster is in form of dark matter (DM), as indicated by galaxy dynamics and gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}.
+Baryonic gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass and individual galaxies account for the remainder (about 5\%).
+The ICM gas mass also comprises a significant fraction of the observable (baryonic) matter in the Universe.
 
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung
-radiation in the soft X-rays regime \citep[see,
-e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these
-temperatures primarily through collisionless structure-formation shocks that
-form as a result of the hierarchical merging and accretion processes. Such
-shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
-provide a means to efficiently accelerate particles \citep[see,
-e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters
-do indeed feature mega-parsec scale halos of non-thermal radio emission,
-indicative of a population of relativistic electrons and positrons (leptons) and
-magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Recent
-observations of possible non-thermal emission from clusters in the the extreme
-ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
-\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004,
-  article:Eckert_etal:2007} may provide further indications of relativistic
-particle populations in clusters, although the interpretation of these
-observations as non-thermal diffuse emission have been disputed on the basis of
-more sensitive observations \citep[see, e.g.,][]{2009ApJ...690..367A,
-  2010ApJ...725.1688A, article:Wik_etal:2009}.
+The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}.
+This plasma has been heated to these temperatures primarily through collisionless structure-formation shocks that form as a result of the hierarchical merging and accretion processes.
+Such shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
+provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}.
+Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}.
+Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
+\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters, although the interpretation of these
+observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations \citep[see, e.g.,][]{2009ApJ...690..367A, 2010ApJ...725.1688A, article:Wik_etal:2009}.
 
-Galaxy clusters have for many years been proposed as sources of gamma rays. If
-shock acceleration in the ICM is an efficient process, a population of highly
-relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in
-the ICM is to be expected. The main energy-loss mechanism for CR hadrons at high
-energies is pion production through the interaction of CRs with nuclei in the
-ICM. Pions are short lived and decay; the charged pions to electrons and
-positrons,\footnote{A charged pion decays to a muon or antimuon, which
-  subsequently decay to an electron or positron as well as neutrinos.} and the
-neutral pion to gamma rays. Due to the low density of the ICM
-($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and
-the volume filling magnetic fields in the ICM, CR hadrons will be confined in
-the cluster on timescales comparable and longer than the Hubble time
-\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them
-to accumulate over time.  Depending on the CR pressure, quantified by the
-CR-to-thermal pressure fraction $X_\CR=\expval{
-  P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma
-rays can be expected.
+Galaxy clusters have for many years been proposed as sources of gamma rays.
+If shock acceleration in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected.
+The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM.
+Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to gamma rays.
+Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume filling magnetic fields in the ICM, CR hadrons will be confined in the cluster on timescales comparable and longer than the Hubble time \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.
+Depending on the CR pressure, quantified by the CR-to-thermal pressure fraction $X_\CR=\expval{P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.
 
-Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as
-well as the temperature decrement of the CMB in the direction of a galaxy
-cluster due to the Sunyaev-Zel'dovich effect which is proportional to the
-line-of-sight integral of the thermal electron pressure. This could then
-severely jeopardize the use of clusters to determine cosmological
-parameters. Comparing X-ray and optical potential profiles in the centers of
-galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that
-can be composed of CRs, magnetic fields or turbulence) relative to the thermal
-gas pressure \citep{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}. An analysis that
-compares spatially resolved weak gravitational lensing and hydrostatic X-ray
-masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic
-in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the
-mean density is 500 times the critical density -- suggesting again a substantial
-non-thermal pressure contribution on large scales
-\citep{2008MNRAS.384.1567M}. High-energy gamma-ray emission is a complementary
-method of constraining the pressure contribution of CRs that is most sensitive
-to the cluster core region. However, it assumes that the CR component is fully
-mixed with the ICM and almost insensitive in detecting a two-phase structure of
-CRs and the thermal ICM.  A fraction $X_\CR$ of only a few percent is required
-in order to produce a gamma-ray flux observable with current generation
-gamma-ray telescopes rendering this technique at least as sensitive as the
-dynamical and hydrostatic method (which are however more general in that they
-are sensitive to any non-thermal pressure component).
+Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as well as the temperature decrement of the CMB in the direction of a galaxy cluster due to the Sunyaev-Zel'dovich effect which is proportional to the line-of-sight integral of the thermal electron pressure.
+This could then severely jeopardize the use of clusters to determine cosmological parameters.
+Comparing X-ray and optical potential profiles in the centers of galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas pressure \citep{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}.
+An analysis that compares spatially resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the
+mean density is 500 times the critical density -- suggesting again a substantial non-thermal pressure contribution on large scales \citep{2008MNRAS.384.1567M}.
+High-energy gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that is most sensitive
+to the cluster core region.
+However, it assumes that the CR component is fully mixed with the ICM and almost insensitive in detecting a two-phase structure of CRs and the thermal ICM.
+A fraction $X_\CR$ of only a few percent is required in order to produce a gamma-ray flux observable with current generation
+gamma-ray telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method (which are however more general in that they are sensitive to any non-thermal pressure component).
 
-Gamma-ray emission can also be produced by Compton up-scattering of ambient
-photons, for example cosmic microwave background (CMB) photons, on
-ultra-relativistic leptons. Those leptons can either be secondaries from the
-above mentioned CR interactions or be injected into the ICM by powerful cluster
-members and be further accelerated by diffusive shock acceleration or turbulent
-reacceleration processes.
+Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example cosmic microwave background (CMB) photons, on ultra-relativistic leptons.
+Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster
+members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.
 
-A third mechanism for gamma-ray production in a galaxy cluster is
-self-annihilation of a DM particle, e.g. a weakly interacting massive particle
-(WIMP). As already mentioned, about 80\% of the cluster mass is in the form of
-dark matter. Recent works \citep{article:EvansFerrerSarkar:2004,
-  article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM
-annihilations is expected to be proportional to the square of the DM density
-integrated along the line of sight, making clusters of galaxies potentially good
-candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009,
-  2011ApJ...726L...6C}. This despite their large distances compared to other
-common targets for DM searches, such as dwarf spheroidal galaxies
-\citep{article:Strigari_etal:2007, article:Acciari_etal:2010,
-  article:Aliu_etal:2009} or the Galactic center
-\citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
-  article:Aharonian_etal:2009b}.
+A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM particle, e.g.
+a weakly interacting massive particle (WIMP).
+As already mentioned, about 80\% of the cluster mass is in the form of dark matter.
+Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the square of the DM density integrated along the line of sight, making clusters of galaxies potentially good
+candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009, 2011ApJ...726L...6C}.
+This despite their large distances compared to other common targets for DM searches, such as dwarf spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006, article:Aharonian_etal:2009b}.
 
-While several observations of clusters of galaxies have been made with
-satellite-borne and ground-based telescopes, a detection of gamma-ray emission
-from a cluster has yet to be made.  Observations with EGRET
-\citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi
-Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided
-upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$
-s$^{-1}$ for Fermi observations) for several galaxy clusters in the 100 MeV to GeV
-band. Upper limits on the VHE gamma-ray flux from a few select clusters,
-including the Coma cluster, have been provided by observations with ground-based
-imaging atmospheric Cherenkov telescopes
-\citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008,
-  article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
+While several observations of clusters of galaxies have been made with satellite-borne and ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
+Observations with EGRET
+\citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several galaxy clusters in the 100 MeV to GeV
+band.
+Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
 
-The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied
-clusters over all wavelengths \citep{article:Voges_etal:1999}. Located at a
-distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is
-one of the closest massive clusters \citep[$M \sim
-10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}. It hosts both
-a giant radio halo
-\citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral
-radio relic, which appears connected to the radio halo with a ``diffuse'' bridge
-\citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested
-that the relic is an infall shock \citep{article:Ensslin_etal:1998} and
-successively demonstrated by cosmological simulations that model the non-thermal
-emission processes \citep{article:PfrommerEnsslinSpringel:2008,
-  article:Pfrommer:2008, article:Battaglia_etal:2009,
-  article:Skillman_etal:2011}. Extended soft thermal X-ray (SXR) emission is
-evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band
-\citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton
-\citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with
-substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$
-of the total intracluster medium pressure \citep{2004A&A...426..387S}. As such it
-is a natural candidate for gamma-ray observations.
+The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}.
+Located at a distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest massive clusters \citep[$M \sim10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}.
+It hosts both a giant radio halo
+\citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
+It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
+Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$ of the total intracluster medium pressure \citep{2004A&A...426..387S}.
+As such it is a natural candidate for gamma-ray observations.
 
-In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, 
-together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
-Throughout the analysis, a present day Hubble constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
+In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, with complementing analysis of available data from the Fermi Gamma-ray Space Telescope.
+The VERITAS and Fermi data have been used to place constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
+Throughout the analyses, a present day Hubble constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
 

### 2011-09-01 ms.tex
Citations updated

@@
 \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters, although the interpretation of these
-observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations \citep[see, e.g.,][]{2009ApJ...690..367A, 2010ApJ...725.1688A, article:Wik_etal:2009}.
+observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009, article:Ajello_etal:2010, article:Wik_etal:2009}.
 

### 2011-09-01 ms.tex
Citations updated

@@
 This could then severely jeopardize the use of clusters to determine cosmological parameters.
-Comparing X-ray and optical potential profiles in the centers of galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas pressure \citep{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}.
+Comparing X-ray and optical potential profiles in the centers of galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas pressure \citep{article:Churazov_etal:2008, article:Churazov_etal:2010}.
 An analysis that compares spatially resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the
-mean density is 500 times the critical density -- suggesting again a substantial non-thermal pressure contribution on large scales \citep{2008MNRAS.384.1567M}.
+mean density is 500 times the critical density -- suggesting again a substantial non-thermal pressure contribution on large scales \citep{article:Mahdavi_etal:2008}.
 High-energy gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that is most sensitive
@@
 Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the square of the DM density integrated along the line of sight, making clusters of galaxies potentially good
-candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009, 2011ApJ...726L...6C}.
+candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011}.
 This despite their large distances compared to other common targets for DM searches, such as dwarf spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006, article:Aharonian_etal:2009b}.
@@
 It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
-Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$ of the total intracluster medium pressure \citep{2004A&A...426..387S}.
+Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$ of the total intracluster medium pressure \citep{article:Schuecker_etal:2004}.
 As such it is a natural candidate for gamma-ray observations.

### 2011-09-02 ms.tex
Removed commented text
clarification added on how to compute B_min

--- 2011-09-01 ms.tex
@@
 \section{Introduction}
-Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of a few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$.
-According to the currently favored hierarchical model of cosmic structure formation, larger objects formed through successive mergers of smaller
-objects with galaxy clusters sitting a top this mass hierarchy \citep[see][for a review]{article:Voit:2005}.
-Most of the mass of a cluster is in form of dark matter (DM), as indicated by galaxy dynamics and gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}.
-Baryonic gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass and individual galaxies account for the remainder (about 5\%).
-The ICM gas mass also comprises a significant fraction of the observable (baryonic) matter in the Universe.
+Clusters of galaxies are the largest virialized objects in the Universe, with
+typical diameters of a few Mpc and masses on the order of $10^{14}$ to $10^{15}
+M_{\odot}$. According to the currently favored hierarchical model of cosmic
+structure formation, larger objects formed through successive mergers of smaller
+objects with galaxy clusters sitting a top this mass hierarchy \citep[see][for a
+review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark
+matter (DM), as indicated by galaxy dynamics and gravitational lensing
+\citep[][]{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the
+intra-cluster medium (ICM) contributes about 15\% of the total cluster mass and
+individual galaxies account for the remainder (about 5\%). The ICM gas mass also
+comprises a significant fraction of the observable (baryonic) matter in the
+Universe.
 
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}.
-This plasma has been heated to these temperatures primarily through collisionless structure-formation shocks that form as a result of the hierarchical merging and accretion processes.
-Such shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
-provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}.
-Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}.
-Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
-\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters, although the interpretation of these
-observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations \citep[see, e.g.,][]{2009ApJ...690..367A, 2010ApJ...725.1688A, article:Wik_etal:2009}.
+The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung
+radiation in the soft X-rays regime \citep[see,
+e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these
+temperatures primarily through collisionless structure-formation shocks that
+form as a result of the hierarchical merging and accretion processes. Such
+shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
+provide a means to efficiently accelerate particles \citep[see,
+e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters
+do indeed feature mega-parsec scale halos of non-thermal radio emission,
+indicative of a population of relativistic electrons and positrons (leptons) and
+magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Recent
+observations of possible non-thermal emission from clusters in the the extreme
+ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
+\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004,
+  article:Eckert_etal:2007} may provide further indications of relativistic
+particle populations in clusters, although the interpretation of these
+observations as non-thermal diffuse emission have been disputed on the basis of
+more sensitive observations \citep[see, e.g.,][]{2009ApJ...690..367A,
+  2010ApJ...725.1688A, article:Wik_etal:2009}.
 
-Galaxy clusters have for many years been proposed as sources of gamma rays.
-If shock acceleration in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected.
-The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM.
-Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to gamma rays.
-Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume filling magnetic fields in the ICM, CR hadrons will be confined in the cluster on timescales comparable and longer than the Hubble time \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.
-Depending on the CR pressure, quantified by the CR-to-thermal pressure fraction $X_\CR=\expval{P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.
+Galaxy clusters have for many years been proposed as sources of gamma rays. If
+shock acceleration in the ICM is an efficient process, a population of highly
+relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in
+the ICM is to be expected. The main energy-loss mechanism for CR hadrons at high
+energies is pion production through the interaction of CRs with nuclei in the
+ICM. Pions are short lived and decay; the charged pions to electrons and
+positrons,\footnote{A charged pion decays to a muon or antimuon, which
+  subsequently decay to an electron or positron as well as neutrinos.} and the
+neutral pion to gamma rays. Due to the low density of the ICM
+($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and
+the volume filling magnetic fields in the ICM, CR hadrons will be confined in
+the cluster on timescales comparable and longer than the Hubble time
+\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them
+to accumulate over time.  Depending on the CR pressure, quantified by the
+CR-to-thermal pressure fraction $X_\CR=\expval{
+  P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma
+rays can be expected.
 
-Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as well as the temperature decrement of the CMB in the direction of a galaxy cluster due to the Sunyaev-Zel'dovich effect which is proportional to the line-of-sight integral of the thermal electron pressure.
-This could then severely jeopardize the use of clusters to determine cosmological parameters.
-Comparing X-ray and optical potential profiles in the centers of galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas pressure \citep{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}.
-An analysis that compares spatially resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the
-mean density is 500 times the critical density -- suggesting again a substantial non-thermal pressure contribution on large scales \citep{2008MNRAS.384.1567M}.
-High-energy gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that is most sensitive
-to the cluster core region.
-However, it assumes that the CR component is fully mixed with the ICM and almost insensitive in detecting a two-phase structure of CRs and the thermal ICM.
-A fraction $X_\CR$ of only a few percent is required in order to produce a gamma-ray flux observable with current generation
-gamma-ray telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method (which are however more general in that they are sensitive to any non-thermal pressure component).
+Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as
+well as the temperature decrement of the CMB in the direction of a galaxy
+cluster due to the Sunyaev-Zel'dovich effect which is proportional to the
+line-of-sight integral of the thermal electron pressure. This could then
+severely jeopardize the use of clusters to determine cosmological
+parameters. Comparing X-ray and optical potential profiles in the centers of
+galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that
+can be composed of CRs, magnetic fields or turbulence) relative to the thermal
+gas pressure \citep{2008MNRAS.388.1062C, 2010MNRAS.404.1165C}. An analysis that
+compares spatially resolved weak gravitational lensing and hydrostatic X-ray
+masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic
+in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the
+mean density is 500 times the critical density -- suggesting again a substantial
+non-thermal pressure contribution on large scales
+\citep{2008MNRAS.384.1567M}. High-energy gamma-ray emission is a complementary
+method of constraining the pressure contribution of CRs that is most sensitive
+to the cluster core region. However, it assumes that the CR component is fully
+mixed with the ICM and almost insensitive in detecting a two-phase structure of
+CRs and the thermal ICM.  A fraction $X_\CR$ of only a few percent is required
+in order to produce a gamma-ray flux observable with current generation
+gamma-ray telescopes rendering this technique at least as sensitive as the
+dynamical and hydrostatic method (which are however more general in that they
+are sensitive to any non-thermal pressure component).
 
-Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example cosmic microwave background (CMB) photons, on ultra-relativistic leptons.
-Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster
-members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.
+Gamma-ray emission can also be produced by Compton up-scattering of ambient
+photons, for example cosmic microwave background (CMB) photons, on
+ultra-relativistic leptons. Those leptons can either be secondaries from the
+above mentioned CR interactions or be injected into the ICM by powerful cluster
+members and be further accelerated by diffusive shock acceleration or turbulent
+reacceleration processes.
 
-A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM particle, e.g.
-a weakly interacting massive particle (WIMP).
-As already mentioned, about 80\% of the cluster mass is in the form of dark matter.
-Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the square of the DM density integrated along the line of sight, making clusters of galaxies potentially good
-candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009, 2011ApJ...726L...6C}.
-This despite their large distances compared to other common targets for DM searches, such as dwarf spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006, article:Aharonian_etal:2009b}.
+A third mechanism for gamma-ray production in a galaxy cluster is
+self-annihilation of a DM particle, e.g. a weakly interacting massive particle
+(WIMP). As already mentioned, about 80\% of the cluster mass is in the form of
+dark matter. Recent works \citep{article:EvansFerrerSarkar:2004,
+  article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM
+annihilations is expected to be proportional to the square of the DM density
+integrated along the line of sight, making clusters of galaxies potentially good
+candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009,
+  2011ApJ...726L...6C}. This despite their large distances compared to other
+common targets for DM searches, such as dwarf spheroidal galaxies
+\citep{article:Strigari_etal:2007, article:Acciari_etal:2010,
+  article:Aliu_etal:2009} or the Galactic center
+\citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
+  article:Aharonian_etal:2009b}.
 
-While several observations of clusters of galaxies have been made with satellite-borne and ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
-Observations with EGRET
-\citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several galaxy clusters in the 100 MeV to GeV
-band.
-Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
+While several observations of clusters of galaxies have been made with
+satellite-borne and ground-based telescopes, a detection of gamma-ray emission
+from a cluster has yet to be made.  Observations with EGRET
+\citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi
+Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided
+upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$
+s$^{-1}$ for Fermi observations) for several galaxy clusters in the 100 MeV to GeV
+band. Upper limits on the VHE gamma-ray flux from a few select clusters,
+including the Coma cluster, have been provided by observations with ground-based
+imaging atmospheric Cherenkov telescopes
+\citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008,
+  article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
 
-The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}.
-Located at a distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest massive clusters \citep[$M \sim10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}.
-It hosts both a giant radio halo
-\citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
-It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
-Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$ of the total intracluster medium pressure \citep{2004A&A...426..387S}.
-As such it is a natural candidate for gamma-ray observations.
+The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied
+clusters over all wavelengths \citep{article:Voges_etal:1999}. Located at a
+distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is
+one of the closest massive clusters \citep[$M \sim
+10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}. It hosts both
+a giant radio halo
+\citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral
+radio relic, which appears connected to the radio halo with a ``diffuse'' bridge
+\citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested
+that the relic is an infall shock \citep{article:Ensslin_etal:1998} and
+successively demonstrated by cosmological simulations that model the non-thermal
+emission processes \citep{article:PfrommerEnsslinSpringel:2008,
+  article:Pfrommer:2008, article:Battaglia_etal:2009,
+  article:Skillman_etal:2011}. Extended soft thermal X-ray (SXR) emission is
+evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band
+\citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton
+\citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with
+substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$
+of the total intracluster medium pressure \citep{2004A&A...426..387S}. As such it
+is a natural candidate for gamma-ray observations.
 
-In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, with complementing analysis of available data from the Fermi Gamma-ray Space Telescope.
-The VERITAS and Fermi data have been used to place constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
-Throughout the analyses, a present day Hubble constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
+In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, 
+together with the resulting constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
+Throughout the analysis, a present day Hubble constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
 
@@
 
-\item In the last step, we scale the secondary radio emission profile linearly with $X_{\CR,0}$ and solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile.
+\item In the last step, we solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile while fixing the profile of $X_{\CR}(r)$ as determined through the previous two steps.
 Note that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution would be degenerate.

### 2011-09-02 ms.tex

--- 2011-09-01 ms.tex
@@
 
-%
-% This part was in \del{...} 
-%
-%the limit for 0.2 deg and alpha_p = 2.3 is compatible with the simulation based
-%one, X_CR < 0.1. However, there is currently a discrepancy in our assumptions
-%about the lower energy cutoff of CRs: in the simulations we use P/mp c = 0.8 (as
-%simulated) while I set this to 0 in my simplified (isobaric) model. The
-%discrepancy can be understood as follows:
-%*) in the isobaric model, we would have to normalize our $X_\CR$ by a factor of 2/3
-%for an effective spectral index of ~ 2.4 (between GeV and 200 GeV) as inferred
-%from the simulations \citep[see Fig 1 in][]{article:PfrommerEnsslin:2004}).
-%*) In the simulation model, we have an increased pressure by this factor of 3/2
-%(in comparison to a power law spectrum with alpha_TeV ~ 2.3 down to a cutoff in
-%the normalized momentum of 0.8) due to the concave curvature of our spectrum.
-%}
-
 \subsection{Minimum gamma-ray flux}

### 2011-09-02 ms.tex
corrected a wrong argumentation in the B_lim section

@@
 In addition there are a few interesting remarks in order.
-(1) For the VERITAS limits, the hardest CR spectral indices are most constraining because of the tightest upper limits.
-The opposite is true for the {\em Fermi} upper limits which probe the region around the pion decay bump characterized by a shape parameter that depends inversely on the CR spectral index \citep{article:PfrommerEnsslin:2004b}.
+(1) For the VERITAS limits, the hardest CR spectral indices correspond to the tightest limits on $B_0$.
+This is because for an upper limit of CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting electrons.
+In order to reproduce the observed synchrotron emission, this allows for smaller magnetic fields.
+The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a pivot point of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100 GeV and hence decreases the radio-emitting secondary electrons.
+Equivalently larger magnetic fields are needed to compensate this in order to match the observed synchrotron flux.
 (2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining.
 This implies tighter lower limits for $B_{0}$.
-However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions with vorticity injection at corrugated structure formation shocks
-\citep{article:PfrommerJones:2011}.
+However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions with vorticity injection at corrugated structure formation shocks \citep{article:PfrommerJones:2011}.
 (3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic field configurations.
-This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the constraints on $B_{0}$ get better for the larger integration area.
+This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the
+constraints on $B_{0}$ get better for the larger integration area.
 Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.

### 2011-09-07 ms.tex
Updates to the DM section

--- 2011-09-02 ms.tex
@@
 \altaffiltext{5}{Heidelberg Institute	for Theoretical	Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
-\altaffiltext{67}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
+\altaffiltext{6}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
 
@@
 Observations of radio halos and relics in clusters indicate populations of relativistic electrons, which are either injected into the intra-cluster medium and accelerated by turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with the intra-cluster gas.
-Those interactions would also produce gamma rays through the decay of neutral pions.
+Those interactions could also produce gamma rays through the decay of neutral pions.
 Reported here are observations of the Coma cluster of galaxies with the VERITAS array of imaging Cherenkov telescopes.
@@
 The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields and in the Coma cluster of galaxies.
-The relative cosmic-ray pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$, is \ldots.
+The relative cosmic-ray pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$, is on the order of 10-20\% when assuming a gamma-ray photon index $\alpha=2.3$.
 The observations imply a lower limit on the intra-cluster magnetic field on the order of a $\mu$G, depending on the magnetic decline and gamma-ray spectral index.
@@
 
-\item In the last step, we solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile while fixing the profile of $X_{\CR}(r)$ as determined through the previous two steps.
+\item In the last step, we scale the secondary radio emission profile linearly with $X_{\CR,0}$ and solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile.
 Note that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution would be degenerate.
@@
 \section{Emission from Dark Matter Annihilations}
-When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated background.
+As already mentioned in the introduction, most of the mass in a galaxy cluster is in the form of DM.
+While the nature of this DM remains unknown, the most compelling theoretical candidate is a WIMP.
+The self-annihilations of WIMPs are expected to produce a flux of secondary gamma rays with a spectral signature that deviates significantly from the power-law spectrum observed in most conventional astrophysical sources.
+The spectrum will also feature a very sharp cutoff at the WIMP mass.
+Observations of these spectral features together with the expected difference in spatial distribution of the gamma-ray flux compared to conventional astrophysical sources allows for a unique means to indirectly detect DM.
+
+The gamma-ray flux due to self-annihilations of WIMPs is given by 
+\begin{equation}
+\frac{dN(\Delta\Omega)}{dE}=\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\left[\frac{dN(E,m_{\chi})}{dE}\right]\int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
+\label{eqn:WIMPflux}
+\end{equation}
+where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, $\rho$ is the DM mass density, and $\lambda$ is the line-of-sight distance to the integration volume.
+
+The two integrals in Eq. (\ref{eqn:WIMPflux}) results in a dimensionless factor representing the astrophysical contribution to the flux
+\begin{equation}
+J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right) \int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
+\end{equation}
+which here has been normalized to the square of the critical density, $\rho_{c}$, and the Hubble radius, $R_{H}$.
+
+Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\mathrm{CL})$, we can place constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$.
+
+%When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated background.
 For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor no longer compensate for the increased count of background events and the signal-to-noise deteriorates.
@@
 VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
+No significant excess of gamma-rays above a threshold of about 220 GeV was detected.
+Flux upper limits at 99\% confidence level were calculated for the cluster core and three member galaxies.
+The core was considered both as a point-like and spatialy extended source.
+The obtained flux upper limits were used to constrain properties of the cluster.
 
@@
 (1) We use a simplified ``isobaric CR model'' that is characterized by a constant CR-to-thermal pressure fraction and has a power-law momentum spectrum.
-While this model is physically not justified a priory, it is simple and widely used in the literature and captures some aspects of more elaborate models such as (2) the simulation-based analytical approach of \citet{article:PinzkePfrommer:2010}.
+While this model is physically not justified a priori, it is simple and widely used in the literature and captures some aspects of more elaborate models such as (2) the simulation-based analytical approach of \citet{article:PinzkePfrommer:2010}.
 This is a ``first principle approach'' that predicts the CR distribution for a given set of assumptions (namely the physics that was simulated).

### 2011-09-07 ms.tex
analysis figures updated, text to follow

--- 2011-09-02 ms.tex
@@
 
-Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as well as the temperature decrement of the CMB in the direction of a galaxy cluster due to the Sunyaev-Zel'dovich effect which is proportional to the line-of-sight integral of the thermal electron pressure.
+Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as well as the temperature decrement of the cosmic microwave background (CMB) in the direction of a galaxy cluster due to the Sunyaev-Zel'dovich effect which is proportional to the line-of-sight integral of the thermal electron pressure.
 This could then severely jeopardize the use of clusters to determine cosmological parameters.
@@
 
-Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example cosmic microwave background (CMB) photons, on ultra-relativistic leptons.
+Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example CMB photons, on ultra-relativistic leptons.
 Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster
@@
 
+%This is more constraining by 50\% in comparison to the model derived from simulations.
+(in comparison to a power law spectrum with $\alpha_\rmn{TeV} \sim 2.2$ down to a cutoff in the normalized momentum of 0.8)
+
 \subsection{Minimum gamma-ray flux}
@@
 \label{eq:B}
-B(r) = B_{0} \,\left(\frac{n_{\rmn{e}(r)}}{n_{\rmn{e}(0)}}\right)^{\alpha_B},
+B(r) = B_{0} \,\left(\frac{n_{\rmn{e}}(r)}{n_{\rmn{e}}(0)}\right)^{\alpha_B},
 \end{equation}
@@
 \begin{center}
-%\scalebox{1.0}{\plotone{f4.eps}}
+\scalebox{1.0}{\plotone{f4.eps}}
 \end{center}

### 2011-09-08 ms.tex
Updates to the DM section

--- 2011-09-07 ms.tex
@@
 
-The gamma-ray flux due to self-annihilations of WIMPs is given by 
+The expected gamma-ray flux due to self-annihilations of WIMPs is given by 
 \begin{equation}
-\frac{dN(\Delta\Omega)}{dE}=\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\left[\frac{dN(E,m_{\chi})}{dE}\right]\int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
+\frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\frac{dN(E,m_{\chi})}{dE} J(\Delta\Omega),
 \label{eqn:WIMPflux}
 \end{equation}
-where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, $\rho$ is the DM mass density, and $\lambda$ is the line-of-sight distance to the integration volume.
+where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends on the DM distribution.
 
-The two integrals in Eq. (\ref{eqn:WIMPflux}) results in a dimensionless factor representing the astrophysical contribution to the flux
+Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\ \mathrm{CL})$, we can place constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$.
+From Eq.
+(\ref{eqn:WIMPflux}) we get
+\begin{equation}
+\expval{\sigma v}(95\%\ \mathrm{CL}) > R_{\gamma}(95\%\ \mathrm{CL}) \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\frac{1}{\int^{m_{\chi}} dE A_{\mathrm{eff}}dN_{\gamma}/dE}
+\end{equation}
+
+The astrophysical factor $J$ can be expressed as
 \begin{equation}
@@
 \end{equation}
-which here has been normalized to the square of the critical density, $\rho_{c}$, and the Hubble radius, $R_{H}$.
+where $\lambda$ represents the line-of-sight.
+Because the self-annihilation of a WIMP is a two-body process, $J(\Delta\Omega)$ is proportional to the square of the DM density $\rho$.
+Here, $J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the Hubble radius, $R_{H}$.
+Because
 
-Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\mathrm{CL})$, we can place constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$.
+In this work we have adopted the DM density profile by Navarro-Frenk-White \citep[NFW;][]{article:NavarroFrenkWhite:1997},
+\begin{equation}
+\rho_{\chi}(r)=\rho_{s}\left(\frac{r}{r_{s}}\right)^{-1}\left(1+\frac{r}{r_{s}}\right)^{-2},
+\end{equation} 
+which parameterizes the distribution of DM by the scale radius $r_{s}$ and the scale density $\rho_{s}$. [how where these calculated?]
 
@@
 \tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background region (ring method) and is used to estimate the level of gamma-ray contamination from DM.}
+\label{table:astrofactor}
 \end{deluxetable}
@@
 & 0.2 & 650 & $9.1\times 10^{-22}$ \\
-& 0.4 & 660 & $1.8\times 10^{-21}$ \\
+& 0.4 & 660 & $1.8\times 10^{-21}$
 \enddata
-\tablecomments{Limits are for different integration regions and DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
+\tablecomments{Upper limits are for different integration regions and DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
+\label{table:DMlimits}
 \end{deluxetable}

### 2011-09-08 ms.tex
B_min proceedure revised, simulation-model adopted to Fermi constraints, text changes propagated

--- 2011-09-07 ms.tex
@@
 Given a density profile as, e.g., inferred by cosmological simulations or X-ray observations, the analytic approach models the CR distribution and the associated radiative emission processes from radio to the gamma-ray band.
-This formalism was derived from high resolution simulations of clusters of galaxies that included radiative hydrodynamics, star formation, supernova feedback, and followed CR physics by tracing the most important injection and loss processes self-consistently while accounting for the CR pressure in the equation of motion \citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007, article:JubelgasSpringelEnsslinPfrommer:2008}.
+This formalism was derived from high-resolution simulations of clusters of galaxies that included radiative hydrodynamics, star formation, supernova feedback, and followed CR physics by tracing the most important injection and loss processes self-consistently while accounting for the CR pressure in the equation of motion \citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007, article:JubelgasSpringelEnsslinPfrommer:2008}.
 The results are in line with earlier numerical results on some of the overall characteristics of the CR distribution and the associated radiative emission processes \citep{article:DolagEnsslin, article:MiniatiRyuKangJones:2001, article:Miniati:2003, article:Pfrommer_etal:2007, article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008}.
@@
 
-We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster galaxies.
-Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius.
-In our further analysis, we use the gamma-ray flux limits of {\em Fermi} in the energy interval of 1--3 GeV which are most constraining as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.
+We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray
+observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral
+distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the
+contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma,
+normalized to the total flux within the virial radius (dotted lines) and the angular apertures tested in
+this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval of 1--3 GeV
+($<0.4^\circ$) is most constraining. However, since the model flux within the finite energy range of
+1--3 GeV is smaller by a factor of 1.5, it falls below the flux upper limits and does not yet
+constrain the simulation model.  In our further analysis, we use the most constraining {\em Fermi}
+flux limits in the energy interval of 1--3 GeV as well as the gamma-ray flux limits of VERITAS in
+the energy range above 220 GeV.
 
-Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster center (dashed red lines) and contained within $R$ (dashed blue lines).
-To compute the CR pressure, we assume a low-momentum cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which reflects the high cooling rates at low CR energies.
-The relative CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the peripheral strong accretion shocks compared to weak central flow shocks.
-Adiabatic compression of a mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on account of the softer equation of state of CRs.
-The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas which diminishes the thermal support relative to that in CRs.
+Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} =
+\expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster
+center (red lines) and contained within $R$ (blue lines).  We normalize the radii by the virial
+radius, $R_\rmn{vir}$, that we define as the radius of a sphere enclosing a mean density that is 200
+times the critical density of the Universe.  To compute the CR pressure, we assume a low-momentum
+cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which
+reflects the high cooling rates at low CR energies. The relative CR pressure rises toward the outer
+regions on account of the higher efficiency of CR acceleration at the peripheral strong accretion
+shocks compared to weak central flow shocks. Adiabatic compression of a mixture of CRs and thermal
+gas disfavours the CR pressure relative to the thermal pressure on account of the softer equation of
+state of CRs. The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal
+cooling of gas which diminishes the thermal support relative to that in CRs.
 
-Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest.
-For the most constraining regions tested (within an aperture of radius 0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at energies $E=200$ GeV).
-Hence we scale the averaged relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of $X_{\CR}<0.091$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of $X_\CR<0.13$ (solid lines of Figure \ref{fig:xcr}).
-
-[Anders: add and discuss Fermi limits on XCR]
+Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest. In
+the case of VERITAS, for the most constraining regions tested (within an aperture of radius
+0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table
+\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at
+energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by that factor,
+keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
+$X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of
+$X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}). Equivalently, the most constraining {\em Fermi}
+upper limit in the energy interval of 1--3 GeV ($<0.4^\circ$) is a factor of 1.1 larger than our
+model predictions (assuming $\alpha=2.1$ which is very close to the simulated spectral index for the
+energy range of 1--3 GeV). Scaling our integrated relative CR pressure profile yields the
+constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a limit within the cluster
+virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}).
 
 \subsection{Simplified analytical model}
-To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}.
-To be independent of additional assumptions and in line with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$.
-Since a priori, the CR spectral index is unconstrained, we vary it within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$.
-This spectral range is compatible with the radio spectral index of the giant radio halo of Coma after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and
-  are $\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.
-Table \ref{table:constraints} shows the resulting constraints on $X_\CR$.
-The VERITAS flux upper limits strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies.
-The limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5).
-The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of 0.4$^{\circ}$.
-The best limit on $X_\CR$ of 0.017 is achieved for $\alpha=2.3$.
+To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical
+work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR
+spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}. To be
+independent of additional assumptions and in line with earlier work in the literature, we do not
+impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$. Since a priori,
+the CR spectral index is unconstrained, we vary it within plausible ranges of
+$2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the radio spectral index of the
+giant radio halo of Coma after accounting for the spectral steepening at frequencies
+$\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
+\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
+  responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
+  times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. Table
+\ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS flux upper limits
+strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate
+the CR pressure) to TeV-energies. The limits within 0.2$^{\circ}$ are most constraining yielding
+limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with a
+constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the simulations
+around 220 GeV). This limit is more constraining by 50\% in comparison to the model derived from
+simulations, which gives $X_\CR<0.15$. This difference is explained by the concave curvature of the
+simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure
+power-law spectrum of $\alpha=2.3$.
 
-%This is more constraining by 50\% in comparison to the model derived from simulations.
-(in comparison to a power law spectrum with $\alpha_\rmn{TeV} \sim 2.2$ down to a cutoff in the normalized momentum of 0.8)
+The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of
+0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly
+worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.  This is comparable to the $X_\CR$-constraint
+in our simulation-based model of $X_\CR<0.024$ (evaluated within the cluster virial
+radius). Naturally, with the Fermi limits we probe the region around GeV-energies that dominate the
+CR pressure and we do not expect any differences in comparison to the simulation-based models on account
+of the concave curvature of the universal CR spectrum found in the simulations.
 
@@
 \label{sec:B}
-We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B>B_\rmn{CMB}$.
-Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assuming the validity of the hadronic model \citep{article:PfrommerEnsslin:2004a}.
+We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B\gg B_\rmn{CMB}$.
+Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assumes the validity of the hadronic model \citep{article:PfrommerEnsslin:2004a}.
 Lowering the gamma-ray constraint will tighten (increase) the magnetic field limit.
@@
 \begin{enumerate}
-\item Given a model for the magnetic field, we determine the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced CR electrons exactly matches the observed radio halo emission over the entire extent.
-To this end, we de-project the fit to the surface brightness profile (using an Abel integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio emissivity,
+\item Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we
+  determine the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced
+  synchrotron emission exactly matches the observed radio halo emission over the entire extent. To
+  this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel integral
+  equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio emissivity,
   \begin{equation}
@@
   \end{equation}
-where $\mathcal{B}$ denotes the beta function.
-It is generically true for weak magnetic fields ($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$ has to increase by a factor of about 100 toward the radio halo periphery to account for the observed extent.
-If we were to adopt a steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative CR pressure would have to rise accordingly by a factor of 100.
+  where $\mathcal{B}$ denotes the beta function. It is generically true for weak magnetic fields
+  ($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$
+  (where $X_B$ denotes the magnetic-to-thermal energy density) has to increase by a factor of about
+  100 toward the radio halo periphery to account for the observed extent. If we were to adopt a
+  steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative
+  CR pressure would have to rise accordingly by a factor of 100.
 
-\item Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness profile, integrate the flux within a radius of $(0.13, 0.2, 0.4)$ degree, and scale the CR profile in order to match the corresponding VERITAS/{\em Fermi} upper limits.
-This scaling factor, $X_{\CR,0}$, depends on the CR spectral index, $\alpha$, (assuming a power-law CR population for simplicity) and the radial decline of the magnetic field, $\alpha_{B}$.
+\item Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness
+  profile, integrate the flux within a radius of $(0.13, 0.2, 0.4)$ degree, and scale the CR profile
+  in order to match the corresponding VERITAS/{\em Fermi} flux upper limits. This scaling factor,
+  $X_{\CR,0}$, depends on the CR spectral index, $\alpha$, (assuming a power-law CR population for
+  simplicity), the radial decline of the magnetic field, $\alpha_{B}$, and our initial guess for
+  $B_0$.
 
-\item In the last step, we solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron profile while fixing the profile of $X_{\CR}(r)$ as determined through the previous two steps.
-Note that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution would be degenerate.
+\item We then solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron
+  profile while fixing the profile of $X_{\CR}(r)$ as determined through the previous two
+  steps. Note that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the
+  solution would be degenerate.
+
+\item Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
+  $B_\rmn{CMB}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as a
+  function of magnetic field strength. Hence we have to iterate through the previous steps until our
+  solution for the minimum magnetic field $B_0$ is converged.
 \end{enumerate}
 
-Table~\ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range for the VERITAS limits from $B_{0} = 0.4$ to $1.2\,\mu$G and for the {\em Fermi} limits from $B_{0} = 1$ to $7\,\mu$G.
-Since these lower limits on $B_0$ are below the values favored by Faraday RM for most of the parameter space spanned by $\alpha_B$ and $\alpha$, the hadronic model is still viable.
-The only exception is the parameter combination of $\alpha_B=0.7$ and $\alpha=2.5$ which starts to be in (weak) tension with Faraday RM data.
-This indicates the power of future gamma-ray observations of Coma in constraining parameters of the hadronic model.
+Table~\ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range
+for the VERITAS limits from $B_{0} = 0.5$ to $1.4\,\mu$G and for the {\em Fermi} limits from $B_{0}
+= 1.1$ to $4.6\,\mu$G.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the
+  Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits on
+$B_0$ are below the values favored by Faraday RM for the entire parameter space spanned by
+$\alpha_B$ and $\alpha$, the hadronic model is perfectly viable.  This indicates the power of future
+gamma-ray observations of Coma in constraining parameters of the hadronic model.
 
-In addition there are a few interesting remarks in order.
-(1) For the VERITAS limits, the hardest CR spectral indices correspond to the tightest limits on $B_0$.
-This is because for an upper limit of CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting electrons.
-In order to reproduce the observed synchrotron emission, this allows for smaller magnetic fields.
-The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a pivot point of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100 GeV and hence decreases the radio-emitting secondary electrons.
-Equivalently larger magnetic fields are needed to compensate this in order to match the observed synchrotron flux.
-(2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining.
-This implies tighter lower limits for $B_{0}$.
-However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions with vorticity injection at corrugated structure formation shocks \citep{article:PfrommerJones:2011}.
-(3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic field configurations.
-This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the
-constraints on $B_{0}$ get better for the larger integration area.
-Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.
+In addition there are a few interesting remarks in order. (1) For the VERITAS limits, the hardest CR
+spectral indices correspond to the tightest limits on $B_0$. This is because for an upper limit of
+CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a
+comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting
+electrons. In order to reproduce the observed synchrotron emission, this allows for smaller magnetic
+fields. The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a
+pivot point of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100
+GeV and hence decreases the radio-emitting secondary electrons. Equivalently larger magnetic fields
+are needed to compensate for this in order to match the observed synchrotron flux.  (2) For a
+steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match
+the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper
+limits are more constraining. This implies tighter lower limits for $B_{0}$.  (3) Interestingly, in
+all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of
+magnetic field configurations.  This is because we need a substantially increasing relative CR
+pressure profile to match the observed radio profiles (for a given magnetic realization); hence that
+CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR
+model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more
+constraining in the case of VERITAS; hence the constraints on $B_{0}$ get better for the larger
+integration area. Physically, this may be achieved by considering CR transport processes such as
+streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in
+the outer cluster regions.
 
-As a final word, we note that the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo emission ($< 1$ Mpc) when assuming a central magnetic field of $B_{0}=3\,\mu$G that is at the lower 2-$\sigma$ interval bound inferred from Faraday RM \citep{article:Bonafede_etal:2010}.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the Coma cluster to a relative magnetic energy density of $\tilde{X}_B=0.005$.} Typical values at 1 Mpc range from $X_{\CR} = 0.02$ ($\alpha_{B}=0.3$, $\alpha=2.1$) to $X_{\CR} = 1$ ($\alpha_{B}=0.7$, $\alpha=2.5$).\footnote{See Figure 3 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in this study.} We caution, however, that the minimum-energy condition is violated at the outer radio halo boundary for the range of minimum
-magnetic-field values inferred by this study.
+As a final word, in Table~\ref{table:Bmin} we additionally show the
+corresponding values for the relative CR pressure (at the largest emission
+radius at 1~Mpc) such that the model reproduces the observed radio surface
+brightness profile. They should be interpreted as upper limits since they are
+derived from flux upper limits. For the {\em Fermi} upper limits, they range
+from 0.1 to 0.4; hence the $X_{\CR}$-profiles always obey the energy condition,
+i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo
+emission ($< 1$ Mpc).\footnote{See Figure 3 in
+  \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming
+  minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7
+  for a parametrization as adopted in this study.  We caution, however, that
+the minimum-energy condition is violated at the outer radio halo boundary for
+the range of minimum magnetic-field values inferred by this study.} The
+corresponding values for $X_\CR$ in the cluster center are smaller than 0.01 for
+the entire parameter space probed in this study. We conclude that the hadronic
+model is not challenged by current Faraday RM data and a perfectly viable
+possibility in explaining the Coma radio halo emission.
 
@@
 \section{Discussion and Conclusions}
-VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
+VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008. [{\em add flux limits}]
 
-We employed various approaches to constrain the CR population and magnetic field distribution that are complementary in their assumptions and hence well suited in assessing underlying Bayesian priors in the models.
-(1) We use a simplified ``isobaric CR model'' that is characterized by a constant CR-to-thermal pressure fraction and has a power-law momentum spectrum.
-While this model is physically not justified a priory, it is simple and widely used in the literature and captures some aspects of more elaborate models such as (2) the simulation-based analytical approach of \citet{article:PinzkePfrommer:2010}.
-This is a ``first principle approach'' that predicts the CR distribution for a given set of assumptions (namely the physics that was simulated).
-It is powerful since it only requires the density profile as input due to the approximate universality of the CR distribution (when neglecting CR diffusion and streaming which appears, however, necessary to explain the radio halo bimodality).
-(3) We finally use a pragmatic approach which models the CR and magnetic distribution such as to reproduce the observed emission profile of the Coma radio halo.
-While this approach is also physically not justified, it is powerful as it shows what the ``correct'' model has to achieve and can point into the direction of the relevant physics.
+We employed various approaches to constrain the CR population and magnetic field distribution that
+are complementary in their assumptions and hence well suited in assessing underlying Bayesian priors
+in the models. (1) We use a simplified ``isobaric CR model'' that is characterized by a constant
+CR-to-thermal pressure fraction and has a power-law momentum spectrum.  While this model is
+physically not justified a priory, it is simple and widely used in the literature and captures some
+aspects of more elaborate models such as (2) the simulation-based analytical approach of
+\citet{article:PinzkePfrommer:2010}. This is a ``first principle approach'' that predicts the CR
+distribution spectrally and spatially for a given set of assumptions (namely the physics that was
+simulated). It is powerful since it only requires the density profile as input due to the
+approximate universality of the CR distribution (when neglecting CR diffusion and streaming which
+appears, however, necessary to explain the radio halo bimodality). (3) We finally use a pragmatic
+approach which models the CR and magnetic distribution such as to reproduce the observed emission
+profile of the Coma radio halo. While this approach is also physically not justified, it is powerful
+as it shows what the ``correct'' model has to achieve and can point into the direction of the
+relevant physics.
 
-Within this pragmatic approach we employ two different directions.
-First, adopting a high magnetic field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining flux upper limits of {\em Fermi} (VERITAS).
-Second, by matching the radio emission profile (i.e., fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR distribution) we obtain lower limits on the magnetic field distribution under consideration.
-Our limits of the central magnetic field range from $B_{0} = 0.4$ to $1.2\,\mu$G (for VERITAS gamma-ray flux limits) and from $B_{0} = 1$ to $7\,\mu$G (for {\em Fermi} gamma-ray flux limits).
-Since these lower limits on $B_0$ are below the values favored by Faraday RM, the hadronic model is still viable.
+Within this pragmatic approach we employ two different directions. First, adopting a high magnetic
+field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the
+hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining
+flux upper limits of {\em Fermi} (VERITAS). Second, by matching the radio emission profile (i.e.,
+fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay
+gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR
+distribution) we obtain lower limits on the magnetic field distribution under consideration. Our
+limits of the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS 
+flux limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for {\em Fermi} flux limits). Since
+all these lower limits on $B_0$ are below the values favored by Faraday RM, $B_{0} =
+4.7^{+0.7}_{-0.8}\,\mu$G \citep{article:Bonafede_etal:2010}, the hadronic model is a very attractive
+explanation of the Coma radio halo.
 
-Using the most constraining VERITAS limits, we can constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray spectral index, $\alpha$, varying between 2.1 and 2.5).
-The best {\em Fermi} flux limit constrains $X_\CR$ to be below 0.017 (for $\alpha=2.3$), only weakly depending on the assumed CR spectral index.
+Applying our simplified ``isobaric CR model'' to the most constraining VERITAS limits, we can
+constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray
+spectral index, $\alpha$, varying between 2.1 and 2.5). We obtain a constraint of $X_\CR<0.1$ for
+$\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit is
+more constraining by a factor of 1.5 in comparison to the simulation-based model which gives
+$X_\CR<0.15$.  This difference is due to the concave curvature of the simulated spectrum which
+accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of
+$\alpha=2.3$.
+
+The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying between
+2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$ which is
+very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain an almost
+coincident constraint with our simulation-based model within the virial radius of
+$X_\CR<0.024$. That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$
+corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc. These are encouraging
+results in that we constrain the CR pressure (of a phase that is fully mixed with the ICM) to be at
+most a small fraction of the overall pressure, $<0.025$. As a result, hydrostatic cluster masses and
+the total Comptonization parameter due to the Sunyaev-Zel'dovich effect attain at most a very small
+bias due to CRs.
 
@@
 \end{center}
-\caption{Integral flux upper limits (this work, Table X) compared with simulated integrated spectra of VHE gamma-ray emission from the Coma cluster.}
+\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi})
+  for different integration radii (shown with different colors), assuming $\alpha=2.1$. These are
+  compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma
+  F_\gamma(>E_\gamma)$, from the Coma cluster (again within different apertures). Note that the {\em
+    Fermi} limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most
+  constraining. Since the model flux within the finite energy range of 1--3 GeV is smaller by a
+  factor of 1.5, it falls below the flux upper limits and does not yet constrain the simulation
+  model.}
 \label{fig:spectrum}
@@
 \end{center}
-\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a function of radial distance from the center of the Coma cluster.
-Model predictions are shown by dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining VERITAS upper limits within 0.2$^\circ$ (solid).
-We compare differential $X_\CR$-profiles (red) to integrated profiles $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (blue) which we use to compare to the upper limits.}
+\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/
+  \expval{P_{\mathrm{th}}}$, as a function of radial distance from the center of
+  the Coma. Model predictions are shown by dashed lines
+  \citep{article:PinzkePfrommer:2010} while these are scaled to match the most
+  constraining VERITAS upper limits within 0.2$^\circ$ (solid) and {\em Fermi}
+  upper limits within 0.4$^\circ$ (dashed). We compare differential
+  $X_\CR$-profiles (red) to integrated profiles
+  $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$
+  (blue) which we use to compare to the upper limits.}
 \label{fig:xcr}
@@
 \hline
-0    & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
+0    & 0.52  & 1.9  & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
 0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
@@
 \cutinhead{{\em Fermi} constraints:}
-0    & -    & -    & 5.2 & 3.5 & 4.7 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
-0.2  & 3.1  & 2.9  & 3.5 & 2.4 & 3.1 & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
-0.4  & 4.7  & 4.4  & 2.5 & 1.7 & 2.3 &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
+0    & 2.2  & 1.4  & 5.2 & 3.5 & 4.7 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
+0.2  & 3.4  & 2.1  & 3.5 & 2.4 & 3.1 & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
+0.4  & 5.2  & 3.2  & 2.5 & 1.7 & 2.3 &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
 \enddata
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo}
+\tablecaption{Constraints on magnetic fields in the hadronic model of
+    the Coma radio halo and the corresponding relative CR pressure (at
+    the largest emission radius) such that the model reproduces the observed
+    radio surface brightness profile.}
 \tablehead{
  &
-\multicolumn{6}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
+\multicolumn{6}{c}{Minimum magnetic field, $B_{0,\rmn{min}}~[\mu\rmn{G}]$:}\\
  & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{{\em Fermi} constraints:} \\
@@
 \startdata
-0.3 & 0.61 & 0.51 & 0.43 & 1.02 & 1.48 & 2.13 \\
-0.5 & 0.82 & 0.68 & 0.58 & 1.40 & 2.11 & 3.24 \\
-0.7 & 1.19 & 0.98 & 0.83 & 2.11 & 3.51 & 6.91 
+0.3 & 0.69 & 0.57 & 0.48 & 1.14 & 1.63 & 2.25 \\
+0.5 & 0.97 & 0.80 & 0.68 & 1.60 & 2.28 & 3.17 \\
+0.7 & 1.40 & 1.17 & 0.99 & 2.32 & 3.32 & 4.61 \\
+\hline
+& \multicolumn{6}{c}{Corresponding $X_{\CR,\rmn{max}}\, (1\,\rmn{Mpc})$:}\\ 
+\hline
+0.3 & 0.46 & 1.05 & ~~4.55 & 0.17 & 0.11 & 0.15 \\
+0.5 & 0.74 & 1.70 & ~~7.47 & 0.27 & 0.18 & 0.25 \\
+0.7 & 1.09 & 2.59 &  11.55 & 0.41 & 0.28 & 0.37 \\
 \enddata

### 2011-09-09 ms.tex
Updates to the DM section

@@
 Comparing X-ray and optical potential profiles in the centers of galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas pressure \citep{article:Churazov_etal:2008, article:Churazov_etal:2010}.
-An analysis that compares spatially resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the
-mean density is 500 times the critical density -- suggesting again a substantial non-thermal pressure contribution on large scales \citep{article:Mahdavi_etal:2008}.
-High-energy gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that is most sensitive
-to the cluster core region.
+An analysis that compares spatially resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the mean density is 500 times the critical density -- suggesting again a substantial non-thermal pressure contribution on large scales \citep{article:Mahdavi_etal:2008}.
+High-energy gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that is most sensitive to the cluster core region.
 However, it assumes that the CR component is fully mixed with the ICM and almost insensitive in detecting a two-phase structure of CRs and the thermal ICM.
-A fraction $X_\CR$ of only a few percent is required in order to produce a gamma-ray flux observable with current generation
-gamma-ray telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method (which are however more general in that they are sensitive to any non-thermal pressure component).
+A fraction $X_\CR$ of only a few percent is required in order to produce a gamma-ray flux observable with current generation gamma-ray telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method (which are however more general in that they are sensitive to any non-thermal pressure component).
 
 Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example CMB photons, on ultra-relativistic leptons.
-Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster
-members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.
+Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.
 
@@
 
-Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} =
-\expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster
-center (red lines) and contained within $R$ (blue lines).  We normalize the radii by the virial
-radius, $R_\rmn{vir}$, that we define as the radius of a sphere enclosing a mean density that is 200
-times the critical density of the Universe.  To compute the CR pressure, we assume a low-momentum
-cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which
-reflects the high cooling rates at low CR energies. The relative CR pressure rises toward the outer
-regions on account of the higher efficiency of CR acceleration at the peripheral strong accretion
-shocks compared to weak central flow shocks. Adiabatic compression of a mixture of CRs and thermal
-gas disfavours the CR pressure relative to the thermal pressure on account of the softer equation of
-state of CRs. The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal
-cooling of gas which diminishes the thermal support relative to that in CRs.
+Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster center (red lines) and contained within $R$ (blue lines).
+We normalize the radii by the virial radius, $R_\rmn{vir}$, that we define as the radius of a sphere enclosing a mean density that is 200 times the critical density of the Universe.
+To compute the CR pressure, we assume a low-momentum cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which reflects the high cooling rates at low CR energies.
+The relative CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the peripheral strong accretion shocks compared to weak central flow shocks.
+Adiabatic compression of a mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on account of the softer equation of state of CRs.
+The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas which diminishes the thermal support relative to that in CRs.
 
@@
 \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at
-energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by that factor,
-keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
+energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
 $X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of
@@
 
-Table~\ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range
-for the VERITAS limits from $B_{0} = 0.5$ to $1.4\,\mu$G and for the {\em Fermi} limits from $B_{0}
-= 1.1$ to $4.6\,\mu$G.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the
-  Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits on
-$B_0$ are below the values favored by Faraday RM for the entire parameter space spanned by
-$\alpha_B$ and $\alpha$, the hadronic model is perfectly viable.  This indicates the power of future
-gamma-ray observations of Coma in constraining parameters of the hadronic model.
+Table \ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range for the VERITAS limits from $B_{0} = 0.5$ to $1.4\,\mu$G and for the {\em Fermi} limits from $B_{0} = 1.1$ to $4.6\,\mu$G.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits on $B_0$ are below the values favored by Faraday RM for the entire parameter space spanned by $\alpha_B$ and $\alpha$, the hadronic model is perfectly viable.
+This indicates the power of future gamma-ray observations of Coma in constraining parameters of the hadronic model.
 
-In addition there are a few interesting remarks in order. (1) For the VERITAS limits, the hardest CR
-spectral indices correspond to the tightest limits on $B_0$. This is because for an upper limit of
-CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a
-comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting
-electrons. In order to reproduce the observed synchrotron emission, this allows for smaller magnetic
-fields. The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a
-pivot point of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100
-GeV and hence decreases the radio-emitting secondary electrons. Equivalently larger magnetic fields
-are needed to compensate for this in order to match the observed synchrotron flux.  (2) For a
-steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match
-the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper
-limits are more constraining. This implies tighter lower limits for $B_{0}$.  (3) Interestingly, in
-all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of
-magnetic field configurations.  This is because we need a substantially increasing relative CR
-pressure profile to match the observed radio profiles (for a given magnetic realization); hence that
-CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR
-model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more
-constraining in the case of VERITAS; hence the constraints on $B_{0}$ get better for the larger
-integration area. Physically, this may be achieved by considering CR transport processes such as
-streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in
-the outer cluster regions.
+In addition there are a few interesting remarks in order.
+(1) For the VERITAS limits, the hardest CR spectral indices correspond to the tightest limits on $B_0$.
+This is because for an upper limit of CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting electrons.
+In order to reproduce the observed synchrotron emission, this allows for smaller magnetic fields.
+The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a pivot point of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100 GeV and hence decreases the radio-emitting secondary electrons.
+Equivalently larger magnetic fields are needed to compensate for this in order to match the observed synchrotron flux.
+(2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining.
+This implies tighter lower limits for $B_{0}$.
+(3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of
+magnetic field configurations.
+This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining in the case of VERITAS; hence the constraints on $B_{0}$ get better for the larger integration area.
+Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.
 
-As a final word, in Table~\ref{table:Bmin} we additionally show the
-corresponding values for the relative CR pressure (at the largest emission
-radius at 1~Mpc) such that the model reproduces the observed radio surface
-brightness profile. They should be interpreted as upper limits since they are
-derived from flux upper limits. For the {\em Fermi} upper limits, they range
-from 0.1 to 0.4; hence the $X_{\CR}$-profiles always obey the energy condition,
-i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo
-emission ($< 1$ Mpc).\footnote{See Figure 3 in
-  \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming
-  minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7
-  for a parametrization as adopted in this study.  We caution, however, that
-the minimum-energy condition is violated at the outer radio halo boundary for
-the range of minimum magnetic-field values inferred by this study.} The
-corresponding values for $X_\CR$ in the cluster center are smaller than 0.01 for
-the entire parameter space probed in this study. We conclude that the hadronic
-model is not challenged by current Faraday RM data and a perfectly viable
-possibility in explaining the Coma radio halo emission.
+As a final word, in Table~\ref{table:Bmin} we additionally show the corresponding values for the relative CR pressure (at the largest emission radius at 1~Mpc) such that the model reproduces the observed radio surface brightness profile.
+They should be interpreted as upper limits since they are derived from flux upper limits.
+For the {\em Fermi} upper limits, they range from 0.1 to 0.4; hence the $X_{\CR}$-profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo
+emission ($< 1$ Mpc).\footnote{See Figure 3 in   \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7
+  for a parametrization as adopted in this study.
+We caution, however, that the minimum-energy condition is violated at the outer radio halo boundary for the range of minimum magnetic-field values inferred by this study.} The corresponding values for $X_\CR$ in the cluster center are smaller than 0.01 for the entire parameter space probed in this study.
+We conclude that the hadronic model is not challenged by current Faraday RM data and a perfectly viable possibility in explaining the Coma radio halo emission.
 
 \section{Emission from Dark Matter Annihilations}
-When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated background.
+As already mentioned in the introduction, most of the mass in a galaxy cluster is in the form of DM.
+While the nature of this DM remains unknown, the most compelling theoretical candidate is a WIMP.
+The self-annihilations of WIMPs are expected to produce a flux of secondary gamma rays with a spectral signature that deviates significantly from the power-law spectrum observed in most conventional astrophysical sources.
+The spectrum will also feature a very sharp cutoff at the WIMP mass.
+Observations of these spectral features together with the expected difference in spatial distribution of the gamma-ray flux compared to conventional astrophysical sources allows for a unique means to indirectly detect DM.
+
+The expected gamma-ray flux due to self-annihilations of WIMPs is given by 
+\begin{equation}
+\frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\frac{dN(E,m_{\chi})}{dE} J(\Delta\Omega),
+\label{eqn:WIMPflux}
+\end{equation}
+where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends on the DM distribution.
+
+Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\ \mathrm{CL})$, we can place constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$.
+From Eq.
+(\ref{eqn:WIMPflux}) we get
+\begin{equation}
+\expval{\sigma v}(95\%\ \mathrm{CL}) > R_{\gamma}(95\%\ \mathrm{CL}) \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\frac{1}{\int^{m_{\chi}} dE A_{\mathrm{eff}}dN_{\gamma}/dE}
+\end{equation}
+The astrophysical factor $J$ can be expressed as
+\begin{equation}
+J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right) \int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
+\end{equation}
+where $\lambda$ represents the line-of-sight.
+Because the self-annihilation of a WIMP is a two-body process, $J(\Delta\Omega)$ is proportional to the square of the DM density $\rho$.
+Here, $J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the Hubble radius, $R_{H}$.
+
+In this work we have adopted the DM density profile by Navarro-Frenk-White \citep[NFW;][]{article:NavarroFrenkWhite:1997},
+\begin{equation}
+\rho_{\chi}(r)=\rho_{s}\left(\frac{r}{r_{s}}\right)^{-1}\left(1+\frac{r}{r_{s}}\right)^{-2},
+\end{equation} 
+which parameterizes the distribution of DM by the scale radius $r_{s}$ and the scale density $\rho_{s}$. [how where these calculated?]
+
+%When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated background.
 For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor no longer compensate for the increased count of background events and the signal-to-noise deteriorates.
@@
 \section{Discussion and Conclusions}
-VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008. [{\em add flux limits}]
+VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
+No significant excess of gamma-rays above a threshold of about 220 GeV was detected.
+Flux upper limits at 99\% confidence level were calculated for the cluster core and three member galaxies.
+The core was considered both as a point-like and spatialy extended source.
+The obtained flux upper limits were used to constrain properties of the cluster.
 
-We employed various approaches to constrain the CR population and magnetic field distribution that
-are complementary in their assumptions and hence well suited in assessing underlying Bayesian priors
-in the models. (1) We use a simplified ``isobaric CR model'' that is characterized by a constant
-CR-to-thermal pressure fraction and has a power-law momentum spectrum.  While this model is
-physically not justified a priory, it is simple and widely used in the literature and captures some
-aspects of more elaborate models such as (2) the simulation-based analytical approach of
-\citet{article:PinzkePfrommer:2010}. This is a ``first principle approach'' that predicts the CR
-distribution spectrally and spatially for a given set of assumptions (namely the physics that was
-simulated). It is powerful since it only requires the density profile as input due to the
-approximate universality of the CR distribution (when neglecting CR diffusion and streaming which
-appears, however, necessary to explain the radio halo bimodality). (3) We finally use a pragmatic
-approach which models the CR and magnetic distribution such as to reproduce the observed emission
-profile of the Coma radio halo. While this approach is also physically not justified, it is powerful
-as it shows what the ``correct'' model has to achieve and can point into the direction of the
-relevant physics.
+We employed various approaches to constrain the CR population and magnetic field distribution that are complementary in their assumptions and hence well suited in assessing underlying Bayesian priors in the models.
+(1) We use a simplified ``isobaric CR model'' that is characterized by a constant CR-to-thermal pressure fraction and has a power-law momentum spectrum.
+While this model is physically not justified a priory, it is simple and widely used in the literature and captures some aspects of more elaborate models such as (2) the simulation-based analytical approach of \citet{article:PinzkePfrommer:2010}.
+This is a ``first principle approach'' that predicts the CR distribution spectrally and spatially for a given set of assumptions (namely the physics that was simulated).
+It is powerful since it only requires the density profile as input due to the approximate universality of the CR distribution (when neglecting CR diffusion and streaming which appears, however, necessary to explain the radio halo bimodality).
+(3) We finally use a pragmatic approach which models the CR and magnetic distribution such as to reproduce the observed emission profile of the Coma radio halo.
+While this approach is also physically not justified, it is powerful
+as it shows what the ``correct'' model has to achieve and can point into the direction of the relevant physics.
 
-Within this pragmatic approach we employ two different directions. First, adopting a high magnetic
-field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the
-hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining
-flux upper limits of {\em Fermi} (VERITAS). Second, by matching the radio emission profile (i.e.,
-fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay
-gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR
-distribution) we obtain lower limits on the magnetic field distribution under consideration. Our
-limits of the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS 
-flux limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for {\em Fermi} flux limits). Since
-all these lower limits on $B_0$ are below the values favored by Faraday RM, $B_{0} =
-4.7^{+0.7}_{-0.8}\,\mu$G \citep{article:Bonafede_etal:2010}, the hadronic model is a very attractive
-explanation of the Coma radio halo.
+Within this pragmatic approach we employ two different directions.
+First, adopting a high magnetic field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining flux upper limits of {\em Fermi} (VERITAS).
+Second, by matching the radio emission profile (i.e., fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR distribution) we obtain lower limits on the magnetic field distribution under consideration.
+Our limits of the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS  flux limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for {\em Fermi} flux limits).
+Since all these lower limits on $B_0$ are below the values favored by Faraday RM, $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G \citep{article:Bonafede_etal:2010}, the hadronic model is a very attractive explanation of the Coma radio halo.
 
-Applying our simplified ``isobaric CR model'' to the most constraining VERITAS limits, we can
-constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray
-spectral index, $\alpha$, varying between 2.1 and 2.5). We obtain a constraint of $X_\CR<0.1$ for
-$\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit is
-more constraining by a factor of 1.5 in comparison to the simulation-based model which gives
-$X_\CR<0.15$.  This difference is due to the concave curvature of the simulated spectrum which
-accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of
-$\alpha=2.3$.
+Applying our simplified ``isobaric CR model'' to the most constraining VERITAS limits, we can constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray spectral index, $\alpha$, varying between 2.1 and 2.5).
+We obtain a constraint of $X_\CR<0.1$ for $\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.
+This limit is more constraining by a factor of 1.5 in comparison to the simulation-based model which gives $X_\CR<0.15$.
+This difference is due to the concave curvature of the simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
 
-The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying between
-2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$ which is
-very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain an almost
-coincident constraint with our simulation-based model within the virial radius of
-$X_\CR<0.024$. That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$
-corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc. These are encouraging
-results in that we constrain the CR pressure (of a phase that is fully mixed with the ICM) to be at
-most a small fraction of the overall pressure, $<0.025$. As a result, hydrostatic cluster masses and
-the total Comptonization parameter due to the Sunyaev-Zel'dovich effect attain at most a very small
-bias due to CRs.
+The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying between 2.3 and 2.1), only weakly depending on the assumed CR spectral index.
+Assuming $\alpha=2.1$ which is very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain an almost coincident constraint with our simulation-based model within the virial radius of $X_\CR<0.024$.
+That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$ corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc.
+These are encouraging results in that we constrain the CR pressure (of a phase that is fully mixed with the ICM) to be at most a small fraction of the overall pressure, $<0.025$.
+As a result, hydrostatic cluster masses and the total Comptonization parameter due to the Sunyaev-Zel'dovich effect attain at most a very small bias due to CRs.
 

### 2011-09-09 ms.tex
spell-checked and typos fixed

@@
 
-We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray
-observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral
-distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the
-contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma,
-normalized to the total flux within the virial radius (dotted lines) and the angular apertures tested in
-this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval of 1--3 GeV
-($<0.4^\circ$) is most constraining. However, since the model flux within the finite energy range of
-1--3 GeV is smaller by a factor of 1.5, it falls below the flux upper limits and does not yet
-constrain the simulation model.  In our further analysis, we use the most constraining {\em Fermi}
-flux limits in the energy interval of 1--3 GeV as well as the gamma-ray flux limits of VERITAS in
-the energy range above 220 GeV.
+We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster galaxies.
+Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius (dotted lines) and the angular apertures tested in this study (solid lines).
+The gamma-ray flux limit of {\em Fermi} in the energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining.
+However, since the model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.
+In our further analysis, we use the most constraining {\em Fermi} flux limits in the energy interval of 1--3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.
 
@@
 \end{equation} 
-which parameterizes the distribution of DM by the scale radius $r_{s}$ and the scale density $\rho_{s}$. [how where these calculated?]
+which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density $\rho_{s}$. [how where these calculated?]
 
@@
 Flux upper limits at 99\% confidence level were calculated for the cluster core and three member galaxies.
-The core was considered both as a point-like and spatialy extended source.
+The core was considered both as a point-like and spatially extended source.
 The obtained flux upper limits were used to constrain properties of the cluster.
@@
 \end{center}
-\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi})
-  for different integration radii (shown with different colors), assuming $\alpha=2.1$. These are
-  compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma
-  F_\gamma(>E_\gamma)$, from the Coma cluster (again within different apertures). Note that the {\em
-    Fermi} limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most
-  constraining. Since the model flux within the finite energy range of 1--3 GeV is smaller by a
-  factor of 1.5, it falls below the flux upper limits and does not yet constrain the simulation
-  model.}
+\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii (shown with different colors), assuming $\alpha=2.1$.
+These are compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma F_\gamma(>E_\gamma)$, from the Coma cluster (again within different apertures).
+Note that the {\em Fermi} limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.
+Since the model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.}
 \label{fig:spectrum}
 \end{figure*}
+
+is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.
 
@@
 \end{center}
-\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/
-  \expval{P_{\mathrm{th}}}$, as a function of radial distance from the center of
-  the Coma. Model predictions are shown by dashed lines
-  \citep{article:PinzkePfrommer:2010} while these are scaled to match the most
-  constraining VERITAS upper limits within 0.2$^\circ$ (solid) and {\em Fermi}
-  upper limits within 0.4$^\circ$ (dashed). We compare differential
-  $X_\CR$-profiles (red) to integrated profiles
-  $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$
-  (blue) which we use to compare to the upper limits.}
+\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a function of radial distance from the center of the Coma.
+Model predictions are shown by dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining VERITAS upper limits within 0.2$^\circ$ (solid) and {\em Fermi} upper limits within 0.4$^\circ$ (dashed).
+We compare differential $X_\CR$-profiles (red) to integrated profiles $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (blue) which we use to compare to the upper limits.}
 \label{fig:xcr}

### 2011-09-09 ms.tex
Line breaks added

@@
 \begin{abstract}
-Theoretical models of galaxy clusters suggest they may be sources of very high-energy (VHE) gamma-ray emission.
-Observations of radio halos and relics in clusters indicate populations of relativistic electrons, which are either injected into the intra-cluster medium and accelerated by turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with the intra-cluster gas.
-Those interactions could also produce gamma rays through the decay of neutral pions.
-Reported here are observations of the Coma cluster of galaxies with the VERITAS array of imaging Cherenkov telescopes.
-The observations were made between March and May 2008.
-Radio observations at 1.41 GHz taken with the Green Bank Telescope and X-ray observations with the ROSAT All-Sky survey was used to a priori select regions of interest in the field of view.
-No significant VHE gamma-ray emission from the Coma cluster was detected by VERITAS.
-Several emission regions are considered, including the cluster core as both unresolved (point-like) and spatially extended, and a select few cluster members.
-The flux upper limits at the 99\% confidence level measured are on the order of $2-5\times 10^{-8}$ ph.
-m$^{-2}$ s$^{-1}$, which is two orders of magnitude higher than model-predicted minimum gamma-ray fluxes.
+Theoretical models of galaxy clusters suggest they may be sources of very high-energy (VHE)
+gamma-ray emission. Observations of radio halos and relics in clusters indicate populations of
+relativistic electrons, which are either injected into the intra-cluster medium and accelerated by
+turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with
+the intra-cluster gas. Those interactions could also produce gamma rays through the decay of
+neutral pions. Reported here are observations of the Coma cluster of galaxies with the VERITAS
+array of imaging Cherenkov telescopes. The observations were made between March and May
+2008. Radio observations at 1.41 GHz taken with the Green Bank Telescope and X-ray observations
+with the ROSAT All-Sky survey was used to a priori select regions of interest in the field of view.
+No significant VHE gamma-ray emission from the Coma cluster was detected by VERITAS. Several
+emission regions are considered, including the cluster core as both unresolved (point-like) and
+spatially extended, and a select few cluster members. The flux upper limits at the 99\% confidence
+level measured are on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$ s$^{-1}$, which is two orders
+of magnitude higher than model-predicted minimum gamma-ray fluxes.
 
-The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles and magnetic fields and in the Coma cluster of galaxies.
-The relative cosmic-ray pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$, is on the order of 10-20\% when assuming a gamma-ray photon index $\alpha=2.3$.
-The observations imply a lower limit on the intra-cluster magnetic field on the order of a $\mu$G, depending on the magnetic decline and gamma-ray spectral index.
-Finally, a constraint on the thermally averaged product of the total self-annihilation cross section and the relative velocity of the dark-matter particles, $\expval{\sigma v}$, is derived and found to be $\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
+The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles
+and magnetic fields and in the Coma cluster of galaxies. The relative cosmic-ray pressure,
+$X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$, is on the order of 10-20\% when assuming
+a gamma-ray photon index $\alpha=2.3$. The observations imply a lower limit on the intra-cluster
+magnetic field on the order of a $\mu$G, depending on the magnetic decline and gamma-ray spectral
+index. Finally, a constraint on the thermally averaged product of the total self-annihilation
+cross section and the relative velocity of the dark-matter particles, $\expval{\sigma v}$,
+is derived and found to be $\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$
+GeV/c$^{2}$.
 \end{abstract}
@@
 
+%
+%
+
 \section{Introduction}
-Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of a few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$.
-According to the currently favored hierarchical model of cosmic structure formation, larger objects formed through successive mergers of smaller
-objects with galaxy clusters sitting a top this mass hierarchy \citep[see][for a review]{article:Voit:2005}.
-Most of the mass of a cluster is in form of dark matter (DM), as indicated by galaxy dynamics and gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}.
-Baryonic gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass and individual galaxies account for the remainder (about 5\%).
-The ICM gas mass also comprises a significant fraction of the observable (baryonic) matter in the Universe.
+Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of
+a few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. According to the currently
+favored hierarchical model of cosmic structure formation, larger objects formed through successive
+mergers of smaller objects with galaxy clusters sitting a top this mass hierarchy
+\citep[see][for a review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark
+matter (DM), as indicated by galaxy dynamics and gravitational lensing
+\citep{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the intra-cluster medium (ICM)
+contributes about 15\% of the total cluster mass and individual galaxies account for the remainder
+(about 5\%). The ICM gas mass also comprises a significant fraction of the observable (baryonic)
+matter in the Universe.
 
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}.
-This plasma has been heated to these temperatures primarily through collisionless structure-formation shocks that form as a result of the hierarchical merging and accretion processes.
-Such shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
-provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}.
-Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}.
-Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
-\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters, although the interpretation of these
-observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009, article:Ajello_etal:2010, article:Wik_etal:2009}.
+The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft
+X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these
+temperatures primarily through collisionless structure-formation shocks that form as a result of
+the hierarchical merging and accretion processes. Such shocks and turbulence in the ICM gas and
+intra-cluster magnetic fields also provide a means to efficiently accelerate particles
+\citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do
+indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of
+relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM
+\citep{article:Cassano_etal:2010}. Recent observations of possible non-thermal emission from
+clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
+\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may
+provide further indications of relativistic particle populations in clusters, although the
+interpretation of these observations as non-thermal diffuse emission have been disputed on the
+basis of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
+article:Ajello_etal:2010, article:Wik_etal:2009}.
 
-Galaxy clusters have for many years been proposed as sources of gamma rays.
-If shock acceleration in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected.
-The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM.
-Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to gamma rays.
-Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume filling magnetic fields in the ICM, CR hadrons will be confined in the cluster on timescales comparable and longer than the Hubble time \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.
-Depending on the CR pressure, quantified by the CR-to-thermal pressure fraction $X_\CR=\expval{P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.
+Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration
+in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons,
+in the form of protons and heavy ions, in the ICM is to be expected. The main energy-loss
+mechanism for CR hadrons at high energies is pion production through the interaction of CRs with
+nuclei in the ICM. Pions are short lived and decay; the charged pions to electrons and positrons,
+\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or
+positron as well as neutrinos.} and the neutral pion to gamma rays. Due to the low density of the
+ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume
+filling magnetic fields in the ICM, CR hadrons will be confined in the cluster on timescales
+comparable and longer than the Hubble time \citep[][]{article:Volk_etal:1996,
+article:Berezinsky_etal:1997} allowing them to accumulate over time. Depending on the CR pressure,
+quantified by the CR-to-thermal pressure fraction
+$X_\CR=\expval{P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma rays
+can be expected.
 
-Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as well as the temperature decrement of the cosmic microwave background (CMB) in the direction of a galaxy cluster due to the Sunyaev-Zel'dovich effect which is proportional to the line-of-sight integral of the thermal electron pressure.
-This could then severely jeopardize the use of clusters to determine cosmological parameters.
-Comparing X-ray and optical potential profiles in the centers of galaxy clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas pressure \citep{article:Churazov_etal:2008, article:Churazov_etal:2010}.
-An analysis that compares spatially resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ -- within which the mean density is 500 times the critical density -- suggesting again a substantial non-thermal pressure contribution on large scales \citep{article:Mahdavi_etal:2008}.
-High-energy gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that is most sensitive to the cluster core region.
-However, it assumes that the CR component is fully mixed with the ICM and almost insensitive in detecting a two-phase structure of CRs and the thermal ICM.
-A fraction $X_\CR$ of only a few percent is required in order to produce a gamma-ray flux observable with current generation gamma-ray telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method (which are however more general in that they are sensitive to any non-thermal pressure component).
+Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as well as the
+temperature decrement of the cosmic microwave background (CMB) in the direction of a galaxy cluster
+due to the Sunyaev-Zel'dovich effect which is proportional to the line-of-sight integral of the
+thermal electron pressure. This could then severely jeopardize the use of clusters to determine
+cosmological parameters. Comparing X-ray and optical potential profiles in the centers of galaxy
+clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs,
+magnetic fields or turbulence) relative to the thermal gas pressure
+\citep{article:Churazov_etal:2008, article:Churazov_etal:2010}. An analysis that compares spatially
+resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters
+detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ --
+within which the mean density is 500 times the critical density -- suggesting again a substantial
+non-thermal pressure contribution on large scales \citep{article:Mahdavi_etal:2008}. High-energy
+gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that
+is most sensitive to the cluster core region. However, it assumes that the CR component is fully
+mixed with the ICM and almost insensitive in detecting a two-phase structure of CRs and the thermal
+ICM.  A fraction $X_\CR$ of only a few percent is required in order to produce a gamma-ray flux
+observable with current generation gamma-ray telescopes rendering this technique at least as
+sensitive as the dynamical and hydrostatic method (which are however more general in that they are
+sensitive to any non-thermal pressure component).
 
-Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example CMB photons, on ultra-relativistic leptons.
-Those leptons can either be secondaries from the above mentioned CR interactions or be injected into the ICM by powerful cluster members and be further accelerated by diffusive shock acceleration or turbulent reacceleration processes.
+Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example
+CMB photons, on ultra-relativistic leptons. Those leptons can either be secondaries from the above
+mentioned CR interactions or be injected into the ICM by powerful cluster members and be further
+accelerated by diffusive shock acceleration or turbulent reacceleration processes.
 
-A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM particle, e.g.
-a weakly interacting massive particle (WIMP).
-As already mentioned, about 80\% of the cluster mass is in the form of dark matter.
-Recent works \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is expected to be proportional to the square of the DM density integrated along the line of sight, making clusters of galaxies potentially good
-candidates for DM searches \citep{article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011}.
-This despite their large distances compared to other common targets for DM searches, such as dwarf spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006, article:Aharonian_etal:2009b}.
+A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM
+particle, e.g. a weakly interacting massive particle (WIMP). As already mentioned, about 80\% of
+the cluster mass is in the form of dark matter. Recent works \citep{article:EvansFerrerSarkar:2004,
+article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is
+expected to be proportional to the square of the DM density integrated along the line of sight,
+making clusters of galaxies potentially good candidates for DM searches
+\citep{article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011}. This despite their large
+distances compared to other common targets for DM searches, such as dwarf spheroidal galaxies
+\citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009} or the
+Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
+article:Aharonian_etal:2009b}.
 
-While several observations of clusters of galaxies have been made with satellite-borne and ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
-Observations with EGRET
-\citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several galaxy clusters in the 100 MeV to GeV
-band.
-Upper limits on the VHE gamma-ray flux from a few select clusters, including the Coma cluster, have been provided by observations with ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
+While several observations of clusters of galaxies have been made with satellite-borne and
+ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
+Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi
+Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the
+gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several
+galaxy clusters in the 100 MeV to GeV band. Upper limits on the VHE gamma-ray flux from a few
+select clusters, including the Coma cluster, have been provided by observations with ground-based
+imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006,
+inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
 
-The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters over all wavelengths \citep{article:Voges_etal:1999}.
-Located at a distance of about 100 Mpc \citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest massive clusters \citep[$M \sim10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}.
-It hosts both a giant radio halo
-\citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic, which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion in][]{article:BrownRudnick:2010}.
-It has been suggested that the relic is an infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations that model the non-thermal emission processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}.
-Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$ of the total intracluster medium pressure \citep{article:Schuecker_etal:2004}.
-As such it is a natural candidate for gamma-ray observations.
+The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters over all
+wavelengths \citep{article:Voges_etal:1999}. Located at a distance of about 100 Mpc
+\citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest massive clusters
+\citep[$M \sim10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}. It hosts both a
+giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral
+radio relic, which appears connected to the radio halo with a ``diffuse'' bridge 
+\citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested that the relic is an
+infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological
+simulations that model the non-thermal emission processes
+\citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009,
+article:Skillman_etal:2011}. Extended soft thermal X-ray (SXR) emission is evident from the ROSAT
+all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations
+with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with
+substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$ of the total
+intracluster medium pressure \citep{article:Schuecker_etal:2004}. As such it is a natural candidate
+for gamma-ray observations.
 
-In this article, results from the VERITAS observations of the Coma cluster of galaxies are reported, with complementing analysis of available data from the Fermi Gamma-ray Space Telescope.
-The VERITAS and Fermi data have been used to place constraints on cosmic-ray particle populations, magnetic fields, and dark matter in the cluster.
-Throughout the analyses, a present day Hubble constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
+In this article, results from the VERITAS observations of the Coma cluster of galaxies are
+reported, with complementing analysis of available data from the Fermi Gamma-ray Space Telescope.
+The VERITAS and Fermi data have been used to place constraints on cosmic-ray particle populations,
+magnetic fields, and dark matter in the cluster. Throughout the analyses, a present day Hubble
+constant of $H_{0} = 100h$ km s$^{-1}$ Mpc$^{-1}$ with $h=0.7$ has been used.
+
+%
+%
 
 \section{VERITAS Observations and Analysis}
-The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an altitude of 1268 m a.s.l.
-at the Fred Lawrence Whipple Observatory in southern Arizona (31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W).
-Each of the telescopes is equipped with a 499 pixel camera covering a 3.5$^{\circ}$ field of view.
-The array, completed in the spring of 2007, is designed to detect gamma-ray emission from astrophysical objects in the energy range from 100 GeV to more than 30 TeV.
-The energy resolution is about 15\% and the angular resolution (68\% containment) is about 0.1$^{\circ}$ per event at 1 TeV.
-The sensitivity of the array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009.
-The move had no impact on the this data set.}
+The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter
+imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an
+altitude of 1268 m a.s.l. at the Fred Lawrence Whipple Observatory in southern Arizona
+(31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes
+is equipped with a 499 pixel camera covering a 3.5$^{\circ}$ field of view. The array, completed in
+the spring of 2007, is designed to detect gamma-ray emission from astrophysical objects in the
+energy range from 100 GeV to more than 30 TeV. The energy resolution is about 15\% and the angular
+resolution (68\% containment) is about 0.1$^{\circ}$ per event at 1 TeV. The sensitivity of the
+array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux
+above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity
+above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009. The
+move had no impact on the this data set.}
 
-The Coma cluster was observed with VERITAS between March and May in 2008 with all four telescopes fully operational.
-The total exposure amounts to 18.6 hours of quality-selected live time, i.e.
-time periods of astronomical darkness, clear sky conditions and without technical problems with the array.
-The center of the cluster was tracked in \emph{wobble} mode, where the expected source location is offset from the center of the field of view, to allow for simultaneous background estimation \citep{article:Formin_etal:1994}.
-All of the observations were made in a small range of zenith angles averaging $\sim 21^{\circ}$.
+The Coma cluster was observed with VERITAS between March and May in 2008 with all four telescopes
+fully operational. The total exposure amounts to 18.6 hours of quality-selected live time, i.e.
+time periods of astronomical darkness, clear sky conditions and without technical problems with the
+array. The center of the cluster was tracked in \emph{wobble} mode, where the expected source
+location is offset from the center of the field of view, to allow for simultaneous background
+estimation \citep{article:Formin_etal:1994}. All of the observations were made in a small range of
+zenith angles averaging $\sim 21^{\circ}$.
 
-The data analysis was performed following the standard VERITAS procedures described in \citet{inproc:Cogan_etal:2007} and \citet{inproc:Daniel_etal:2007}.
-Prior to event reconstruction and selection, all shower images are calibrated and cleaned.
-Showers are then reconstructed for events with at least two contributing telescope images that pass the following quality selection criteria: more than four participating pixels in the camera, number of photoelectrons in the image is larger than 75, and the distance from the image centroid to the center of the camera is less than $1.43^{\circ}$.
-These quality selection criteria impose an energy threshold\footnote{Defined as the energy corresponding to the maximum of the product function of the observed spectrum with the collection area} of about 220 GeV.
-In addition, events for which only images from the two closest-spaced telescopes\footnote{In the array configuration prior to summer 2009, two telescopes had a separation of only 35 m.} survive quality selection are rejected, as they introduce an irreducible high background rate, due to local muons, degrading the instrument sensitivity \citep{article:MaierKnapp:2007}.
+The data analysis was performed following the standard VERITAS procedures described in
+\citet{inproc:Cogan_etal:2007} and \citet{inproc:Daniel_etal:2007}. Prior to event reconstruction
+and selection, all shower images are calibrated and cleaned. Showers are then reconstructed for
+events with at least two contributing telescope images that pass the following quality selection
+criteria: more than four participating pixels in the camera, number of photoelectrons in the image
+is larger than 75, and the distance from the image centroid to the center of the camera is less
+than $1.43^{\circ}$. These quality selection criteria impose an energy threshold\footnote{Defined
+as the energy corresponding to the maximum of the product function of the observed spectrum with
+the collection area} of about 220 GeV. In addition, events for which only images from the two
+closest-spaced telescopes\footnote{In the array configuration prior to summer 2009, two telescopes 
+had a separation of only 35 m.} survive quality selection are rejected, as they introduce an
+irreducible high background rate, due to local muons, degrading the instrument sensitivity
+\citep{article:MaierKnapp:2007}.
 
-Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters \citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parametrized moment analysis of the shower images \citep{inproc:Hillas:1985}.
-The gamma-hadron separation cuts used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level) and a photon index of -2.4 using data taken on the Crab Nebula during the same epoch and are termed \emph{standard} cuts.
-Because the VHE gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about -2.3, these standard cuts are suitable for the analysis of the Coma cluster data set.
+Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters
+\citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parametrized
+moment analysis of the shower images \citep{inproc:Hillas:1985}. The gamma-hadron separation cuts
+used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level)
+and a photon index of -2.4 using data taken on the Crab Nebula during the same epoch and are termed
+\emph{standard} cuts. Because the VHE gamma-ray spectrum for the Coma cluster is expected to be
+hard, photon index of about -2.3, these standard cuts are suitable for the analysis of the Coma
+cluster data set.
 
-The Coma cluster is a very rich cluster of galaxies with many plausible sites for gamma-ray emission: the core region, the peripheral radio relic, as well as individual powerful cluster member galaxies.
-VERITAS has a large enough field of view to allow investigation of several of these scenarios.
-In this work the focus has been on the core region and three cluster members.
-The latter are treated as point sources in the analysis, whereas the core is treated as both a point source and a mildly extended source.
-The intrinsic source extension is assumed to be $0.2^{\circ}$ and $0.4^{\circ}$, based on the extension of the thermal soft X-ray emission from the core.
-There is evidence of a recent merger event between the two central galaxies NGC 4889 and NGC 4874 \citep{article:Tribble:1993}.
-There is also evidence for an excess of non-thermal X-ray emission from these galaxies as well as the galaxy NGC 4921 \citep{article:Neumann_etal:2003}.
-Therefore, searches for point-like VHE gamma-ray emission have been conducted at the locations of these galaxies.
-The regions of interest considered in this work are summarized in Table \ref{table:roi}.
+The Coma cluster is a very rich cluster of galaxies with many plausible sites for gamma-ray
+emission: the core region, the peripheral radio relic, as well as individual powerful cluster
+member galaxies. VERITAS has a large enough field of view to allow investigation of several of
+these scenarios. In this work the focus has been on the core region and three cluster members. The
+latter are treated as point sources in the analysis, whereas the core is treated as both a point
+source and a mildly extended source. The intrinsic source extension is assumed to be $0.2^{\circ}$
+and $0.4^{\circ}$, based on the extension of the thermal soft X-ray emission from the core. There
+is evidence of a recent merger event between the two central galaxies NGC 4889 and NGC 4874
+\citep{article:Tribble:1993}. There is also evidence for an excess of non-thermal X-ray emission
+from these galaxies as well as the galaxy NGC 4921 \citep{article:Neumann_etal:2003}. Therefore,
+searches for point-like VHE gamma-ray emission have been conducted at the locations of these
+galaxies. The regions of interest considered in this work are summarized in Table \ref{table:roi}.
 
-The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs misinterpreted as gamma rays (the cuts described above reject more than 99\% of all CRs).
-The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess.
-The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.
-Significance skymaps over the VERITAS field of view produced with a $0.2^{\circ}$ sampling radius are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.
+The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background
+due to CRs misinterpreted as gamma rays (the cuts described above reject more than 99\% of all
+CRs). The total number of events in a given region of interest is then compared to the estimated
+background from the off-source region scaled by the ratio of the solid angles to produce a final
+excess. The VHE gamma-ray significance is then calculated using the method by
+\citet{article:LiMa:1983}. Significance skymaps over the VERITAS field of view produced with a
+$0.2^{\circ}$ sampling radius are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio
+contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz
+observations \citep{article:BrownRudnick:2010} respectively.
+
+%
+%
 
 \section{VERITAS Results}
-No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as illustrated by the $\theta^{2}$ distribution shown in Figure \ref{fig:thetasq}.
-The $\theta^{2}$ distribution is a radial comparison of the ON-source event distribution with the estimated background.
-It extends out to a radius of $0.42^{\circ}$ to cover all regions of interest considered in this work.
-A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke_etal:2005} assuming a Gaussian background.
-A lower bound of zero is imposed on the signal rate to handle the negative excesses seen for several of the regions of interest.
-Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent of unity.
+No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as
+illustrated by the $\theta^{2}$ distribution shown in Figure \ref{fig:thetasq}. The $\theta^{2}$
+distribution is a radial comparison of the ON-source event distribution with the estimated
+background. It extends out to a radius of $0.42^{\circ}$ to cover all regions of interest
+considered in this work. A 99\% confidence level upper limit is calculated for each region of
+interest using the method described by \citet{article:Rolke_etal:2005} assuming a Gaussian
+background. A lower bound of zero is imposed on the signal rate to handle the negative excesses
+seen for several of the regions of interest. Figure \ref{fig:sigdist} shows that the VERITAS data
+is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent
+of unity.
 
-Table \ref{table:results} lists the upper limits for the selected regions of interest tabulated in Table \ref{table:roi}.
-These upper-limit calculations depend on the gamma-ray spectrum, which in this work is assumed to be a power law with a spectral index $\alpha=2.1, 2.3$, and $2.5$.
+Table \ref{table:results} lists the upper limits for the selected regions of interest tabulated in
+Table \ref{table:roi}. These upper-limit calculations depend on the gamma-ray spectrum, which in
+this work is assumed to be a power law with a spectral index $\alpha=2.1, 2.3$, and $2.5$.
+
+%
+%
 
 \section{Fermi-LAT Analysis and Results}
-The Large Area Telescope (LAT) on board the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi}) has observed the Coma cluster in all-sky survey mode since its launch in June 2008.
-The \emph{Fermi}-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus very complimentary to the VERITAS observations.
-\citet{article:Ackermann_etal:2010} reported on the search for gamma-ray emission from thirty-three galaxy clusters in the data from the first 18 months, including the Coma cluster, for which an upper limit of $4.58\times 10^{-9}$ ph.
-cm$^{-2}$ s$^{-1}$ in the 0.2 to 100 GeV energy band was reported.
-This limit is expected to improve as the exposure is increased.
-In this work an updated analysis which includes additional data taken during the period 2010 February 5 to 2011 June 10 is presented as a compliment to the VERITAS results.
+The Large Area Telescope (LAT) on board the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi})
+has observed the Coma cluster in all-sky survey mode since its launch in June 2008. The
+\emph{Fermi}-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus
+very complimentary to the VERITAS observations. \citet{article:Ackermann_etal:2010} reported on the
+search for gamma-ray emission from thirty-three galaxy clusters in the data from the first 18
+months, including the Coma cluster, for which an upper limit of $4.58\times 10^{-9}$ ph. cm$^{-2}$
+s$^{-1}$ in the 0.2 to 100 GeV energy band was reported. This limit is expected to improve as the
+exposure is increased. In this work an updated analysis which includes additional data taken during
+the period 2010 February 5 to 2011 June 10 is presented as a compliment to the VERITAS results.
 
-The analysis of this work follows the same procedure as described in detail in \citet{article:Abdo_etal:2009}.
-To eliminate albedo gamma rays from the Earth limb, a zenith angle cut of 105$^{\circ}$ is applied.
-The \emph{Fermi} Science Tools version v9r23p1 and Instrumental Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events calibrated  in flight) were used throughout this work.
-Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful.
-The \emph{Fermi}-LAT collaboration estimates the systematic uncertainties at 10 GeV to be around 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}.
-The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and $2.5$.
+The analysis of this work follows the same procedure as described in detail in
+\citet{article:Abdo_etal:2009}. To eliminate albedo gamma rays from the Earth limb, a zenith angle
+cut of 105$^{\circ}$ is applied. The \emph{Fermi} Science Tools version v9r23p1 and Instrumental
+Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events
+calibrated  in flight) were used throughout this work. Only photons above 1 GeV are considered,
+where the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates
+the systematic uncertainties at 10 GeV to be around 20\%.
+\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits
+at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like
+or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray emission is
+assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and $2.5$.
+
+%
+%
 
 \section{Gamma Ray Emission from Cosmic Rays}
-We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution in the Coma cluster with the VERITAS and \emph{Fermi}-LAT upper limits from this work.
-This approach includes (1) an analytic model derived from cosmological hydrodynamical simulations of the formation of galaxy clusters, (2) a simplified multi-frequency analytical approach that assumes a constant CR-to-thermal energy density and a power-law spectrum in momentum, and (3) an approach that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray flux in the hadronic model -- independent of the magnetic field distribution.
-This translates into a minimum CR pressure which, if challenged by tight gamma-ray limits/detections, enables scrutinizing the hadronic interaction model of the formation of giant radio halos.
-Modelling the CR distribution through different techniques enable to bracket our ignorance about the underlying plasma
-physics that shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modelling \citep[see][for a discussion]{article:PinzkePfrommerBergstrom}.
+We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution
+in the Coma cluster with the VERITAS and \emph{Fermi}-LAT upper limits from this work. This
+approach includes (1) an analytic model derived from cosmological hydrodynamical simulations of the
+formation of galaxy clusters, (2) a simplified multi-frequency analytical approach that assumes a
+constant CR-to-thermal energy density and a power-law spectrum in momentum, and (3) an approach
+that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on the
+expected $\gamma$-ray flux in the hadronic model -- independent of the magnetic field distribution.
+This translates into a minimum CR pressure which, if challenged by tight gamma-ray
+limits/detections, enables scrutinizing the hadronic interaction model of the formation of giant
+radio halos. Modelling the CR distribution through different techniques enable to bracket our
+ignorance about the underlying plasma physics that shape the CR distribution and hence reflect the
+Bayesian priors that are imposed on the modelling
+\citep[see][for a discussion]{article:PinzkePfrommerBergstrom}.
+
+%
+%
 
 \subsection{Simulation-based approach}
-We adopt the universal spectral and spatial gamma-ray model developed by \citet{article:PinzkePfrommer:2010} to estimate the emission from decaying neutral pions that dominates over the IC emission from primary and secondary electrons above 100 MeV in clusters.
-Given a density profile as, e.g., inferred by cosmological simulations or X-ray observations, the analytic approach models the CR distribution and the associated radiative emission processes from radio to the gamma-ray band.
-This formalism was derived from high-resolution simulations of clusters of galaxies that included radiative hydrodynamics, star formation, supernova feedback, and followed CR physics by tracing the most important injection and loss processes self-consistently while accounting for the CR pressure in the equation of motion \citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007, article:JubelgasSpringelEnsslinPfrommer:2008}.
-The results are in line with earlier numerical results on some of the overall characteristics of the CR distribution and the associated radiative emission processes \citep{article:DolagEnsslin, article:MiniatiRyuKangJones:2001, article:Miniati:2003, article:Pfrommer_etal:2007, article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008}.
+We adopt the universal spectral and spatial gamma-ray model developed by
+\citet{article:PinzkePfrommer:2010} to estimate the emission from decaying neutral pions that
+dominates over the IC emission from primary and secondary electrons above 100 MeV in clusters.
+Given a density profile as, e.g., inferred by cosmological simulations or X-ray observations, the
+analytic approach models the CR distribution and the associated radiative emission processes from
+radio to the gamma-ray band. This formalism was derived from high-resolution simulations of
+clusters of galaxies that included radiative hydrodynamics, star formation, supernova feedback, and
+followed CR physics by tracing the most important injection and loss processes self-consistently
+while accounting for the CR pressure in the equation of motion
+\citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007,
+article:JubelgasSpringelEnsslinPfrommer:2008}. The results are in line with earlier numerical
+results on some of the overall characteristics of the CR distribution and the associated radiative
+emission processes \citep{article:DolagEnsslin, article:MiniatiRyuKangJones:2001,
+article:Miniati:2003, article:Pfrommer_etal:2007, article:PfrommerEnsslinSpringel:2008,
+article:Pfrommer:2008}.
 
-The overall normalization of the CR and gamma-ray distribution scales with the maximum acceleration efficiency at structure formation shock waves.
-Following recent observations at supernova remnants \citep{article:Helder_etal:2009} as well as theoretical studies \citep{article:KangJones:2005}, we adopt an optimistic but nevertheless realistic value of this parameter and assume that 50\% of the dissipated energy at strong shocks is injected into CRs while this efficiency rapidly decreases for weaker shocks.
-Since the vast majority of internal formation shocks (merger and flow shocks) are weak shocks with Mach numbers $M\lesssim3$ \citep[e.g.,][]{article:Ryu_etal:2003}, they do not significantly contribute to the CR population in clusters.
-Instead, strong shocks during the formation epoch of clusters and strong accretion shocks at the present time (at the boundary of voids and filaments/super-cluster regions) dominate the injection of CRs which are adiabatically transported through the cluster.
-Hence, these model predictions provide a plausible upper limit for the CR contribution from structure formation shocks in galaxy clusters which can be scaled with the effective acceleration efficiency.
-Other possible CR sources, such as AGN and starburst-driven galactic winds have been neglected for simplicity which could in principle increase the expected gamma-ray yield.
+The overall normalization of the CR and gamma-ray distribution scales with the maximum acceleration
+efficiency at structure formation shock waves. Following recent observations at supernova remnants
+\citep{article:Helder_etal:2009} as well as theoretical studies \citep{article:KangJones:2005}, we
+adopt an optimistic but nevertheless realistic value of this parameter and assume that 50\% of the
+dissipated energy at strong shocks is injected into CRs while this efficiency rapidly decreases for
+weaker shocks. Since the vast majority of internal formation shocks (merger and flow shocks) are
+weak shocks with Mach numbers $M\lesssim3$ \citep[e.g.,][]{article:Ryu_etal:2003}, they do not
+significantly contribute to the CR population in clusters. Instead, strong shocks during the
+formation epoch of clusters and strong accretion shocks at the present time (at the boundary of
+voids and filaments/super-cluster regions) dominate the injection of CRs which are adiabatically
+transported through the cluster. Hence, these model predictions provide a plausible upper limit for
+the CR contribution from structure formation shocks in galaxy clusters which can be scaled with the
+effective acceleration efficiency. Other possible CR sources, such as AGN and starburst-driven
+galactic winds have been neglected for simplicity which could in principle increase the expected
+gamma-ray yield.
 
-These cosmological simulations only considered advective transport of CRs by turbulent gas motions which produces centrally enhanced profiles.
-However, other means of CR transport such as diffusion and streaming may flatten the CR radial profiles.
-It has been suggested that advection is dominant only during mergers, in which case relaxed clusters could have a reduced gamma-ray luminosity by up to a factor of five compared with merging clusters \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}.
-The goal of this and other future work of seeking for gamma-ray emission from clusters is to constrain the acceleration physics and transport properties of CRs.
+These cosmological simulations only considered advective transport of CRs by turbulent gas motions
+which produces centrally enhanced profiles.  However, other means of CR transport such as diffusion
+and streaming may flatten the CR radial profiles. It has been suggested that advection is dominant
+only during mergers, in which case relaxed clusters could have a reduced gamma-ray luminosity by up
+to a factor of five compared with merging clusters
+\citep{article:EnsslinPfrommerMiniatiSubramanian:2011}. The goal of this and other future work of
+seeking for gamma-ray emission from clusters is to constrain the acceleration physics and transport
+properties of CRs.
 
-We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster galaxies.
-Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius (dotted lines) and the angular apertures tested in this study (solid lines).
-The gamma-ray flux limit of {\em Fermi} in the energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining.
-However, since the model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.
-In our further analysis, we use the most constraining {\em Fermi} flux limits in the energy interval of 1--3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.
+We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray
+observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral
+distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the
+contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma,
+normalized to the total flux within the virial radius (dotted lines) and the angular apertures
+tested in this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval
+of 1--3 GeV ($<0.4^\circ$) is most constraining. However, since the model flux within the finite
+energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV,
+it falls below the flux upper limits which do not yet constrain the simulation model. In our
+further analysis, we use the most constraining {\em Fermi} flux limits in the energy interval of
+1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.
 
-Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster center (red lines) and contained within $R$ (blue lines).
-We normalize the radii by the virial radius, $R_\rmn{vir}$, that we define as the radius of a sphere enclosing a mean density that is 200 times the critical density of the Universe.
-To compute the CR pressure, we assume a low-momentum cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which reflects the high cooling rates at low CR energies.
-The relative CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the peripheral strong accretion shocks compared to weak central flow shocks.
-Adiabatic compression of a mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on account of the softer equation of state of CRs.
-The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas which diminishes the thermal support relative to that in CRs.
+Figure \ref{fig:xcr} shows the relative CR pressure,
+$X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the
+Coma cluster center (red lines) and contained within $R$ (blue lines).  We normalize the radii by
+the virial radius, $R_\rmn{vir}$, that we define as the radius of a sphere enclosing a mean density
+that is 200 times the critical density of the Universe.  To compute the CR pressure, we assume a
+low-momentum cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological
+simulations which reflects the high cooling rates at low CR energies. The relative CR pressure
+rises toward the outer regions on account of the higher efficiency of CR acceleration at the
+peripheral strong accretion shocks compared to weak central flow shocks. Adiabatic compression of a
+mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on
+account of the softer equation of state of CRs. The weak increase of $X_{\CR}$ toward the core is
+due to the comparably fast thermal cooling of gas which diminishes the thermal support relative to
+that in CRs.
 
-Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest. In
-the case of VERITAS, for the most constraining regions tested (within an aperture of radius
+Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest.
+In the case of VERITAS, for the most constraining regions tested (within an aperture of radius
 0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table
-\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at
-energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
-$X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of
-$X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}). Equivalently, the most constraining {\em Fermi}
-upper limit in the energy interval of 1--3 GeV ($<0.4^\circ$) is a factor of 1.1 larger than our
-model predictions (assuming $\alpha=2.1$ which is very close to the simulated spectral index for the
-energy range of 1--3 GeV). Scaling our integrated relative CR pressure profile yields the
-constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a limit within the cluster
-virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}).
+\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one
+at energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by
+that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure
+of $X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius
+of $X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}). Equivalently, the most constraining
+{\em Fermi} upper limit in the energy interval of 1--3 GeV ($<0.4^\circ$) is a factor of 1.1 larger
+than our model predictions (assuming $\alpha=2.1$ which is very close to the simulated spectral
+index for the energy range of 1-3 GeV). Scaling our integrated relative CR pressure profile yields
+the constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a limit within the
+cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}).
+
+%
+%
 
@@
 $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
-\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
-  responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
-  times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. Table
-\ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS flux upper limits
-strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate
-the CR pressure) to TeV-energies. The limits within 0.2$^{\circ}$ are most constraining yielding
-limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with a
-constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the simulations
-around 220 GeV). This limit is more constraining by 50\% in comparison to the model derived from
-simulations, which gives $X_\CR<0.15$. This difference is explained by the concave curvature of the
-simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure
-power-law spectrum of $\alpha=2.3$.
+\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR
+protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are
+$\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.
+Table \ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS flux upper
+limits strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that
+dominate the CR pressure) to TeV-energies. The limits within 0.2$^{\circ}$ are most constraining
+yielding limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with
+a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the
+simulations around 220 GeV). This limit is more constraining by 50\% in comparison to the model
+derived from simulations, which gives $X_\CR<0.15$. This difference is explained by the concave
+curvature of the simulated spectrum which accumulates additional pressure toward GeV energies in
+comparison to a pure power-law spectrum of $\alpha=2.3$.
 
@@
 worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.  This is comparable to the $X_\CR$-constraint
-in our simulation-based model of $X_\CR<0.024$ (evaluated within the cluster virial
-radius). Naturally, with the Fermi limits we probe the region around GeV-energies that dominate the
-CR pressure and we do not expect any differences in comparison to the simulation-based models on account
-of the concave curvature of the universal CR spectrum found in the simulations.
+in our simulation-based model of $X_\CR<0.024$ (evaluated within the cluster virial radius).
+Naturally, with the Fermi limits we probe the region around GeV-energies that dominate the CR
+pressure and we do not expect any differences in comparison to the simulation-based models on
+account of the concave curvature of the universal CR spectrum found in the simulations.
+
+%
+%
 
 \subsection{Minimum gamma-ray flux}
-For clusters that host radio halos we are able to derive a minimum gamma-ray flux in the hadronic model of CR interactions.
-The idea is based on the fact that a stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and thermal gas \citep{article:Voelk:1989, article:Pohl:1994, article:Pfrommer:2008}, in particular with $\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.
-Hence we can derive a minimum gamma-ray flux in the hadronic model
+For clusters that host radio halos we are able to derive a minimum gamma-ray flux in the hadronic
+model of CR interactions. The idea is based on the fact that a stationary distribution of CR
+electrons loses all its energy to synchrotron radiation for strong magnetic fields
+($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the ratio of gamma-ray to synchrotron flux becomes
+independent of the spatial distribution of CRs and thermal gas \citep{article:Voelk:1989,
+article:Pohl:1994, article:Pfrommer:2008}, in particular with $\alpha_{\nu}\simeq 1$ as the
+observed synchrotron spectral index.  Hence we can derive a minimum gamma-ray flux in the hadronic
+model
 \begin{equation}
@@
 \end{equation}
-where $L_{\nu}$ is the observed luminosity of the radio mini-halo, $D_{\rmn{lum}}$ denotes the luminosity distance to the respective cluster, $A_\gamma$ and $A_\nu$ are dimensional constants that depend on the hadronic physics of the interaction \citep{article:Pfrommer:2008, Pfrommer_etal:2008}.
-Lowering the magnetic field would require an increase in the energy density of CR electrons to reproduce the observed synchrotron luminosity and thus increase the associated gamma-ray flux.
+where $L_{\nu}$ is the observed luminosity of the radio mini-halo, $D_{\rmn{lum}}$ denotes the
+luminosity distance to the respective cluster, $A_\gamma$ and $A_\nu$ are dimensional constants
+that depend on the hadronic physics of the interaction \citep{article:Pfrommer:2008,
+Pfrommer_etal:2008}. Lowering the magnetic field would require an increase in the energy density of
+CR electrons to reproduce the observed synchrotron luminosity and thus increase the associated
+gamma-ray flux.
 
-To derive a minimum gamma-ray flux that is comparable to the upper limits, we need to determine the radio flux within the corresponding angular regions.
-To this end, we fit the point-source subtracted, azimuthally averaged radio halo profile at 1.38 GHz \citep{article:Deiss_etal:1997} with a $\beta$-model,
+To derive a minimum gamma-ray flux that is comparable to the upper limits, we need to determine the
+radio flux within the corresponding angular regions. To this end, we fit the point-source
+subtracted, azimuthally averaged radio halo profile at 1.38 GHz \citep{article:Deiss_etal:1997}
+with a $\beta$-model,
 \begin{equation}
@@
 \end{equation}
-where $S_{0} = 1.1 \times 10^{-3}\,\rmn{Jy\,arcmin}^{-2}$, $r_{\rmn{c}} = 450$ kpc, and $\beta = 0.78$.
-Within the error bars, this profile is consistent with 326-MHz data taken by \citet{article:Govoni_etal:2001} when scaled with a radio spectral index of 1.15.
+where $S_{0} = 1.1 \times 10^{-3}\,\rmn{Jy\,arcmin}^{-2}$, $r_{\rmn{c}} = 450$ kpc, and
+$\beta = 0.78$.  Within the error bars, this profile is consistent with 326-MHz data taken by
+\citet{article:Govoni_etal:2001} when scaled with a radio spectral index of 1.15.
 
-The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV})$ and the minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/\tilde{F}$ are shown in Table \ref{table:constraints}, where $F_\rmn{iso} = X_\CR\,\tilde{F}$ is the gamma-ray flux in the {\em isobaric model of CRs} introduced in the previous section.
-Even in the most constraining cases, these are a factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$, $<0.2^{\circ}$) and a factor of about 20 below the {\em Fermi} upper limits (adopting $\alpha=2.3$, $<0.4^{\circ}$).
+The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV})$ and the minimum relative
+CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/\tilde{F}$ are shown in Table
+\ref{table:constraints}, where $F_\rmn{iso} = X_\CR\,\tilde{F}$ is the gamma-ray flux in the {\em
+isobaric model of CRs} introduced in the previous section. Even in the most constraining cases,
+these are a factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$,
+$<0.2^{\circ}$) and a factor of about 20 below the {\em Fermi} upper limits (adopting $\alpha=2.3$,
+$<0.4^{\circ}$).
+
+%
+%
 
@@
 \label{sec:B}
-We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray emission in the hadronic model by assuming high magnetic fields, $B\gg B_\rmn{CMB}$.
-Hence, we can turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio emission which, however, assumes the validity of the hadronic model \citep{article:PfrommerEnsslin:2004a}.
-Lowering the gamma-ray constraint will tighten (increase) the magnetic field limit.
-Once this gets in conflict with magnetic field measurements by means of other methods, e.g., Faraday rotation measure (RM)\footnote{Generally, Faraday RM analysis of the magnetic-field strength by, e.g., background sources through clusters are degenerate with the magnetic coherence scale and may be biased by the unknown correlation between magnetic and density fluctuations.}, this would challenge the hadronic model of radio halos.
-The method that we use to constrain the magnetic field inherits a dependence on the assumed spatial structure that we parametrize by
+We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray
+emission in the hadronic model by assuming high magnetic fields, $B\gg B_\rmn{CMB}$. Hence, we can
+turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR
+pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio
+emission which, however, assumes the validity of the hadronic model
+\citep{article:PfrommerEnsslin:2004a}. Lowering the gamma-ray constraint will tighten (increase)
+the magnetic field limit. Once this gets in conflict with magnetic field measurements by means of
+other methods, e.g., Faraday rotation measure (RM)\footnote{Generally, Faraday RM analysis of the
+magnetic-field strength by, e.g., background sources through clusters are degenerate with the
+magnetic coherence scale and may be biased by the unknown correlation between magnetic and density
+fluctuations.}, this would challenge the hadronic model of radio halos. The method that we use to
+constrain the magnetic field inherits a dependence on the assumed spatial structure that we
+parametrize by
 \begin{equation}
@@
 \end{equation}
-as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD) simulations \citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}.
-In fact, the magnetic field in the Coma cluster is among the best constrained, because its proximity permits RM observations of
-seven radio-sources located at projected distances of 50 to 1500 kpc from the cluster center.
-The best-fit model obtains $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and $\alpha_{B} = 0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}.
-We aim for constraining the central field strength, $B_{0}$, which depends on the magnetic decline, $\alpha_{B}$, that we vary (within reasonable ranges of $\Delta\alpha_{B}=0.2$ as suggested from the Faraday RM studies) to address this dependence.
-We proceed as follows:
+as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD) simulations
+\citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}. In fact,
+the magnetic field in the Coma cluster is among the best constrained, because its proximity permits
+RM observations of seven radio-sources located at projected distances of 50 to 1500 kpc from the
+cluster center. The best-fit model obtains $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and
+$\alpha_{B} = 0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim for constraining the
+central field strength, $B_{0}$, which depends on the magnetic decline, $\alpha_{B}$, that we vary
+(within reasonable ranges of $\Delta\alpha_{B}=0.2$ as suggested from the Faraday RM studies) to
+address this dependence. We proceed as follows:
 
 \begin{enumerate}
-\item Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we
-  determine the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced
+\item
+Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we determine
+the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced
 synchrotron emission exactly matches the observed radio halo emission over the entire extent. To 
-  this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel integral
-  equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio emissivity,
+this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel
+integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio
+emissivity,
+
 \begin{equation}
@@
 100 toward the radio halo periphery to account for the observed extent. If we were to adopt a
-  steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative
-  CR pressure would have to rise accordingly by a factor of 100.
+steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative CR
+pressure would have to rise accordingly by a factor of 100.
 
-\item Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness
+\item
+Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness
 profile, integrate the flux within a radius of $(0.13, 0.2, 0.4)$ degree, and scale the CR profile
@@
 
-\item We then solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron
-  profile while fixing the profile of $X_{\CR}(r)$ as determined through the previous two
-  steps. Note that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the
-  solution would be degenerate.
+\item
+We then solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron
+profile while fixing the profile of $X_{\CR}(r)$ as determined through the previous two steps. Note
+that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution
+would be degenerate.
 
-\item Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
+\item
+Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
 $B_\rmn{CMB}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as a
@@
 
-Table \ref{table:Bmin} shows the results on the lower limit of the central magnetic field that range for the VERITAS limits from $B_{0} = 0.5$ to $1.4\,\mu$G and for the {\em Fermi} limits from $B_{0} = 1.1$ to $4.6\,\mu$G.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits on $B_0$ are below the values favored by Faraday RM for the entire parameter space spanned by $\alpha_B$ and $\alpha$, the hadronic model is perfectly viable.
-This indicates the power of future gamma-ray observations of Coma in constraining parameters of the hadronic model.
+Table \ref{table:Bmin} shows the results on the lower limit of the central magnetic field that
+range for the VERITAS limits from $B_{0} = 0.5$ to $1.4\,\mu$G and for the {\em Fermi} limits from
+$B_{0} = 1.1$ to $4.6\,\mu$G.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds
+in the Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits
+on $B_0$ are below the values favored by Faraday RM for the entire parameter space spanned by
+$\alpha_B$ and $\alpha$, the hadronic model is perfectly viable.  This indicates the power of
+future gamma-ray observations of Coma in constraining parameters of the hadronic model.
 
-In addition there are a few interesting remarks in order.
-(1) For the VERITAS limits, the hardest CR spectral indices correspond to the tightest limits on $B_0$.
-This is because for an upper limit of CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting electrons.
+In addition there are a few interesting remarks in order. (1) For the VERITAS limits, the hardest
+CR spectral indices correspond to the tightest limits on $B_0$. This is because for an upper limit
+of CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a
+comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting electrons.
 In order to reproduce the observed synchrotron emission, this allows for smaller magnetic fields.
-The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a pivot point of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100 GeV and hence decreases the radio-emitting secondary electrons.
-Equivalently larger magnetic fields are needed to compensate for this in order to match the observed synchrotron flux.
-(2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining.
-This implies tighter lower limits for $B_{0}$.
-(3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of
-magnetic field configurations.
-This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining in the case of VERITAS; hence the constraints on $B_{0}$ get better for the larger integration area.
-Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.
+The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a pivot point
+of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100 GeV and
+hence decreases the radio-emitting secondary electrons. Equivalently larger magnetic fields are
+needed to compensate for this in order to match the observed synchrotron flux.  (2) For a steeper
+magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the
+observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits
+are more constraining. This implies tighter lower limits for $B_{0}$.  (3) Interestingly, in all
+cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic
+field configurations.  This is because we need a substantially increasing relative CR pressure
+profile to match the observed radio profiles (for a given magnetic realization); hence that CR
+realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model''
+assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more
+constraining in the case of VERITAS; hence the constraints on $B_{0}$ get better for the larger
+integration area. Physically, this may be achieved by considering CR transport processes such as
+streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in
+the outer cluster regions.
 
-As a final word, in Table~\ref{table:Bmin} we additionally show the corresponding values for the relative CR pressure (at the largest emission radius at 1~Mpc) such that the model reproduces the observed radio surface brightness profile.
-They should be interpreted as upper limits since they are derived from flux upper limits.
-For the {\em Fermi} upper limits, they range from 0.1 to 0.4; hence the $X_{\CR}$-profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$ over the entire range of the radio halo
-emission ($< 1$ Mpc).\footnote{See Figure 3 in   \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7
-  for a parametrization as adopted in this study.
-We caution, however, that the minimum-energy condition is violated at the outer radio halo boundary for the range of minimum magnetic-field values inferred by this study.} The corresponding values for $X_\CR$ in the cluster center are smaller than 0.01 for the entire parameter space probed in this study.
-We conclude that the hadronic model is not challenged by current Faraday RM data and a perfectly viable possibility in explaining the Coma radio halo emission.
+As a final word, in Table~\ref{table:Bmin} we additionally show the corresponding values for the
+relative CR pressure (at the largest emission radius at 1~Mpc) such that the model reproduces the
+observed radio surface brightness profile. They should be interpreted as upper limits since they
+are derived from flux upper limits. For the {\em Fermi} upper limits, they range from 0.1 to 0.4;
+hence the $X_{\CR}$-profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$
+over the entire range of the radio halo emission ($< 1$ Mpc).\footnote{See Figure 3 in
+\citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
+conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in
+this study.  We caution, however, that the minimum-energy condition is violated at the outer radio
+halo boundary for the range of minimum magnetic-field values inferred by this study.} The
+corresponding values for $X_\CR$ in the cluster center are smaller than 0.01 for the entire
+parameter space probed in this study. We conclude that the hadronic model is not challenged by
+current Faraday RM data and a perfectly viable possibility in explaining the Coma radio halo
+emission.
+
+%
+%
 
 \section{Emission from Dark Matter Annihilations}
-As already mentioned in the introduction, most of the mass in a galaxy cluster is in the form of DM.
-While the nature of this DM remains unknown, the most compelling theoretical candidate is a WIMP.
-The self-annihilations of WIMPs are expected to produce a flux of secondary gamma rays with a spectral signature that deviates significantly from the power-law spectrum observed in most conventional astrophysical sources.
-The spectrum will also feature a very sharp cutoff at the WIMP mass.
-Observations of these spectral features together with the expected difference in spatial distribution of the gamma-ray flux compared to conventional astrophysical sources allows for a unique means to indirectly detect DM.
+As already mentioned in the introduction, most of the mass in a galaxy cluster is in the form of
+DM. While the nature of this DM remains unknown, the most compelling theoretical candidate is a
+WIMP. The self-annihilations of WIMPs are expected to produce a flux of secondary gamma rays with a
+spectral signature that deviates significantly from the power-law spectrum observed in most
+conventional astrophysical sources. The spectrum will also feature a very sharp cutoff at the WIMP
+mass. Observations of these spectral features together with the expected difference in spatial
+distribution of the gamma-ray flux compared to conventional astrophysical sources allows for a
+unique means to indirectly detect DM.
 
@@
 \begin{equation}
-\frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\frac{dN(E,m_{\chi})}{dE} J(\Delta\Omega),
+\frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=
+\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\frac{dN(E,m_{\chi})}{dE} J(\Delta\Omega),
 \label{eqn:WIMPflux}
 \end{equation}
-where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends on the DM distribution.
+where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross
+section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential
+gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the
+astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends
+on the DM distribution.
 
-Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\ \mathrm{CL})$, we can place constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$.
-From Eq.
+Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\ \mathrm{CL})$, we can place
+constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. From Eq.
 (\ref{eqn:WIMPflux}) we get
 \begin{equation}
-\expval{\sigma v}(95\%\ \mathrm{CL}) > R_{\gamma}(95\%\ \mathrm{CL}) \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\frac{1}{\int^{m_{\chi}} dE A_{\mathrm{eff}}dN_{\gamma}/dE}
+\expval{\sigma v}(95\%\ \mathrm{CL}) > 
+R_{\gamma}(95\%\ \mathrm{CL}) \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}
+\frac{1}{\int^{m_{\chi}} dE A_{\mathrm{eff}}dN_{\gamma}/dE}
 \end{equation}
@@
 \begin{equation}
-J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right) \int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
+J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right)
+\int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
 \end{equation}
-where $\lambda$ represents the line-of-sight.
-Because the self-annihilation of a WIMP is a two-body process, $J(\Delta\Omega)$ is proportional to the square of the DM density $\rho$.
-Here, $J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the Hubble radius, $R_{H}$.
+where $\lambda$ represents the line-of-sight. Because the self-annihilation of a WIMP is a two-body
+process, $J(\Delta\Omega)$ is proportional to the square of the DM density $\rho$. Here,
+$J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the
+Hubble radius, $R_{H}$.
 
-In this work we have adopted the DM density profile by Navarro-Frenk-White \citep[NFW;][]{article:NavarroFrenkWhite:1997},
+In this work we have adopted the DM density profile by Navarro-Frenk-White
+\citep[NFW;][]{article:NavarroFrenkWhite:1997},
 \begin{equation}
@@
 \end{equation} 
-which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density $\rho_{s}$. [how where these calculated?]
+which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density
+$\rho_{s}$. [how where these calculated?]
 
-%When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated background.
-For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor no longer compensate for the increased count of background events and the signal-to-noise deteriorates.
+%When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result
+%from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated
+%background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor
+%no longer compensate for the increased count of background events and the signal-to-noise
+%deteriorates.
+
+%
+%
 
 \section{Discussion and Conclusions}
-VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008.
-No significant excess of gamma-rays above a threshold of about 220 GeV was detected.
-Flux upper limits at 99\% confidence level were calculated for the cluster core and three member galaxies.
-The core was considered both as a point-like and spatially extended source.
-The obtained flux upper limits were used to constrain properties of the cluster.
+VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time
+between March and May in 2008. No significant excess of gamma-rays above a threshold of about 220
+GeV was detected. Flux upper limits at 99\% confidence level were calculated for the cluster core
+and three member galaxies. The core was considered both as a point-like and spatially extended
+source. The obtained flux upper limits were used to constrain properties of the cluster.
 
-We employed various approaches to constrain the CR population and magnetic field distribution that are complementary in their assumptions and hence well suited in assessing underlying Bayesian priors in the models.
-(1) We use a simplified ``isobaric CR model'' that is characterized by a constant CR-to-thermal pressure fraction and has a power-law momentum spectrum.
-While this model is physically not justified a priory, it is simple and widely used in the literature and captures some aspects of more elaborate models such as (2) the simulation-based analytical approach of \citet{article:PinzkePfrommer:2010}.
-This is a ``first principle approach'' that predicts the CR distribution spectrally and spatially for a given set of assumptions (namely the physics that was simulated).
-It is powerful since it only requires the density profile as input due to the approximate universality of the CR distribution (when neglecting CR diffusion and streaming which appears, however, necessary to explain the radio halo bimodality).
-(3) We finally use a pragmatic approach which models the CR and magnetic distribution such as to reproduce the observed emission profile of the Coma radio halo.
-While this approach is also physically not justified, it is powerful
-as it shows what the ``correct'' model has to achieve and can point into the direction of the relevant physics.
+We employed various approaches to constrain the CR population and magnetic field distribution that
+are complementary in their assumptions and hence well suited in assessing underlying Bayesian
+priors in the models. (1) We use a simplified ``isobaric CR model'' that is characterized by a
+constant CR-to-thermal pressure fraction and has a power-law momentum spectrum.  While this model
+is physically not justified a priory, it is simple and widely used in the literature and captures
+some aspects of more elaborate models such as (2) the simulation-based analytical approach of
+\citet{article:PinzkePfrommer:2010}. This is a ``first principle approach'' that predicts the CR
+distribution spectrally and spatially for a given set of assumptions (namely the physics that was
+simulated). It is powerful since it only requires the density profile as input due to the
+approximate universality of the CR distribution (when neglecting CR diffusion and streaming which
+appears, however, necessary to explain the radio halo bimodality). (3) We finally use a pragmatic
+approach which models the CR and magnetic distribution such as to reproduce the observed emission
+profile of the Coma radio halo. While this approach is also physically not justified, it is
+powerful as it shows what the ``correct'' model has to achieve and can point into the direction of
+the relevant physics.
 
-Within this pragmatic approach we employ two different directions.
-First, adopting a high magnetic field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining flux upper limits of {\em Fermi} (VERITAS).
-Second, by matching the radio emission profile (i.e., fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR distribution) we obtain lower limits on the magnetic field distribution under consideration.
-Our limits of the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS  flux limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for {\em Fermi} flux limits).
-Since all these lower limits on $B_0$ are below the values favored by Faraday RM, $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G \citep{article:Bonafede_etal:2010}, the hadronic model is a very attractive explanation of the Coma radio halo.
+Within this pragmatic approach we employ two different directions. First, adopting a high magnetic
+field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the
+hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining
+flux upper limits of {\em Fermi} (VERITAS). Second, by matching the radio emission profile (i.e.,
+fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay
+gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR
+distribution) we obtain lower limits on the magnetic field distribution under consideration. Our
+limits of the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS  flux
+limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for {\em Fermi} flux limits). Since all these lower
+limits on $B_0$ are below the values favored by Faraday RM, $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G
+\citep{article:Bonafede_etal:2010}, the hadronic model is a very attractive explanation of the Coma
+radio halo.
 
-Applying our simplified ``isobaric CR model'' to the most constraining VERITAS limits, we can constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray spectral index, $\alpha$, varying between 2.1 and 2.5).
-We obtain a constraint of $X_\CR<0.1$ for $\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.
-This limit is more constraining by a factor of 1.5 in comparison to the simulation-based model which gives $X_\CR<0.15$.
-This difference is due to the concave curvature of the simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
+Applying our simplified ``isobaric CR model'' to the most constraining VERITAS limits, we can
+constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray
+spectral index, $\alpha$, varying between 2.1 and 2.5). We obtain a constraint of $X_\CR<0.1$ for
+$\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit
+is more constraining by a factor of 1.5 in comparison to the simulation-based model which gives
+$X_\CR<0.15$.  This difference is due to the concave curvature of the simulated spectrum which
+accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of
+$\alpha=2.3$.
 
-The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying between 2.3 and 2.1), only weakly depending on the assumed CR spectral index.
-Assuming $\alpha=2.1$ which is very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain an almost coincident constraint with our simulation-based model within the virial radius of $X_\CR<0.024$.
-That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$ corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc.
-These are encouraging results in that we constrain the CR pressure (of a phase that is fully mixed with the ICM) to be at most a small fraction of the overall pressure, $<0.025$.
-As a result, hydrostatic cluster masses and the total Comptonization parameter due to the Sunyaev-Zel'dovich effect attain at most a very small bias due to CRs.
+The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying
+between 2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$
+which is very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain an
+almost coincident constraint with our simulation-based model within the virial radius of
+$X_\CR<0.024$. That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$
+corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc. These are encouraging
+results in that we constrain the CR pressure (of a phase that is fully mixed with the ICM) to be at
+most a small fraction of the overall pressure, $<0.025$. As a result, hydrostatic cluster masses
+and the total Comptonization parameter due to the Sunyaev-Zel'dovich effect attain at most a very
+small bias due to CRs.
 
 \acknowledgments
-This research was supported by grants from the U.S.
-Department of Energy, the U.S.
-National Science Foundation, and the Smithsonian Institution, by NSERC in Canada, by Science Foundation Ireland, and by STFC in the UK.
-We acknowledge the excellent work of the technical support staff at the FLWO and the collaborating institutions in the construction and operation of the instrument.
-C.P.
-gratefully acknowledges financial support of the Klaus Tschira Foundation.
+This research was supported by grants from the U.S. Department of Energy, the U.S. National Science
+Foundation, and the Smithsonian Institution, by NSERC in Canada, by Science Foundation Ireland, and
+by STFC in the UK. We acknowledge the excellent work of the technical support staff at the FLWO and
+the collaborating institutions in the construction and operation of the instrument. C.P. gratefully
+acknowledges financial support of the Klaus Tschira Foundation.
 
@@
 \end{center}
-\caption{\emph{Left}: Smoothed significance map of the Coma cluster calculated from the observed excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view.
-The excess counts were derived using a ring background model \citep{article:Aharonian_etal:2001}.
-White contours show the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}.
-\emph{Right}: Same as above but with overlaid contours from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where strong point sources have been subtracted.
-Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan) considered for the extended source analyses presented here.}
+\caption{\emph{Left}: Smoothed significance map of the Coma cluster calculated from the observed
+excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view. The excess counts
+were derived using a ring background model \citep{article:Aharonian_etal:2001}. White contours show
+the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey
+\citep{article:BrielHenryBohringer:1992}. \emph{Right}: Same as above but with overlaid contours
+from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where strong point sources
+have been subtracted. Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan)
+considered for the extended source analyses presented here.}
 \label{fig:skymaps}
@@
 \end{center}
-\caption{$\theta^{2}$ distribution from VERITAS observations of the Coma cluster of galaxies.
-The points with error bars represent the ON-source data sample and the filled area is the estimated background due to cosmic rays.
-Each bin represents an annulus around the Coma cluster core position.
-The data were derived from the ring background model using a $0.2^{\circ}$ sampling radius.}
+\caption{$\theta^{2}$ distribution from VERITAS observations of the Coma cluster of galaxies. The
+points with error bars represent the ON-source data sample and the filled area is the estimated
+background due to cosmic rays. Each bin represents an annulus around the Coma cluster core
+position. The data were derived from the ring background model using a $0.2^{\circ}$ sampling
+radius.}
 \label{fig:thetasq}
@@
 \end{center}
-\caption{Distribution of significance for Figure \ref{fig:skymaps} and a sampling radius of $0.2^{\circ}$.
-The line is a Gaussian fit to the data, with mean close to zero and almost unit standard deviation.}
+\caption{Distribution of significance for Figure \ref{fig:skymaps} and a sampling radius of
+$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean close to zero and almost unit
+standard deviation.}
 \label{fig:sigdist}
@@
 \end{center}
-\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii (shown with different colors), assuming $\alpha=2.1$.
-These are compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma F_\gamma(>E_\gamma)$, from the Coma cluster (again within different apertures).
-Note that the {\em Fermi} limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.
-Since the model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.}
+\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi})
+for different integration radii (shown with different colors), assuming $\alpha=2.1$. These are
+compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma F_\gamma(>E_\gamma)$,
+from the Coma cluster (again within different apertures). Note that the {\em Fermi} limit for the
+energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining. Since the
+model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison
+to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the
+simulation model.}
 \label{fig:spectrum}
 \end{figure*}
-
-is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.
 
@@
 \end{center}
-\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a function of radial distance from the center of the Coma.
-Model predictions are shown by dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining VERITAS upper limits within 0.2$^\circ$ (solid) and {\em Fermi} upper limits within 0.4$^\circ$ (dashed).
-We compare differential $X_\CR$-profiles (red) to integrated profiles $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (blue) which we use to compare to the upper limits.}
+\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a
+function of radial distance from the center of the Coma. Model predictions are shown by dashed
+lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining
+VERITAS upper limits within 0.2$^\circ$ (solid) and {\em Fermi} upper limits within 0.4$^\circ$
+(dashed). We compare differential $X_\CR$-profiles (red) to integrated profiles
+$X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (blue) which we use to
+compare to the upper limits.}
 \label{fig:xcr}
@@
 \end{center}
-\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ as a function of the DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
+\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ as a function of the DM
+particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this
+work.}
 \label{fig:dm}
@@
 \enddata
-\tablecomments{The cluster core is considered both as a point source and a modestly extended source.
-Three central galaxies are also considered in point-source searches.
-The choice is based on evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the location of these galaxies.}
+\tablecomments{The cluster core is considered both as a point source and a modestly extended
+source. Three central galaxies are also considered in point-source searches. The choice is based on
+evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the
+location of these galaxies.}
 \label{table:roi}
@@
 \tablewidth{0pc}
-\tablecaption{VERITAS flux upper limits for different regions of interest in the Coma cluster of galaxies and surroundings}
+\tablecaption{VERITAS flux upper limits for different regions of interest in the Coma cluster of
+galaxies and surroundings}
 \rotate
 \tablehead{
-\colhead{Source} & \colhead{RoI\tablenotemark{a} [deg]} & \colhead{$N_{S}$} & \colhead{S\tablenotemark{b} [$\sigma$]} &
+\colhead{Source} & 
+\colhead{RoI\tablenotemark{a} [deg]} & 
+\colhead{$N_{S}$} & 
+\colhead{S\tablenotemark{b} [$\sigma$]} &
 \multicolumn{6}{c}{Flux U.L.\tablenotemark{c}} \\
-\colhead{} & \colhead{} & \colhead{} & \colhead{} & \multicolumn{2}{c}{$\alpha=2.1$} &
+\colhead{} & 
+\colhead{} & 
+\colhead{} & 
+\colhead{} &
+\multicolumn{2}{c}{$\alpha=2.1$} &
 \multicolumn{2}{c}{$\alpha=2.3$} &
@@
 \enddata
-\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
+\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
+analysis PSF.}
 \tablenotetext{b}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
-\tablenotetext{c}{99\% confidence level upper limit in units of $10^{-8}$ ph.
-m$^{-2}$ s$^{-1}$ calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
+\tablenotetext{c}{99\% confidence level upper limit in units of $10^{-8}$ ph. m$^{-2}$ s$^{-1}$
+calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with
+corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
 \label{table:results}
@@
                       & $1-3$ GeV & $3-10$ GeV & $10-30$ GeV\\
-\small{Spatial Model} & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}} (\small{Significance})\\
+\small{Spatial Model} & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux
+U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}}
+(\small{Significance})\\
 \hline
@@
 \enddata
-\tablenotetext{a}{99\% confidence level upper limit in units of $10^{-10}$ ph. cm$^{-2}$ s$^{-1}$.}
+\tablenotetext{a}{99\% confidence level upper limit in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$.}
 \label{table:fermi}
@@
 \tablehead{
-\colhead{Spatial model} & \multicolumn{3}{c}{S[$\sigma$]\tablenotemark{a}} & \multicolumn{3}{c}{Flux U.L.\tablenotemark{b}} \\
-\colhead{} & \colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} & 
-\colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} \\
+\colhead{Spatial model} & 
+\multicolumn{3}{c}{S[$\sigma$]\tablenotemark{a}} & 
+\multicolumn{3}{c}{Flux U.L.\tablenotemark{b}} \\
+\colhead{} & 
+\colhead{1-3 GeV} & 
+\colhead{3-10 GeV} & 
+\colhead{10-30 GeV} & 
+\colhead{1-3 GeV} & 
+\colhead{3-10 GeV} & 
+\colhead{10-30 GeV} \\
 \hline
@@
 \tablenotetext{a}{Statistical significance.}
-\tablenotetext{b}{95\% confidence level upper limit in units of $10^{-10}$ ph. cm$^{-2}$ s$^{-1}$.}
+\tablenotetext{b}{95\% confidence level upper limit in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$.}
 \label{table:fermi}
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions} \rotate
+\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial
+extensions} \rotate
 \tabletypesize{\small}
@@
 \enddata
-\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
-\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ from the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}: at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for Fermi.
-}
-\tablenotetext{c}{Integrated gamma-ray flux from the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph.
-m$^{-2}$ s$^{-1}$ for VERITAS and  above $E=1~\rmn{GeV}$ in units of $10^{-6}$ ph.
-m$^{-2}$ s$^{-1}$ for Fermi.}
-\tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
+\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
+analysis PSF.}
+\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ from the simulation-based analytic model
+by \citet{article:PinzkePfrommer:2010}: at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$
+for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for Fermi. }
+\tablenotetext{c}{Integrated gamma-ray flux from the simulation-based analytic model by
+\citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$
+s$^{-1}$ for VERITAS and  above $E=1~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
+Fermi.} 
+\tablenotetext{d}{Constraint on the relative CR pressure,
+$X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the
+cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
 \tablenotetext{e}{Minimum gamma-ray flux of the hadronic model described in the
-  text. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS) and
-  $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ {\em (Fermi)}.}
-\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ in the hadronic model described in the text.}
+text. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS) and $10^{-8}$ ph. m$^{-2}$
+s$^{-1}$ {\em (Fermi)}.}
+\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ in the
+hadronic model described in the text.}
 \label{table:constraints}
@@
 \enddata
-\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
+\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the
+central field strength, $B_{0}$, which are defined by
+$B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
 \label{table:Bmin}
@@
 \tablehead{
-\colhead{RoI [deg]} & $\expval{J}_{\rmn{signal}}$ [GeV$^{2}$ cm$^{-5}$ sr] & $\alpha\expval{J}_{\rmn{bkg}}$ [GeV$^{2}$ cm$^{-5}$ sr]
+\colhead{RoI [deg]} &
+\colhead{$\expval{J}_{\rmn{signal}}$ [GeV$^{2}$ cm$^{-5}$ sr]} & 
+\colhead{$\alpha\expval{J}_{\rmn{bkg}}$ [GeV$^{2}$ cm$^{-5}$ sr]}
 }
@@
 \enddata
-\tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background region (ring method) and is used to estimate the level of gamma-ray contamination from DM.}
+\tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background
+region (ring method) and is used to estimate the level of gamma-ray contamination from DM.}
 \label{table:astrofactor}
@@
 \enddata
-\tablecomments{Upper limits are for different integration regions and DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
+\tablecomments{Upper limits are for different integration regions and DM particle mass $m_{\chi}$
+derived from the VERITAS gamma-ray flux upper limits presented in this work.}
 \label{table:DMlimits}

### 2011-09-09 ms.tex
small changes to text

--- 2011-09-09 ms.tex
@@
 \subsection{Simplified analytical model}
-To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical
-work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR
-spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}. To be
-independent of additional assumptions and in line with earlier work in the literature, we do not
-impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$. Since a priori,
-the CR spectral index is unconstrained, we vary it within plausible ranges of
-$2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the radio spectral index of the
-giant radio halo of Coma after accounting for the spectral steepening at frequencies
-$\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
-\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
-  responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
-  times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. Table
-\ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS flux upper limits
-strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate
-the CR pressure) to TeV-energies. The limits within 0.2$^{\circ}$ are most constraining yielding
-limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with a
-constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the simulations
-around 220 GeV). This limit is more constraining by 50\% in comparison to the model derived from
-simulations, which gives $X_\CR<0.15$. This difference is explained by the concave curvature of the
-simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure
-power-law spectrum of $\alpha=2.3$.
+To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs} following the approach of \citet{2004A&A...413...17P}.
+To be independent of additional assumptions and in line with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$.
+Since a priori, the CR spectral index is unconstrained, we vary it within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$.
+This spectral range is compatible with the radio spectral index of the giant radio halo of Coma after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.
+Table \ref{table:constraints} shows the resulting constraints on $X_\CR$.
+The VERITAS flux upper limits strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies.
+The limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the simulations around 220 GeV).
+This limit is more constraining by 50\% in comparison to the model derived from simulations, which gives $X_\CR<0.15$.
+This difference is explained by the concave curvature of the simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
 
-The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of
-0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly
-worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.  This is comparable to the $X_\CR$-constraint
-in our simulation-based model of $X_\CR<0.024$ (evaluated within the cluster virial
-radius). Naturally, with the Fermi limits we probe the region around GeV-energies that dominate the
-CR pressure and we do not expect any differences in comparison to the simulation-based models on account
-of the concave curvature of the universal CR spectrum found in the simulations.
+The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of 0.4$^{\circ}$.
+The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
+This is comparable to the $X_\CR$-constraint in our simulation-based model of $X_\CR<0.024$ (evaluated within the cluster virial radius).
+Naturally, with the Fermi limits we probe the region around GeV-energies that dominate the CR pressure and we do not expect any differences in comparison to the simulation-based models on account of the concave curvature of the universal CR spectrum found in the simulations.
 

### 2011-09-09 ms.tex

--- 2011-09-09 ms.tex
@@
 X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these
-temperatures primarily through collisionless structure-formation shocks that form as a result of
-the hierarchical merging and accretion processes. Such shocks and turbulence in the ICM gas and
-intra-cluster magnetic fields also provide a means to efficiently accelerate particles
-\citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do
-indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of
-relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM
-\citep{article:Cassano_etal:2010}. Recent observations of possible non-thermal emission from
+temperatures primarily through collisionless structure-formation shocks that form as a result of the
+hierarchical merging and accretion processes. Such shocks and turbulence in the ICM gas and
+intra-cluster magnetic fields also provide a means to efficiently accelerate particles \citep[see,
+e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do indeed feature
+mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic
+electrons and positrons (leptons) and magnetic fields permeating the ICM
+\citep{article:Cassano_etal:2010}. The two competing theories seeking to explain the radio halo
+emission feature the ``hadronic model'' where the radio-emitting electrons are produced in inelastic
+collisions of CR ions with thermal gas protons from the ICM \citep[][and references
+therein]{article:EnsslinPfrommerMiniatiSubramanian:2011} and the ``re-acceleration model'' where a
+CR electron population within the ICM at energies around 100 MeV might be sufficiently long lived so
+that during states of powerful ICM turbulence, e.g., after a cluster merger, non-resonant
+interactions of these CR electrons with plasma waves might be efficient enough to accelerate them to
+high enough energies ($\sim 10$~GeV) so that they emit observable radio emission \citep[][and
+references therein]{2010arXiv1008.0184B}.  Recent observations of possible non-thermal emission from
 clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
@@
 provide further indications of relativistic particle populations in clusters, although the
-interpretation of these observations as non-thermal diffuse emission have been disputed on the
-basis of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
+interpretation of these observations as non-thermal diffuse emission have been disputed on the basis
+of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
   article:Ajello_etal:2010, article:Wik_etal:2009}.
@@
 \section{Gamma Ray Emission from Cosmic Rays}
-We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution
-in the Coma cluster with the VERITAS and \emph{Fermi}-LAT upper limits from this work. This
-approach includes (1) an analytic model derived from cosmological hydrodynamical simulations of the
-formation of galaxy clusters, (2) a simplified multi-frequency analytical approach that assumes a
-constant CR-to-thermal energy density and a power-law spectrum in momentum, and (3) an approach
-that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on the
-expected $\gamma$-ray flux in the hadronic model -- independent of the magnetic field distribution.
-This translates into a minimum CR pressure which, if challenged by tight gamma-ray
-limits/detections, enables scrutinizing the hadronic interaction model of the formation of giant
-radio halos. Modelling the CR distribution through different techniques enable to bracket our
-ignorance about the underlying plasma physics that shape the CR distribution and hence reflect the
-Bayesian priors that are imposed on the modelling
-\citep[see][for a discussion]{article:PinzkePfrommerBergstrom}.
+We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution in
+the Coma cluster with the VERITAS and \emph{Fermi}-LAT upper limits from this work. This approach
+includes (1) a simplified multi-frequency analytical approach that assumes a constant CR-to-thermal
+energy density and a power-law spectrum in momentum, (2) an analytic model derived from cosmological
+hydrodynamical simulations of the formation of galaxy clusters, and (3) an approach that uses the
+observed luminosity of the giant radio halo in Coma to place a lower limit on the expected
+$\gamma$-ray flux in the hadronic model -- where the radio-emitting electrons are secondaries from
+CR interactions and which is independent of the magnetic field distribution.  This translates into a
+minimum CR pressure which, if challenged by tight gamma-ray limits/detections, enables scrutinizing
+the hadronic interaction model of the formation of giant radio halos. Alternatively, by realizing a
+spatial CR distribution that is just consitent with the flux upper limits and requiring the model to
+match the observed radio data, this enables us to derive a lower limit on the magnetic field
+distribution. This approach, however, assumes the validity of the hadronic interaction model in
+explaining the radio halo data.  Modelling the CR distribution through different techniques enable
+us to bracket our ignorance about the underlying plasma physics that shape the CR distribution and
+hence reflect the Bayesian priors that are imposed on the modelling \citep[see][for a
+discussion]{article:PinzkePfrommerBergstrom}.
+
+%
+%
+
+\subsection{Simplified analytical model}
+\label{sec:simple}
+
+We start by adopting a simplified analytical model that assumes a power-law CR spectrum and a
+constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs} following the approach
+of \citet{article:PfrommerEnsslin:2004b}. To be independent of additional assumptions and in line
+with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution
+function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is unconstrained, we vary it
+within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the
+radio spectral index of the giant radio halo of Coma after accounting for the spectral steepening at
+frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
+\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
+  responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
+  times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.  To model
+the thermal pressure, we adopt the electron density profile for the Coma cluster that has been
+inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and use a constant
+temperature of $kT= 8.25$~keV throughout the virial region.
+
+Table \ref{table:constraints} shows the resulting constraints on the relative CR pressure, $X_{\CR}
+= \expval{P_{\CR}}/\expval{P_\rmn{th}}$, averaged within the virial radius, $R_\rmn{vir}=2.2$~Mpc,
+that we define as the radius of a sphere enclosing a mean density that is 200 times the critical
+density of the Universe. The VERITAS flux upper limits strongly depend on $\alpha$ due to the
+comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies. The
+limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$ between 0.048 and 0.43
+(for $\alpha$ varying between 2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close
+to the spectral index predicted by the simulations of \citet{article:PinzkePfrommer:2010} around 220
+GeV).  The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an
+aperture of 0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only
+slightly worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
 
@@
 \subsection{Simulation-based approach}
-We adopt the universal spectral and spatial gamma-ray model developed by
-\citet{article:PinzkePfrommer:2010} to estimate the emission from decaying neutral pions that
-dominates over the IC emission from primary and secondary electrons above 100 MeV in clusters.
-Given a density profile as, e.g., inferred by cosmological simulations or X-ray observations, the
-analytic approach models the CR distribution and the associated radiative emission processes from
-radio to the gamma-ray band. This formalism was derived from high-resolution simulations of
-clusters of galaxies that included radiative hydrodynamics, star formation, supernova feedback, and
-followed CR physics by tracing the most important injection and loss processes self-consistently
-while accounting for the CR pressure in the equation of motion
+
+We complement the simplified analytical analysis with a more realistic and predictive approach
+derived from cosmological hydrodynamical simulations. We adopt the universal spectral and spatial
+gamma-ray model developed by \citet{article:PinzkePfrommer:2010} to estimate the emission from
+decaying neutral pions that dominates over the IC emission from primary and secondary electrons
+above 100 MeV in clusters.  Given a density profile as, e.g., inferred by cosmological simulations
+or X-ray observations, the analytic approach models the CR distribution and the associated radiative
+emission processes from radio to the gamma-ray band. This formalism was derived from high-resolution
+simulations of clusters of galaxies that included radiative hydrodynamics, star formation, supernova
+feedback, and followed CR physics by tracing the most important injection and loss processes
+self-consistently while accounting for the CR pressure in the equation of motion
 \citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007,
@@
 
-The overall normalization of the CR and gamma-ray distribution scales with the maximum acceleration
-efficiency at structure formation shock waves. Following recent observations at supernova remnants
-\citep{article:Helder_etal:2009} as well as theoretical studies \citep{article:KangJones:2005}, we
-adopt an optimistic but nevertheless realistic value of this parameter and assume that 50\% of the
-dissipated energy at strong shocks is injected into CRs while this efficiency rapidly decreases for
-weaker shocks. Since the vast majority of internal formation shocks (merger and flow shocks) are
-weak shocks with Mach numbers $M\lesssim3$ \citep[e.g.,][]{article:Ryu_etal:2003}, they do not
-significantly contribute to the CR population in clusters. Instead, strong shocks during the
-formation epoch of clusters and strong accretion shocks at the present time (at the boundary of
-voids and filaments/super-cluster regions) dominate the injection of CRs which are adiabatically
-transported through the cluster. Hence, these model predictions provide a plausible upper limit for
-the CR contribution from structure formation shocks in galaxy clusters which can be scaled with the
-effective acceleration efficiency. Other possible CR sources, such as AGN and starburst-driven
-galactic winds have been neglected for simplicity which could in principle increase the expected
-gamma-ray yield.
+The overall normalization of the CR and gamma-ray distribution scales (non-linearly) with the
+maximum acceleration efficiency at structure formation shock waves. Following recent observations at
+supernova remnants \citep{article:Helder_etal:2009} as well as theoretical studies
+\citep{article:KangJones:2005}, we adopt an optimistic but nevertheless realistic value of this
+parameter and assume that 50\% of the dissipated energy at strong shocks is injected into CRs while
+this efficiency rapidly decreases for weaker shocks. Since the vast majority of internal formation
+shocks (merger and flow shocks) are weak shocks with Mach numbers $M\lesssim3$
+\citep[e.g.,][]{article:Ryu_etal:2003}, they do not significantly contribute to the CR population in
+clusters. Instead, strong shocks during the formation epoch of clusters and strong accretion shocks
+at the present time (at the boundary of voids and filaments/super-cluster regions) dominate the
+injection of CRs which are adiabatically transported through the cluster. Hence, these model
+predictions provide a plausible upper limit for the CR contribution from structure formation shocks
+in galaxy clusters which can be scaled with the effective acceleration efficiency. Other possible CR
+sources, such as AGN and starburst-driven galactic winds have been neglected for simplicity which
+could in principle increase the expected gamma-ray yield.
 
@@
 
-We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray
-observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral
-distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the
-contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma,
-normalized to the total flux within the virial radius (dotted lines) and the angular apertures
-tested in this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval
-of 1--3 GeV ($<0.4^\circ$) is most constraining. However, since the model flux within the finite
-energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV,
-it falls below the flux upper limits which do not yet constrain the simulation model. In our
-further analysis, we use the most constraining {\em Fermi} flux limits in the energy interval of
-1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.
-
-Figure \ref{fig:xcr} shows the relative CR pressure,
-$X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the
-Coma cluster center (red lines) and contained within $R$ (blue lines).  We normalize the radii by
-the virial radius, $R_\rmn{vir}$, that we define as the radius of a sphere enclosing a mean density
-that is 200 times the critical density of the Universe.  To compute the CR pressure, we assume a
-low-momentum cutoff of the CR distribution at $q = 0.8\,m_p c$ as found in the cosmological
-simulations which reflects the high cooling rates at low CR energies. The relative CR pressure
-rises toward the outer regions on account of the higher efficiency of CR acceleration at the
-peripheral strong accretion shocks compared to weak central flow shocks. Adiabatic compression of a
-mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on
-account of the softer equation of state of CRs. The weak increase of $X_{\CR}$ toward the core is
-due to the comparably fast thermal cooling of gas which diminishes the thermal support relative to
-that in CRs.
-
-Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest.
+We adopt the electron density profile as in Sect.~\ref{sec:simple} and model the temperature profile
+of Coma with a constant central temperature of $kT= 8.25$~keV and a characteristic decline toward
+the cluster periphery in accordance with a fit to the universal profile derived from cosmological
+cluster simulations \citep{article:PinzkePfrommer:2010, article:Pfrommer_etal:2007} that also
+follows the behavior of a nearby sample of deep {\em Chandra} cluster data
+\citep{2005ApJ...628..655V}. This enables us to adopt the spatial and spectral distribution of CRs
+according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of
+cluster galaxies.
+
+Figure \ref{fig:spectrum} shows the expected integral spectral energy distribution of Coma within
+the virial radius (dotted lines). Additionally shown are integrals of the differential spectrum for
+finited energy intervals across the angular apertures tested in this study (solid lines). These
+modeled fluxes a compared to {\em Fermi} and VERITAS flux upper limits of the same energy intervals,
+summarized in Table \ref{table:constraints}.  The gamma-ray flux limit of {\em Fermi} in the energy
+interval of 1--3 GeV ($<0.4^\circ$) is most constraining but still above the model predictions that
+assume an optimistic value of the shock acceleration efficiency and CR transport parameters as laid
+out above.  In our further analysis, we use the most constraining {\em Fermi} flux limits in the
+energy interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above
+220 GeV.
+
+Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} =
+\expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster
+center (red lines) and contained within $R$ (blue lines). All radii are shown in units of the virial
+radius, $R_\rmn{vir}=2.2$~Mpc. To compute the CR pressure, we assume a low-momentum cutoff of the CR
+distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which reflects the high
+cooling rates at low CR energies. The relative CR pressure rises toward the outer regions on account
+of the higher efficiency of CR acceleration at the peripheral strong accretion shocks compared to
+weak central flow shocks. Adiabatic compression of a mixture of CRs and thermal gas disfavours the
+CR pressure relative to the thermal pressure on account of the softer equation of state of CRs. The
+weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas
+which diminishes the thermal support relative to that in CRs.
+
 In the case of VERITAS, for the most constraining regions tested (within an aperture of radius
 0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table
-\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one
-at energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by
-that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure
-of $X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius
-of $X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}). Equivalently, the most constraining
-{\em Fermi} upper limit in the energy interval of 1--3 GeV ($<0.4^\circ$) is a factor of 1.1 larger
-than our model predictions (assuming $\alpha=2.1$ which is very close to the simulated spectral
-index for the energy range of 1-3 GeV). Scaling our integrated relative CR pressure profile yields
-the constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a limit within the
-cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}).
-
-%
-%
-
-\subsection{Simplified analytical model}
-To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical
-work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR
-spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}. To be
-independent of additional assumptions and in line with earlier work in the literature, we do not
-impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$. Since a priori,
-the CR spectral index is unconstrained, we vary it within plausible ranges of
-$2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the radio spectral index of the
-giant radio halo of Coma after accounting for the spectral steepening at frequencies
-$\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
-\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR
-protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are
-$\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.
-Table \ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS flux upper
-limits strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that
-dominate the CR pressure) to TeV-energies. The limits within 0.2$^{\circ}$ are most constraining
-yielding limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with
-a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the
-simulations around 220 GeV). This limit is more constraining by 50\% in comparison to the model
-derived from simulations, which gives $X_\CR<0.15$. This difference is explained by the concave
-curvature of the simulated spectrum which accumulates additional pressure toward GeV energies in
-comparison to a pure power-law spectrum of $\alpha=2.3$.
-
-The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of
-0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly
-worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.  This is comparable to the $X_\CR$-constraint
-in our simulation-based model of $X_\CR<0.024$ (evaluated within the cluster virial radius).
-Naturally, with the Fermi limits we probe the region around GeV-energies that dominate the CR
-pressure and we do not expect any differences in comparison to the simulation-based models on
-account of the concave curvature of the universal CR spectrum found in the simulations.
+\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at
+energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by that
+factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
+$X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of
+$X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}).  This limit is less constraining by 50\% in
+comparison to the simplified analytical model, which gives $X_\CR<0.1$. This difference is
+explained by the concave curvature of the simulated spectrum which accumulates additional pressure
+toward GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
+
+Equivalently, the most constraining {\em Fermi} upper limit in the energy interval of 1--3 GeV
+($<0.4^\circ$) is a factor of 1.1 larger than our model predictions (assuming $\alpha=2.1$ which is
+very close to the simulated spectral index for the energy range of 1-3 GeV). Scaling our integrated
+relative CR pressure profile yields the constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that
+translates to a limit within the cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure
+\ref{fig:xcr}).  The $X_\CR$-constraint evaluated within the cluster virial radius is comparable to
+the constraint in our simplified model of $X_\CR<0.025$.  Naturally, with the Fermi limits we probe
+the region around GeV-energies that dominate the CR pressure and we do not expect any differences in
+comparison to the simplified power-law model in comparison to the universal CR spectrum with its
+concave curvature found in the simulations.
 
@@
 \subsection{Minimum gamma-ray flux}
+\label{sec:Fmin}
 For clusters that host radio halos we are able to derive a minimum gamma-ray flux in the hadronic
-model of CR interactions. The idea is based on the fact that a stationary distribution of CR
-electrons loses all its energy to synchrotron radiation for strong magnetic fields
-($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the ratio of gamma-ray to synchrotron flux becomes
-independent of the spatial distribution of CRs and thermal gas \citep{article:Voelk:1989,
-article:Pohl:1994, article:Pfrommer:2008}, in particular with $\alpha_{\nu}\simeq 1$ as the
-observed synchrotron spectral index.  Hence we can derive a minimum gamma-ray flux in the hadronic
-model
+model of radio halos -- where the radio-emitting electrons are secondaries from CR interactions. The
+idea is based on the fact that a stationary distribution of CR electrons loses all its energy to
+synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the
+ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and
+thermal gas \citep{article:Voelk:1989, article:Pohl:1994, article:Pfrommer:2008}, in particular with
+$\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.  Hence we can derive a minimum
+gamma-ray flux in the hadronic model
 \begin{equation}
@@
 
-\section{Constraining the Magnetic Field}
+\subsection{Constraining the Magnetic Field}
 \label{sec:B}
@@
 pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio
-emission which, however, assumes the validity of the hadronic model
-\citep{article:PfrommerEnsslin:2004a}. Lowering the gamma-ray constraint will tighten (increase)
-the magnetic field limit. Once this gets in conflict with magnetic field measurements by means of
-other methods, e.g., Faraday rotation measure (RM)\footnote{Generally, Faraday RM analysis of the
-magnetic-field strength by, e.g., background sources through clusters are degenerate with the
-magnetic coherence scale and may be biased by the unknown correlation between magnetic and density
-fluctuations.}, this would challenge the hadronic model of radio halos. The method that we use to
-constrain the magnetic field inherits a dependence on the assumed spatial structure that we
-parametrize by
+emission \citep{article:PfrommerEnsslin:2004a}. This, however, assumes the validity of the hadronic
+model of radio halos -- where the radio-emitting electrons are secondaries from CR
+interactions. Lowering the gamma-ray constraint will tighten (increase) the magnetic field
+limit. Once this gets in conflict with magnetic field measurements by means of other methods, e.g.,
+Faraday rotation measure (RM)\footnote{Generally, Faraday RM analysis of the magnetic-field strength
+  by, e.g., background sources through clusters are degenerate with the magnetic coherence scale and
+  may be biased by the unknown correlation between magnetic and density fluctuations.}, this would
+challenge the hadronic model of radio halos. The method that we use to constrain the magnetic field
+inherits a dependence on the assumed spatial structure that we parametrize by
 \begin{equation}
@@
 \end{center}
-\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi})
-for different integration radii (shown with different colors), assuming $\alpha=2.1$. These are
-compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma F_\gamma(>E_\gamma)$,
-from the Coma cluster (again within different apertures). Note that the {\em Fermi} limit for the
-energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining. Since the
-model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison
-to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the
-simulation model.}
+\caption{{\em Figure TBC} Integral flux upper limits for Coma (this work, Tables~\ref{table:results}
+  and \ref{table:fermi}) for different integration radii (shown with different colors), assuming
+  $\alpha=2.1$. These are compared to integrated spectra of the same energy interval and aperture,
+  assuming the universal gamma-ray spectrum of clusters \citep{article:PinzkePfrommer:2010}. To
+  guide the eye, we show the underlying universal integral energy distribution of pion decay
+  gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic interactions of CRs and ICM
+  protons (dotted). Note that the {\em Fermi} limit for the energy interval of 1--3 GeV within the
+  aperture of 0.4$^\circ$ is most constraining.}
 \label{fig:spectrum}
@@
 \end{center}
-\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a
+\caption{{\em Figure TBC} CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a
 function of radial distance from the center of the Coma. Model predictions are shown by dashed
@@
 
-\begin{deluxetable}{cccccccccccc}
-\tablecolumns{12}
+\begin{deluxetable}{cccccc}
+\tablecolumns{6}
 \tablewidth{0pc}
-\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial
-extensions} \rotate
+\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified analytic
+  model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV and
+  $>220$~GeV (simulation-based model).} \rotate
 \tabletypesize{\small}
@@
 \colhead{RoI\tablenotemark{a} [deg]} 
-    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
-    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
-    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
-    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
-& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
+    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
+    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{c}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{d}}   \\
+& \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$} & & 
+}
+\startdata
+\multicolumn{6}{c}{VERITAS constraints:}\\
+\hline
+0.13 & 10  & 23 & 97 & 0.52  & 1.9  \\
+0.2  & 4.8 & 10 & 43 & 0.80  & 2.9  \\
+0.4  & 6.7 & 15 & 62 & 1.21  & 4.4  \\
+\cutinhead{{\em Fermi} constraints:}
+0.13 & 5.2 & 3.5 & 4.7 & 2.2  & 1.4  \\
+0.2  & 3.5 & 2.4 & 3.1 & 3.4  & 2.1  \\
+0.4  & 2.5 & 1.7 & 2.3 & 5.2  & 3.2  \\
+\enddata
+\tablenotetext{a}{Intrinsic source radius; we approximate the aperture of the point source-limits by the
+analysis PSF of 0.13$^\circ$.}
+\tablenotetext{b}{Constraint on the relative CR pressure,
+$X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the
+cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
+\tablenotetext{c}{Differential gamma-ray flux $E^{2}dF/dE$ from the simulation-based analytic model
+by \citet{article:PinzkePfrommer:2010}: at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$
+for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for Fermi. }
+\tablenotetext{d}{Integrated gamma-ray flux from the simulation-based analytic model by
+\citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$
+s$^{-1}$ for VERITAS and  above $E=1~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
+Fermi.} 
+\label{table:constraints}
+\end{deluxetable}
+
+\begin{deluxetable}{ccccccc}
+\tablecolumns{7}
+\tablewidth{0pc}
+\tablecaption{Minimum gamma-ray fluxes in the hadronic model of radio halos, where the
+  radio-emitting electrons are secondaries from CR interactions and corresponding minimum relative
+  CR pressures for Coma} \rotate
+\tabletypesize{\small}
+\tablehead{
+\colhead{RoI\tablenotemark{a} [deg]} 
+    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{b}} 
+    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{c} } \\
 & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
@@
 \startdata
-\multicolumn{12}{c}{VERITAS constraints:}\\
+\multicolumn{7}{c}{VERITAS energy range, $E>220$~GeV:}\\
 \hline
-0    & 0.52  & 1.9  & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
-0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
-0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
-\cutinhead{{\em Fermi} constraints:}
-0    & 2.2  & 1.4  & 5.2 & 3.5 & 4.7 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
-0.2  & 3.4  & 2.1  & 3.5 & 2.4 & 3.1 & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
-0.4  & 5.2  & 3.2  & 2.5 & 1.7 & 2.3 &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
+0.13 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
+0.2  & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
+0.4  & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
+\cutinhead{{\em Fermi} energy range, 1--3~GeV:}
+0.13 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
+0.2  & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
+0.4  &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
 \enddata
-\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
-analysis PSF.}
-\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ from the simulation-based analytic model
-by \citet{article:PinzkePfrommer:2010}: at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$
-for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for Fermi. }
-\tablenotetext{c}{Integrated gamma-ray flux from the simulation-based analytic model by
-\citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$
-s$^{-1}$ for VERITAS and  above $E=1~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
-Fermi.} 
-\tablenotetext{d}{Constraint on the relative CR pressure,
-$X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the
-cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
-\tablenotetext{e}{Minimum gamma-ray flux of the hadronic model described in the
-text. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS) and $10^{-8}$ ph. m$^{-2}$
-s$^{-1}$ {\em (Fermi)}.}
-\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ in the
-hadronic model described in the text.}
+\tablenotetext{a}{Intrinsic source radius; we approximate the aperture of the point source-limits by the
+analysis PSF of 0.13$^\circ$.}
+\tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in Sect~\ref{sec:Fmin}. 
+Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph. m$^{-2}$
+s$^{-1}$ {\em (Fermi) energy range}.}
+\tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the
+hadronic model described in Sect~\ref{sec:Fmin}.}
 \label{table:constraints}

### 2011-09-09 ms.tex
Minor changes

--- 2011-09-09 ms.tex
@@
 cosmological parameters. Comparing X-ray and optical potential profiles in the centers of galaxy
-clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs,
+clusters yields an upper limit of 20-30 \% of non-thermal pressure (that can be composed of CRs,
 magnetic fields or turbulence) relative to the thermal gas pressure
@@
 \footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits
-at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like
+at the 99\% confidence level in the energy range 1-30 GeV, assuming both a unresolved, point-like
 or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray emission is
@@
 tested in this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval
-of 1--3 GeV ($<0.4^\circ$) is most constraining. However, since the model flux within the finite
-energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV,
+of 1-3 GeV ($<0.4^\circ$) is most constraining. However, since the model flux within the finite
+energy range of 1-3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV,
 it falls below the flux upper limits which do not yet constrain the simulation model. In our
@@
 of $X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}). Equivalently, the most constraining
-{\em Fermi} upper limit in the energy interval of 1--3 GeV ($<0.4^\circ$) is a factor of 1.1 larger
+{\em Fermi} upper limit in the energy interval of 1-3 GeV ($<0.4^\circ$) is a factor of 1.1 larger
 than our model predictions (assuming $\alpha=2.1$ which is very close to the simulated spectral
@@
 section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential
-gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the
-astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends
-on the DM distribution.
+gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is a
+dimensionless factor, referred to as the astrophysical factor, which determines the DM annihilation
+rate and depends on the DM distribution.
 
@@
 which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density
-$\rho_{s}$. [how where these calculated?]
+$\rho_{s}$.
 
@@
 
-The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying
+The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017-0.025 (for $\alpha$ varying
 between 2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$
-which is very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain an
+which is very close to the simulated spectral index for the energy range of 1-3 GeV, we obtain an
 almost coincident constraint with our simulation-based model within the virial radius of
@@
 from the Coma cluster (again within different apertures). Note that the {\em Fermi} limit for the
-energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining. Since the
-model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison
+energy interval of 1-3 GeV within the aperture of 0.4$^\circ$ is most constraining. Since the
+model flux within the finite energy range of 1-3 GeV is smaller by a factor of 1.5 in comparison
 to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the

### 2011-09-12 ms.tex
Some minor changes; spellign etc

--- 2011-09-09 ms.tex
@@
 \newcommand{\ket}{\rangle}
-
 \shorttitle{Coma Cluster Observations with VERITAS}
@@
 favored hierarchical model of cosmic structure formation, larger objects formed through successive
-mergers of smaller objects with galaxy clusters sitting a top this mass hierarchy
+mergers of smaller objects with galaxy clusters sitting on top of this mass hierarchy
 \citep[see][for a review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark
@@
 emission feature the ``hadronic model'' where the radio-emitting electrons are produced in inelastic
-collisions of CR ions with thermal gas protons from the ICM \citep[][and references
+collisions of cosmic-ray (CR)  ions with thermal gas protons from the ICM \citep[][and references
 therein]{article:EnsslinPfrommerMiniatiSubramanian:2011} and the ``re-acceleration model'' where a
@@
 interactions of these CR electrons with plasma waves might be efficient enough to accelerate them to
-high enough energies ($\sim 10$~GeV) so that they emit observable radio emission \citep[][and
-references therein]{2010arXiv1008.0184B}.  Recent observations of possible non-thermal emission from
-clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
-\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may
-provide further indications of relativistic particle populations in clusters, although the
-interpretation of these observations as non-thermal diffuse emission have been disputed on the basis
-of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
+high enough energies ($\sim 10$~GeV) for them to emit observable radio emission
+\citep[][and references therein]{article:BrunettiLazarian:2010}. Recent observations of possible
+non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998}
+and hard X-rays \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004,
+article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters,
+although the interpretation of these observations as non-thermal diffuse emission have been disputed on
+the basis of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
 article:Ajello_etal:2010, article:Wik_etal:2009}.
@@
 Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration
-in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons,
+in the ICM is an efficient process, a population of highly relativistic CR hadrons,
 in the form of protons and heavy ions, in the ICM is to be expected. The main energy-loss
 mechanism for CR hadrons at high energies is pion production through the interaction of CRs with
-nuclei in the ICM. Pions are short lived and decay; the charged pions to electrons and positrons,
-\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or
-positron as well as neutrinos.} and the neutral pion to gamma rays. Due to the low density of the
+nuclei in the ICM. Pions are short lived and decay; the charged pions to electrons and
+positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to gamma rays.
+Due to the low density of the
 ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume
@@
 detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ --
-within which the mean density is 500 times the critical density -- suggesting again a substantial
+the radius within which the mean density is 500 times the critical density -- suggesting again a substantial
 non-thermal pressure contribution on large scales \citep{article:Mahdavi_etal:2008}. High-energy
@@
 While several observations of clusters of galaxies have been made with satellite-borne and
-ground-based telescopes, a detection of gamma-ray emission from a cluster has yet to be made.
-Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the Fermi
-Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the
+ground-based gamma-ray telescopes, a detection of gamma-ray emission from a cluster has yet to be
+made. Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the
+Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the
 gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several
-galaxy clusters in the 100 MeV to GeV band. Upper limits on the VHE gamma-ray flux from a few
-select clusters, including the Coma cluster, have been provided by observations with ground-based
-imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006,
+galaxy clusters in the MeV to GeV band. Upper limits on the very-high-energy (VHE) gamma-ray flux
+from a few select clusters, including the Coma cluster, have been provided by observations with
+ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006,
 inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
@@
 The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter
-imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an
-altitude of 1268 m a.s.l. at the Fred Lawrence Whipple Observatory in southern Arizona
-(31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes
-is equipped with a 499 pixel camera covering a 3.5$^{\circ}$ field of view. The array, completed in
-the spring of 2007, is designed to detect gamma-ray emission from astrophysical objects in the
-energy range from 100 GeV to more than 30 TeV. The energy resolution is about 15\% and the angular
-resolution (68\% containment) is about 0.1$^{\circ}$ per event at 1 TeV. The sensitivity of the
-array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux
-above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity
-above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009. The
-move had no impact on the this data set.}
+IACTs \citep{article:Holder_etal:2006} located at an altitude of 1268 m a.s.l. at the Fred Lawrence Whipple
+Observatory in southern Arizona (31$^{\circ}$~40\arcmin~30\arcsec~N,
+110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes is equipped with a 499 pixel camera
+covering a 3.5$^{\circ}$ field of view. The array, completed in the spring of 2007, is designed to detect
+gamma-ray emission from astrophysical objects in the energy range from 100 GeV to more than 30 TeV.
+The energy resolution is about 15\% and the angular resolution (68\% containment) is about 0.1$^{\circ}$
+per event at 1 TeV. The sensitivity of the array allows for detection of a point source with a flux of 1\% of
+the steady Crab Nebula flux above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The
+integral flux sensitivity above 300 GeV was improved by about 30\% with the move of one telescope in
+the summer of 2009. The move had no impact on this data set.}
 
@@
 used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level)
-and a photon index of -2.4 using data taken on the Crab Nebula during the same epoch and are termed
-\emph{standard} cuts. Because the VHE gamma-ray spectrum for the Coma cluster is expected to be
-hard, photon index of about -2.3, these standard cuts are suitable for the analysis of the Coma
-cluster data set.
+and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because the
+VHE gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about 2.3,
+these cuts are suitable for the analysis of the Coma cluster data set.
 
@@
 
-\section{VERITAS Results}
+\subsection{VERITAS Results}
 No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as
@@
 within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the
-radio spectral index of the giant radio halo of Coma after accounting for the spectral steepening at
-frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
-\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
+radio spectral index of the giant radio halo of the Coma cluster after accounting for the spectral
+steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
+\citep{article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
 responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
-  times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}.  To model
+times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.} To model
 the thermal pressure, we adopt the electron density profile for the Coma cluster that has been
@@
 
-Table \ref{table:constraints} shows the resulting constraints on the relative CR pressure, $X_{\CR}
+Table \ref{table:constraints_simple} shows the resulting constraints on the relative CR pressure, $X_{\CR}
 = \expval{P_{\CR}}/\expval{P_\rmn{th}}$, averaged within the virial radius, $R_\rmn{vir}=2.2$~Mpc,
@@
 comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies. The
-limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$ between 0.048 and 0.43
+limits within 0.2$^{\circ}$ are the most constraining, yielding limits on $X_\CR$ between 0.048 and 0.43
 (for $\alpha$ varying between 2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close
@@
 gamma-ray model developed by \citet{article:PinzkePfrommer:2010} to estimate the emission from
-decaying neutral pions that dominates over the IC emission from primary and secondary electrons
-above 100 MeV in clusters.  Given a density profile as, e.g., inferred by cosmological simulations
-or X-ray observations, the analytic approach models the CR distribution and the associated radiative
-emission processes from radio to the gamma-ray band. This formalism was derived from high-resolution
-simulations of clusters of galaxies that included radiative hydrodynamics, star formation, supernova
-feedback, and followed CR physics by tracing the most important injection and loss processes
-self-consistently while accounting for the CR pressure in the equation of motion
+decaying neutral pions that dominates over the inverse Compton (IC) emission from primary and
+secondary electrons above 100 MeV in clusters.  Given a density profile as, e.g., inferred by
+cosmological simulations or X-ray observations, the analytic approach models the CR distribution and
+the associated radiative emission processes from radio to the gamma-ray band. This formalism was
+derived from high-resolution simulations of clusters of galaxies that included radiative hydrodynamics,
+star formation, supernova feedback, and followed CR physics by tracing the most important injection
+and loss processes self-consistently while accounting for the CR pressure in the equation of motion
 \citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007,
@@
 results on some of the overall characteristics of the CR distribution and the associated radiative
-emission processes \citep{article:DolagEnsslin, article:MiniatiRyuKangJones:2001,
+emission processes \citep{article:DolagEnsslin:2000, article:MiniatiRyuKangJones:2001,
   article:Miniati:2003, article:Pfrommer_etal:2007, article:PfrommerEnsslinSpringel:2008,
@@
 
-We adopt the electron density profile as in Sect.~\ref{sec:simple} and model the temperature profile
-of Coma with a constant central temperature of $kT= 8.25$~keV and a characteristic decline toward
-the cluster periphery in accordance with a fit to the universal profile derived from cosmological
-cluster simulations \citep{article:PinzkePfrommer:2010, article:Pfrommer_etal:2007} that also
-follows the behavior of a nearby sample of deep {\em Chandra} cluster data
-\citep{2005ApJ...628..655V}. This enables us to adopt the spatial and spectral distribution of CRs
-according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of
-cluster galaxies.
+We adopt the electron density profile as in \S \ref{sec:simple} and model the temperature profile
+of the Coma cluster with a constant central temperature of $kT= 8.25$~keV and a characteristic
+decline toward the cluster periphery in accordance with a fit to the universal profile derived from
+cosmological cluster simulations \citep{article:PinzkePfrommer:2010, article:Pfrommer_etal:2007} that
+also follows the behavior of a nearby sample of deep {\em Chandra} cluster data
+\citep{article:Vikhlinin_etal:2005}. This enables us to adopt the spatial and spectral distribution
+of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution
+of cluster galaxies.
 
@@
 finited energy intervals across the angular apertures tested in this study (solid lines). These
-modeled fluxes a compared to {\em Fermi} and VERITAS flux upper limits of the same energy intervals,
+model fluxes are compared to {\em Fermi} and VERITAS flux upper limits of the same energy intervals,
 summarized in Table \ref{table:constraints}.  The gamma-ray flux limit of {\em Fermi} in the energy
@@
 section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential
-gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the
-astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends
-on the DM distribution.
-
-Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\ \mathrm{CL})$, we can place
+gamma-ray yield per annihilation,\footnote{In this work, we have calculated the differential
+gamma-ray yield per annihilation using the Pythia Monte Carlo simulator.} $\Delta\Omega$ is the
+observed solid angle, and $J$ is the astrophysical factor - a dimensionless factor which determines
+the DM annihilation rate and depends on the DM distribution.
+
+Given the upper limit on the observed gamma-ray rate,
+$R_{\gamma}(95\%\ \mathrm{CL}) = N_{\gamma}(95\%\ \mathrm{CL}) / T_{\mathrm{obs}}$, we can place
 constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. From Eq.
@@
 \end{equation}
-The astrophysical factor $J$ can be expressed as
+Because the self-annihilation of a WIMP is a two-body process, the astrophysical factor
+$J(\Delta\Omega)$ can be expressed as the line-of-sight integral of the DM density squared
 \begin{equation}
@@
 \end{equation}
-where $\lambda$ represents the line-of-sight. Because the self-annihilation of a WIMP is a two-body
-process, $J(\Delta\Omega)$ is proportional to the square of the DM density $\rho$. Here,
+where $\lambda$ represents the line-of-sight. Here,
 $J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the
-Hubble radius, $R_{H}$.
-
-In this work we have adopted the DM density profile by Navarro-Frenk-White
-\citep[NFW;][]{article:NavarroFrenkWhite:1997},
+Hubble radius, $R_{H}$. In this work we have adopted the DM density profile by
+Navarro-Frenk-White \citep[NFW;][]{article:NavarroFrenkWhite:1997},
 \begin{equation}
@@
 which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density
-$\rho_{s}$. [how where these calculated?]
-
-%When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result
-%from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated
-%background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor
-%no longer compensate for the increased count of background events and the signal-to-noise
-%deteriorates.
+$\rho_{s}$. Using weak-lensing measurements of the virial mass in the Coma cluster
+\citep{article:Gavazzi_etal:2009} we obtained the values $r_{s}=0.654$ Mpc and
+$\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
+astrophysical factor calculated for the different VERITAS appertures considered in this work.
+It also lists the astrophysical factor calculated for the background region, which has been used
+to estimate the gamma-ray contamination due to DM in the background region.
+
+The resulting exclusion regions in the $(\expval{\sigma v}, m_{\chi})$ parameter space are shown in
+Figure \ref{fig:dm} for three different DM self-annihilation channels: W$^{+}$W$^{-}$,
+b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$. Depending on the chosen apperture the limits are on
+the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The numerical values for each of the channels
+are listed in Table \ref{table:DMlimits}. We note that these are based on conservative estimates of the
+astrophysical factor $J$.
+
+We also note that when the size of the integration region is increased, the limits on $\expval{\sigma v}$
+result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated
+background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor
+no longer compensate for the increased count of background events and the signal-to-noise
+deteriorates.
 
@@
 Fermi.} 
-\label{table:constraints}
+\label{table:constraints_simple}
 \end{deluxetable}
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on magnetic fields in the hadronic model of
-    the Coma radio halo and the corresponding relative CR pressure (at
-    the largest emission radius) such that the model reproduces the observed
-    radio surface brightness profile.}
+\tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo and the
+corresponding relative CR pressure (at the largest emission radius) such that the model reproduces the
+observed radio surface brightness profile.}
 \tablehead{

### 2011-09-14 ms.tex
Incorporated Martin's edits

@@
 
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft
-X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these
-temperatures primarily through collisionless structure-formation shocks that form as a result of the
+The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung in the soft
+X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated
+primarily through collisionless structure-formation shocks that form as a result of the
 hierarchical merging and accretion processes. Such shocks and turbulence in the ICM gas and
@@
 electrons and positrons (leptons) and magnetic fields permeating the ICM
-\citep{article:Cassano_etal:2010}. The two competing theories seeking to explain the radio halo
-emission feature the ``hadronic model'' where the radio-emitting electrons are produced in inelastic
-collisions of cosmic-ray (CR)  ions with thermal gas protons from the ICM \citep[][and references
-therein]{article:EnsslinPfrommerMiniatiSubramanian:2011} and the ``re-acceleration model'' where a
-CR electron population within the ICM at energies around 100 MeV might be sufficiently long lived so
-that during states of powerful ICM turbulence, e.g., after a cluster merger, non-resonant
-interactions of these CR electrons with plasma waves might be efficient enough to accelerate them to
-high enough energies ($\sim 10$~GeV) for them to emit observable radio emission
-\citep[][and references therein]{article:BrunettiLazarian:2010}. Recent observations of possible
-non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998}
-and hard X-rays \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004,
-article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters,
-although the interpretation of these observations as non-thermal diffuse emission have been disputed on
-the basis of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
-article:Ajello_etal:2010, article:Wik_etal:2009}.
+\citep{article:Cassano_etal:2010}. The two theories competing to explain the radio halo
+are the ``hadronic model'', in which the radio-emitting electrons are produced in inelastic
+collisions of cosmic-ray (CR)  ions with thermal gas of the ICM \citep{article:Dennison:1980},
+%\citep[][and references therein]{article:EnsslinPfrommerMiniatiSubramanian:2011}
+and the ``re-acceleration model'', in which during states of strong ICM turbulence, e.g. after a
+cluster merger, interactions of a long-lived pool of 100-MeV electrons with plasma waves might
+be efficient enough to accelerate them to energies ($\sim 10$ GeV) sufficient to produce observable
+radio emisson \citep[][and references therein]{article:BrunettiLazarian:2010}. Recent observations of
+possibly non-thermal emission from clusters in the the extreme ultraviolet
+\citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of
+relativistic particle populations in clusters, although the interpretation of these observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations
+\citep[see, e.g.,][]{article:Ajello_etal:2009, article:Ajello_etal:2010, article:Wik_etal:2009}.
 
 Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration
-in the ICM is an efficient process, a population of highly relativistic CR hadrons,
-in the form of protons and heavy ions, in the ICM is to be expected. The main energy-loss
-mechanism for CR hadrons at high energies is pion production through the interaction of CRs with
-nuclei in the ICM. Pions are short lived and decay; the charged pions to electrons and
-positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to gamma rays.
-Due to the low density of the
-ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume
-filling magnetic fields in the ICM, CR hadrons will be confined in the cluster on timescales
-comparable and longer than the Hubble time \citep[][]{article:Volk_etal:1996,
+in the ICM is an efficient process, a population of highly relativistic CR protons and heavy ions is to
+be expected in the ICM. The main energy-loss mechanism for CR hadrons at high energies is pion
+production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay; the
+charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
+which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to
+gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
+scales of a cluster and the volume filling magnetic fields in the ICM, CR hadrons will be confined in
+the cluster on timescales comparable to or longer than the Hubble time \citep[][]{article:Volk_etal:1996,
 article:Berezinsky_etal:1997} allowing them to accumulate over time. Depending on the CR pressure,
@@
 
-Moreover, a substantial value of $X_\CR$ can bias hydrostatic cluster masses as well as the
+A substantial value of $X_\CR$ can bias hydrostatic estimates of cluster masses as well as the
 temperature decrement of the cosmic microwave background (CMB) in the direction of a galaxy cluster
-due to the Sunyaev-Zel'dovich effect which is proportional to the line-of-sight integral of the
-thermal electron pressure. This could then severely jeopardize the use of clusters to determine
-cosmological parameters. Comparing X-ray and optical potential profiles in the centers of galaxy
-clusters yields an upper limit of 20--30 \% of non-thermal pressure (that can be composed of CRs,
-magnetic fields or turbulence) relative to the thermal gas pressure
+due to the Sunyaev-Zel'dovich effect. This could then severely jeopardize the use of clusters to
+determine cosmological parameters. Comparing X-ray and optical potential profiles in the centers of
+galaxy clusters yields an upper limit of 20-30 \% of non-thermal pressure (that can be composed of
+CRs, magnetic fields or turbulence) relative to the thermal gas pressure
 \citep{article:Churazov_etal:2008, article:Churazov_etal:2010}. An analysis that compares spatially
 resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters
-detects a deficit of the hydrostatic in comparison to the lensing mass of $20 \%$ at $R_{500}$ --
-the radius within which the mean density is 500 times the critical density -- suggesting again a substantial
-non-thermal pressure contribution on large scales \citep{article:Mahdavi_etal:2008}. High-energy
-gamma-ray emission is a complementary method of constraining the pressure contribution of CRs that
-is most sensitive to the cluster core region. However, it assumes that the CR component is fully
-mixed with the ICM and almost insensitive in detecting a two-phase structure of CRs and the thermal
-ICM.  A fraction $X_\CR$ of only a few percent is required in order to produce a gamma-ray flux
-observable with current generation gamma-ray telescopes rendering this technique at least as
-sensitive as the dynamical and hydrostatic method (which are however more general in that they are
-sensitive to any non-thermal pressure component).
+detects a deficit of the hydrostatic mass estimate compared to the lensing mass of $20 \%$ at
+$R_{500}$ -- the radius within which the mean density is 500 times the critical density --
+suggesting again a substantial non-thermal pressure contribution on large scales
+\citep{article:Mahdavi_etal:2008}. Observing high-energy gamma-ray emission is a complementary
+method of constraining the pressure contribution of CRs that is most sensitive to the cluster core
+region. However, it assumes that the CR component is fully mixed with the ICM and may not a
+two-phase structure of CRs and the thermal ICM. A fraction $X_\CR$ of only a few percent is
+required in order to produce a gamma-ray flux observable with current generation gamma-ray
+telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method
+(which are more general in that they are sensitive to any non-thermal pressure component).
 
@@
 mentioned CR interactions or be injected into the ICM by powerful cluster members and be further
-accelerated by diffusive shock acceleration or turbulent reacceleration processes.
+accelerated by diffusive shock acceleration or turbulent reacceleration processes
+\citep[][and references therein]{article:SchlickeiserSieversThiemann:1987}.
 
@@
 particle, e.g. a weakly interacting massive particle (WIMP). As already mentioned, about 80\% of
-the cluster mass is in the form of dark matter. Recent works \citep{article:EvansFerrerSarkar:2004,
-article:BergstromHooper:2006} have shown that the gamma-ray emissivity from DM annihilations is
-expected to be proportional to the square of the DM density integrated along the line of sight,
-making clusters of galaxies potentially good candidates for DM searches
-\citep{article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011}. This despite their large
-distances compared to other common targets for DM searches, such as dwarf spheroidal galaxies
-\citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009} or the
-Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
+the cluster mass is in the form of dark matter. The gamma-ray emissivity from DM annihilations is
+proportional to the square of the DM density integrated along the line of sight, making galaxy clusters
+potentially good candidates for DM searches \citep{article:EvansFerrerSarkar:2004,
+article:BergstromHooper:2006, article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011},
+despite their large distances compared to other common targets for DM searches, such as dwarf
+spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009}
+or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
 article:Aharonian_etal:2009b}.
@@
 radio relic, which appears connected to the radio halo with a ``diffuse'' bridge 
-\citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested that the relic is an
-infall shock \citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological
-simulations that model the non-thermal emission processes
-\citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008, article:Battaglia_etal:2009,
-article:Skillman_etal:2011}. Extended soft thermal X-ray (SXR) emission is evident from the ROSAT
-all-sky survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992} and observations
-with XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo with
-substantial turbulent pressure support that shows a lower limit of $\sim 10 \%$ of the total
-intracluster medium pressure \citep{article:Schuecker_etal:2004}. As such it is a natural candidate
-for gamma-ray observations.
+\citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested
+\citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations, which
+model the non-thermal emission processes, \citep{article:PfrommerEnsslinSpringel:2008,
+article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}, that the relic is
+an infall shock. Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky
+survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992}. Observations with
+XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo supported by
+substantial turbulent pressure of at least $\sim 10 \%$ of the total pressure
+\citep{article:Schuecker_etal:2004}. The Coma cluster is a natural candidate for gamma-ray
+observations.
 
@@
 The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter
-IACTs \citep{article:Holder_etal:2006} located at an altitude of 1268 m a.s.l. at the Fred Lawrence Whipple
-Observatory in southern Arizona (31$^{\circ}$~40\arcmin~30\arcsec~N,
-110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes is equipped with a 499 pixel camera
-covering a 3.5$^{\circ}$ field of view. The array, completed in the spring of 2007, is designed to detect
-gamma-ray emission from astrophysical objects in the energy range from 100 GeV to more than 30 TeV.
-The energy resolution is about 15\% and the angular resolution (68\% containment) is about 0.1$^{\circ}$
-per event at 1 TeV. The sensitivity of the array allows for detection of a point source with a flux of 1\% of
-the steady Crab Nebula flux above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The
-integral flux sensitivity above 300 GeV was improved by about 30\% with the move of one telescope in
-the summer of 2009. The move had no impact on this data set.}
+imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an
+altitude of 1268 m a.s.l. at the Fred Lawrence Whipple Observatory in southern Arizona
+(31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes
+is equipped with a 499 pixel camera covering a 3.5$^{\circ}$ field of view. The array, completed in
+the spring of 2007, is designed to detect gamma-ray emission from astrophysical objects in the
+energy range from 100 GeV to more than 30 TeV. The energy resolution is about 15\% and the angular
+resolution (68\% containment) is about 0.1$^{\circ}$ per event at 1 TeV. The sensitivity of the
+array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux
+above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity
+above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009. The
+move had no impact on this data set.}
 
@@
 these scenarios. In this work the focus has been on the core region and three cluster members. The
-latter are treated as point sources in the analysis, whereas the core is treated as both a point
-source and a mildly extended source. The intrinsic source extension is assumed to be $0.2^{\circ}$
-and $0.4^{\circ}$, based on the extension of the thermal soft X-ray emission from the core. There
+latter are treated as point sources in the analysis, whereas the core is treated as either a point
+source or a mildly extended source with intrinsic source radius $0.2^{\circ}$ or $0.4^{\circ}$,
+similar to the extension of the thermal soft X-ray emission from the core. There
 is evidence of a recent merger event between the two central galaxies NGC 4889 and NGC 4874
@@
 \section{Gamma Ray Emission from Cosmic Rays}
-We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution in
-the Coma cluster with the VERITAS and \emph{Fermi}-LAT upper limits from this work. This approach
-includes (1) a simplified multi-frequency analytical approach that assumes a constant CR-to-thermal
-energy density and a power-law spectrum in momentum, (2) an analytic model derived from cosmological
-hydrodynamical simulations of the formation of galaxy clusters, and (3) an approach that uses the
+We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution
+in the Coma cluster using the upper limits dereived from VERITAS and \emph{Fermi}-LAT data in this
+work. This approach includes (1) a simplified multi-frequency analytical approach that assumes a
+constant CR-to-thermal energy density and a power-law spectrum in momentum, (2) an analytic model
+derived from cosmological hydrodynamical simulations of the formation of galaxy clusters, and (3)
+an approach that uses the
 observed luminosity of the giant radio halo in Coma to place a lower limit on the expected
@@
 match the observed radio data, this enables us to derive a lower limit on the magnetic field
-distribution. This approach, however, assumes the validity of the hadronic interaction model in
-explaining the radio halo data.  Modelling the CR distribution through different techniques enable
+distribution. We stress again that his approach assumes the validity of the hadronic interaction
+model. Modelling the CR distribution through different techniques enable
 us to bracket our ignorance about the underlying plasma physics that shape the CR distribution and
@@
 with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution
-function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is unconstrained, we vary it
-within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the
+function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is unconstrained, we vary it in
+the range $2.1<\alpha_{\rmn{p}}<2.5$, which is compatible with the
 radio spectral index of the giant radio halo of the Coma cluster after accounting for the spectral
@@
 comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies. The
-limits within 0.2$^{\circ}$ are the most constraining, yielding limits on $X_\CR$ between 0.048 and 0.43
+flux measurements within 0.2$^{\circ}$ are the most constraining and yield limits on $X_\CR$
+between 0.048 and 0.43
 (for $\alpha$ varying between 2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close
@@
 \subsection{Simulation-based approach}
-
 We complement the simplified analytical analysis with a more realistic and predictive approach
@@
 gamma-ray model developed by \citet{article:PinzkePfrommer:2010} to estimate the emission from
-decaying neutral pions that dominates over the inverse Compton (IC) emission from primary and
-secondary electrons above 100 MeV in clusters.  Given a density profile as, e.g., inferred by
+decaying neutral pions which in clusters dominates over the inverse Compton (IC) emission above
+100 MeV. Given a density profile as, e.g., inferred by
 cosmological simulations or X-ray observations, the analytic approach models the CR distribution and
@@
 
-The overall normalization of the CR and gamma-ray distribution scales (non-linearly) with the
-maximum acceleration efficiency at structure formation shock waves. Following recent observations at
+The overall normalization of the CR and gamma-ray distribution scales non-linearly with the
+acceleration efficiency at structure formation shock. Following recent observations at
 supernova remnants \citep{article:Helder_etal:2009} as well as theoretical studies
@@
 at the present time (at the boundary of voids and filaments/super-cluster regions) dominate the
-injection of CRs which are adiabatically transported through the cluster. Hence, these model
-predictions provide a plausible upper limit for the CR contribution from structure formation shocks
+injection of CRs which subsequently are adiabatically transported through the cluster. Hence, the model
+provides a plausible upper limit for the CR contribution from structure formation shocks
 in galaxy clusters which can be scaled with the effective acceleration efficiency. Other possible CR
@@
 These cosmological simulations only considered advective transport of CRs by turbulent gas motions
-which produces centrally enhanced profiles.  However, other means of CR transport such as diffusion
+which lead to centrally enhanced density profiles.  However, other means of CR transport such as diffusion
 and streaming may flatten the CR radial profiles. It has been suggested that advection is dominant
@@
 
-We adopt the electron density profile as in \S \ref{sec:simple} and model the temperature profile
+We adopt the density profile of thermal electrons as discussed in \S \ref{sec:simple} and model the
+temperature profile
 of the Coma cluster with a constant central temperature of $kT= 8.25$~keV and a characteristic
 decline toward the cluster periphery in accordance with a fit to the universal profile derived from
-cosmological cluster simulations \citep{article:PinzkePfrommer:2010, article:Pfrommer_etal:2007} that
-also follows the behavior of a nearby sample of deep {\em Chandra} cluster data
+cosmological cluster simulations \citep{article:PinzkePfrommer:2010, article:Pfrommer_etal:2007}
+and the behavior of a nearby sample of deep {\em Chandra} cluster data
 \citep{article:Vikhlinin_etal:2005}. This enables us to adopt the spatial and spectral distribution
@@
 interval of 1--3 GeV ($<0.4^\circ$) is most constraining but still above the model predictions that
-assume an optimistic value of the shock acceleration efficiency and CR transport parameters as laid
+assume an optimistically large shock acceleration efficiency and CR transport parameters as laid
 out above.  In our further analysis, we use the most constraining {\em Fermi} flux limits in the
@@
 radius, $R_\rmn{vir}=2.2$~Mpc. To compute the CR pressure, we assume a low-momentum cutoff of the CR
-distribution at $q = 0.8\,m_p c$ as found in the cosmological simulations which reflects the high
-cooling rates at low CR energies. The relative CR pressure rises toward the outer regions on account
-of the higher efficiency of CR acceleration at the peripheral strong accretion shocks compared to
-weak central flow shocks. Adiabatic compression of a mixture of CRs and thermal gas disfavours the
+distribution at $q = 0.8\,m_p c$ to reflect tge high cooling rates at low CR energies. The relative CR
+pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the
+peripheral accretion shocks compared to the weak central flow shocks. Adiabatic compression of a
+mixture of CRs and thermal gas disfavours the
 CR pressure relative to the thermal pressure on account of the softer equation of state of CRs. The
-weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas
-which diminishes the thermal support relative to that in CRs.
+weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas.
 
 In the case of VERITAS, for the most constraining regions tested (within an aperture of radius
-0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table
+0.2$^{\circ}$), the predicted CR pressure is a factor of 7.2 below the inferred upper limits of VERITAS
+(see Table
 \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at
-energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by that
+energies $E_\gamma=200$ GeV). To first order, we can scale the averaged relative CR pressure of
+our model by that
 factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
@@
 
-Equivalently, the most constraining {\em Fermi} upper limit in the energy interval of 1--3 GeV
+Equivalently, the most constraining {\em Fermi} upper limit in the energy interval of 1-3 GeV
 ($<0.4^\circ$) is a factor of 1.1 larger than our model predictions (assuming $\alpha=2.1$ which is
@@
 comparison to the simplified power-law model in comparison to the universal CR spectrum with its
-concave curvature found in the simulations.
+concave CR spectrum found in the simulations.
 
@@
 \label{sec:Fmin}
-For clusters that host radio halos we are able to derive a minimum gamma-ray flux in the hadronic
-model of radio halos -- where the radio-emitting electrons are secondaries from CR interactions. The
-idea is based on the fact that a stationary distribution of CR electrons loses all its energy to
-synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G) so that the
+For clusters that host radio halos we can derive a minimum gamma-ray flux in the hadronic
+model of radio halos -- where the radio-emitting electrons are secondaries from CR interactions. 
+Hadronic interactions channel about the same power into secondary electrons and $\pi^{0}$-decay
+gamma rays. A stationary distribution of CR electrons loses all its energy to
+synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G), and thus the
 ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and
@@
 CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/\tilde{F}$ are shown in Table
-\ref{table:constraints}, where $F_\rmn{iso} = X_\CR\,\tilde{F}$ is the gamma-ray flux in the {\em
-isobaric model of CRs} introduced in the previous section. Even in the most constraining cases,
+\ref{table:constraints}, where $F_\rmn{iso} = X_\CR\,\tilde{F}$ is the gamma-ray flux in the simplified
+model introduced in \S\ref{sec:simple}. Even in the most constraining cases,
 these are a factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$,
@@
 \label{sec:B}
-We have seen in the previous section that we can obtain an absolute lower limit on the gamma-ray
-emission in the hadronic model by assuming high magnetic fields, $B\gg B_\rmn{CMB}$. Hence, we can
-turn this around by using our upper limit on the gamma-ray emission (and by extension on the CR
-pressure) to infer a lower limit on the magnetic field that is needed to explain the observed radio
-emission \citep{article:PfrommerEnsslin:2004a}. This, however, assumes the validity of the hadronic
-model of radio halos -- where the radio-emitting electrons are secondaries from CR
-interactions. Lowering the gamma-ray constraint will tighten (increase) the magnetic field
-limit. Once this gets in conflict with magnetic field measurements by means of other methods, e.g.,
-Faraday rotation measure (RM)\footnote{Generally, Faraday RM analysis of the magnetic-field strength
-  by, e.g., background sources through clusters are degenerate with the magnetic coherence scale and
-  may be biased by the unknown correlation between magnetic and density fluctuations.}, this would
-challenge the hadronic model of radio halos. The method that we use to constrain the magnetic field
-inherits a dependence on the assumed spatial structure that we parametrize by
+In the previous section we have obtained an absolute lower limit in the gamma-ray emission in
+the hadronic model by assuming high magnetic fields, $B\gg B_\rmn{CMB}$. We can turn the
+argument around and use our upper limit on the gamma-ray emission (and by extension on the
+CR pressure) to infer a lower limit on the magnetic field needed to explain the observed radio
+emission. This, again, assumes the validity of the hadronic model of radio halos, in which the
+radio-emitting electrons are secondaries from CR interactions. Lowering the gamma-ray
+constraint will tighten the magnetic field limit. In case of a conflict with magnetic field
+measurements by other methods, e.g., Faraday rotation measure (RM),\footnote{Generally,
+Faraday RM analysis of the magnetic field strength by, e.g., background sources through
+clusters are degenerate with the magnetic coherence scale and may be biased by the unknown
+correlation between magnetic and density fluctuations.} the hadronic model of radio halos would
+be challenged. The method we use to constrain the magnetic field inherits a dependence on
+the assumed radial scaling which we parameterize as
 \begin{equation}
@@
 RM observations of seven radio-sources located at projected distances of 50 to 1500 kpc from the
-cluster center. The best-fit model obtains $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and
+cluster center. The best-fit model yields $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and
 $\alpha_{B} = 0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim for constraining the
-central field strength, $B_{0}$, which depends on the magnetic decline, $\alpha_{B}$, that we vary
-(within reasonable ranges of $\Delta\alpha_{B}=0.2$ as suggested from the Faraday RM studies) to
-address this dependence. We proceed as follows:
+central field strength, $B_{0}$, and permit the magnetic decline, $\alpha_{B}$, to vary
+within a reasonable range of $\Delta\alpha_{B}=0.2$ as suggested by the Faraday RM studies.
+We proceed as follows:
 
@@
 Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we determine
-the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced
-synchrotron emission exactly matches the observed radio halo emission over the entire extent. To 
+the profile of the relative CR pressure, $X_{\CR}(r)$, by matching the hadronically produced
+synchrotron emission to the observed radio halo emission over the entire extent. To 
 this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel
@@
 simplicity), the radial decline of the magnetic field, $\alpha_{B}$, and our initial guess for
-$B_0$.
+$B_{0}$.
 
 \item
-We then solve for $B_{0}$ subject to the boundary condition to match the observed synchrotron
-profile while fixing the profile of $X_{\CR}(r)$ as determined through the previous two steps. Note
+We then solve for $B_{0}$ while matching the observed synchrotron profile while fixing the profile
+of $X_{\CR}(r)$ as determined through the previous two steps. Note
 that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution
@@
 Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
-$B_\rmn{CMB}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as a
+$B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as a
 function of magnetic field strength. Hence we have to iterate through the previous steps until our
-solution for the minimum magnetic field $B_0$ is converged.
+solution for the minimum magnetic field $B_{0}$ is converged.
 \end{enumerate}
 
-Table \ref{table:Bmin} shows the results on the lower limit of the central magnetic field that
-range for the VERITAS limits from $B_{0} = 0.5$ to $1.4\,\mu$G and for the {\em Fermi} limits from
-$B_{0} = 1.1$ to $4.6\,\mu$G.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds
+Table \ref{table:Bmin} shows the resulting lower limit of the central magnetic field that
+range from $B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from
+$B_{0} = 1.1$ to $4.6\,\mu$G in the case of \emph{Fermi}.\footnote{Note that a central magnetic
+field of $3\,\mu$G corresponds 
 in the Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits
-on $B_0$ are below the values favored by Faraday RM for the entire parameter space spanned by
-$\alpha_B$ and $\alpha$, the hadronic model is perfectly viable.  This indicates the power of
-future gamma-ray observations of Coma in constraining parameters of the hadronic model.
-
-In addition there are a few interesting remarks in order. (1) For the VERITAS limits, the hardest
-CR spectral indices correspond to the tightest limits on $B_0$. This is because for an upper limit
-of CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a
-comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting electrons.
-In order to reproduce the observed synchrotron emission, this allows for smaller magnetic fields.
-The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a pivot point
-of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100 GeV and
-hence decreases the radio-emitting secondary electrons. Equivalently larger magnetic fields are
-needed to compensate for this in order to match the observed synchrotron flux.  (2) For a steeper
+on $B_{0}$ are below the values favored by Faraday RM for the entire parameter space spanned by
+$\alpha_{B}$ and $\alpha$, the hadronic model is still viable. Future gamma-ray observations of
+the Coma cluster may put more stringent constraints on the parameters of the hadronic model.
+
+A few remarks are in order. (1) For the VERITAS limits, the hardest
+CR spectral indices correspond to the tightest limits on $B_{0}$, because the CR flux is constrained
+around 1 TeV and a comparably small fraction of CRs at 100 GeV would be available to produce
+radio-emitting electrons. A high magnetic field would be required to match the observed
+synchrotron emission. The opposite is true for the \emph{Fermi} upper limits at 1 GeV, which
+probe CRs around a pivot point of 8 GeV: a soft CR spectral index implies a comparably small
+fraction of CRs at 100 GeV and hence a strong magnetic field is needed to match the observed
+synchrotron flux. (2) For a steeper
 magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the
@@
 are more constraining. This implies tighter lower limits for $B_{0}$.  (3) Interestingly, in all
-cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic
-field configurations.  This is because we need a substantially increasing relative CR pressure
-profile to match the observed radio profiles (for a given magnetic realization); hence that CR
-realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model''
-assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more
-constraining in the case of VERITAS; hence the constraints on $B_{0}$ get better for the larger
-integration area. Physically, this may be achieved by considering CR transport processes such as
-streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in
-the outer cluster regions.
+cases, the 0.4$^{\circ}$-aperture limits that are the most constraining. For a given magnetic
+realization a substantially increasing relative CR pressure profile is needed to match the
+observed radio profiles, and therefore that CR realization produces a larger flux within 0.4$^{\circ}$
+in comparison with the simplified CR model ($X_{\CR} = \rmn{const.}$). for which the
+0.2$^{\circ}$-aperture limits are more constraining in the case of VERITAS. Physically, the large
+CR pressure in the cluster periphery may arise from CR streaming into the large available phase
+space in the outer regions.
 
@@
 conventional astrophysical sources. The spectrum will also feature a very sharp cutoff at the WIMP
-mass. Observations of these spectral features together with the expected difference in spatial
-distribution of the gamma-ray flux compared to conventional astrophysical sources allows for a
-unique means to indirectly detect DM.
+mass. Observations of these spectral characteristics together with the expected difference in spatial
+distribution of the gamma-ray intensity compared to conventional astrophysical sources allows for a
+an indirect detection DM.
 
@@
 $\rho_{s}$. Using weak-lensing measurements of the virial mass in the Coma cluster
-\citep{article:Gavazzi_etal:2009} we obtained the values $r_{s}=0.654$ Mpc and
+\citep{article:Gavazzi_etal:2009} we find for these parameters $r_{s}=0.654$ Mpc and
 $\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
@@
 are listed in Table \ref{table:DMlimits}. We note that these are based on conservative estimates of the
-astrophysical factor $J$.
+astrophysical factor $J$, as we do not assume boosting by clumping or the Sommerfeld effect.
 

### 2011-09-19 ms.tex
New first paragraph of the abstract

@@
 Theoretical models of galaxy clusters suggest they may be sources of very high-energy (VHE)
-gamma-ray emission. Observations of radio halos and relics in clusters indicate populations of
-relativistic electrons, which are either injected into the intra-cluster medium and accelerated by
-turbulent shocks or secondaries from interactions of cosmic-ray hadrons (protons and ions) with
-the intra-cluster gas. Those interactions could also produce gamma rays through the decay of
-neutral pions. Reported here are observations of the Coma cluster of galaxies with the VERITAS
-array of imaging Cherenkov telescopes. The observations were made between March and May
-2008. Radio observations at 1.41 GHz taken with the Green Bank Telescope and X-ray observations
-with the ROSAT All-Sky survey was used to a priori select regions of interest in the field of view.
-No significant VHE gamma-ray emission from the Coma cluster was detected by VERITAS. Several
-emission regions are considered, including the cluster core as both unresolved (point-like) and
-spatially extended, and a select few cluster members. The flux upper limits at the 99\% confidence
-level measured are on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$ s$^{-1}$, which is two orders
-of magnitude higher than model-predicted minimum gamma-ray fluxes.
-
-The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray particles
-and magnetic fields and in the Coma cluster of galaxies. The relative cosmic-ray pressure,
-$X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$, is on the order of 10-20\% when assuming
-a gamma-ray photon index $\alpha=2.3$. The observations imply a lower limit on the intra-cluster
-magnetic field on the order of a $\mu$G, depending on the magnetic decline and gamma-ray spectral
-index. Finally, a constraint on the thermally averaged product of the total self-annihilation
+gamma-ray emission. Observations of radio halos and relics in clusters are indicative efficient
+acceleration processes and the gamma-ray emission is the result of highly relativistic
+cosmic-ray protons and ions interacting with intracluster gas and magnetic fields. Reported
+here are VHE gamma-ray observations of the Coma cluster of galaxies with the VERITAS array
+of imaging Cherenkov telescopes, with complementing Fermi Gamma-ray Space Telescope
+observations at GeV energies. No significant gamma-ray emission from the Coma cluster
+was detected. Flux upper limits at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS, $>$220 GeV) and
+$\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ ({\em Fermi}, 1-3 GeV), respectively. The limits are
+two orders of magnitude higher than model-predicted minimum gamma-ray fluxes, which
+assumes the radio-emitting electrons to be all secondaries from cosmic-ray interactions.
+
+The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray
+particles and magnetic fields and in the Coma cluster of galaxies. Using a simplified analytical
+approach, the relative cosmic-ray pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$,
+is constrained to be smaller than 20\% from VERITAS data and smaller than 4\% from
+{\em Fermi} data. 
+The observations imply a lower limit on
+the intra-cluster magnetic field on the order of a $\mu$G, depending on the magnetic decline
+and gamma-ray spectral index. Finally, a constraint on the thermally averaged product of the total self-annihilation
 cross section and the relative velocity of the dark-matter particles, $\expval{\sigma v}$,
@@
   model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV and
-  $>220$~GeV (simulation-based model).} \rotate
+  $>220$~GeV (simulation-based model).}
+\rotate
 \tabletypesize{\small}
@@
 radio-emitting electrons are secondaries from CR interactions and corresponding minimum relative
-CR pressures for Coma} \rotate
+CR pressures for Coma}
+\rotate
 \tabletypesize{\small}
@@
 Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph. m$^{-2}$
-s$^{-1}$ {\em (Fermi) energy range}.}
+s$^{-1}$ ({\em Fermi} energy range).}
 \tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the

### 2011-09-20 ms.tex
rewrote abstract

@@
 \begin{abstract}
-Theoretical models of galaxy clusters suggest they may be sources of very high-energy (VHE)
-gamma-ray emission. Observations of radio halos and relics in clusters are indicative efficient
-acceleration processes and the gamma-ray emission is the result of highly relativistic
-cosmic-ray protons and ions interacting with intracluster gas and magnetic fields. Reported
-here are VHE gamma-ray observations of the Coma cluster of galaxies with the VERITAS array
-of imaging Cherenkov telescopes, with complementing Fermi Gamma-ray Space Telescope
-observations at GeV energies. No significant gamma-ray emission from the Coma cluster
-was detected. Flux upper limits at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS, $>$220 GeV) and
-$\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ ({\em Fermi}, 1-3 GeV), respectively. The limits are
-two orders of magnitude higher than model-predicted minimum gamma-ray fluxes, which
-assumes the radio-emitting electrons to be all secondaries from cosmic-ray interactions.
-
-The gamma-ray flux upper limits have been used to constrain the populations of cosmic-ray
-particles and magnetic fields and in the Coma cluster of galaxies. Using a simplified analytical
-approach, the relative cosmic-ray pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/\expval{P_{\rmn{th}}}$,
-is constrained to be smaller than 20\% from VERITAS data and smaller than 4\% from
-{\em Fermi} data. 
-The observations imply a lower limit on
-the intra-cluster magnetic field on the order of a $\mu$G, depending on the magnetic decline
-and gamma-ray spectral index. Finally, a constraint on the thermally averaged product of the total self-annihilation
-cross section and the relative velocity of the dark-matter particles, $\expval{\sigma v}$,
-is derived and found to be $\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$
-GeV/c$^{2}$.
+  Observations of radio halos and relics in galaxy clusters are indicative of efficient acceleration
+  processes of electrons while this process should be even more efficient for protons. In
+  combination with their long cooling time which exceeds the Hubble time, this suggests they may also
+  be sources of very high-energy (VHE) gamma-ray emission as a result of highly relativistic
+  cosmic-ray (CR) protons and ions interacting with intracluster gas. Reported here are VHE
+  gamma-ray observations of the Coma galaxy cluster with the VERITAS array of imaging Cherenkov
+  telescopes, with complementing Fermi Gamma-ray Space Telescope observations at GeV energies. No
+  significant gamma-ray emission from the Coma cluster was detected. Flux upper limits at the 99\%
+  confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$ s$^{-1}$
+  (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ ({\em Fermi}, 1-3 GeV),
+  respectively. For {\em Fermi} (VERITAS), the limits are a factor of 20 (60) higher than
+  model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons to be all
+  secondaries from cosmic-ray interactions. We use the gamma-ray flux upper limits to constrain the
+  populations of CRs and magnetic fields and in Coma. Using an analytical approach informed by
+  cosmological cluster simulations, the CR-to-thermal pressure is constrained to be smaller than
+  15\% from VERITAS data and smaller than 2.5\% from {\em Fermi} data (averaged within the virial
+  radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic CR
+  interactions, the observations imply a lower limit on the intra-cluster magnetic field strengths
+  of about $1$--$2\mu$G, depending on the magnetic decline and gamma-ray spectral index.  Since
+  these values are well below those inferred by Faraday rotation measurements in Coma, this renders
+  the hadronic model a very plausible explanation of the Coma radio halo. Finally, a constraint on
+  the thermally averaged product of the total self-annihilation cross section and the relative
+  velocity of the dark-matter particles, $\expval{\sigma v}$, is derived and found to be $\lesssim
+  10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
 \end{abstract}
@@
 be efficient enough to accelerate them to energies ($\sim 10$ GeV) sufficient to produce observable
-radio emisson \citep[][and references therein]{article:BrunettiLazarian:2010}. Recent observations of
+radio emission \citep[][and references therein]{article:BrunettiLazarian:2010}. Recent observations of
 possibly non-thermal emission from clusters in the the extreme ultraviolet
@@
 We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution
-in the Coma cluster using the upper limits dereived from VERITAS and \emph{Fermi}-LAT data in this
+in the Coma cluster using the upper limits derived from VERITAS and \emph{Fermi}-LAT data in this
 work. This approach includes (1) a simplified multi-frequency analytical approach that assumes a
@@
 the hadronic interaction model of the formation of giant radio halos. Alternatively, by realizing a
-spatial CR distribution that is just consitent with the flux upper limits and requiring the model to
+spatial CR distribution that is just consistent with the flux upper limits and requiring the model to
 match the observed radio data, this enables us to derive a lower limit on the magnetic field
@@
 \subsection{Simulation-based approach}
+\label{sec:simulation}
 We complement the simplified analytical analysis with a more realistic and predictive approach
@@
 the virial radius (dotted lines). Additionally shown are integrals of the differential spectrum for
-finited energy intervals across the angular apertures tested in this study (solid lines). These
+finite energy intervals across the angular apertures tested in this study (solid lines). These
 model fluxes are compared to {\em Fermi} and VERITAS flux upper limits of the same energy intervals,
@@
 \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster
-center (red lines) and contained within $R$ (blue lines). All radii are shown in units of the virial
+center (grey lines) and contained within $R$ (black lines). All radii are shown in units of the virial
 radius, $R_\rmn{vir}=2.2$~Mpc. To compute the CR pressure, we assume a low-momentum cutoff of the CR
-distribution at $q = 0.8\,m_p c$ to reflect tge high cooling rates at low CR energies. The relative CR
+distribution at $q = 0.8\,m_p c$ to reflect the high cooling rates at low CR energies. The relative CR
 pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the
@@
 be challenged. The method we use to constrain the magnetic field inherits a dependence on
-the assumed radial scaling which we parameterize as
+the assumed radial scaling which we parametrize as
 \begin{equation}
@@
 relative CR pressure (at the largest emission radius at 1~Mpc) such that the model reproduces the
-observed radio surface brightness profile. They should be interpreted as upper limits since they
-are derived from flux upper limits. For the {\em Fermi} upper limits, they range from 0.1 to 0.4;
-hence the $X_{\CR}$-profiles always obey the energy condition, i.e., $P_{\CR} < P_{\mathrm{th}}$
-over the entire range of the radio halo emission ($< 1$ Mpc).\footnote{See Figure 3 in
-\citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
+observed radio surface brightness profile.\footnote{Note that in this section, we determine the
+  radial behavior of $X_\CR$ by adopting a specific model for the magnetic field and requiring the
+  modeled synchrotron surface brightness profile to match the observed data of the Coma radio
+  halo. This is in contrast to the simplified analytical CR model where $X_\CR=\rmn{const.}$
+  (Sect.\ref{sec:simple}) and to the simulation-based model where $X_\CR(r)$ is derived from
+  cosmological cluster simulations (Sect.\ref{sec:simulation}).} They should be interpreted as upper
+limits since they are derived from flux upper limits. For the {\em Fermi} upper limits, they range
+from 0.1 to 0.4; hence the $X_{\CR}$-profiles always obey the energy condition, i.e., $P_{\CR} <
+P_{\mathrm{th}}$ over the entire range of the radio halo emission ($< 1$ Mpc).\footnote{See Figure 3
+  in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
   conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in
@@
 $\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
-astrophysical factor calculated for the different VERITAS appertures considered in this work.
+astrophysical factor calculated for the different VERITAS apertures considered in this work.
 It also lists the astrophysical factor calculated for the background region, which has been used
@@
 Figure \ref{fig:dm} for three different DM self-annihilation channels: W$^{+}$W$^{-}$,
-b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$. Depending on the chosen apperture the limits are on
+b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$. Depending on the chosen aperture the limits are on
 the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The numerical values for each of the channels
@@
 \end{center}
-\caption{{\em Figure TBC} Integral flux upper limits for Coma (this work, Tables~\ref{table:results}
+\caption{Integral flux upper limits for Coma (this work, Tables~\ref{table:results}
   and \ref{table:fermi}) for different integration radii (shown with different colors), assuming
@@
 \end{center}
-\caption{{\em Figure TBC} CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a
+\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a
 function of radial distance from the center of the Coma. Model predictions are shown by dashed
@@
 VERITAS upper limits within 0.2$^\circ$ (solid) and {\em Fermi} upper limits within 0.4$^\circ$
-(dashed). We compare differential $X_\CR$-profiles (red) to integrated profiles
-$X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (blue) which we use to
+(dashed). We compare differential $X_\CR$-profiles (grey) to integrated profiles
+$X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (black) which we use to
 compare to the upper limits.}
@@
 s$^{-1}$ ({\em Fermi} energy range).}
-\tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the
-hadronic model described in Sect~\ref{sec:Fmin}.}
+\tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the hadronic model
+  described in Sect~\ref{sec:Fmin}. For simplicity, we duplicate $X_{\CR,\,\rmn{min}}$ for the
+  VERITAS and {\em Fermi} constraints: for a given realization of the CR pressure (and a magnetic
+  field model which is trivial here as we assume $B \gg B_\rmn{CMB}$), we can derive the radio flux
+  as well as gamma-ray fluxes in various bands ($>1$ GeV, $>220$ GeV).}
 \label{table:constraints}
@@
 \begin{deluxetable}{ccccccc}
-\tablecolumns{4}
-\tablewidth{0pc}
+  \tablecolumns{4} \tablewidth{0pc} 
   \tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo and the
-corresponding relative CR pressure (at the largest emission radius) such that the model reproduces the
-observed radio surface brightness profile.}
-\tablehead{
- &
-\multicolumn{6}{c}{Minimum magnetic field, $B_{0,\rmn{min}}~[\mu\rmn{G}]$:}\\
+    corresponding relative CR pressure (at the largest emission radius of 1 Mpc) such that the model
+    reproduces the observed radio surface brightness profile.}
+  \tablehead{ &
+    \multicolumn{6}{c}{Minimum magnetic field, $B_{0,\rmn{min}}~[\mu\rmn{G}]$\tablenotemark{a}:}\\
     & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{{\em Fermi} constraints:} \\
-\colhead{$\alpha_{B}$}
- & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
- & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
-}
-\startdata
+    \colhead{$\alpha_{B}$} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} &
+    \colhead{$\alpha=2.5$} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} &
+    \colhead{$\alpha=2.5$} } \startdata
   0.3 & 0.69 & 0.57 & 0.48 & 1.14 & 1.63 & 2.25 \\
@@
   \hline
-& \multicolumn{6}{c}{Corresponding $X_{\CR,\rmn{max}}\, (1\,\rmn{Mpc})$:}\\ 
+  & \multicolumn{6}{c}{Corresponding $X_{\CR}\, (1\,\rmn{Mpc})$:}\\
   \hline
@@
 \enddata
-\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the
-central field strength, $B_{0}$, which are defined by
-$B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
+\tablenotetext{a}{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the
+  central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r) /
+  n_{\rmn{e}}(0)]^{\alpha_B}$.}  
 \label{table:Bmin}

### 2011-09-22 ms.tex
CP's final changes before the internal referee process

@@
   processes of electrons while this process should be even more efficient for protons. In
-  combination with their long cooling time which exceeds the Hubble time, this suggests they may also
-  be sources of very high-energy (VHE) gamma-ray emission as a result of highly relativistic
+  combination with their long cooling time which exceeds the Hubble time, this suggests they may
+  also be sources of very high-energy (VHE) gamma-ray emission as a result of highly relativistic
   cosmic-ray (CR) protons and ions interacting with intracluster gas. Reported here are VHE
@@
   (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ ({\em Fermi}, 1-3 GeV),
-  respectively. For {\em Fermi} (VERITAS), the limits are a factor of 20 (60) higher than
-  model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons to be all
-  secondaries from cosmic-ray interactions. We use the gamma-ray flux upper limits to constrain the
-  populations of CRs and magnetic fields and in Coma. Using an analytical approach informed by
-  cosmological cluster simulations, the CR-to-thermal pressure is constrained to be smaller than
-  15\% from VERITAS data and smaller than 2.5\% from {\em Fermi} data (averaged within the virial
+  respectively. For VERITAS ({\em Fermi}), the limits are a factor of 60 (20) higher than
+  model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons of the Coma
+  radio halo to be all secondaries from cosmic-ray interactions. We use the gamma-ray flux upper
+  limits to constrain the populations of CRs and magnetic fields and in Coma. Using an analytical
+  approach informed by cosmological cluster simulations, the CR-to-thermal pressure is constrained
+  to be $< 15\%$ from VERITAS data and $< 2.5\%$ from {\em Fermi} data (averaged within the virial
   radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic CR
-  interactions, the observations imply a lower limit on the intra-cluster magnetic field strengths
-  of about $1$--$2\mu$G, depending on the magnetic decline and gamma-ray spectral index.  Since
-  these values are well below those inferred by Faraday rotation measurements in Coma, this renders
-  the hadronic model a very plausible explanation of the Coma radio halo. Finally, a constraint on
-  the thermally averaged product of the total self-annihilation cross section and the relative
-  velocity of the dark-matter particles, $\expval{\sigma v}$, is derived and found to be $\lesssim
-  10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
+  interactions, the observations imply a lower limit on the central magnetic field in Coma of
+  $0.5$--$3\mu$G, depending on the magnetic decline and gamma-ray spectral index.  Since these
+  values are well below those inferred by Faraday rotation measurements in Coma, this makes the
+  hadronic model a very plausible explanation of the Coma radio halo. Finally, a constraint on the
+  thermally averaged product of the total self-annihilation cross section and the relative velocity
+  of the dark-matter particles, $\expval{\sigma v}$, is derived and found to be $\lesssim 10^{-21}$
+  cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
 \end{abstract}
@@
 
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung in the soft
-X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated
-primarily through collisionless structure-formation shocks that form as a result of the
-hierarchical merging and accretion processes. Such shocks and turbulence in the ICM gas and
-intra-cluster magnetic fields also provide a means to efficiently accelerate particles \citep[see,
+The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung in the soft X-ray regime
+\citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated primarily through
+collisionless structure-formation shocks that form as a result of the hierarchical merging and
+accretion processes. Such shocks and turbulence in the ICM gas in combination with intra-cluster
+magnetic fields also provide a means to efficiently accelerate particles \citep[see,
 e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do indeed feature
@@
 electrons and positrons (leptons) and magnetic fields permeating the ICM
-\citep{article:Cassano_etal:2010}. The two theories competing to explain the radio halo
-are the ``hadronic model'', in which the radio-emitting electrons are produced in inelastic
-collisions of cosmic-ray (CR)  ions with thermal gas of the ICM \citep{article:Dennison:1980},
-%\citep[][and references therein]{article:EnsslinPfrommerMiniatiSubramanian:2011}
-and the ``re-acceleration model'', in which during states of strong ICM turbulence, e.g. after a
-cluster merger, interactions of a long-lived pool of 100-MeV electrons with plasma waves might
-be efficient enough to accelerate them to energies ($\sim 10$ GeV) sufficient to produce observable
-radio emission \citep[][and references therein]{article:BrunettiLazarian:2010}. Recent observations of
-possibly non-thermal emission from clusters in the the extreme ultraviolet
-\citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of
-relativistic particle populations in clusters, although the interpretation of these observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations
-\citep[see, e.g.,][]{article:Ajello_etal:2009, article:Ajello_etal:2010, article:Wik_etal:2009}.
+\citep{article:Cassano_etal:2010}. The two theories competing to explain the radio halo are the
+``hadronic model'', in which the radio-emitting electrons are produced in inelastic collisions of
+cosmic-ray (CR) ions with thermal gas of the ICM \citep{article:Dennison:1980,
+  article:EnsslinPfrommerMiniatiSubramanian:2011}, and the ``re-acceleration model'', in which
+during states of strong ICM turbulence, e.g. after a cluster merger, interactions of a long-lived
+pool of 100-MeV electrons with plasma waves might be efficient enough to accelerate them to energies
+($\sim 10$ GeV) sufficient to produce observable radio emission \citep[][and references
+therein]{article:BrunettiLazarian:2010}. Recent observations of possibly non-thermal emission from
+clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
+\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may
+provide further indications of relativistic particle populations in clusters, although the
+interpretation of these observations as non-thermal diffuse emission have been disputed on the basis
+of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
+  article:Ajello_etal:2010, article:Wik_etal:2009}.
 
@@
 gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
-scales of a cluster and the volume filling magnetic fields in the ICM, CR hadrons will be confined in
+scales of a cluster and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
 the cluster on timescales comparable to or longer than the Hubble time \citep[][]{article:Volk_etal:1996,
@@
 method of constraining the pressure contribution of CRs that is most sensitive to the cluster core
-region. However, it assumes that the CR component is fully mixed with the ICM and may not a
-two-phase structure of CRs and the thermal ICM. A fraction $X_\CR$ of only a few percent is
+region. However, it assumes that the CR component is fully mixed with the ICM and may not allow to
+detect a two-phase structure of CRs and the thermal ICM. A fraction $X_\CR$ of only a few percent is
 required in order to produce a gamma-ray flux observable with current generation gamma-ray
@@
 galaxy clusters in the MeV to GeV band. Upper limits on the very-high-energy (VHE) gamma-ray flux
-from a few select clusters, including the Coma cluster, have been provided by observations with
+from a few selected clusters, including the Coma cluster, have been provided by observations with
 ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006,
@@
 wavelengths \citep{article:Voges_etal:1999}. Located at a distance of about 100 Mpc
-\citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest massive clusters
-\citep[$M \sim10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}. It hosts both a
-giant radio halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral
-radio relic, which appears connected to the radio halo with a ``diffuse'' bridge 
-\citep[see discussion in][]{article:BrownRudnick:2010}. It has been suggested
-\citep{article:Ensslin_etal:1998} and successively demonstrated by cosmological simulations, which
-model the non-thermal emission processes, \citep{article:PfrommerEnsslinSpringel:2008,
-article:Pfrommer:2008, article:Battaglia_etal:2009, article:Skillman_etal:2011}, that the relic is
-an infall shock. Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky
-survey in the 0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992}. Observations with
-XMM-Newton \citep{article:Briel_etal:2001} revealed substructure in the X-ray halo supported by
-substantial turbulent pressure of at least $\sim 10 \%$ of the total pressure
+\citep[$z=0.023$;][]{article:StrubleRood:1999}, it is one of the closest massive clusters \citep[$M
+\sim10^{15}M_{\odot}$;][]{article:Smith:1983, article:Kubo_etal:2008}. It hosts both a giant radio
+halo \citep{article:Giovannini_etal:1993,article:Thierbach_etal:2003} and peripheral radio relic,
+which appears connected to the radio halo with a ``diffuse'' bridge \citep[see discussion
+in][]{article:BrownRudnick:2010}. It has been suggested \citep{article:Ensslin_etal:1998} and
+successively demonstrated by cosmological simulations, which model the non-thermal emission
+processes, \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008,
+  article:Battaglia_etal:2009, article:Skillman_etal:2011}, that the relic could well be an infall
+shock. Extended soft thermal X-ray (SXR) emission is evident from the ROSAT all-sky survey in the
+0.1 to 2.4 keV band \citep{article:BrielHenryBohringer:1992}. Observations with XMM-Newton
+\citep{article:Briel_etal:2001} revealed substructure in the X-ray halo supported by substantial
+turbulent pressure of at least $\sim 10 \%$ of the total pressure
 \citep{article:Schuecker_etal:2004}. The Coma cluster is a natural candidate for gamma-ray
@@
 as the energy corresponding to the maximum of the product function of the observed spectrum with
-the collection area} of about 220 GeV. In addition, events for which only images from the two
+the collection area.} of about 220 GeV. In addition, events for which only images from the two
 closest-spaced telescopes\footnote{In the array configuration prior to summer 2009, two telescopes 
@@
 Table \ref{table:roi}. These upper-limit calculations depend on the gamma-ray spectrum, which in
-this work is assumed to be a power law with a spectral index $\alpha=2.1, 2.3$, and $2.5$.
+this work is assumed to be a power law in energy, $F\propto E^{-\alpha}$, with a spectral index
+$\alpha=2.1, 2.3$, and $2.5$.
 
@@
 Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events
-calibrated  in flight) were used throughout this work. Only photons above 1 GeV are considered,
-where the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates
-the systematic uncertainties at 10 GeV to be around 20\%.
-\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits
-at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like
-or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray emission is
-assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and $2.5$.
+calibrated in flight) were used throughout this work. Only photons above 1 GeV are considered, where
+the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates the
+systematic uncertainties at 10 GeV to be around
+20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper
+limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved,
+point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray
+emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and
+$2.5$.
 
@@
 with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution
-function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is unconstrained, we vary it in
-the range $2.1<\alpha_{\rmn{p}}<2.5$, which is compatible with the
-radio spectral index of the giant radio halo of the Coma cluster after accounting for the spectral
-steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
-\citep{article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
+function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is unconstrained,\footnote{The
+  hadronic interaction physics guarantees that the CR spectral index coincides with that of the
+  resulting pion-decay gamma-ray emission.} we vary it in the range $2.1<\alpha<2.5$, which is
+compatible with the radio spectral index of the giant radio halo of the Coma cluster after
+accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the
+Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
+  article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
   responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
@@
 
-Table \ref{table:constraints_simple} shows the resulting constraints on the relative CR pressure, $X_{\CR}
-= \expval{P_{\CR}}/\expval{P_\rmn{th}}$, averaged within the virial radius, $R_\rmn{vir}=2.2$~Mpc,
-that we define as the radius of a sphere enclosing a mean density that is 200 times the critical
-density of the Universe. The VERITAS flux upper limits strongly depend on $\alpha$ due to the
-comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies. The
-flux measurements within 0.2$^{\circ}$ are the most constraining and yield limits on $X_\CR$
-between 0.048 and 0.43
-(for $\alpha$ varying between 2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close
-to the spectral index predicted by the simulations of \citet{article:PinzkePfrommer:2010} around 220
-GeV).  The {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an
-aperture of 0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only
-slightly worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
+Table \ref{table:constraints_simple} shows the resulting constraints on the relative CR pressure,
+$X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$, averaged within the virial radius,
+$R_\rmn{vir}=2.2$~Mpc, that we define as the radius of a sphere enclosing a mean density that is 200
+times the critical density of the Universe. Constraints on $X_\CR$ with VERITAS flux upper limits
+strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate
+the CR pressure) to TeV energies. The flux measurements within 0.2$^{\circ}$ are the most
+constraining and yield limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1
+and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted
+by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV).  Constraints on $X_\CR$
+with {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of
+0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly
+worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
 
@@
 The overall normalization of the CR and gamma-ray distribution scales non-linearly with the
-acceleration efficiency at structure formation shock. Following recent observations at
-supernova remnants \citep{article:Helder_etal:2009} as well as theoretical studies
+acceleration efficiency at structure formation shocks. Following recent observations at supernova
+remnants \citep{article:Helder_etal:2009} as well as theoretical studies
 \citep{article:KangJones:2005}, we adopt an optimistic but nevertheless realistic value of this
@@
 at the present time (at the boundary of voids and filaments/super-cluster regions) dominate the
-injection of CRs which subsequently are adiabatically transported through the cluster. Hence, the model
-provides a plausible upper limit for the CR contribution from structure formation shocks
-in galaxy clusters which can be scaled with the effective acceleration efficiency. Other possible CR
+acceleration of CRs which subsequently are adiabatically transported through the cluster. Hence, the
+model provides a plausible upper limit for the CR contribution from structure formation shocks in
+galaxy clusters which can be scaled with the effective acceleration efficiency. Other possible CR
 sources, such as AGN and starburst-driven galactic winds have been neglected for simplicity which
@@
 In the case of VERITAS, for the most constraining regions tested (within an aperture of radius
-0.2$^{\circ}$), the predicted CR pressure is a factor of 7.2 below the inferred upper limits of VERITAS
-(see Table
-\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at
-energies $E_\gamma=200$ GeV). To first order, we can scale the averaged relative CR pressure of
-our model by that
-factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
-$X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of
-$X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}).  This limit is less constraining by 50\% in
-comparison to the simplified analytical model, which gives $X_\CR<0.1$. This difference is
-explained by the concave curvature of the simulated spectrum which accumulates additional pressure
-toward GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
+0.2$^{\circ}$), the predicted CR pressure is a factor of 7.2 below the inferred upper limits of
+VERITAS (see Table \ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches
+the simulated one at energies $E_\gamma=200$ GeV). To first order, we can scale the averaged
+relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated
+limit of the relative CR pressure of $X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit
+within the cluster virial radius of $X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}).  This limit
+is less constraining by 50\% in comparison to the simplified analytical model, which gives
+$X_\CR<0.1$. This difference is explained by the concavity of the simulated spectrum which therefore
+carries more pressure at GeV energies than a pure power-law spectrum of $\alpha=2.3$.
 
@@
 \label{eq:Fmin}
-\mathcal{F}_{\gamma,\rmn{min}} = \frac{\dps A_{\gamma}}{\dps A_{\nu}}\frac{\dps L_{\nu}}{\dps 4\pi D_{\rmn{lum}}^{2}},
+F_{\gamma,\rmn{min}} = \frac{\dps A_{\gamma}}{\dps A_{\nu}}\frac{\dps L_{\nu}}{\dps 4\pi D_{\rmn{lum}}^{2}},
 \end{equation}
@@
 
-The results for the minimum gamma-ray flux $F_{\rmn{min}}(>220~\rmn{GeV})$ and the minimum relative
-CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/\tilde{F}$ are shown in Table
-\ref{table:constraints}, where $F_\rmn{iso} = X_\CR\,\tilde{F}$ is the gamma-ray flux in the simplified
-model introduced in \S\ref{sec:simple}. Even in the most constraining cases,
-these are a factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$,
-$<0.2^{\circ}$) and a factor of about 20 below the {\em Fermi} upper limits (adopting $\alpha=2.3$,
-$<0.4^{\circ}$).
+The results for the minimum gamma-ray flux $F_{\gamma,\rmn{min}}(>220~\rmn{GeV})$ and the minimum
+relative CR pressure, $X_{\CR,\,\rmn{min}} = X_\CR F_{\gamma,\rmn{min}}/F_{\gamma,\rmn{iso}}$ are
+shown in Table \ref{table:constraints}, where $F_{\gamma,\rmn{iso}}$ is the gamma-ray flux in the
+simplified model introduced in \S\ref{sec:simple}. Even in the most constraining cases, these are a
+factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$, $<0.2^{\circ}$) and a
+factor of about 20 below the {\em Fermi} upper limits (adopting $\alpha=2.3$, $<0.4^{\circ}$). Note
+that these minimum gamma-ray fluxes are sensitive to a running of the CR proton spectral index with
+energy as a result of, e.g., momentum-dependent diffusion: assuming a plausible value for the
+central magnetic field of Coma of 5~$\mu$G \citep{article:Bonafede_etal:2010}, the radio halo
+emission at GHz frequencies is dominated by the electrons with a energy $E_\rmn{e} \sim 2.5$ GeV
+(which corresponds to proton energies $E_\rmn{p} \sim 40$ GeV). Gamma rays with an energy of $200$
+GeV are produced by CR protons with an energy of $E_\rmn{p} \sim 1.6$ TeV -- a factor of 50 higher
+than those probed by radio halo observations. A steepening of the CR proton spectral index of 0.2
+between 40 GeV and 1.6 TeV would imply a decrease in the minimum gamma-ray flux by a factor of two.
 
@@
 \item
-We then solve for $B_{0}$ while matching the observed synchrotron profile while fixing the profile
+We then solve for $B_{0}$ while matching the observed synchrotron profile and fixing the profile
 of $X_{\CR}(r)$ as determined through the previous two steps. Note
@@
 
-Table \ref{table:Bmin} shows the resulting lower limit of the central magnetic field that
-range from $B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from
-$B_{0} = 1.1$ to $4.6\,\mu$G in the case of \emph{Fermi}.\footnote{Note that a central magnetic
-field of $3\,\mu$G corresponds 
-in the Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits
-on $B_{0}$ are below the values favored by Faraday RM for the entire parameter space spanned by
-$\alpha_{B}$ and $\alpha$, the hadronic model is still viable. Future gamma-ray observations of
-the Coma cluster may put more stringent constraints on the parameters of the hadronic model.
+Table \ref{table:Bmin} shows the resulting lower limit of the central magnetic field that range from
+$B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from $B_{0} = 1.1$ to $4.6\,\mu$G in the
+case of \emph{Fermi}.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the
+  Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits on
+$B_{0}$ are below the values favored by Faraday RM for the entire parameter space spanned by
+$\alpha_{B}$ and $\alpha$, the hadronic model is a viable explanation of the Coma radio halo. Future
+gamma-ray observations of the Coma cluster may put more stringent constraints on the parameters of
+the hadronic model.
 
@@
 observed radio profiles, and therefore that CR realization produces a larger flux within 0.4$^{\circ}$
-in comparison with the simplified CR model ($X_{\CR} = \rmn{const.}$). for which the
+in comparison with the simplified CR model ($X_{\CR} = \rmn{const.}$), for which the
 0.2$^{\circ}$-aperture limits are more constraining in the case of VERITAS. Physically, the large
@@
 which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density
-$\rho_{s}$. Using weak-lensing measurements of the virial mass in the Coma cluster
-\citep{article:Gavazzi_etal:2009} we find for these parameters $r_{s}=0.654$ Mpc and
+$\rho_{s}$.  Weak-lensing measurements of the virial mass in the Coma cluster
+\citep{article:Gavazzi_etal:2009} yield for these parameters $r_{s}=0.654$ Mpc and
 $\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
@@
 spectral index, $\alpha$, varying between 2.1 and 2.5). We obtain a constraint of $X_\CR<0.1$ for
-$\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit
-is more constraining by a factor of 1.5 in comparison to the simulation-based model which gives
-$X_\CR<0.15$.  This difference is due to the concave curvature of the simulated spectrum which
-accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of
-$\alpha=2.3$.
+$\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit is
+more constraining by a factor of 1.5 in comparison to the simulation-based model which gives
+$X_\CR<0.15$. This difference is due to the concave form of the simulated spectrum which provides
+more pressure at GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
 
@@
 \end{center}
-\caption{Integral flux upper limits for Coma (this work, Tables~\ref{table:results}
-  and \ref{table:fermi}) for different integration radii (shown with different colors), assuming
+\caption{Integral flux upper limits for Coma (this work, Tables~\ref{table:results} and
+  \ref{table:fermi}) for different integration radii (shown with different grey scales), assuming
   $\alpha=2.1$. These are compared to integrated spectra of the same energy interval and aperture,
@@
     & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
-    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{c}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{d}}   \\
+    & \colhead{$F_{\gamma,\rmn{sim}}(E)$\tablenotemark{c}} & \colhead{$F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{d}}   \\
 & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$} & & 
@@
   field model which is trivial here as we assume $B \gg B_\rmn{CMB}$), we can derive the radio flux
-  as well as gamma-ray fluxes in various bands ($>1$ GeV, $>220$ GeV).}
+  as well as gamma-ray fluxes in various bands (1--3 GeV, $>220$ GeV).}
 \label{table:constraints}

### 2011-09-23 ms.tex
Updated the DM section per Martin's suggestions

@@
 As already mentioned in the introduction, most of the mass in a galaxy cluster is in the form of
-DM. While the nature of this DM remains unknown, the most compelling theoretical candidate is a
-WIMP. The self-annihilations of WIMPs are expected to produce a flux of secondary gamma rays with a
-spectral signature that deviates significantly from the power-law spectrum observed in most
-conventional astrophysical sources. The spectrum will also feature a very sharp cutoff at the WIMP
-mass. Observations of these spectral characteristics together with the expected difference in spatial
-distribution of the gamma-ray intensity compared to conventional astrophysical sources allows for a
-an indirect detection DM.
+DM. While the nature of DM remains unknown, the most compelling theoretical candidate is a
+WIMP. The self-annihilations of WIMPs are expected to produce secondary gamma rays with a
+spectral signature that deviates significantly from the power-law spectra observed from most
+conventional astrophysical sources. The spectrum will also feature a sharp cutoff at the WIMP
+mass. These spectral features together with the expected difference in the
+intensity distribution compared to conventional astrophysical sources allow an
+indirect detection of DM.
 
@@
 \frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=
-\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\frac{dN(E,m_{\chi})}{dE} J(\Delta\Omega),
+\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\,N_\gamma (E)\, J(\Delta\Omega),
 \label{eqn:WIMPflux}
 \end{equation}
-where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross
-section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential
-gamma-ray yield per annihilation,\footnote{In this work, we have calculated the differential
-gamma-ray yield per annihilation using the Pythia Monte Carlo simulator.} $\Delta\Omega$ is the
+where $\expval{\sigma v}$ is the thermally-averaged product of the total self-annihilation cross
+section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $N_\gamma (E)$ is the differential
+gamma-ray yield per annihilation\footnote{In this work, we have calculated the differential
+gamma-ray yield per annihilation using the Pythia Monte-Carlo simulator.}, $\Delta\Omega$ is the
 observed solid angle, and $J$ is the astrophysical factor - a dimensionless factor which determines
@@
 Given the upper limit on the observed gamma-ray rate,
-$R_{\gamma}(95\%\ \mathrm{CL}) = N_{\gamma}(95\%\ \mathrm{CL}) / T_{\mathrm{obs}}$, we can place
+$R_{\gamma}(99\%\ \mathrm{CL}) = N_{\gamma}(99\%\ \mathrm{CL}) / T_{\mathrm{obs}}$, we can place
 constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. From Eq.
-(\ref{eqn:WIMPflux}) we get
+(\ref{eqn:WIMPflux}) we find
 \begin{equation}
-\expval{\sigma v}(95\%\ \mathrm{CL}) > 
-R_{\gamma}(95\%\ \mathrm{CL}) \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}
-\frac{1}{\int^{m_{\chi}} dE A_{\mathrm{eff}}dN_{\gamma}/dE}
+\expval{\sigma v}(99\%\ \mathrm{CL}) <
+R_{\gamma}(99\%\ \mathrm{CL})\, \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\,
+\frac{1}{\int^{m_{\chi}} dE\ A_{\mathrm{eff}}\,N_\gamma (E)}
 \end{equation}
@@
 J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right)
-\int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
+\int_{\Delta\Omega}d\Omega\int d\lambda\ \rho^{2}(\lambda,\Omega),
 \end{equation}
@@
 Hubble radius, $R_{H}$. In this work we have adopted the DM density profile by
-Navarro-Frenk-White \citep[NFW;][]{article:NavarroFrenkWhite:1997},
+\citet{article:NavarroFrenkWhite:1997},
 \begin{equation}
@@
 which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density
-$\rho_{s}$.  Weak-lensing measurements of the virial mass in the Coma cluster
-\citep{article:Gavazzi_etal:2009} yield for these parameters $r_{s}=0.654$ Mpc and
+$\rho_{s}$. Using weak-lensing measurements of the virial mass in the Coma cluster
+\citep{article:Gavazzi_etal:2009} we find for these parameters $r_{s}=0.654$ Mpc and
 $\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
-astrophysical factor calculated for the different VERITAS apertures considered in this work.
-It also lists the astrophysical factor calculated for the background region, which has been used
+astrophysical factors calculated for the different VERITAS apertures considered in this work.
+It also lists the astrophysical factor calculated for the background region, which is used
 to estimate the gamma-ray contamination due to DM in the background region.
@@
 Figure \ref{fig:dm} for three different DM self-annihilation channels: W$^{+}$W$^{-}$,
-b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$. Depending on the chosen aperture the limits are on
+b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$. Depending on the chosen aperture, the limits are on
 the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The numerical values for each of the channels
@@
 result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated
-background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor
-no longer compensate for the increased count of background events and the signal-to-noise
+background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factors
+no longer compensate for the increased number of background events, and the signal-to-noise
 deteriorates.

### 2011-10-06 ms.tex
Gordana's scientific comments addressed

@@
 
-Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration
-in the ICM is an efficient process, a population of highly relativistic CR protons and heavy ions is to
+Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration in
+the ICM is an efficient process, a population of highly relativistic CR protons and heavy ions is to
 be expected in the ICM. The main energy-loss mechanism for CR hadrons at high energies is pion
-production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay; the
-charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
+production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay;
+the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
   which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to
 gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
-scales of a cluster and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
-the cluster on timescales comparable to or longer than the Hubble time \citep[][]{article:Volk_etal:1996,
-article:Berezinsky_etal:1997} allowing them to accumulate over time. Depending on the CR pressure,
-quantified by the CR-to-thermal pressure fraction
-$X_\CR=\expval{P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma rays
-can be expected.
-
-A substantial value of $X_\CR$ can bias hydrostatic estimates of cluster masses as well as the
-temperature decrement of the cosmic microwave background (CMB) in the direction of a galaxy cluster
-due to the Sunyaev-Zel'dovich effect. This could then severely jeopardize the use of clusters to
-determine cosmological parameters. Comparing X-ray and optical potential profiles in the centers of
-galaxy clusters yields an upper limit of 20-30 \% of non-thermal pressure (that can be composed of
-CRs, magnetic fields or turbulence) relative to the thermal gas pressure
-\citep{article:Churazov_etal:2008, article:Churazov_etal:2010}. An analysis that compares spatially
-resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy clusters
-detects a deficit of the hydrostatic mass estimate compared to the lensing mass of $20 \%$ at
-$R_{500}$ -- the radius within which the mean density is 500 times the critical density --
+scales of a cluster and the volume-filling magnetic fields in the ICM, CR hadrons will be confined
+in the cluster on timescales comparable to or longer than the Hubble time
+\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over
+time. Already a very modest CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/
+\expval{P_{\mathrm{th}}}$, of a few per cent implies an observable flux of high-energy gamma rays
+\citep[e.g.,][]{article:PfrommerEnsslin:2004b}. For a given CR distribution function, the
+hadronically induced gamma-ray flux is directly proportional to $X_{\CR}$.
+
+Hydrostatic estimates of cluster masses, which are determined by balancing the thermal pressure
+force and the gravitational force, are biased low by the presence of any substantial non-thermal
+pressure component, including a CR pressure contribution. Similarly, a substantial relative CR
+pressure can bias the temperature decrement of the cosmic microwave background (CMB) in the
+direction of a galaxy cluster due to the Sunyaev-Zel'dovich effect. This could then severely
+jeopardize the use of clusters to determine cosmological parameters. Comparing X-ray and optical
+potential profiles in the centers of galaxy clusters yields an upper limit of 20-30\% of non-thermal
+pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas
+pressure \citep{article:Churazov_etal:2008, article:Churazov_etal:2010}. An analysis that compares
+spatially resolved weak gravitational lensing and hydrostatic X-ray masses for a sample of 18 galaxy
+clusters detects a deficit of the hydrostatic mass estimate compared to the lensing mass of $20\%$
+at $R_{500}$ -- the radius within which the mean density is 500 times the critical density --
 suggesting again a substantial non-thermal pressure contribution on large scales
@@
 used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level)
-and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because the
-VHE gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about 2.3,
-these cuts are suitable for the analysis of the Coma cluster data set.
+and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because the VHE
+gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about 2.3
+\citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma cluster
+data set.
 
@@
 of \citet{article:PfrommerEnsslin:2004b}. To be independent of additional assumptions and in line
-with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution
-function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is unconstrained,\footnote{The
-  hadronic interaction physics guarantees that the CR spectral index coincides with that of the
-  resulting pion-decay gamma-ray emission.} we vary it in the range $2.1<\alpha<2.5$, which is
-compatible with the radio spectral index of the giant radio halo of the Coma cluster after
-accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the
-Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
+with earlier work in the literature, we do not impose a low-momentum cutoff, $q$, on the CR
+distribution function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is
+unconstrained,\footnote{The hadronic interaction physics guarantees that the CR spectral index
+  coincides with that of the resulting pion-decay gamma-ray emission.} we vary it in the range
+$2.1<\alpha<2.5$, which is compatible with the radio spectral index of the giant radio halo of the
+Coma cluster after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to
+the Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
   article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
@@
 the virial radius (dotted lines). Additionally shown are integrals of the differential spectrum for
-finite energy intervals across the angular apertures tested in this study (solid lines). These
-model fluxes are compared to {\em Fermi} and VERITAS flux upper limits of the same energy intervals,
-summarized in Table \ref{table:constraints}.  The gamma-ray flux limit of {\em Fermi} in the energy
-interval of 1--3 GeV ($<0.4^\circ$) is most constraining but still above the model predictions that
-assume an optimistically large shock acceleration efficiency and CR transport parameters as laid
-out above.  In our further analysis, we use the most constraining {\em Fermi} flux limits in the
-energy interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above
-220 GeV.
+finite energy intervals across the angular apertures tested in this study (solid lines). These model
+fluxes (summarized in Table \ref{table:constraints_simple}) are compared to {\em Fermi} and VERITAS
+flux upper limits of the same energy intervals.  The gamma-ray flux limit of {\em Fermi} in the
+energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining but still above the model
+predictions that assume an optimistically large shock acceleration efficiency and CR transport
+parameters as laid out above.  In our further analysis, we use the most constraining {\em Fermi}
+flux limits in the energy interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the
+energy range above 220 GeV.
 
@@
 as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD) simulations
-\citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}. In fact,
-the magnetic field in the Coma cluster is among the best constrained, because its proximity permits
-RM observations of seven radio-sources located at projected distances of 50 to 1500 kpc from the
-cluster center. The best-fit model yields $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and
-$\alpha_{B} = 0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim for constraining the
-central field strength, $B_{0}$, and permit the magnetic decline, $\alpha_{B}$, to vary
-within a reasonable range of $\Delta\alpha_{B}=0.2$ as suggested by the Faraday RM studies.
-We proceed as follows:
+\citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}. Here
+$n_{\rmn{e}}$ denotes the Coma electron density profile \citep{article:BrielHenryBohringer:1992}.
+In fact, the magnetic field in the Coma cluster is among the best constrained, because its proximity
+permits RM observations of seven radio-sources located at projected distances of 50 to 1500 kpc from
+the cluster center. The best-fit model yields $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and $\alpha_{B} =
+0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim for constraining the central field
+strength, $B_{0}$, and permit the magnetic decline, $\alpha_{B}$, to vary within a reasonable range
+of $\Delta\alpha_{B}=0.2$ as suggested by the Faraday RM studies.  We proceed as follows:
 

### 2011-10-06 ms.tex
equation for L_synch added

@@
 \label{sec:Fmin}
-For clusters that host radio halos we can derive a minimum gamma-ray flux in the hadronic
-model of radio halos -- where the radio-emitting electrons are secondaries from CR interactions. 
-Hadronic interactions channel about the same power into secondary electrons and $\pi^{0}$-decay
-gamma rays. A stationary distribution of CR electrons loses all its energy to
-synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G), and thus the
+
+For clusters that host radio halos we can derive a minimum gamma-ray flux in the hadronic model of
+radio halos -- where the radio-emitting electrons are secondaries from CR interactions.  Hadronic
+interactions channel about the same power into secondary electrons and $\pi^{0}$-decay gamma rays. A
+stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong
+magnetic fields ($B \gg B_\rmn{CMB} \simeq 3.2 \mu$G, where $B_\rmn{CMB}$ is the equivalent magnetic
+field strength of the CMB so that $B_\rmn{CMB}^2/8\pi$ equals the CMB energy density). Thus the
 ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and
@@
 that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution
-would be degenerate.
-
-\item
-Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
-$B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as a
-function of magnetic field strength. Hence we have to iterate through the previous steps until our
-solution for the minimum magnetic field $B_{0}$ is converged.
+would be degenerate since the luminosity of the radio halo scales as
+\begin{equation}
+\label{eq:Lnu}
+L_{\nu} \propto \int dV Q(E)\,\frac{B^{1+\alpha_\nu}}{B^2 + B_{\rmn{CMB}}^2} \to \int dV Q(E),
+\end{equation}
+where $Q(E)$ denotes the electron source function.
+
+\item Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
+  $B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as
+  a function of magnetic field strength (see Eqn.~(\ref{eq:Lnu})). Hence we have to iterate through
+  the previous steps until our solution for the minimum magnetic field $B_{0}$ is converged.
 \end{enumerate}

### 2011-10-10 ms.tex
Further edits as suggested by G. Tesic

@@
 mergers of smaller objects with galaxy clusters sitting on top of this mass hierarchy
-\citep[see][for a review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark
-matter (DM), as indicated by galaxy dynamics and gravitational lensing
+\citep[see][for a review]{article:Voit:2005}. Most of the mass ($\sim$80\%) in a cluster is in form
+of dark matter (DM), as indicated by galaxy dynamics and gravitational lensing
 \citep{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the intra-cluster medium (ICM)
@@
 magnetic fields also provide a means to efficiently accelerate particles \citep[see,
-e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do indeed feature
+e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters feature
 mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic
@@
 
-Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration in
-the ICM is an efficient process, a population of highly relativistic CR protons and heavy ions is to
-be expected in the ICM. The main energy-loss mechanism for CR hadrons at high energies is pion
+Galaxy clusters have, for many years, been proposed as sources of gamma rays. If shock acceleration
+in the ICM is an efficient process, a population of highly relativistic CR protons and heavy ions
+is to be expected in the ICM. The main energy-loss mechanism for CR hadrons at high energies is pion
 production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay;
@@
 \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over
-time. Already a very modest CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/
-\expval{P_{\mathrm{th}}}$, of a few per cent implies an observable flux of high-energy gamma rays
-\citep[e.g.,][]{article:PfrommerEnsslin:2004b}. For a given CR distribution function, the
-hadronically induced gamma-ray flux is directly proportional to $X_{\CR}$.
+time. For a given CR distribution function, the hadronically induced gamma-ray flux is directly
+proportional to the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/
+\expval{P_{\mathrm{th}}}$. Already a very modest $X_{\CR}$ of a few percent implies an observable
+flux of high-energy gamma rays \citep[e.g.,][]{article:PfrommerEnsslin:2004b}.
 
@@
 clusters detects a deficit of the hydrostatic mass estimate compared to the lensing mass of $20\%$
-at $R_{500}$ -- the radius within which the mean density is 500 times the critical density --
-suggesting again a substantial non-thermal pressure contribution on large scales
+at $R_{500}$ -- the radius within which the mean density is 500 times the critical density of the
+Universe -- suggesting again a substantial non-thermal pressure contribution on large scales
 \citep{article:Mahdavi_etal:2008}. Observing high-energy gamma-ray emission is a complementary
 method of constraining the pressure contribution of CRs that is most sensitive to the cluster core
-region. However, it assumes that the CR component is fully mixed with the ICM and may not allow to
-detect a two-phase structure of CRs and the thermal ICM. A fraction $X_\CR$ of only a few percent is
-required in order to produce a gamma-ray flux observable with current generation gamma-ray
-telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method
-(which are more general in that they are sensitive to any non-thermal pressure component).
+region. However, it assumes that the CR component is fully mixed with the ICM and may not allow for
+a detection of a two-phase structure of CRs and the thermal ICM. A fraction $X_\CR$ of only a few 
+percent is required in order to produce a gamma-ray flux observable with current generation of
+gamma-ray telescopes rendering this technique at least as sensitive as the dynamical and
+hydrostatic method (which are more general in that they are sensitive to any non-thermal pressure
+component).
 
@@
 the cluster mass is in the form of dark matter. The gamma-ray emissivity from DM annihilations is
-proportional to the square of the DM density integrated along the line of sight, making galaxy clusters
-potentially good candidates for DM searches \citep{article:EvansFerrerSarkar:2004,
+proportional to the square of the DM density integrated along the line of sight, making galaxy
+clusters potentially good candidates for DM searches \citep{article:EvansFerrerSarkar:2004,
 article:BergstromHooper:2006, article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011},
 despite their large distances compared to other common targets for DM searches, such as dwarf
-spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,article:Aliu_etal:2009}
-or the Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
-article:Aharonian_etal:2009b}.
+spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,
+article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004,
+article:Aharonian_etal:2006, article:Aharonian_etal:2009b, article:Abramowski_etal:2011}.
 
@@
 made. Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the
-Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on the
-gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for several
-galaxy clusters in the MeV to GeV band. Upper limits on the very-high-energy (VHE) gamma-ray flux
-from a few selected clusters, including the Coma cluster, have been provided by observations with
-ground-based imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Perkins_etal:2006,
-inproc:Perkins_etal:2008, article:Aharonian_etal:2009a, article:Aleksic_etal:2010}.
+Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on
+the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for
+several galaxy clusters in the MeV to GeV band. Upper limits on the very-high-energy (VHE)
+gamma-ray flux from a select few clusters, including the Coma cluster, have been provided by
+observations with ground-based imaging atmospheric Cherenkov telescopes
+\citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009a,
+article:Aleksic_etal:2010}.
 
@@
 successively demonstrated by cosmological simulations, which model the non-thermal emission
-processes, \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008,
+processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008,
 article:Battaglia_etal:2009, article:Skillman_etal:2011}, that the relic could well be an infall
@@
 imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an
-altitude of 1268 m a.s.l. at the Fred Lawrence Whipple Observatory in southern Arizona
+altitude of $\sim$1250 m a.s.l. at the Fred Lawrence Whipple Observatory in southern Arizona
 (31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes
@@
 and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because the VHE
-gamma-ray spectrum for the Coma cluster is expected to be hard, photon index of about 2.3
+gamma-ray spectrum for the Coma cluster is expected to be hard, with a photon index of about 2.3
 \citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma cluster
@@
 distribution is a radial comparison of the ON-source event distribution with the estimated
-background. It extends out to a radius of $0.42^{\circ}$ to cover all regions of interest
+background. It extends out to a radius of 0.42 square degrees to cover all regions of interest
 considered in this work. A 99\% confidence level upper limit is calculated for each region of
@@
 the hadronic interaction model of the formation of giant radio halos. Alternatively, by realizing a
-spatial CR distribution that is just consistent with the flux upper limits and requiring the model to
-match the observed radio data, this enables us to derive a lower limit on the magnetic field
+spatial CR distribution that is just consistent with the flux upper limits and requiring the model
+to match the observed radio data, this enables us to derive a lower limit on the magnetic field
 distribution. We stress again that his approach assumes the validity of the hadronic interaction
@@
 the associated radiative emission processes from radio to the gamma-ray band. This formalism was
-derived from high-resolution simulations of clusters of galaxies that included radiative hydrodynamics,
+derived from high-resolution simulations of clusters of galaxies that included radiative
+hydrodynamics,
 star formation, supernova feedback, and followed CR physics by tracing the most important injection
@@
 These cosmological simulations only considered advective transport of CRs by turbulent gas motions
-which lead to centrally enhanced density profiles.  However, other means of CR transport such as diffusion
+which lead to centrally enhanced density profiles.  However, other means of CR transport such as
+diffusion
 and streaming may flatten the CR radial profiles. It has been suggested that advection is dominant
@@
 are more constraining. This implies tighter lower limits for $B_{0}$. (3) Interestingly, in all
-cases, the 0.4$^{\circ}$-aperture limits that are the most constraining. For a given magnetic
+cases, the 0.4$^{\circ}$-aperture limits are the most constraining. For a given magnetic
 realization a substantially increasing relative CR pressure profile is needed to match the
-observed radio profiles, and therefore that CR realization produces a larger flux within 0.4$^{\circ}$
-in comparison with the simplified CR model ($X_{\CR} = \rmn{const.}$), for which the
+observed radio profiles, and therefore that CR realization produces a larger flux within 
+0.4$^{\circ}$ in comparison with the simplified CR model ($X_{\CR} = \rmn{const.}$), for which the
 0.2$^{\circ}$-aperture limits are more constraining in the case of VERITAS. Physically, the large
@@
 R_{\gamma}(99\%\ \mathrm{CL})\, \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\,
-\frac{1}{\int^{m_{\chi}} dE\ A_{\mathrm{eff}}\,N_\gamma (E)}
+\frac{1}{\int^{m_{\chi}} dE\ A_{\mathrm{eff}}\,N_\gamma (E)},
 \end{equation}
+where $A_{\mathrm{eff}}$ is the effective area of the gamma-ray detector.
 Because the self-annihilation of a WIMP is a two-body process, the astrophysical factor
@@
 the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The numerical values for each of the channels
-are listed in Table \ref{table:DMlimits}. We note that these are based on conservative estimates of the
-astrophysical factor $J$, as we do not assume boosting by clumping or the Sommerfeld effect.
-
-We also note that when the size of the integration region is increased, the limits on $\expval{\sigma v}$
-result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated
-background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factors
-no longer compensate for the increased number of background events, and the signal-to-noise
-deteriorates.
+are listed in Table \ref{table:DMlimits}. We note that these are based on conservative estimates of
+the astrophysical factor $J$, as we do not assume boosting by clumping or the Sommerfeld effect.
+
+We also note that when the size of the integration region is increased, the limits on
+$\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor
+$\expval{J}$ and the integrated background. For integration regions larger than 0.2$^{\circ}$ in
+radius, the astrophysical factors no longer compensate for the increased number of background
+events, and the signal-to-noise deteriorates.
 
@@
 approximate universality of the CR distribution (when neglecting CR diffusion and streaming which
-appears, however, necessary to explain the radio halo bimodality). (3) We finally use a pragmatic
-approach which models the CR and magnetic distribution such as to reproduce the observed emission
+appears necessary to explain the radio halo bimodality). (3) We finally use a pragmatic
+approach which models the CR and magnetic distribution in order to reproduce the observed emission
 profile of the Coma radio halo. While this approach is also physically not justified, it is

### 2011-10-13 ms.tex
addressed Jeremy's comments in abstract, Sects. 1, 4, 6 and Fig 4

@@
 %\documentclass[twocolumn]{emulateapj}
+\usepackage{xspace}
 
@@
 %\def\C#1{{\bf #1}}
+
+\def\Fermi{{\em Fermi}\xspace}
 
@@
 %\title{VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
-\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
+%\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
+\title{Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi}
 \author{N. Karlsson\altaffilmark{1,2}, M. Pohl\altaffilmark{3,4}}
@@
 \begin{abstract}
-Observations of radio halos and relics in galaxy clusters are indicative of efficient acceleration
-processes of electrons while this process should be even more efficient for protons. In
-combination with their long cooling time which exceeds the Hubble time, this suggests they may
-also be sources of very high-energy (VHE) gamma-ray emission as a result of highly relativistic
-cosmic-ray (CR) protons and ions interacting with intracluster gas. Reported here are VHE
-gamma-ray observations of the Coma galaxy cluster with the VERITAS array of imaging Cherenkov
-telescopes, with complementing Fermi Gamma-ray Space Telescope observations at GeV energies. No
-significant gamma-ray emission from the Coma cluster was detected. Flux upper limits at the 99\%
-confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$ s$^{-1}$
-(VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ ({\em Fermi}, 1-3 GeV),
-respectively. For VERITAS ({\em Fermi}), the limits are a factor of 60 (20) higher than
+  Observations of radio halos and relics in galaxy clusters indicate efficient electron acceleration
+  processes; the same processes are even more efficient for protons. Since protons have a cooling
+  time which exceeds the Hubble time in clusters, they can accumulate suggesting that clusters may
+  also be sources of very high-energy (VHE; $E>100$ GeV) gamma-ray emission resulting from the
+  interactions of highly relativistic cosmic-ray (CR) hadrons with the intracluster gas. Reported
+  here are VHE gamma-ray observations of the Coma galaxy cluster with the VERITAS array of imaging
+  Cherenkov telescopes, with complementing \Fermi Gamma-ray Space Telescope observations at GeV
+  energies. No significant gamma-ray emission from the Coma cluster was detected. Flux upper limits
+  at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$
+  s$^{-1}$ (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ (\Fermi, 1-3
+  GeV), respectively. For VERITAS (\Fermi), the limits are a factor of 60 (20) higher than
   model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons of the Coma
@@
   approach informed by cosmological cluster simulations, the CR-to-thermal pressure is constrained
-to be $< 15\%$ from VERITAS data and $< 2.5\%$ from {\em Fermi} data (averaged within the virial
+  to be $< 15\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
   radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic CR
   interactions, the observations imply a lower limit on the central magnetic field in Coma of
-$0.5$--$3\mu$G, depending on the magnetic decline and gamma-ray spectral index.  Since these
-values are well below those inferred by Faraday rotation measurements in Coma, this makes the
-hadronic model a very plausible explanation of the Coma radio halo. Finally, a constraint on the
-thermally averaged product of the total self-annihilation cross section and the relative velocity
-of the dark-matter particles, $\expval{\sigma v}$, is derived and found to be $\lesssim 10^{-21}$
-cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
+  $1$--$3\mu$G, depending on how the magnetic field declines with radius and on the gamma-ray
+  spectral index. Since these values are well below those inferred by Faraday rotation measurements
+  in Coma, this makes the hadronic model a very plausible explanation of the Coma radio
+  halo. Finally, a constraint on the thermally averaged product of the total self-annihilation cross
+  section and the relative velocity of the dark-matter particles, $\expval{\sigma v}$, is derived
+  and found to be $\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
 \end{abstract}
@@
 \section{Introduction}
-Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of
-a few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. According to the currently
+Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of a
+few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. According to the currently
 favored hierarchical model of cosmic structure formation, larger objects formed through successive
 mergers of smaller objects with galaxy clusters sitting on top of this mass hierarchy
-\citep[see][for a review]{article:Voit:2005}. Most of the mass ($\sim$80\%) in a cluster is in form
-of dark matter (DM), as indicated by galaxy dynamics and gravitational lensing
+\citep[see][for a review]{article:Voit:2005}. Most of the mass ($\sim$80\%) in a cluster is dark
+matter (DM), as indicated by galaxy dynamics and gravitational lensing
 \citep{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the intra-cluster medium (ICM)
@@
 magnetic fields also provide a means to efficiently accelerate particles \citep[see,
-e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters feature
-mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic
-electrons and positrons (leptons) and magnetic fields permeating the ICM
-\citep{article:Cassano_etal:2010}. The two theories competing to explain the radio halo are the
-``hadronic model'', in which the radio-emitting electrons are produced in inelastic collisions of
-cosmic-ray (CR) ions with thermal gas of the ICM \citep{article:Dennison:1980,
-  article:EnsslinPfrommerMiniatiSubramanian:2011}, and the ``re-acceleration model'', in which
-during states of strong ICM turbulence, e.g. after a cluster merger, interactions of a long-lived
-pool of 100-MeV electrons with plasma waves might be efficient enough to accelerate them to energies
-($\sim 10$ GeV) sufficient to produce observable radio emission \citep[][and references
-therein]{article:BrunettiLazarian:2010}. Recent observations of possibly non-thermal emission from
-clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
+e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters feature mega-parsec
+scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and
+positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Two
+theories are competing to explain radio halos. In the ``hadronic model'', the radio-emitting
+electrons are produced in inelastic collisions of cosmic-ray (CR) ions with the thermal gas of the
+ICM \citep{article:Dennison:1980, article:EnsslinPfrommerMiniatiSubramanian:2011}. In the
+``re-acceleration model'', a long-lived pool of 100-MeV electrons---previously accelerated by
+formation shocks, galactic winds, or jets of active galactic nuclei (AGN)---interacts with plasma
+waves that are excited during states of strong ICM turbulence, e.g. after a cluster merger. This may
+result in second order Fermi acceleration and may produce energetic electrons ($\sim 10$ GeV)
+sufficient to explain observable radio emission \citep{article:SchlickeiserSieversThiemann:1987,
+  article:BrunettiLazarian:2010}. Observations of possibly non-thermal emission from clusters
+in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
 \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may
@@
 Galaxy clusters have, for many years, been proposed as sources of gamma rays. If shock acceleration
-in the ICM is an efficient process, a population of highly relativistic CR protons and heavy ions
-is to be expected in the ICM. The main energy-loss mechanism for CR hadrons at high energies is pion
-production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay;
+in the ICM is an efficient process, a population of highly relativistic CR protons and heavy ions is
+to be expected in the ICM. The main energy-loss mechanism for CR hadrons at high energies is pion
+production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay,
 the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
-  which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to
+  which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion to
 gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
-scales of a cluster and the volume-filling magnetic fields in the ICM, CR hadrons will be confined
-in the cluster on timescales comparable to or longer than the Hubble time
-\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over
-time. For a given CR distribution function, the hadronically induced gamma-ray flux is directly
-proportional to the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/
-\expval{P_{\mathrm{th}}}$. Already a very modest $X_{\CR}$ of a few percent implies an observable
-flux of high-energy gamma rays \citep[e.g.,][]{article:PfrommerEnsslin:2004b}.
+size of a cluster and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
+the cluster on timescales comparable to or longer than the Hubble time
+\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate. For a
+given CR distribution function, the hadronically induced gamma-ray flux is directly proportional to
+the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$. A very
+modest $X_{\CR}$ of a few percent implies an observable flux of gamma rays
+\citep[e.g.,][]{article:PfrommerEnsslin:2004b}.
 
@@
 Universe -- suggesting again a substantial non-thermal pressure contribution on large scales
-\citep{article:Mahdavi_etal:2008}. Observing high-energy gamma-ray emission is a complementary
-method of constraining the pressure contribution of CRs that is most sensitive to the cluster core
+\citep{article:Mahdavi_etal:2008}. Observing gamma-ray emission is a complementary method of
+constraining the pressure contribution of CRs that is most sensitive to the cluster core
 region. However, it assumes that the CR component is fully mixed with the ICM and may not allow for
-a detection of a two-phase structure of CRs and the thermal ICM. A fraction $X_\CR$ of only a few 
-percent is required in order to produce a gamma-ray flux observable with current generation of
-gamma-ray telescopes rendering this technique at least as sensitive as the dynamical and
-hydrostatic method (which are more general in that they are sensitive to any non-thermal pressure
-component).
+a detection of a two-phase structure of CRs and the thermal ICM. An $X_\CR$ of only a few percent is
+required in order to produce a gamma-ray flux observable with the current generation of gamma-ray
+telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method
+(which are more general in that they are sensitive to any non-thermal pressure component).
 
@@
 made. Observations with EGRET \citep{article:Sreekumar_etal:1996, article:Reimer_etal:2003} and the
-Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on
-the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for Fermi observations) for
+\Fermi Gamma-ray Space Telescope \citep{article:Ackermann_etal:2010} have provided upper limits on
+the gamma-ray fluxes (typically $\sim10^{-9}$ ph cm$^{2}$ s$^{-1}$ for \Fermi observations) for
 several galaxy clusters in the MeV to GeV band. Upper limits on the very-high-energy (VHE)
@@
 In this article, results from the VERITAS observations of the Coma cluster of galaxies are
-reported, with complementing analysis of available data from the Fermi Gamma-ray Space Telescope.
-The VERITAS and Fermi data have been used to place constraints on cosmic-ray particle populations,
+reported, with complementing analysis of available data from the \Fermi Gamma-ray Space Telescope.
+The VERITAS and \Fermi data have been used to place constraints on cosmic-ray particle populations,
 magnetic fields, and dark matter in the cluster. Throughout the analyses, a present day Hubble
@@
 The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter
-imaging atmospheric Cherenkov telescopes \citep[IACTs;][]{article:Holder_etal:2006} located at an
+imaging atmospheric Cherenkov telescopes \citep{article:Holder_etal:2006} located at an
 altitude of $\sim$1250 m a.s.l. at the Fred Lawrence Whipple Observatory in southern Arizona
@@
 
-\section{Fermi-LAT Analysis and Results}
-The Large Area Telescope (LAT) on board the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi})
+\section{\Fermi-LAT Analysis and Results}
+The Large Area Telescope (LAT) on board the \Fermi Gamma-ray Space Telescope (\Fermi)
 has observed the Coma cluster in all-sky survey mode since its launch in June 2008. The
-\emph{Fermi}-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus
+\Fermi-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus
 very complimentary to the VERITAS observations. \citet{article:Ackermann_etal:2010} reported on the
@@
 \citet{article:Abdo_etal:2009}. To eliminate albedo gamma rays from the Earth limb, a zenith angle
-cut of 105$^{\circ}$ is applied. The \emph{Fermi} Science Tools version v9r23p1 and Instrumental
+cut of 105$^{\circ}$ is applied. The \Fermi Science Tools version v9r23p1 and Instrumental
 Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events
 calibrated in flight) were used throughout this work. Only photons above 1 GeV are considered, where
-the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates the
+the constraints on the flux are most meaningful. The \Fermi-LAT collaboration estimates the
 systematic uncertainties at 10 GeV to be around
@@
 \section{Gamma Ray Emission from Cosmic Rays}
-We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution
-in the Coma cluster using the upper limits derived from VERITAS and \emph{Fermi}-LAT data in this
-work. This approach includes (1) a simplified multi-frequency analytical approach that assumes a
-constant CR-to-thermal energy density and a power-law spectrum in momentum, (2) an analytic model
-derived from cosmological hydrodynamical simulations of the formation of galaxy clusters, and (3)
-an approach that uses the
-observed luminosity of the giant radio halo in Coma to place a lower limit on the expected
-$\gamma$-ray flux in the hadronic model -- where the radio-emitting electrons are secondaries from
-CR interactions and which is independent of the magnetic field distribution.  This translates into a
-minimum CR pressure which, if challenged by tight gamma-ray limits/detections, enables scrutinizing
-the hadronic interaction model of the formation of giant radio halos. Alternatively, by realizing a
-spatial CR distribution that is just consistent with the flux upper limits and requiring the model
-to match the observed radio data, this enables us to derive a lower limit on the magnetic field
-distribution. We stress again that his approach assumes the validity of the hadronic interaction
-model. Modelling the CR distribution through different techniques enable
-us to bracket our ignorance about the underlying plasma physics that shape the CR distribution and
-hence reflect the Bayesian priors that are imposed on the modelling \citep[see][for a
-discussion]{article:PinzkePfrommerBergstrom}.
+We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution in
+the Coma cluster using the upper limits derived from VERITAS and \Fermi-LAT data in this work. This
+approach includes (1) a simplified multi-frequency analytical approach that assumes a constant
+CR-to-thermal energy density and a power-law spectrum in momentum, (2) an analytic model derived
+from cosmological hydrodynamical simulations of the formation of galaxy clusters, and (3) an
+approach that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on
+the expected $\gamma$-ray flux in the hadronic model -- where the radio-emitting electrons are
+secondaries from CR interactions and which is independent of the magnetic field distribution.  This
+last approach translates into a minimum CR pressure which, if challenged by tight gamma-ray limits/detections,
+enables scrutinizing the hadronic interaction model of the formation of giant radio
+halos. Alternatively, realizing a spatial CR distribution that is consistent with the flux
+upper limits and requiring the model to match the observed radio data, enables us to derive a
+lower limit on the magnetic field distribution. We stress again that this approach assumes the
+validity of the hadronic interaction model. Modelling the CR distribution through different
+techniques enable us to bracket our lack of understanding about the underlying plasma physics that shape the CR
+distribution and hence reflect the Bayesian priors that are imposed on the modelling \citep[see][for
+a discussion]{article:PinzkePfrommerBergstrom}.
 
@@
 by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV).  Constraints on $X_\CR$
-with {\em Fermi} limits depend only weakly on $\alpha$ and are most constraining for an aperture of
+with \Fermi limits depend only weakly on $\alpha$ and are most constraining for an aperture of
 0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly
@@
 at the present time (at the boundary of voids and filaments/super-cluster regions) dominate the
-acceleration of CRs which subsequently are adiabatically transported through the cluster. Hence, the
+acceleration of CRs which are adiabatically transported through the cluster. Hence, the
 model provides a plausible upper limit for the CR contribution from structure formation shocks in
 galaxy clusters which can be scaled with the effective acceleration efficiency. Other possible CR
-sources, such as AGN and starburst-driven galactic winds have been neglected for simplicity which
+sources, such as AGN and starburst-driven galactic winds have been neglected for simplicity but
 could in principle increase the expected gamma-ray yield.
 
-These cosmological simulations only considered advective transport of CRs by turbulent gas motions
+These cosmological simulations only consider advective transport of CRs by turbulent gas motions
 which lead to centrally enhanced density profiles.  However, other means of CR transport such as
-diffusion
-and streaming may flatten the CR radial profiles. It has been suggested that advection is dominant
-only during mergers, in which case relaxed clusters could have a reduced gamma-ray luminosity by up
-to a factor of five compared with merging clusters
-\citep{article:EnsslinPfrommerMiniatiSubramanian:2011}. The goal of this and other future work of
-seeking for gamma-ray emission from clusters is to constrain the acceleration physics and transport
-properties of CRs.
+diffusion and streaming may flatten the CR radial profiles. It has been suggested that advection is
+dominant only during mergers, in which case relaxed clusters could have a reduced gamma-ray
+luminosity by up to a factor of five compared with merging clusters
+\citep{article:EnsslinPfrommerMiniatiSubramanian:2011}. Hence, tight upper limits on the gamma-ray
+emission are able to constrain a combination of acceleration physics and transport properties of
+CRs.
 
@@
 finite energy intervals across the angular apertures tested in this study (solid lines). These model
-fluxes (summarized in Table \ref{table:constraints_simple}) are compared to {\em Fermi} and VERITAS
-flux upper limits of the same energy intervals.  The gamma-ray flux limit of {\em Fermi} in the
+fluxes (summarized in Table \ref{table:constraints_simple}) are compared to \Fermi and VERITAS
+flux upper limits of the same energy intervals.  The gamma-ray flux limit of \Fermi in the
 energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining but still above the model
 predictions that assume an optimistically large shock acceleration efficiency and CR transport
-parameters as laid out above.  In our further analysis, we use the most constraining {\em Fermi}
+parameters as laid out above.  In our further analysis, we use the most constraining \Fermi
 flux limits in the energy interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the
@@
 \expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster
-center (grey lines) and contained within $R$ (black lines). All radii are shown in units of the virial
-radius, $R_\rmn{vir}=2.2$~Mpc. To compute the CR pressure, we assume a low-momentum cutoff of the CR
-distribution at $q = 0.8\,m_p c$ to reflect the high cooling rates at low CR energies. The relative CR
-pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at the
-peripheral accretion shocks compared to the weak central flow shocks. Adiabatic compression of a
-mixture of CRs and thermal gas disfavours the
-CR pressure relative to the thermal pressure on account of the softer equation of state of CRs. The
-weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas.
+center and contained within $R$. All radii are shown in units of the virial radius,
+$R_\rmn{vir}=2.2$~Mpc. To compute the CR pressure, we assume a low-momentum cutoff of the CR
+distribution at $q = 0.8\,m_p c$ to reflect the high cooling rates at low CR energies. The relative
+CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at
+the peripheral accretion shocks compared to the weak central flow shocks. Adiabatic compression of a
+mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on
+account of the softer equation of state of CRs. The weak increase of $X_{\CR}$ toward the core is
+due to the comparably fast thermal cooling of gas.
 
@@
 
-Equivalently, the most constraining {\em Fermi} upper limit in the energy interval of 1-3 GeV
+Equivalently, the most constraining \Fermi upper limit in the energy interval of 1-3 GeV
 ($<0.4^\circ$) is a factor of 1.1 larger than our model predictions (assuming $\alpha=2.1$ which is
@@
 \ref{fig:xcr}).  The $X_\CR$-constraint evaluated within the cluster virial radius is comparable to
-the constraint in our simplified model of $X_\CR<0.025$.  Naturally, with the Fermi limits we probe
+the constraint in our simplified model of $X_\CR<0.025$.  Naturally, with the \Fermi limits we probe
 the region around GeV-energies that dominate the CR pressure and we do not expect any differences in
@@
 factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$, $<0.2^{\circ}$) and a
-factor of about 20 below the {\em Fermi} upper limits (adopting $\alpha=2.3$, $<0.4^{\circ}$). Note
+factor of about 20 below the \Fermi upper limits (adopting $\alpha=2.3$, $<0.4^{\circ}$). Note
 that these minimum gamma-ray fluxes are sensitive to a running of the CR proton spectral index with
@@
 \label{sec:B}
-In the previous section we have obtained an absolute lower limit in the gamma-ray emission in
+In the previous section we have obtained an absolute lower limit on the gamma-ray emission in
 the hadronic model by assuming high magnetic fields, $B\gg B_\rmn{CMB}$. We can turn the
@@
 profile, integrate the flux within a radius of $(0.13, 0.2, 0.4)$ degree, and scale the CR profile
-in order to match the corresponding VERITAS/{\em Fermi} flux upper limits. This scaling factor,
+in order to match the corresponding VERITAS/\Fermi flux upper limits. This scaling factor,
 $X_{\CR,0}$, depends on the CR spectral index, $\alpha$, (assuming a power-law CR population for
@@
 $B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from $B_{0} = 1.1$ to $4.6\,\mu$G in the
-case of \emph{Fermi}.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the
+case of \Fermi.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the
 Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits on
@@
 radio-emitting electrons. A high magnetic field would be required to match the observed
-synchrotron emission. The opposite is true for the \emph{Fermi} upper limits at 1 GeV, which
+synchrotron emission. The opposite is true for the \Fermi upper limits at 1 GeV, which
 probe CRs around a pivot point of 8 GeV: a soft CR spectral index implies a comparably small
@@
 cosmological cluster simulations (Sect.\ref{sec:simulation}).} They should be interpreted as upper
-limits since they are derived from flux upper limits. For the {\em Fermi} upper limits, they range
+limits since they are derived from flux upper limits. For the \Fermi upper limits, they range
 from 0.1 to 0.4; hence the $X_{\CR}$-profiles always obey the energy condition, i.e., $P_{\CR} <
@@
 
-Within this pragmatic approach we employ two different directions. First, adopting a high magnetic
+Within this pragmatic approach we employ two different methods. First, adopting a high magnetic
 field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the
 hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining
-flux upper limits of {\em Fermi} (VERITAS). Second, by matching the radio emission profile (i.e.,
+flux upper limits of \Fermi (VERITAS). Second, by matching the radio emission profile (i.e.,
 fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay
@@
 limits of the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS  flux
-limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for {\em Fermi} flux limits). Since all these lower
+limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for \Fermi flux limits). Since all these lower
 limits on $B_0$ are below the values favored by Faraday RM, $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G
@@
 
-The {\em Fermi} flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying
+The \Fermi flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying
 between 2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$
@@
   gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic interactions of CRs and ICM
-  protons (dotted). Note that the {\em Fermi} limit for the energy interval of 1--3 GeV within the
+  protons (dotted). Note that the \Fermi limit for the energy interval of 1--3 GeV within the
   aperture of 0.4$^\circ$ is most constraining.}
@@
 lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining
-VERITAS upper limits within 0.2$^\circ$ (solid) and {\em Fermi} upper limits within 0.4$^\circ$
+VERITAS upper limits within 0.2$^\circ$ (solid) and \Fermi upper limits within 0.4$^\circ$
 (dashed). We compare differential $X_\CR$-profiles (grey) to integrated profiles
@@
 \tablewidth{0pc}
-\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core}
+\tablecaption{\Fermi-LAT upper limits for the Coma cluster core}
 \tablehead{
@@
 0.4  & 6.7 & 15 & 62 & 1.21  & 4.4  \\
-\cutinhead{{\em Fermi} constraints:}
+\cutinhead{\Fermi constraints:}
 0.13 & 5.2 & 3.5 & 4.7 & 2.2  & 1.4  \\
@@
 by \citet{article:PinzkePfrommer:2010}: at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$
-for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for Fermi. }
+for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for \Fermi. }
 \tablenotetext{d}{Integrated gamma-ray flux from the simulation-based analytic model by
@@
 0.4  & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
-\cutinhead{{\em Fermi} energy range, 1--3~GeV:}
+\cutinhead{\Fermi energy range, 1--3~GeV:}
 0.13 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
@@
 Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph. m$^{-2}$
-s$^{-1}$ ({\em Fermi} energy range).}
+s$^{-1}$ (\Fermi energy range).}
 \tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the hadronic model
   described in Sect~\ref{sec:Fmin}. For simplicity, we duplicate $X_{\CR,\,\rmn{min}}$ for the
-  VERITAS and {\em Fermi} constraints: for a given realization of the CR pressure (and a magnetic
+  VERITAS and \Fermi constraints: for a given realization of the CR pressure (and a magnetic
   field model which is trivial here as we assume $B \gg B_\rmn{CMB}$), we can derive the radio flux
@@
     \multicolumn{6}{c}{Minimum magnetic field, $B_{0,\rmn{min}}~[\mu\rmn{G}]$\tablenotemark{a}:}\\
-    & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{{\em Fermi} constraints:} \\
+    & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{\Fermi constraints:} \\
     \colhead{$\alpha_{B}$} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} &

### 2011-10-18 ms.tex
Further changes according to Jeremy's and Gordana's suggestions

@@
 gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
-size of a cluster and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
+size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
 the cluster on timescales comparable to or longer than the Hubble time
@@
 is larger than 75, and the distance from the image centroid to the center of the camera is less
-than $1.43^{\circ}$. These quality selection criteria impose an energy threshold\footnote{Defined
-as the energy corresponding to the maximum of the product function of the observed spectrum with
-the collection area.} of about 220 GeV. In addition, events for which only images from the two
-closest-spaced telescopes\footnote{In the array configuration prior to summer 2009, two telescopes 
-had a separation of only 35 m.} survive quality selection are rejected, as they introduce an
-irreducible high background rate, due to local muons, degrading the instrument sensitivity
-\citep{article:MaierKnapp:2007}.
+than $1.43^{\circ}$. These quality selection criteria impose an energy threshold\footnote{The energy
+threshold is defined as the energy corresponding to the maximum of the product function of the
+observed spectrum with the collection area. It does not vary significantly for the different source
+scenarios and assumed spectral indices reported in this work.} of about 220 GeV. In addition,
+events for which only images from the two closest-spaced telescopes\footnote{In the arra
+configuration prior to summer 2009, two telescopes  had a separation of only 35 m.} survive quality
+selection are rejected, as they introduce an irreducible high background rate, due to local muons, 
+degrading the instrument sensitivity \citep{article:MaierKnapp:2007}.
 
@@
 \citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma cluster
-data set.
+data set. It is noted that slightly varying the spectral index ($\pm$ 0.2) does not significantly
+impact the cuts used for quality selection cuts and gamma-hadron separation in this work.
 
@@
 background from the off-source region scaled by the ratio of the solid angles to produce a final
-excess. The VHE gamma-ray significance is then calculated using the method by
+excess. The VHE gamma-ray significance is then calculated according to Formula 17 in
 \citet{article:LiMa:1983}. Significance skymaps over the VERITAS field of view produced with a
@@
 distribution is a radial comparison of the ON-source event distribution with the estimated
-background. It extends out to a radius of 0.42 square degrees to cover all regions of interest
-considered in this work. A 99\% confidence level upper limit is calculated for each region of
+background. It extends out to 0.42 square degrees to cover both the case of point-like and extended
+emission from the core of the Coma cluster. The $\theta^{2}$ distributions for the member galaxies
+alos considered in this work are very similar to that in Figure \ref{fig:thetasq} and show no
+excess of gamma rays. A 99\% confidence level upper limit is calculated for each region of
 interest using the method described by \citet{article:Rolke_etal:2005} assuming a Gaussian
 background. A lower bound of zero is imposed on the signal rate to handle the negative excesses
-seen for several of the regions of interest. Figure \ref{fig:sigdist} shows that the VERITAS data
-is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent
-of unity.
+seen for several of the regions of interest. Figure \ref{fig:sigdist} shows the distribution of
+significances over the VERITAS skymap, which is well fit by a Gaussian with a mean close to zero and
+a standard deviation within a few percent of unity.
 
@@
 has observed the Coma cluster in all-sky survey mode since its launch in June 2008. The
-\Fermi-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is thus
+\Fermi-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is
 very complimentary to the VERITAS observations. \citet{article:Ackermann_etal:2010} reported on the
@@
 cut of 105$^{\circ}$ is applied. The \Fermi Science Tools version v9r23p1 and Instrumental
-Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events
-calibrated in flight) were used throughout this work. Only photons above 1 GeV are considered, where
-the constraints on the flux are most meaningful. The \Fermi-LAT collaboration estimates the
-systematic uncertainties at 10 GeV to be around
+Response Functions (IRFs) P6\_V11\_Diffuse were used throughout this work. Only photons above 1 GeV
+are considered, where the constraints on the flux are most meaningful. The \Fermi-LAT collaboration
+estimates the systematic uncertainties at 10 GeV to be around
 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper
-limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved,
+limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both an unresolved,
 point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray
@@
 secondaries from CR interactions and which is independent of the magnetic field distribution.  This
-last approach translates into a minimum CR pressure which, if challenged by tight gamma-ray limits/detections,
-enables scrutinizing the hadronic interaction model of the formation of giant radio
-halos. Alternatively, realizing a spatial CR distribution that is consistent with the flux
+last approach translates into a minimum CR pressure which, if challenged by tight gamma-ray
+limits/detections, enables scrutinizing the hadronic interaction model of the formation of giant
+radio halos. Alternatively, realizing a spatial CR distribution that is consistent with the flux
 upper limits and requiring the model to match the observed radio data, enables us to derive a
@@
 validity of the hadronic interaction model. Modelling the CR distribution through different
-techniques enable us to bracket our lack of understanding about the underlying plasma physics that shape the CR
-distribution and hence reflect the Bayesian priors that are imposed on the modelling \citep[see][for
-a discussion]{article:PinzkePfrommerBergstrom}.
+techniques enable us to bracket our lack of understanding about the underlying plasma physics that
+shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modelling
+\citep[see][for a discussion]{article:PinzkePfrommerBergstrom}.
 
@@
 \section{Discussion and Conclusions}
-VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time
-between March and May in 2008. No significant excess of gamma-rays above a threshold of about 220
-GeV was detected. Flux upper limits at 99\% confidence level were calculated for the cluster core
-and three member galaxies. The core was considered both as a point-like and spatially extended
-source. The obtained flux upper limits were used to constrain properties of the cluster.
-
-We employed various approaches to constrain the CR population and magnetic field distribution that
-are complementary in their assumptions and hence well suited in assessing underlying Bayesian
-priors in the models. (1) We use a simplified ``isobaric CR model'' that is characterized by a
+We have reported on the observations of the Coma cluster of galaxies in VHE gamma rays with VERITAS
+and complementary observations with the \emph{Fermi}-LAT. VERITAS observed the Coma cluster of
+galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008. No
+significant excess of gamma-rays above an energy threshold of about 220 GeV was detected. The
+\emph{Fermi}-LAT has observed the Coma cluster in all-sky survey mode since its launch in June
+2008. We have used all data available from launch to June 2011 for an updated analysis over already
+published results \citep{article:Ackermann_etal:2010}. Again, no significant excess of gamma rays
+was detected. We have used the VERITAS and \emph{Fermi}-LAT data to calculate flux upper limits at
+the 99\% confidence level for the cluster core, considered as both a point-like and spatially
+extended source, and three member galaxies. The flux upper limits obtained was then used to
+constrain properties of the cluster.
+
+We have employed various approaches to constrain the CR population and magnetic field distribution
+that are complementary in their assumptions and hence well suited in assessing underlying Bayesian
+priors in the models. (1) We used a simplified ``isobaric CR model'' that is characterized by a
 constant CR-to-thermal pressure fraction and has a power-law momentum spectrum. While this model
@@
 approximate universality of the CR distribution (when neglecting CR diffusion and streaming which
-appears necessary to explain the radio halo bimodality). (3) We finally use a pragmatic
+appears necessary to explain the radio halo bimodality). (3) We finally used a pragmatic
 approach which models the CR and magnetic distribution in order to reproduce the observed emission
@@
 small bias due to CRs.
+
+We have also used the flux upper limits obtained with VERITAS to constrain the thermally averaged
+product of the total self-annihilation cross section and the relative velocity of the dark matter
+particles. Assuming the dark matter is a WIMP and follows the density profile by 
+\citet{article:NavarroFrenkWhite:1997} we calculated the limits on $\expval{\sigma v}$ to be on the
+order of $10^{-20}$ to $10^{-21}$ cm$^{-3}$ s$^{-1}$ depending on the chosen aperture. These limits
+are based on conservative estimates of the astrophysical factor, which does not inlcude any boosting
+from clumping or the Sommerfeld effect.
 
@@
 \caption{$\theta^{2}$ distribution from VERITAS observations of the Coma cluster of galaxies. The
-points with error bars represent the ON-source data sample and the filled area is the estimated
-background due to cosmic rays. Each bin represents an annulus around the Coma cluster core
+points with error bars represent the ON-source data sample and the filled area is the background estimation in the OFF-source regions. Each bin represents an annulus around the Coma cluster core
 position. The data were derived from the ring background model using a $0.2^{\circ}$ sampling

### 2011-11-14 ms.tex
Minor typo in abstract fixed
Updated the VERITAS acknowledgment blurb

@@
   radio halo to be all secondaries from cosmic-ray interactions. We use the gamma-ray flux upper
-  limits to constrain the populations of CRs and magnetic fields and in Coma. Using an analytical
+  limits to constrain the populations of CRs and magnetic fields in Coma. Using an analytical
   approach informed by cosmological cluster simulations, the CR-to-thermal pressure is constrained
@@
 \acknowledgments
-This research was supported by grants from the U.S. Department of Energy, the U.S. National Science
-Foundation, and the Smithsonian Institution, by NSERC in Canada, by Science Foundation Ireland, and
-by STFC in the UK. We acknowledge the excellent work of the technical support staff at the FLWO and
-the collaborating institutions in the construction and operation of the instrument. C.P. gratefully
-acknowledges financial support of the Klaus Tschira Foundation.
+This research is supported by grants from the U.S. Department of Energy Office of Science, the U.S.
+National Science Foundation and the Smithsonian Institution, by NSERC in Canada, by Science
+Foundation Ireland (SFI 10/RFP/AST2748) and by STFC in the U.K. We acknowledge the excellent work
+of the technical support staff at the Fred Lawrence Whipple Observatory and at the collaborating
+institutions in the construction and operation of the instrument.
 

### 2011-12-02 ms.tex
Edited manuscript for typos etc.

@@
 \usepackage{xspace}
+\RequirePackage{lineno}
 
@@
 
+\linenumbers
+
 \begin{document}
@@
 \begin{abstract}
+\linenumbers
 Observations of radio halos and relics in galaxy clusters indicate efficient electron acceleration
@@
 location is offset from the center of the field of view, to allow for simultaneous background
-estimation \citep{article:Formin_etal:1994}. All of the observations were made in a small range of
+estimation \citep{article:Fomin_etal:1994}. All of the observations were made in a small range of
 zenith angles averaging $\sim 21^{\circ}$.
@@
 scenarios and assumed spectral indices reported in this work.} of about 220 GeV. In addition,
-events for which only images from the two closest-spaced telescopes\footnote{In the arra
+events for which only images from the two closest-spaced telescopes\footnote{In the array
 configuration prior to summer 2009, two telescopes  had a separation of only 35 m.} survive quality
-selection are rejected, as they introduce an irreducible high background rate, due to local muons, 
+selection are rejected, as they introduce an irreducible high background rate due to local muons, 
 degrading the instrument sensitivity \citep{article:MaierKnapp:2007}.
@@
 Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters
-\citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parametrized
+\citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parameterized
 moment analysis of the shower images \citep{inproc:Hillas:1985}. The gamma-hadron separation cuts
@@
 emission from the core of the Coma cluster. The $\theta^{2}$ distributions for the member galaxies
-alos considered in this work are very similar to that in Figure \ref{fig:thetasq} and show no
+also considered in this work are very similar to that in Figure \ref{fig:thetasq} and show no
 excess of gamma rays. A 99\% confidence level upper limit is calculated for each region of
@@
 lower limit on the magnetic field distribution. We stress again that this approach assumes the
-validity of the hadronic interaction model. Modelling the CR distribution through different
+validity of the hadronic interaction model. Modeling the CR distribution through different
 techniques enable us to bracket our lack of understanding about the underlying plasma physics that
-shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modelling
+shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modeling
 \citep[see][for a discussion]{article:PinzkePfrommerBergstrom}.
@@
 the peripheral accretion shocks compared to the weak central flow shocks. Adiabatic compression of a
-mixture of CRs and thermal gas disfavours the CR pressure relative to the thermal pressure on
+mixture of CRs and thermal gas disfavors the CR pressure relative to the thermal pressure on
 account of the softer equation of state of CRs. The weak increase of $X_{\CR}$ toward the core is
@@
 be challenged. The method we use to constrain the magnetic field inherits a dependence on
-the assumed radial scaling which we parametrize as
+the assumed radial scaling which we parameterize as
 \begin{equation}
@@
 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
-conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in
+conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parameterization as adopted in
 this study. We caution, however, that the minimum-energy condition is violated at the outer radio
@@
 \end{equation}
-which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density
+which parameterizes the distribution of DM by the scale radius $r_{s}$ and the scale density
 $\rho_{s}$. Using weak-lensing measurements of the virial mass in the Coma cluster
@@
 the 99\% confidence level for the cluster core, considered as both a point-like and spatially
-extended source, and three member galaxies. The flux upper limits obtained was then used to
+extended source, and three member galaxies. The flux upper limits obtained were then used to
 constrain properties of the cluster.
@@
 constant CR-to-thermal pressure fraction and has a power-law momentum spectrum. While this model
-is physically not justified a priory, it is simple and widely used in the literature and captures
+is physically not justified a priori, it is simple and widely used in the literature and captures
 some aspects of more elaborate models such as (2) the simulation-based analytical approach of
@@
 \colhead{RoI\tablenotemark{a} [deg]} & 
-\colhead{$N_{S}$} & 
-\colhead{S\tablenotemark{b} [$\sigma$]} &
-\multicolumn{6}{c}{Flux U.L.\tablenotemark{c}} \\
+\colhead{$N_{S}$\tablenotemark{b}} & 
+\colhead{S\tablenotemark{c} [$\sigma$]} &
+\multicolumn{6}{c}{Flux U.L.\tablenotemark{d}} \\
 \colhead{} & 
@@
 analysis PSF.}
-\tablenotetext{b}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
-\tablenotetext{c}{99\% confidence level upper limit in units of $10^{-8}$ ph. m$^{-2}$ s$^{-1}$
+\tablenotetext{b}{Event counts in the source region.}
+\tablenotetext{c}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
+\tablenotetext{d}{99\% confidence level upper limit in units of $10^{-8}$ ph. m$^{-2}$ s$^{-1}$
 calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with

### 2011-12-02 ms.tex
Added in the VERITAS author list

@@
 \title{Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi}
-\author{N. Karlsson\altaffilmark{1,2}, M. Pohl\altaffilmark{3,4}}
-\affil{(the VERITAS collaboration)} 
+\author{
+T. Arlen\altaffilmark{1},
+M. Beilicke\altaffilmark{2},
+W. Benbow\altaffilmark{3},
+V. Bugaev\altaffilmark{2},
+K. Byrum\altaffilmark{4},
+A. Cannon\altaffilmark{5},
+A. Cesarini\altaffilmark{6},
+L. Ciupik\altaffilmark{7},
+J. Dumm\altaffilmark{8},
+G. Finnegan\altaffilmark{9},
+L. Fortson\altaffilmark{8},
+A. Furniss\altaffilmark{10},
+N. Galante\altaffilmark{3},
+G. Gyuk\altaffilmark{7},
+P. Kaaret\altaffilmark{11},
+N. Karlsson\altaffilmark{8,23},
+D. Kieda\altaffilmark{9},
+H. Krawczynski\altaffilmark{2},
+G. Maier\altaffilmark{12},
+P. Majumdar\altaffilmark{1},
+S. McArthur\altaffilmark{2},
+A. McCann\altaffilmark{13},
+P. Moriarty\altaffilmark{14},
+A. N. Otte\altaffilmark{15},
+J. S. Perkins\altaffilmark{16,17},
+M. Pohl\altaffilmark{18,12},
+H. Prokoph\altaffilmark{12},
+E. Roache\altaffilmark{3},
+J. Ruppel\altaffilmark{18,12},
+D. B. Saxon\altaffilmark{19},
+G. H. Sembroski\altaffilmark{20},
+C. Skole\altaffilmark{12},
+I. Telezhinsky\altaffilmark{18,12},
+G. Te\v{s}i\'{c}\altaffilmark{13},
+S. Thibadeau\altaffilmark{2},
+R. Welsing\altaffilmark{12}}
+
 %%\email{nkarlsson@physics.umn.edu}
 \and
-\author{S. Federici\altaffilmark{3,4}, C. Pfrommer\altaffilmark{1,5},
-A. Pinzke\altaffilmark{6}}
-
-\altaffiltext{1}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
-\altaffiltext{2}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
-\altaffiltext{3}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
-\altaffiltext{4}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm, Germany}
-\altaffiltext{5}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
-\altaffiltext{6}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
+\author{S. Federici\altaffilmark{12,18}, C. Pfrommer\altaffilmark{21,23},
+A. Pinzke\altaffilmark{22}}
+
+%% affiliations
+\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA 90095, USA}
+\altaffiltext{2}{Department of Physics, Washington University, St. Louis, MO 63130, USA}
+\altaffiltext{3}{Fred Lawrence Whipple Observatory, Harvard-Smithsonian Center for Astrophysics, Amado, AZ 85645, USA}
+\altaffiltext{4}{Argonne National Laboratory, 9700 S. Cass Avenue, Argonne, IL 60439, USA}
+\altaffiltext{5}{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
+\altaffiltext{6}{School of Physics, National University of Ireland Galway, University Road, Galway, Ireland}
+\altaffiltext{7}{Astronomy Department, Adler Planetarium and Astronomy Museum, Chicago, IL 60605, USA}
+\altaffiltext{8}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
+\altaffiltext{9}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
+\altaffiltext{10}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
+\altaffiltext{11}{Department of Physics and Astronomy, University of Iowa, Van Allen Hall, Iowa City, IA 52242, USA}
+\altaffiltext{12}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
+\altaffiltext{13}{Physics Department, McGill University, Montreal, QC H3A 2T8, Canada}
+\altaffiltext{14}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
+\altaffiltext{15}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
+\altaffiltext{16}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
+\altaffiltext{17}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
+\altaffiltext{18}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm,Germany}
+\altaffiltext{19}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}
+\altaffiltext{20}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
+\altaffiltext{21}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
+\altaffiltext{22}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
+\altaffiltext{23}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
 

### 2011-12-09 ms.tex
Matt Vivier's comments included

@@
 %\def\del#1{{\bf (DELETED TEXT)}}
-\def\C#1{#1}
-%\def\C#1{{\bf #1}}
+%\def\C#1{#1}
+\def\C#1{{\bf #1}}
 
@@
 \section{Introduction}
-Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of a
+Clusters of galaxies are the largest virialized objects in the Universe, with typical sizes of a
 few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. According to the currently
@@
 the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
-which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion to
-gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
-size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
-the cluster on timescales comparable to or longer than the Hubble time
+  which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion
+to gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the
+large size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in the
+cluster on timescales comparable to or longer than the Hubble time
 \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate. For a
 given CR distribution function, the hadronically induced gamma-ray flux is directly proportional to
-the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$. A very
+the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$
+\citep[e.g.,][]{article:Ensslin_etal:2007}, \C{where the brackets indicate volume averages.} A very
 modest $X_{\CR}$ of a few percent implies an observable flux of gamma rays
@@
 several galaxy clusters in the MeV to GeV band. Upper limits on the very-high-energy (VHE)
-gamma-ray flux from a select few clusters, including the Coma cluster, have been provided by
+gamma-ray flux from a small sample of clusters, including the Coma cluster, have been provided by
 observations with ground-based imaging atmospheric Cherenkov telescopes
@@
 Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters
-\citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parameterized
+\citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parametrized
 moment analysis of the shower images \citep{inproc:Hillas:1985}. The gamma-hadron separation cuts
@@
 validity of the hadronic interaction model. Modeling the CR distribution through different
-techniques enable us to bracket our lack of understanding about the underlying plasma physics that
+techniques enables us to bracket our lack of understanding about the underlying plasma physics that
 shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modeling
@@
 with earlier work in the literature, we do not impose a low-momentum cutoff, $q$, on the CR
-distribution function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is
-unconstrained,\footnote{The hadronic interaction physics guarantees that the CR spectral index
-coincides with that of the resulting pion-decay gamma-ray emission.} we vary it in the range
+distribution function, i.e., we adopt $q=0$. Since {\em a priori}, the CR spectral index is
+unconstrained\footnote{The hadronic interaction physics guarantees that the CR spectral index
+coincides with that of the resulting pion-decay gamma-ray emission.}, we vary it in the range
 $2.1<\alpha<2.5$, which is compatible with the radio spectral index of the giant radio halo of the
@@
 the Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
-article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
+article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
 responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
-times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.} To model
+times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. To model
 the thermal pressure, we adopt the electron density profile for the Coma cluster that has been
@@
 times the critical density of the Universe. Constraints on $X_\CR$ with VERITAS flux upper limits
-strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate
-the CR pressure) to TeV energies. The flux measurements within 0.2$^{\circ}$ are the most
-constraining and yield limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1
+\C{(99\%\ CL)} strongly depend on $\alpha$. This is due to the comparably large \C{energy range from
+  GeV energies (that dominate the CR pressure, provided $\alpha>2$ and a non-relativistic
+  low-momentum cutoff, i.e., $q<m_p c$) to energies at 220 GeV, where our quality selection criteria
+  imposed the energy threshold. These gamma-ray energies correspond to 1.6 TeV CRs -- an energy
+  ratio of more than 3 orders of magnitudes which explains the sensitivity to small changes in
+  $\alpha$.} The flux measurements within 0.2$^{\circ}$ are the most constraining due to a
+competition between integrated signal and background for an increasing size of the radius of
+integration. This yields limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1
 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted
 by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV).  Constraints on $X_\CR$
-with \Fermi limits depend only weakly on $\alpha$ and are most constraining for an aperture of
-0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly
-worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
+with \Fermi limits \C{(99\%\ CL)} depend only weakly on $\alpha$ \C{since the energy range at GeV
+  energies probed by \Fermi are influenced by the pion-decay bump which is characterized by a shape
+  parameter that depends inversely on the CR spectral index \citep{article:PfrommerEnsslin:2004b},
+  partly absorbing the pressure ratios of different energy ranges. $X_\CR$-constraints with \Fermi
+  limits are most constraining for an aperture of 0.4$^{\circ}$; despite the slightly weaker flux
+  upper limits in comparison to the smaller radii of integration, we expect a considerably larger
+  gamma-ray luminosity due to the increasing volume in this model.} The best limit of $X_\CR< 0.017$
+is achieved for $\alpha=2.3$ and only slightly worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
 
@@
 Figure \ref{fig:spectrum} shows the expected integral spectral energy distribution of Coma within
-the virial radius (dotted lines). Additionally shown are integrals of the differential spectrum for
-finite energy intervals across the angular apertures tested in this study (solid lines). These model
-fluxes (summarized in Table \ref{table:constraints_simple}) are compared to \Fermi and VERITAS
-flux upper limits of the same energy intervals.  The gamma-ray flux limit of \Fermi in the
-energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining but still above the model
-predictions that assume an optimistically large shock acceleration efficiency and CR transport
-parameters as laid out above.  In our further analysis, we use the most constraining \Fermi
-flux limits in the energy interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the
-energy range above 220 GeV.
+the virial radius (dotted lines). \C{This suggests a spectral index of $\alpha=2.1$ in the energy
+  interval of 1--3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV).}  Additionally
+shown are integrals of the differential spectrum for finite energy intervals across the angular
+apertures tested in this study (solid lines). These model fluxes (summarized in Table
+\ref{table:constraints_simple}) are compared to \Fermi and VERITAS flux upper limits of the same
+energy intervals.  \C{Constraints on $X_\CR$} with the gamma-ray flux limit of \Fermi in the energy
+interval of 1--3 GeV ($<0.4^\circ$) are most constraining but still above the model predictions that
+assume an optimistically large shock acceleration efficiency and CR transport parameters as laid out
+above.  In our further analysis, we use the most constraining \Fermi flux limits in the energy
+interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220
+GeV.
 
@@
 central magnetic field of Coma of 5~$\mu$G \citep{article:Bonafede_etal:2010}, the radio halo
-emission at GHz frequencies is dominated by the electrons with a energy $E_\rmn{e} \sim 2.5$ GeV
+emission at GHz frequencies is dominated by the electrons with an energy $E_\rmn{e} \sim 2.5$ GeV
 (which corresponds to proton energies $E_\rmn{p} \sim 40$ GeV). Gamma rays with an energy of $200$
@@
 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
-conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parameterization as adopted in
+conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted in
 this study. We caution, however, that the minimum-energy condition is violated at the outer radio
@@
 \end{equation}
-which parameterizes the distribution of DM by the scale radius $r_{s}$ and the scale density
+which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density
 $\rho_{s}$. Using weak-lensing measurements of the virial mass in the Coma cluster
@@
 order of $10^{-20}$ to $10^{-21}$ cm$^{-3}$ s$^{-1}$ depending on the chosen aperture. These limits
-are based on conservative estimates of the astrophysical factor, which does not inlcude any boosting
+are based on conservative estimates of the astrophysical factor, which does not include any boosting
 from clumping or the Sommerfeld effect.
@@
   central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r) /
-  n_{\rmn{e}}(0)]^{\alpha_B}$.}  
+  n_{\rmn{e}}(0)]^{\alpha_B}$. \C{In all cases we used the most constraining $\rmn{RoI}=0.4^\circ$, see
+  Sect.~\ref{sec:B} for details.}}
 \label{table:Bmin}

### 2011-12-14 ms.tex
F_min discussion clarified

@@
 unconstrained\footnote{The hadronic interaction physics guarantees that the CR spectral index
-coincides with that of the resulting pion-decay gamma-ray emission.}, we vary it in the range
-$2.1<\alpha<2.5$, which is compatible with the radio spectral index of the giant radio halo of the
-Coma cluster after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to
-the Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
+  coincides with that of the resulting pion-decay gamma-ray emission \citep[see discussion
+  in][]{article:PfrommerEnsslin:2004b}.}, we vary it in the range $2.1<\alpha<2.5$, which is
+compatible with the radio spectral index of the giant radio halo of the Coma cluster after
+accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the
+Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
   article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
@@
 shown in Table \ref{table:constraints}, where $F_{\gamma,\rmn{iso}}$ is the gamma-ray flux in the
-simplified model introduced in \S\ref{sec:simple}. Even in the most constraining cases, these are a
-factor of about 60 below the VERITAS upper limits (adopting $\alpha=2.1$, $<0.2^{\circ}$) and a
-factor of about 20 below the \Fermi upper limits (adopting $\alpha=2.3$, $<0.4^{\circ}$). Note
-that these minimum gamma-ray fluxes are sensitive to a running of the CR proton spectral index with
-energy as a result of, e.g., momentum-dependent diffusion: assuming a plausible value for the
-central magnetic field of Coma of 5~$\mu$G \citep{article:Bonafede_etal:2010}, the radio halo
-emission at GHz frequencies is dominated by the electrons with an energy $E_\rmn{e} \sim 2.5$ GeV
-(which corresponds to proton energies $E_\rmn{p} \sim 40$ GeV). Gamma rays with an energy of $200$
-GeV are produced by CR protons with an energy of $E_\rmn{p} \sim 1.6$ TeV -- a factor of 50 higher
-than those probed by radio halo observations. A steepening of the CR proton spectral index of 0.2
-between 40 GeV and 1.6 TeV would imply a decrease in the minimum gamma-ray flux by a factor of two.
+simplified model introduced in \S\ref{sec:simple}. \C{Even in the most constraining cases and
+  assuming $\alpha\leq 2.3$, these are a factor of $\sim 60$ below the VERITAS upper limits (for
+  $\alpha=2.1$, $<0.2^{\circ}$) and a factor of $\sim 20$ below the \Fermi upper limits (for
+  $\alpha=2.3$, $<0.4^{\circ}$)}. Note that these minimum gamma-ray fluxes are sensitive to a
+running of the CR proton spectral index with energy as a result of, e.g., momentum-dependent
+diffusion: assuming a plausible value for the central magnetic field of Coma of 5~$\mu$G
+\citep{article:Bonafede_etal:2010}, the radio halo emission at GHz frequencies is dominated by the
+electrons with an energy $E_\rmn{e} \sim 2.5$ GeV (which corresponds to proton energies $E_\rmn{p}
+\sim 40$ GeV). Gamma rays with an energy of $200$ GeV are produced by CR protons with an energy of
+$E_\rmn{p} \sim 1.6$ TeV -- a factor of 50 higher than those probed by radio halo observations. A
+steepening of the CR proton spectral index of 0.2 between 40 GeV and 1.6 TeV would imply a decrease
+in the minimum gamma-ray flux by a factor of two.
 

### 2011-12-15 ms.tex
Anders' changes with small updates to the simulation-based constraints

@@
 approach informed by cosmological cluster simulations, the CR-to-thermal pressure is constrained
-to be $< 15\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
+to be \C{$< 16\%$} from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
 radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic CR
@@
 \C{(99\%\ CL)} strongly depend on $\alpha$. This is due to the comparably large \C{energy range from
-  GeV energies (that dominate the CR pressure, provided $\alpha>2$ and a non-relativistic
-  low-momentum cutoff, i.e., $q<m_p c$) to energies at 220 GeV, where our quality selection criteria
-  imposed the energy threshold. These gamma-ray energies correspond to 1.6 TeV CRs -- an energy
-  ratio of more than 3 orders of magnitudes which explains the sensitivity to small changes in
-  $\alpha$.} The flux measurements within 0.2$^{\circ}$ are the most constraining due to a
-competition between integrated signal and background for an increasing size of the radius of
+  GeV energies (that dominate the CR pressure, provided $\alpha>2$ and the CR population has a
+  non-relativistic low-momentum cutoff, i.e., $q<m_p c$) to energies at 220 GeV, where our quality
+  selection criteria imposed the energy threshold. These gamma-ray energies correspond to 1.6 TeV
+  CRs -- an energy ratio of more than 3 orders of magnitudes which explains the sensitivity to small
+  changes in $\alpha$.} The flux measurements within 0.2$^{\circ}$ are the most constraining due to
+a competition between integrated signal and background for an increasing size of the radius of
 integration. This yields limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1
@@
 relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated
-limit of the relative CR pressure of $X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit
-within the cluster virial radius of $X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}).  This limit
+limit of the relative CR pressure of \C{$X_{\CR}<0.112$} within 0.2$^{\circ}$ that translates to a limit
+within the cluster virial radius of \C{$X_\CR<0.162$} (solid lines of Figure \ref{fig:xcr}).  This limit
 is less constraining by 50\% in comparison to the simplified analytical model, which gives
@@
 $\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit is
-more constraining by a factor of 1.5 in comparison to the simulation-based model which gives
-$X_\CR<0.15$. This difference is due to the concave form of the simulated spectrum which provides
+more constraining by a factor of \C{1.6} in comparison to the simulation-based model which gives
+$X_\CR<0.16$. This difference is due to the concave form of the simulated spectrum which provides
 more pressure at GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
@@
 \caption{Integral flux upper limits for Coma (this work, Tables~\ref{table:results} and
-  \ref{table:fermi}) for different integration radii (shown with different grey scales), assuming
-  $\alpha=2.1$. These are compared to integrated spectra of the same energy interval and aperture,
-  assuming the universal gamma-ray spectrum of clusters \citep{article:PinzkePfrommer:2010}. To
-  guide the eye, we show the underlying universal integral energy distribution of pion decay
-  gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic interactions of CRs and ICM
-  protons (dotted). Note that the \Fermi limit for the energy interval of 1--3 GeV within the
-  aperture of 0.4$^\circ$ is most constraining.}
+  \ref{table:fermi}) for different integration radii (\C{error bars} with different grey scales),
+  \C{assuming that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is
+    adopted.}  These are compared to integrated spectra of the same energy interval and aperture,
+  assuming the universal gamma-ray spectrum of clusters \citep[\C{lines with different grey
+    scales,}][]{article:PinzkePfrommer:2010}. To guide the eye, we show the underlying universal
+  integral energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting
+  from hadronic interactions of CRs and ICM protons (dotted). \C{For visualization purposes all
+    photon fluxes are weighted with the smallest energy in each interval.} Note that the \Fermi
+  limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most
+  constraining.}
 \label{fig:spectrum}
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified analytic
+\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified, \C{isobaric} analytic
   model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV and
@@
     & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
-    & \colhead{$F_{\gamma,\rmn{sim}}(E)$\tablenotemark{c}} & \colhead{$F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{d}}   \\
+    & \colhead{$F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{c}}  
+    & \colhead{$F_{\rmn{UL}}/F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{d}} \\
 & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$} & & 
@@
 \hline
-0.13 & 10  & 23 & 97 & 0.52  & 1.9  \\
-0.2  & 4.8 & 10 & 43 & 0.80  & 2.9  \\
-0.4  & 6.7 & 15 & 62 & 1.21  & 4.4  \\
+0.13 & 10  & 23 & 97 & 1.9 & 14.8\\
+0.2  & 4.8 & 10 & 43 & 2.9 & 7.2\\
+0.4  & 6.7 & 15 & 62 & 4.4 & 10.8\\
 \cutinhead{\Fermi constraints:}
-0.13 & 5.2 & 3.5 & 4.7 & 2.2  & 1.4  \\
-0.2  & 3.5 & 2.4 & 3.1 & 3.4  & 2.1  \\
-0.4  & 2.5 & 1.7 & 2.3 & 5.2  & 3.2  \\
+0.13 & 5.2 & 3.5 & 4.7 & 1.4 & 1.96\\
+0.2  & 3.5 & 2.4 & 3.1 & 2.1 & 1.46\\
+0.4  & 2.5 & 1.7 & 2.3 & 3.2 & 1.10\\
 \enddata
@@
 cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
-\tablenotetext{c}{Differential gamma-ray flux $E^{2}dF/dE$ from the simulation-based analytic model
-by \citet{article:PinzkePfrommer:2010}: at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$
-for VERITAS and between $E=1-3$ GeV in units of $10^{-9}$ GeV m$^{-2}$ s$^{-1}$ for \Fermi. }
-\tablenotetext{d}{Integrated gamma-ray flux from the simulation-based analytic model by
+\tablenotetext{c}{Integrated gamma-ray flux from the simulation-based analytic model by
 \citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$
-s$^{-1}$ for VERITAS and  above $E=1~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
+s$^{-1}$ for VERITAS and between $E=1-3~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
 Fermi.} 
+\tablenotetext{d}{\C{Ratio of flux upper limits ($F_{\rmn{UL}}$) to the integrated gamma-ray flux
+ from the simulation-based analytic model: in VERITAS band above $E=220~\rmn{GeV}$ an $\alpha=2.3$ is 
+ assumed for the U.L., and in \Fermi band between $E=1-3$ GeV an $\alpha=2.1$ is assumed for the U.L..}}
 \label{table:constraints_simple}

### 2011-12-16 ms.tex
typo corrected
Updated CPs acknowledgement

--- 2011-12-09 ms.tex
@@
 %\def\del#1{{\bf (DELETED TEXT)}}
-%\def\C#1{#1}
-\def\C#1{{\bf #1}}
+\def\C#1{#1}
+%\def\C#1{{\bf #1}}
 
@@
 \section{Introduction}
-Clusters of galaxies are the largest virialized objects in the Universe, with typical sizes of a
+Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of a
 few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. According to the currently
@@
 the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
-  which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion
-to gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the
-large size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in the
-cluster on timescales comparable to or longer than the Hubble time
+which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion to
+gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
+size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
+the cluster on timescales comparable to or longer than the Hubble time
 \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate. For a
 given CR distribution function, the hadronically induced gamma-ray flux is directly proportional to
-the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$
-\citep[e.g.,][]{article:Ensslin_etal:2007}, \C{where the brackets indicate volume averages.} A very
+the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$. A very
 modest $X_{\CR}$ of a few percent implies an observable flux of gamma rays
@@
 several galaxy clusters in the MeV to GeV band. Upper limits on the very-high-energy (VHE)
-gamma-ray flux from a small sample of clusters, including the Coma cluster, have been provided by
+gamma-ray flux from a select few clusters, including the Coma cluster, have been provided by
 observations with ground-based imaging atmospheric Cherenkov telescopes
@@
 validity of the hadronic interaction model. Modeling the CR distribution through different
-techniques enables us to bracket our lack of understanding about the underlying plasma physics that
+techniques enable us to bracket our lack of understanding about the underlying plasma physics that
 shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modeling
@@
 with earlier work in the literature, we do not impose a low-momentum cutoff, $q$, on the CR
-distribution function, i.e., we adopt $q=0$. Since {\em a priori}, the CR spectral index is
-unconstrained\footnote{The hadronic interaction physics guarantees that the CR spectral index
-coincides with that of the resulting pion-decay gamma-ray emission.}, we vary it in the range
+distribution function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is
+unconstrained,\footnote{The hadronic interaction physics guarantees that the CR spectral index
+coincides with that of the resulting pion-decay gamma-ray emission.} we vary it in the range
 $2.1<\alpha<2.5$, which is compatible with the radio spectral index of the giant radio halo of the
@@
 the Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
-article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
+article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
 responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
-times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. To model
+times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.} To model
 the thermal pressure, we adopt the electron density profile for the Coma cluster that has been
@@
 times the critical density of the Universe. Constraints on $X_\CR$ with VERITAS flux upper limits
-\C{(99\%\ CL)} strongly depend on $\alpha$. This is due to the comparably large \C{energy range from
-  GeV energies (that dominate the CR pressure, provided $\alpha>2$ and a non-relativistic
-  low-momentum cutoff, i.e., $q<m_p c$) to energies at 220 GeV, where our quality selection criteria
-  imposed the energy threshold. These gamma-ray energies correspond to 1.6 TeV CRs -- an energy
-  ratio of more than 3 orders of magnitudes which explains the sensitivity to small changes in
-  $\alpha$.} The flux measurements within 0.2$^{\circ}$ are the most constraining due to a
-competition between integrated signal and background for an increasing size of the radius of
-integration. This yields limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1
+strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate
+the CR pressure) to TeV energies. The flux measurements within 0.2$^{\circ}$ are the most
+constraining and yield limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1
 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted
 by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV).  Constraints on $X_\CR$
-with \Fermi limits \C{(99\%\ CL)} depend only weakly on $\alpha$ \C{since the energy range at GeV
-  energies probed by \Fermi are influenced by the pion-decay bump which is characterized by a shape
-  parameter that depends inversely on the CR spectral index \citep{article:PfrommerEnsslin:2004b},
-  partly absorbing the pressure ratios of different energy ranges. $X_\CR$-constraints with \Fermi
-  limits are most constraining for an aperture of 0.4$^{\circ}$; despite the slightly weaker flux
-  upper limits in comparison to the smaller radii of integration, we expect a considerably larger
-  gamma-ray luminosity due to the increasing volume in this model.} The best limit of $X_\CR< 0.017$
-is achieved for $\alpha=2.3$ and only slightly worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
+with \Fermi limits depend only weakly on $\alpha$ and are most constraining for an aperture of
+0.4$^{\circ}$.  The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$ and only slightly
+worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
 
@@
 Figure \ref{fig:spectrum} shows the expected integral spectral energy distribution of Coma within
-the virial radius (dotted lines). \C{This suggests a spectral index of $\alpha=2.1$ in the energy
-  interval of 1--3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV).}  Additionally
-shown are integrals of the differential spectrum for finite energy intervals across the angular
-apertures tested in this study (solid lines). These model fluxes (summarized in Table
-\ref{table:constraints_simple}) are compared to \Fermi and VERITAS flux upper limits of the same
-energy intervals.  \C{Constraints on $X_\CR$} with the gamma-ray flux limit of \Fermi in the energy
-interval of 1--3 GeV ($<0.4^\circ$) are most constraining but still above the model predictions that
-assume an optimistically large shock acceleration efficiency and CR transport parameters as laid out
-above.  In our further analysis, we use the most constraining \Fermi flux limits in the energy
-interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220
-GeV.
+the virial radius (dotted lines). Additionally shown are integrals of the differential spectrum for
+finite energy intervals across the angular apertures tested in this study (solid lines). These model
+fluxes (summarized in Table \ref{table:constraints_simple}) are compared to \Fermi and VERITAS
+flux upper limits of the same energy intervals.  The gamma-ray flux limit of \Fermi in the
+energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining but still above the model
+predictions that assume an optimistically large shock acceleration efficiency and CR transport
+parameters as laid out above.  In our further analysis, we use the most constraining \Fermi
+flux limits in the energy interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the
+energy range above 220 GeV.
 
@@
 central magnetic field of Coma of 5~$\mu$G \citep{article:Bonafede_etal:2010}, the radio halo
-emission at GHz frequencies is dominated by the electrons with an energy $E_\rmn{e} \sim 2.5$ GeV
+emission at GHz frequencies is dominated by the electrons with a energy $E_\rmn{e} \sim 2.5$ GeV
 (which corresponds to proton energies $E_\rmn{p} \sim 40$ GeV). Gamma rays with an energy of $200$
@@
 order of $10^{-20}$ to $10^{-21}$ cm$^{-3}$ s$^{-1}$ depending on the chosen aperture. These limits
-are based on conservative estimates of the astrophysical factor, which does not include any boosting
+are based on conservative estimates of the astrophysical factor, which does not inlcude any boosting
 from clumping or the Sommerfeld effect.
@@
 of the technical support staff at the Fred Lawrence Whipple Observatory and at the collaborating
-institutions in the construction and operation of the instrument.
+institutions in the construction and operation of the instrument. C.P. gratefully acknowledges 
+financial support of the Klaus Tschira Foundation.
 
@@
   central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r) /
-  n_{\rmn{e}}(0)]^{\alpha_B}$. \C{In all cases we used the most constraining $\rmn{RoI}=0.4^\circ$, see
-  Sect.~\ref{sec:B} for details.}}
+  n_{\rmn{e}}(0)]^{\alpha_B}$.}  
 \label{table:Bmin}

### 2011-12-17 ms.tex

@@
 approach informed by cosmological cluster simulations, the CR-to-thermal pressure is constrained
-to be $< 15\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
+to be $< 16\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
 radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic CR

### 2011-12-17 ms.tex
Edits

--- 2011-12-15 ms.tex
@@
 approach informed by cosmological cluster simulations, the CR-to-thermal pressure is constrained
-to be \C{$< 16\%$} from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
+to be $< 16\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
 radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic CR
@@
 \end{abstract}
+
+%
+%
 
@@
 the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
-  which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion
-to gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the
-large size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in the
-cluster on timescales comparable to or longer than the Hubble time
+which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion to
+gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
+size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
+the cluster on timescales comparable to or longer than the Hubble time
 \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate. For a
@@
 the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$
-\citep[e.g.,][]{article:Ensslin_etal:2007}, \C{where the brackets indicate volume averages.} A very
-modest $X_{\CR}$ of a few percent implies an observable flux of gamma rays
+\citep[see, e.g.,][]{article:Ensslin_etal:2007}, where the brackets indicates volume averages. A
+very modest $X_{\CR}$ of a few percent implies an observable flux of gamma rays
 \citep[e.g.,][]{article:PfrommerEnsslin:2004b}.
@@
 distribution function, i.e., we adopt $q=0$. Since {\em a priori}, the CR spectral index is
-unconstrained\footnote{The hadronic interaction physics guarantees that the CR spectral index
-  coincides with that of the resulting pion-decay gamma-ray emission \citep[see discussion
-  in][]{article:PfrommerEnsslin:2004b}.}, we vary it in the range $2.1<\alpha<2.5$, which is
-compatible with the radio spectral index of the giant radio halo of the Coma cluster after
-accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the
-Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
-  article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
+unconstrained,\footnote{The hadronic interaction physics guarantees that the CR spectral index
+coincides with that of the resulting pion-decay gamma-ray emission
+\citep[see discussion in][]{article:PfrommerEnsslin:2004b}.} we vary it in the range
+$2.1<\alpha<2.5$, which is compatible with the radio spectral index of the giant radio halo of the
+Coma cluster after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to
+the Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
+article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
 responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
-  times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. To model
+times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.} To model
 the thermal pressure, we adopt the electron density profile for the Coma cluster that has been
@@
 times the critical density of the Universe. Constraints on $X_\CR$ with VERITAS flux upper limits
-\C{(99\%\ CL)} strongly depend on $\alpha$. This is due to the comparably large \C{energy range from
+(99\% CL) strongly depend on $\alpha$.This is due to the comparably large energy range from
 GeV energies (that dominate the CR pressure, provided $\alpha>2$ and the CR population has a
@@
 CRs -- an energy ratio of more than 3 orders of magnitudes which explains the sensitivity to small
-  changes in $\alpha$.} The flux measurements within 0.2$^{\circ}$ are the most constraining due to
+changes in $\alpha$. The flux measurements within 0.2$^{\circ}$ are the most constraining due to
 a competition between integrated signal and background for an increasing size of the radius of
@@
 by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV). Constraints on $X_\CR$
-with \Fermi limits \C{(99\%\ CL)} depend only weakly on $\alpha$ \C{since the energy range at GeV
+with \Fermi limits (99\%\ CL) depend only weakly on $\alpha$ since the energy range at GeV
 energies probed by \Fermi are influenced by the pion-decay bump which is characterized by a shape
@@
 upper limits in comparison to the smaller radii of integration, we expect a considerably larger
-  gamma-ray luminosity due to the increasing volume in this model.} The best limit of $X_\CR< 0.017$
+gamma-ray luminosity due to the increasing volume in this model. The best limit of $X_\CR< 0.017$
 is achieved for $\alpha=2.3$ and only slightly worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
@@
 Figure \ref{fig:spectrum} shows the expected integral spectral energy distribution of Coma within
-the virial radius (dotted lines). \C{This suggests a spectral index of $\alpha=2.1$ in the energy
-  interval of 1--3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV).}  Additionally
+the virial radius (dotted lines). This suggests a spectral index of $\alpha=2.1$ in the energy
+interval of 1--3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV). Additionally
 shown are integrals of the differential spectrum for finite energy intervals across the angular
@@
 \ref{table:constraints_simple}) are compared to \Fermi and VERITAS flux upper limits of the same
-energy intervals.  \C{Constraints on $X_\CR$} with the gamma-ray flux limit of \Fermi in the energy
+energy intervals. Constraints on $X_\CR$ with the gamma-ray flux limit of \Fermi in the energy
 interval of 1--3 GeV ($<0.4^\circ$) are most constraining but still above the model predictions that
@@
 relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated
-limit of the relative CR pressure of \C{$X_{\CR}<0.112$} within 0.2$^{\circ}$ that translates to a limit
-within the cluster virial radius of \C{$X_\CR<0.162$} (solid lines of Figure \ref{fig:xcr}).  This limit
+limit of the relative CR pressure of $X_{\CR}<0.112$ within 0.2$^{\circ}$ that translates to a limit
+within the cluster virial radius of $X_\CR<0.162$ (solid lines of Figure \ref{fig:xcr}). This limit
 is less constraining by 50\% in comparison to the simplified analytical model, which gives
@@
 halo. This is in contrast to the simplified analytical CR model where $X_\CR=\rmn{const.}$
-(Sect.\ref{sec:simple}) and to the simulation-based model where $X_\CR(r)$ is derived from
-cosmological cluster simulations (Sect.\ref{sec:simulation}).} They should be interpreted as upper
+(\S~\ref{sec:simple}) and to the simulation-based model where $X_\CR(r)$ is derived from
+cosmological cluster simulations (\S~\ref{sec:simulation}).} They should be interpreted as upper
 limits since they are derived from flux upper limits. For the \Fermi upper limits, they range
@@
 $\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit is
-more constraining by a factor of \C{1.6} in comparison to the simulation-based model which gives
+more constraining by a factor of 1.6 in comparison to the simulation-based model which gives
 $X_\CR<0.16$. This difference is due to the concave form of the simulated spectrum which provides
@@
 \caption{Integral flux upper limits for Coma (this work, Tables~\ref{table:results} and
-  \ref{table:fermi}) for different integration radii (\C{error bars} with different grey scales),
-  \C{assuming that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is
-    adopted.}  These are compared to integrated spectra of the same energy interval and aperture,
-  assuming the universal gamma-ray spectrum of clusters \citep[\C{lines with different grey
-    scales,}][]{article:PinzkePfrommer:2010}. To guide the eye, we show the underlying universal
-  integral energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting
-  from hadronic interactions of CRs and ICM protons (dotted). \C{For visualization purposes all
-    photon fluxes are weighted with the smallest energy in each interval.} Note that the \Fermi
-  limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most
-  constraining.}
+\ref{table:fermi}) for different integration radii (arrows with different grey scales), assuming
+that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is adopted. These are
+compared to integrated spectra of the same energy interval and aperture, assuming the universal
+gamma-ray spectrum of clusters \citep[lines with different grey
+scales,][]{article:PinzkePfrommer:2010}.To guide the eye, we show the underlying universal integral
+energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic
+interactions of CRs and ICM protons (dotted). For visualization purposes all photon fluxes are
+weighted with the smallest energy in each interval. Note that the \Fermi limit for the energy
+interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.}
 \label{fig:spectrum}
@@
 \end{deluxetable}
+
+%
+%
 
@@
 
+%
+%
+
 \begin{deluxetable}{lccc}
@@
 
+%
+%
+
 \begin{deluxetable}{cccccc}
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified, \C{isobaric} analytic
-  model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV and
-  $>220$~GeV (simulation-based model).}
+\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified, isobaric
+analytic model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV
+and $>220$~GeV (simulation-based model).}
 \rotate
@@
 & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
-    & \colhead{$F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{c}}  
+& \colhead{$F_{\gamma,\rmn{sim}}(E)$\tablenotemark{c}}
 & \colhead{$F_{\rmn{UL}}/F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{d}} \\
@@
 Fermi.} 
-\tablenotetext{d}{\C{Ratio of flux upper limits ($F_{\rmn{UL}}$) to the integrated gamma-ray flux
- from the simulation-based analytic model: in VERITAS band above $E=220~\rmn{GeV}$ an $\alpha=2.3$ is 
- assumed for the U.L., and in \Fermi band between $E=1-3$ GeV an $\alpha=2.1$ is assumed for the U.L..}}
+\tablenotetext{d}{Ratio of flux upper limits ($F_{\rmn{UL}}$) to the integrated gamma-ray flux
+from the simulation-based analytic model: in VERITAS band above $E=220~\rmn{GeV}$ an $\alpha=2.3$
+is assumed for the U.L., and in \Fermi band between $E=1-3$ GeV an $\alpha=2.1$ is assumed for the
+U.L.}
 \label{table:constraints_simple}
 \end{deluxetable}
+
+%
+%
 
@@
 \enddata
-\tablenotetext{a}{Intrinsic source radius; we approximate the aperture of the point source-limits by the
-analysis PSF of 0.13$^\circ$.}
-\tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in Sect~\ref{sec:Fmin}. 
-Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph. m$^{-2}$
-s$^{-1}$ (\Fermi energy range).}
+\tablenotetext{a}{Intrinsic source radius; we approximate the aperture of the point source-limits
+by the analysis PSF of 0.13$^\circ$.}
+\tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in \S~\ref{sec:Fmin}. 
+Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph.
+m$^{-2}$ s$^{-1}$ (\Fermi energy range).}
 \tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the hadronic model
-  described in Sect~\ref{sec:Fmin}. For simplicity, we duplicate $X_{\CR,\,\rmn{min}}$ for the
-  VERITAS and \Fermi constraints: for a given realization of the CR pressure (and a magnetic
-  field model which is trivial here as we assume $B \gg B_\rmn{CMB}$), we can derive the radio flux
-  as well as gamma-ray fluxes in various bands (1--3 GeV, $>220$ GeV).}
+described in \S~\ref{sec:Fmin}. For simplicity, we duplicate $X_{\CR,\,\rmn{min}}$ for the VERITAS
+and \Fermi constraints: for a given realization of the CR pressure (and a magnetic field model
+which is trivial here as we assume $B \gg B_\rmn{CMB}$), we can derive the radio flux as well as
+gamma-ray fluxes in various bands (1--3 GeV, $>220$ GeV).}
 \label{table:constraints}
 \end{deluxetable}
+
+%
+%
 
@@
 \enddata
-\tablenotetext{a}{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the
-  central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r) /
-  n_{\rmn{e}}(0)]^{\alpha_B}$. \C{In all cases we used the most constraining $\rmn{RoI}=0.4^\circ$, see
-  Sect.~\ref{sec:B} for details.}}
+\tablenotetext{a}{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and
+the central field strength, $B_{0}$, which are defined by
+$B(r) = B_{0}\,[n_\rmn{e}(r) / n_{\rmn{e}}(0)]^{\alpha_B}$. In all cases we used the most constraining
+$\rmn{RoI}=0.4^\circ$, see \S~\ref{sec:B} for details.}  
 \label{table:Bmin}
 \end{deluxetable}
+
+%
+%
 

### 2011-12-18 ms.tex
Edited abstract according to MV comments

@@
 \newcommand{\ket}{\rangle}
-\shorttitle{Coma Cluster Observations with VERITAS}
+\shorttitle{Coma Cluster Observations with VERITAS and \Fermi}
 \shortauthors{VERITAS collaboration}
@@
 in Coma, this makes the hadronic model a very plausible explanation of the Coma radio
-halo. Finally, a constraint on the thermally averaged product of the total self-annihilation cross
-section and the relative velocity of the dark-matter particles, $\expval{\sigma v}$, is derived
-and found to be $\lesssim 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi}\gtrsim 1000$ GeV/c$^{2}$.
+halo. Finally, since galaxy clusters are dark matter (DM) dominated, the VERITAS upper limits have
+been used to place constraint on the thermally averaged product of the total self-annihilation cross
+section and the relative velocity of the DM particles, $\expval{\sigma v}$. This is found
+to be about $10^{-20} - 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi} = 300$ GeV/c$^{2}$.
 \end{abstract}

### 2011-12-18 ms.tex
Edited abstract according to MV comments
Edited introduction on DM based on MVs comments

@@
 
-A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM
+A third mechanism for gamma-ray production in a galaxy cluster could be self-annihilation of a DM
 particle, e.g. a weakly interacting massive particle (WIMP). As already mentioned, about 80\% of
-the cluster mass is in the form of dark matter. The gamma-ray emissivity from DM annihilations is
-proportional to the square of the DM density integrated along the line of sight, making galaxy
-clusters potentially good candidates for DM searches \citep{article:EvansFerrerSarkar:2004,
-article:BergstromHooper:2006, article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011},
-despite their large distances compared to other common targets for DM searches, such as dwarf
-spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,
-article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004,
-article:Aharonian_etal:2006, article:Aharonian_etal:2009b, article:Abramowski_etal:2011}.
+the cluster mass is in the form of dark matter, which makes galaxy clusters interesting targets for
+DM searches \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006,
+article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011} despite their large distances
+compared to other common targets for DM searches, such as dwarf spheroidal galaxies
+\citep{article:Strigari_etal:2007, article:Acciari_etal:2010, article:Aliu_etal:2009} or the
+Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
+article:Aharonian_etal:2009b, article:Abramowski_etal:2011}.
 

### 2011-12-18 ms.tex
'a priori' in italics

@@
 moment analysis of the shower images \citep{inproc:Hillas:1985}. The gamma-hadron separation cuts
-used in this analysis were optimized a priori for a weak point source (3\% Crab Nebula flux level)
-and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because the VHE
-gamma-ray spectrum for the Coma cluster is expected to be hard, with a photon index of about 2.3
-\citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma cluster
-data set. It is noted that slightly varying the spectral index ($\pm$ 0.2) does not significantly
-impact the cuts used for quality selection cuts and gamma-hadron separation in this work.
+used in this analysis were optimized {\em a priori} for a weak point source (3\% Crab Nebula flux
+level) and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because
+the VHE gamma-ray spectrum for the Coma cluster is expected to be hard, with a photon index of
+about 2.3 \citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma
+cluster data set. It is noted that slightly varying the spectral index ($\pm$ 0.2) does not
+significantly impact the cuts used for quality selection cuts and gamma-hadron separation in this
+work.
 
@@
 constant CR-to-thermal pressure fraction and has a power-law momentum spectrum. While this model
-is physically not justified a priori, it is simple and widely used in the literature and captures
-some aspects of more elaborate models such as (2) the simulation-based analytical approach of
-\citet{article:PinzkePfrommer:2010}. This is a ``first principle approach'' that predicts the CR
+is physically not justified {\em a priori}, it is simple and widely used in the literature and
+captures some aspects of more elaborate models such as (2) the simulation-based analytical approach 
+of \citet{article:PinzkePfrommer:2010}. This is a ``first principle approach'' that predicts the CR
 distribution spectrally and spatially for a given set of assumptions (namely the physics that was

### 2011-12-19 ms.tex
Edit with a lot of MVs comments incorporated

@@
 level) and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because
-the VHE gamma-ray spectrum for the Coma cluster is expected to be hard, with a photon index of
+the VHE gamma-ray spectrum for the Coma cluster is expected to be a power-law with a photon index of
 about 2.3 \citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma
@@
 these scenarios. In this work the focus has been on the core region and three cluster members. The
-latter are treated as point sources in the analysis, whereas the core is treated as either a point
+core region is treated as either a point
 source or a mildly extended source with intrinsic source radius $0.2^{\circ}$ or $0.4^{\circ}$,
@@
 
-Table \ref{table:results} lists the upper limits for the selected regions of interest tabulated in
+Table \ref{table:results} lists the upper limits for the selected regions of interest shown in
 Table \ref{table:roi}. These upper-limit calculations depend on the gamma-ray spectrum, which in
@@
 limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both an unresolved,
-point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray
+point-like or spatially extended emission, are shown in Table \ref{table:fermi}. The gamma-ray
 emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and
@@
 DM. While the nature of DM remains unknown, the most compelling theoretical candidate is a
-WIMP. The self-annihilations of WIMPs are expected to produce secondary gamma rays with a
-spectral signature that deviates significantly from the power-law spectra observed from most
-conventional astrophysical sources. The spectrum will also feature a sharp cutoff at the WIMP
-mass. These spectral features together with the expected difference in the
-intensity distribution compared to conventional astrophysical sources allow an
-indirect detection of DM.
+WIMP. The self-annihilation of WIMPs can either produce monoenergetic gamma ray lines or a
+continuum of secondary gamma rays that deviates significantly from the power-law spectra observed
+from most conventional astrophysical sources, with a sharp cut-off at the WIMP mass. These spectral
+features together with the expected difference in the intensity distribution compared to
+conventional astrophysical sources allow a clear, indirect detection of DM.
 
@@
 \frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=
-\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\,N_\gamma (E)\, J(\Delta\Omega),
+\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\,\frac{N_{\gamma}}{dE}\, J(\Delta\Omega),
 \label{eqn:WIMPflux}
@@
 where $\expval{\sigma v}$ is the thermally-averaged product of the total self-annihilation cross
-section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $N_\gamma (E)$ is the differential
-gamma-ray yield per annihilation\footnote{In this work, we have calculated the differential
-gamma-ray yield per annihilation using the Pythia Monte-Carlo simulator.}, $\Delta\Omega$ is the
-observed solid angle, and $J$ is the astrophysical factor - a dimensionless factor which determines
-the DM annihilation rate and depends on the DM distribution.
+section and the relative WIMP velocity, $m_{\chi}$ is the WIMP mass, $\frac{N_{\gamma}}{dE}$ is the
+differential gamma-ray yield per annihilation\footnote{In this work, we have calculated the
+differential gamma-ray yield per annihilation using the Pythia Monte-Carlo simulator.},
+$\Delta\Omega$ is the observed solid angle, and $J$ is the astrophysical factor - a dimensionless
+factor which determines the DM annihilation rate and depends on the DM distribution.
 
@@
 $R_{\gamma}(99\%\ \mathrm{CL}) = N_{\gamma}(99\%\ \mathrm{CL}) / T_{\mathrm{obs}}$, we can place
-constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. From Eq.
-(\ref{eqn:WIMPflux}) we find
+constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. Integrating Eq.
+(\ref{eqn:WIMPflux}) over energy we find
 \begin{equation}
@@
 R_{\gamma}(99\%\ \mathrm{CL})\, \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\,
-\frac{1}{\int^{m_{\chi}} dE\ A_{\mathrm{eff}}\,N_\gamma (E)},
+\frac{1}{\int^{m_{\chi}}_{0} dE\ A_{\mathrm{eff}}\,N_\gamma (E)},
 \end{equation}
@@
 Because the self-annihilation of a WIMP is a two-body process, the astrophysical factor
-$J(\Delta\Omega)$ can be expressed as the line-of-sight integral of the DM density squared
+$J(\Delta\Omega)$ is the line-of-sight integral of the DM density squared
 \begin{equation}
-J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right)
-\int_{\Delta\Omega}d\Omega\int d\lambda\ \rho^{2}(\lambda,\Omega),
+J(\Delta\Omega)=\int_{\Delta\Omega}d\Omega\int d\lambda\ \rho_{\chi}(\lambda)^{2}(\lambda,\Omega),
 \end{equation}
-where $\lambda$ represents the line-of-sight. Here,
-$J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the
-Hubble radius, $R_{H}$. In this work we have adopted the DM density profile by
+where $\lambda$ represents the line-of-sight. In this work, we have modeled the Coma DM
+distribution with a Navarro, Frenk and White (NFW) profile,
 \citet{article:NavarroFrenkWhite:1997},
@@
 \end{equation}
-which parameterizes the distribution of DM by the scale radius $r_{s}$ and the scale density
-$\rho_{s}$. Using weak-lensing measurements of the virial mass in the Coma cluster
-\citep{article:Gavazzi_etal:2009} we find for these parameters $r_{s}=0.654$ Mpc and
+where $r_{s}$ is the scale radius and $\rho_{s}$ isthe scale density. Using weak weak-lensing
+measurements of the virial mass in the Coma cluster \citep{article:Gavazzi_etal:2009} and the DM
+halo mass-concentration relation derived from N-body simulation of structure formation 
+\citep{article:Bullock_etal:2001}, we find for these parameters $r_{s}=0.654$ Mpc and
 $\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
@@
 The resulting exclusion regions in the $(\expval{\sigma v}, m_{\chi})$ parameter space are shown in
-Figure \ref{fig:dm} for three different DM self-annihilation channels: W$^{+}$W$^{-}$,
-b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$. Depending on the chosen aperture, the limits are on
-the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The numerical values for each of the channels
-are listed in Table \ref{table:DMlimits}. We note that these are based on conservative estimates of
-the astrophysical factor $J$, as we do not assume boosting by clumping or the Sommerfeld effect.
+Figure \ref{fig:dm} for three different DM self-annihilation channels, W$^{+}$W$^{-}$,
+b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$, independently of any WIMP models. Depending on the
+chosen aperture, the limits are on
+the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The minimum for each exclusion curve and
+corresponding DM particle mass is listed in Table \ref{table:DMlimits}. We note that these are
+based on conservative estimates of the astrophysical factor $J$, as we do not assume boosting by
+clumping or the Sommerfeld effect.
 
@@
 product of the total self-annihilation cross section and the relative velocity of the dark matter
-particles. Assuming the dark matter is a WIMP and follows the density profile by 
-\citet{article:NavarroFrenkWhite:1997} we calculated the limits on $\expval{\sigma v}$ to be on the
-order of $10^{-20}$ to $10^{-21}$ cm$^{-3}$ s$^{-1}$ depending on the chosen aperture. These limits
-are based on conservative estimates of the astrophysical factor, which does not include any boosting
-from clumping or the Sommerfeld effect.
+particles. Modeling the Coma cluster DM halo with a NFW profile we derived limits on
+$\expval{\sigma v}$ to be on the order of $10^{-20}$ to $10^{-21}$ cm$^{-3}$ s$^{-1}$ depending on
+the chosen aperture. These limits are based on conservative estimates of the astrophysical factor,
+which does not include any boosting from clumping or the Sommerfeld effect.
 
@@
 \caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ as a function of the DM
-particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this
-work.}
+particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits ($0.2^{\circ}$
+aperture) presented in this work.}
 \label{fig:dm}
@@
 \hline
-0.13 & 10 & 23 & 97 & 1.9 & 14.8\\
+0 & 10 & 23 & 97 & 1.9 & 14.8\\
 0.2 & 4.8 & 10 & 43 & 2.9 & 7.2\\
@@
 \cutinhead{\Fermi constraints:}
-0.13 & 5.2 & 3.5 & 4.7 & 1.4 & 1.96\\
+0 & 5.2 & 3.5 & 4.7 & 1.4 & 1.96\\
 0.2 & 3.5 & 2.4 & 3.1 & 2.1 & 1.46\\
@@
 \enddata
-\tablenotetext{a}{Intrinsic source radius; we approximate the aperture of the point source-limits by the
-analysis PSF of 0.13$^\circ$.}
+\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
+analysis PSF.}
 \tablenotetext{b}{Constraint on the relative CR pressure,
@@
 \enddata
-\tablenotetext{a}{Intrinsic source radius; we approximate the aperture of the point source-limits
-by the analysis PSF of 0.13$^\circ$.}
+\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
+analysis PSF.}
 \tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in \S~\ref{sec:Fmin}. 
@@
 \tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background
-region (ring method) and is used to estimate the level of gamma-ray contamination from DM.}
+region (ring method) and is used to estimate the level of gamma-ray contamination from DM. $\alpha$
+is the size ratio of the ON vs OFF source regions.}
 \label{table:astrofactor}

### 2011-12-19 ms.tex
Edit with a lot of MVs comments incorporated

@@
 It also lists the astrophysical factor calculated for the background region, which is used
-to estimate the gamma-ray contamination due to DM in the background region.
+to estimate the gamma-ray contamination from DM annihilation in the background region.
 

### 2011-12-19 ms.tex
Edit with more of MVs comments incorporated

@@
 are considered, where the constraints on the flux are most meaningful. The \Fermi-LAT collaboration
-estimates the systematic uncertainties at 10 GeV to be around
+estimates the systematic uncertainties on the effective area at 10 GeV to be around
 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper
@@
 b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$, independently of any WIMP models. Depending on the
-chosen aperture, the limits are on
-the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The minimum for each exclusion curve and
-corresponding DM particle mass is listed in Table \ref{table:DMlimits}. We note that these are
-based on conservative estimates of the astrophysical factor $J$, as we do not assume boosting by
-clumping or the Sommerfeld effect.
+chosen aperture, the limits are on the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The
+minimum for each exclusion curve and corresponding DM particle mass is listed in Table
+\ref{table:DMlimits}. We note that these limits are derived with conservative estimates of the
+astrophysical factor J. They do not include any boost to the annihilation rate possibly due to DM
+substructures populating the Coma halo, which could scale down the present limits by a factor
+O(100) in the most optimistic cases.
 
@@
 $\expval{\sigma v}$ to be on the order of $10^{-20}$ to $10^{-21}$ cm$^{-3}$ s$^{-1}$ depending on
-the chosen aperture. These limits are based on conservative estimates of the astrophysical factor,
-which does not include any boosting from clumping or the Sommerfeld effect.
+the chosen aperture. These limits are based on conservative estimates of the astrophysical factor
+where a possible boost to the annihilation rate due to DM substructures in the cluster halo has
+been neglected. Including such a boost could scale down the present limits by a factor $O(100)$ in
+the most optimistic cases.
 

### 2011-12-19 ms.tex
Some minor edits
Updated the author list

@@
 L. Ciupik\altaffilmark{7},
-J. Dumm\altaffilmark{8},
-G. Finnegan\altaffilmark{9},
-L. Fortson\altaffilmark{8},
-A. Furniss\altaffilmark{10},
+E. Collins-Hughes\altaffilmark{5},
+W. Cui\altaffilmark{8},
+R. Dickherber\altaffilmark{2},
+J. Dumm\altaffilmark{9},
+Q. Feng\altaffilmark{8},
+G. Finnegan\altaffilmark{10},
+L. Fortson\altaffilmark{9},
+A. Furniss\altaffilmark{11},
 N. Galante\altaffilmark{3},
+J. Grube\altaffilmark{7},
 G. Gyuk\altaffilmark{7},
-P. Kaaret\altaffilmark{11},
-N. Karlsson\altaffilmark{8,23},
-D. Kieda\altaffilmark{9},
+H. Huan\altaffilmark{12},
+G. Hughes\altaffilmark{13},
+T. B. Humensky\altaffilmark{14},
+P. Kaaret\altaffilmark{15},
+N. Karlsson\altaffilmark{9,27},
+Y. Khassen\altaffilmark{5},
+D. Kieda\altaffilmark{10},
 H. Krawczynski\altaffilmark{2},
-G. Maier\altaffilmark{12},
+G. Maier\altaffilmark{13},
 P. Majumdar\altaffilmark{1},
 S. McArthur\altaffilmark{2},
-A. McCann\altaffilmark{13},
-P. Moriarty\altaffilmark{14},
-A. N. Otte\altaffilmark{15},
-J. S. Perkins\altaffilmark{16,17},
-M. Pohl\altaffilmark{18,12},
-H. Prokoph\altaffilmark{12},
+A. McCann\altaffilmark{16},
+P. Moriarty\altaffilmark{17},
+M. Orr\altaffilmark{18},
+A. N. Otte\altaffilmark{19},
+J. S. Perkins\altaffilmark{20,21},
+M. Pohl\altaffilmark{22,13},
+H. Prokoph\altaffilmark{13},
+P. T. Reynolds\altaffilmark{23},
 E. Roache\altaffilmark{3},
-J. Ruppel\altaffilmark{18,12},
-D. B. Saxon\altaffilmark{19},
-G. H. Sembroski\altaffilmark{20},
-C. Skole\altaffilmark{12},
-I. Telezhinsky\altaffilmark{18,12},
-G. Te\v{s}i\'{c}\altaffilmark{13},
+J. Ruppel\altaffilmark{22,13},
+D. B. Saxon\altaffilmark{24},
+G. H. Sembroski\altaffilmark{8},
+C. Skole\altaffilmark{13},
+A. W. Smith\altaffilmark{10},
+I. Telezhinsky\altaffilmark{22,13},
+G. Te\v{s}i\'{c}\altaffilmark{16},
 S. Thibadeau\altaffilmark{2},
-R. Welsing\altaffilmark{12}}
-
-%%\email{nkarlsson@physics.umn.edu}
+M. Vivier\altaffilmark{24},
+J. E. Ward\altaffilmark{5},
+R. Welsing\altaffilmark{13}
+}
+
 \and
-\author{S. Federici\altaffilmark{12,18}, C. Pfrommer\altaffilmark{21,23},
-A. Pinzke\altaffilmark{22}}
-
-%% affiliations
+\author{S. Federici\altaffilmark{13,22}, C. Pfrommer\altaffilmark{25,27},
+A. Pinzke\altaffilmark{26}}
+
 \altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA 90095, USA}
@@
 \altaffiltext{7}{Astronomy Department, Adler Planetarium and Astronomy Museum, Chicago, IL 60605, USA}
-\altaffiltext{8}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
-\altaffiltext{9}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
-\altaffiltext{10}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
-\altaffiltext{11}{Department of Physics and Astronomy, University of Iowa, Van Allen Hall, Iowa City, IA 52242, USA}
-\altaffiltext{12}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
-\altaffiltext{13}{Physics Department, McGill University, Montreal, QC H3A 2T8, Canada}
-\altaffiltext{14}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
-\altaffiltext{15}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
-\altaffiltext{16}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
-\altaffiltext{17}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
-\altaffiltext{18}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm,Germany}
-\altaffiltext{19}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}
-\altaffiltext{20}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
-\altaffiltext{21}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
-\altaffiltext{22}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
-\altaffiltext{23}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
-
+\altaffiltext{8}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
+\altaffiltext{9}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
+\altaffiltext{10}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
+\altaffiltext{11}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
+\altaffiltext{12}{Enrico Fermi Institute, University of Chicago, Chicago, IL 60637, USA}
+\altaffiltext{13}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
+\altaffiltext{14}{Physics Department, Columbia University, New York, NY 10027, USA}
+\altaffiltext{15}{Department of Physics and Astronomy, University of Iowa, Van Allen Hall, Iowa City, IA 52242, USA}
+\altaffiltext{16}{Physics Department, McGill University, Montreal, QC H3A 2T8, Canada}
+\altaffiltext{17}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
+\altaffiltext{18}{Department of Physics and Astronomy, Iowa State University, Ames, IA 50011, USA}
+\altaffiltext{19}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
+\altaffiltext{20}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
+\altaffiltext{21}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
+\altaffiltext{22}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm,Germany}
+\altaffiltext{23}{Department of Applied Physics and Instrumentation, Cork Institute of Technology, Bishopstown, Cork, Ireland}
+\altaffiltext{24}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}
+
+% Christoph, Anders and Simone:
+\altaffiltext{25}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
+\altaffiltext{26}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
+\altaffiltext{27}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
+
+%%\email{nkarlsson@physics.umn.edu}
 %%\journalinfo{The Astrophysical Journal}
@@
 synchrotron emission to the observed radio halo emission over the entire extent. To 
-this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel
+this end, we de-project the fit to the surface brightness profile of Eq. \ref{beta} (using an Abel
 integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio
@@
   $B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as
-  a function of magnetic field strength (see Eqn.~(\ref{eq:Lnu})). Hence we have to iterate through
+  a function of magnetic field strength (see Eq. (\ref{eq:Lnu})). Hence we have to iterate through
   the previous steps until our solution for the minimum magnetic field $B_{0}$ is converged.
@@
 \tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
-analysis PSF.}
+gamma-ray PSF.}
 \tablenotetext{b}{Event counts in the source region.}
@@
 \tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
-analysis PSF.}
+gamma-ray PSF.}
 \tablenotetext{b}{Constraint on the relative CR pressure,
@@
 \tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
-analysis PSF.}
+gamma-ray PSF.}
 \tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in \S~\ref{sec:Fmin}. 

### 2012-02-03 ms.tex
Pat's and Rene's edits mostly included (some of Rene's major comments still needs attention).

@@
 also be sources of very high-energy (VHE; $E>100$ GeV) gamma-ray emission resulting from the
-interactions of highly relativistic cosmic-ray (CR) hadrons with the intracluster gas. Reported
-here are VHE gamma-ray observations of the Coma galaxy cluster with the VERITAS array of imaging
+interactions of highly relativistic cosmic-ray (CR) hadrons with the intracluster gas. We report
+here on VHE gamma-ray observations of the Coma galaxy cluster with the VERITAS array of imaging
 Cherenkov telescopes, with complementing \Fermi Gamma-ray Space Telescope observations at GeV
-energies. No significant gamma-ray emission from the Coma cluster was detected. Flux upper limits
-at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph. m$^{-2}$
-s$^{-1}$ (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ (\Fermi, 1-3
+energies. No significant gamma-ray emission from the Coma cluster was detected. Integral flux upper
+limits at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph.
+m$^{-2}$ s$^{-1}$ (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ (\Fermi, 1-3
 GeV), respectively. For VERITAS (\Fermi), the limits are a factor of 60 (20) higher than
 model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons of the Coma
-radio halo to be all secondaries from cosmic-ray interactions. We use the gamma-ray flux upper
+radio halo are all secondaries from cosmic-ray interactions. We use the gamma-ray flux upper
 limits to constrain the populations of CRs and magnetic fields in Coma. Using an analytical
-approach informed by cosmological cluster simulations, the CR-to-thermal pressure is constrained
+approach motivated by cosmological cluster simulations, the CR-to-thermal pressure is constrained
 to be $< 16\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
@@
 halo. Finally, since galaxy clusters are dark matter (DM) dominated, the VERITAS upper limits have
-been used to place constraint on the thermally averaged product of the total self-annihilation cross
-section and the relative velocity of the DM particles, $\expval{\sigma v}$. This is found
-to be about $10^{-20} - 10^{-21}$ cm$^{3}$ s$^{-1}$ for $m_{\chi} = 300$ GeV/c$^{2}$.
+been used to place constraints on the thermally averaged product of the total self-annihilation
+cross section and the relative velocity of the DM particles, $\expval{\sigma v}$. This is found
+to be about $10^{-20} - 10^{-21}$ cm$^{3}$ s$^{-1}$ for a DM particle mass $m_{\chi} = 300$
+GeV/c$^{2}$.
 \end{abstract}
@@
 
-The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung in the soft X-ray regime
+The ICM is a hot ($T\sim 10^{8}$ K) plasma emitting thermal bremsstrahlung in the soft X-ray regime
 \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated primarily through
@@
 accretion processes. Such shocks and turbulence in the ICM gas in combination with intra-cluster
-magnetic fields also provide a means to efficiently accelerate particles \citep[see,
-e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters feature mega-parsec
-scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and
-positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Two
-theories are competing to explain radio halos. In the ``hadronic model'', the radio-emitting
+magnetic fields also provide a means to accelerate particles efficiently \citep[see,
+e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters feature megaparsec
+scale halos of nonthermal radio emission, indicative of a population of relativistic electrons and
+positrons\footnote{From here on electrons and positrons are collectively referred to as electrons.}
+and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. There are two competing
+theories to explain radio halos. In the ``hadronic model'', the radio-emitting
 electrons are produced in inelastic collisions of cosmic-ray (CR) ions with the thermal gas of the
@@
 formation shocks, galactic winds, or jets of active galactic nuclei (AGN)---interacts with plasma
-waves that are excited during states of strong ICM turbulence, e.g. after a cluster merger. This may
-result in second order Fermi acceleration and may produce energetic electrons ($\sim 10$ GeV)
-sufficient to explain observable radio emission \citep{article:SchlickeiserSieversThiemann:1987,
-article:BrunettiLazarian:2010}. Observations of possibly non-thermal emission from clusters
-in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
+waves that are excited during states of strong ICM turbulence, e.g., after a cluster merger. This
+may result in second order Fermi acceleration and may produce energetic electrons ($\sim 10$ GeV)
+sufficient to explain the observable radio emission \citep{article:SchlickeiserSieversThiemann:1987,
+article:BrunettiLazarian:2010}. Observations of possibly nonthermal emission from clusters
+in the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
 \citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may
-provide further indications of relativistic particle populations in clusters, although the
-interpretation of these observations as non-thermal diffuse emission have been disputed on the basis
+provide further indication of relativistic particle populations in clusters, although the
+interpretation of these observations as nonthermal diffuse emission has been disputed on the basis
 of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009,
@@
 to be expected in the ICM. The main energy-loss mechanism for CR hadrons at high energies is pion
-production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay,
-the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon,
-which subsequently decays to an electron or positron as well as neutrinos.} and the neutral pion to
-gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large
-size and the volume-filling magnetic fields in the ICM, CR hadrons will be confined in
-the cluster on timescales comparable to or longer than the Hubble time
-\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate. For a
-given CR distribution function, the hadronically induced gamma-ray flux is directly proportional to
-the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$
-\citep[see, e.g.,][]{article:Ensslin_etal:2007}, where the brackets indicates volume averages. A
-very modest $X_{\CR}$ of a few percent implies an observable flux of gamma rays
-\citep[e.g.,][]{article:PfrommerEnsslin:2004b}.
+production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay.
+The decay of neutral pions produces gamma rays and the decay of charged pions produces muons, which 
+then decay to electrons and positrons. Due to the low density of the ICM
+($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large size and the volume-filling magnetic fields in
+the ICM, CR hadrons will be confined in the cluster on timescales comparable to, or longer than,
+the Hubble time \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} and they can
+therefore accumulate. For a given CR distribution function, the hadronically induced gamma-ray
+flux is directly proportional to the CR-to-thermal pressure fraction,
+$X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$ \citep[see, e.g.,][]{article:Ensslin_etal:2007},
+where the brackets indicates volume averages. A very modest $X_{\CR}$ of a few percent implies an
+observable flux of gamma rays \citep[e.g.,][]{article:PfrommerEnsslin:2004b}.
 
 Hydrostatic estimates of cluster masses, which are determined by balancing the thermal pressure
-force and the gravitational force, are biased low by the presence of any substantial non-thermal
+force and the gravitational force, are biased low by the presence of any substantial nonthermal
 pressure component, including a CR pressure contribution. Similarly, a substantial relative CR
-pressure can bias the temperature decrement of the cosmic microwave background (CMB) in the
-direction of a galaxy cluster due to the Sunyaev-Zel'dovich effect. This could then severely
+pressure can bias the temperature decrement of the cosmic microwave background (CMB) due to the
+Sunyaev-Zel'dovich effect in the direction of a galaxy cluster. This could then severely
 jeopardize the use of clusters to determine cosmological parameters. Comparing X-ray and optical
-potential profiles in the centers of galaxy clusters yields an upper limit of 20-30\% of non-thermal
+potential profiles in the centers of galaxy clusters yields an upper limit of 20-30\% of nonthermal
 pressure (that can be composed of CRs, magnetic fields or turbulence) relative to the thermal gas
@@
 at $R_{500}$ -- the radius within which the mean density is 500 times the critical density of the
-Universe -- suggesting again a substantial non-thermal pressure contribution on large scales
+Universe -- suggesting again a substantial nonthermal pressure contribution on large scales
 \citep{article:Mahdavi_etal:2008}. Observing gamma-ray emission is a complementary method of
@@
 required in order to produce a gamma-ray flux observable with the current generation of gamma-ray
-telescopes rendering this technique at least as sensitive as the dynamical and hydrostatic method
-(which are more general in that they are sensitive to any non-thermal pressure component).
+telescopes, rendering this technique at least as sensitive as the dynamical and hydrostatic methods
+(which are more general in that they are sensitive to any nonthermal pressure component).
 
 Gamma-ray emission can also be produced by Compton up-scattering of ambient photons, for example
-CMB photons, on ultra-relativistic leptons. Those leptons can either be secondaries from the above
-mentioned CR interactions or be injected into the ICM by powerful cluster members and be further
-accelerated by diffusive shock acceleration or turbulent reacceleration processes
+CMB photons, on ultra-relativistic electrons. Those electrons can either be secondaries from the
+above mentioned CR interactions or injected into the ICM by powerful cluster members and
+further accelerated by diffusive shock acceleration or turbulent reacceleration processes
 \citep[][and references therein]{article:SchlickeiserSieversThiemann:1987}.
@@
 A third mechanism for gamma-ray production in a galaxy cluster could be self-annihilation of a DM
-particle, e.g. a weakly interacting massive particle (WIMP). As already mentioned, about 80\% of
+particle, e.g., a weakly interacting massive particle (WIMP). As already mentioned, about 80\% of
 the cluster mass is in the form of dark matter, which makes galaxy clusters interesting targets for
@@
 
-The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters over all
+The Coma cluster of galaxies (ACO 1656) is one of the most thoroughly studied clusters across all
 wavelengths \citep{article:Voges_etal:1999}. Located at a distance of about 100 Mpc
@@
 in][]{article:BrownRudnick:2010}. It has been suggested \citep{article:Ensslin_etal:1998} and
-successively demonstrated by cosmological simulations, which model the non-thermal emission
+successively demonstrated by cosmological simulations which model the nonthermal emission
 processes \citep{article:PfrommerEnsslinSpringel:2008, article:Pfrommer:2008,
@@
 \section{VERITAS Observations and Analysis}
-The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m diameter
+The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m-diameter
 imaging atmospheric Cherenkov telescopes \citep{article:Holder_etal:2006} located at an
@@
 (31$^{\circ}$~40\arcmin~30\arcsec~N, 110$^{\circ}$~57\arcmin~07\arcsec~W). Each of the telescopes
-is equipped with a 499 pixel camera covering a 3.5$^{\circ}$ field of view. The array, completed in
-the spring of 2007, is designed to detect gamma-ray emission from astrophysical objects in the
-energy range from 100 GeV to more than 30 TeV. The energy resolution is about 15\% and the angular
-resolution (68\% containment) is about 0.1$^{\circ}$ per event at 1 TeV. The sensitivity of the
-array allows for detection of a point source with a flux of 1\% of the steady Crab Nebula flux
-above 300 GeV at the $5\sigma$ level in under 30 hours.\footnote{The integral flux sensitivity
-above 300 GeV was improved by about 30\% with the move of one telescope in the summer of 2009. The
-move had no impact on this data set.}
+is equipped with a 499-pixel camera covering a 3.5$^{\circ}$ field of view. The array, completed in
+the fall of 2007, is designed to detect gamma-ray emission from astrophysical objects in the
+energy range from 100 GeV to more than 30 TeV. The energy resolution is $\sim 15$\% and the angular
+resolution (68\% containment) is $\sim 0.1^{\circ}$ per event at 1 TeV. At the time of the Coma
+cluster observations, the sensitivity of the array allowed for detection of a point source with a
+flux of 1\% of the steady Crab Nebula flux above 300 GeV at the confidence level of five standard
+deviations ($5\sigma$) in under 45 hours.\footnote{The integral flux sensitivity above 300 GeV was
+improved by about 30\% with the relocation of one telescope in the summer of 2009.}
 
 The Coma cluster was observed with VERITAS between March and May in 2008 with all four telescopes
-fully operational. The total exposure amounts to 18.6 hours of quality-selected live time, i.e.
-time periods of astronomical darkness, clear sky conditions and without technical problems with the
+fully operational. The total exposure amounts to 18.6 hours of quality-selected live time, i.e.,
+time periods of astronomical darkness with clear sky conditions and no technical problems with the
 array. The center of the cluster was tracked in \emph{wobble} mode, where the expected source
-location is offset from the center of the field of view, to allow for simultaneous background
-estimation \citep{article:Fomin_etal:1994}. All of the observations were made in a small range of
-zenith angles averaging $\sim 21^{\circ}$.
+location is offset from the center of the field of view by 0.5 degrees, to allow for simultaneous
+background estimation \citep{article:Fomin_etal:1994}. All of the observations were made in a small
+range with average zenith angle $\sim 21^{\circ}$.
 
@@
 and selection, all shower images are calibrated and cleaned. Showers are then reconstructed for
-events with at least two contributing telescope images that pass the following quality selection
+events with at least two telescopes contributing images that pass the following quality selection
 criteria: more than four participating pixels in the camera, number of photoelectrons in the image
-is larger than 75, and the distance from the image centroid to the center of the camera is less
+larger than 75, and the distance from the image centroid to the center of the camera less
 than $1.43^{\circ}$. These quality selection criteria impose an energy threshold\footnote{The energy
 threshold is defined as the energy corresponding to the maximum of the product function of the
-observed spectrum with the collection area. It does not vary significantly for the different source
+observed spectrum and the collection area. It does not vary significantly for the different source
 scenarios and assumed spectral indices reported in this work.} of about 220 GeV. In addition,
@@
 
-Gamma-ray like events are separated from the CR background by imposing cuts on scaled parameters
-\citep{article:Aharonian_etal:1997, article:Krawczynski_etal:2006} calculated from a parameterized
-moment analysis of the shower images \citep{inproc:Hillas:1985}. The gamma-hadron separation cuts
-used in this analysis were optimized {\em a priori} for a weak point source (3\% Crab Nebula flux
-level) and a photon index of 2.4 using data taken on the Crab Nebula during the same epoch. Because
-the VHE gamma-ray spectrum for the Coma cluster is expected to be a power-law with a photon index of
-about 2.3 \citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma
-cluster data set. It is noted that slightly varying the spectral index ($\pm$ 0.2) does not
-significantly impact the cuts used for quality selection cuts and gamma-hadron separation in this
-work.
+Gamma-ray-like events are separated from the CR background by imposing selection criteria (cuts) on
+the mean-scaled length and width parameters \citep{article:Aharonian_etal:1997,
+article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images
+\citep{inproc:Hillas:1985}. The gamma-hadron separation cuts used in this analysis were optimized
+{\em a priori} for a weak point source (3\% Crab Nebula flux level) and a differential spectral
+index of 2.4, using data taken on the Crab Nebula during the same epoch. Because the VHE gamma-ray
+spectrum for the Coma cluster is expected to be a power-law function with an index of about 2.3
+\citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma cluster
+data set. It is noted that slightly varying the spectral index
+($\pm$ 0.2) does not significantly impact the cuts used for quality selection and gamma-hadron
+separation in this work.
 
 The Coma cluster is a very rich cluster of galaxies with many plausible sites for gamma-ray
-emission: the core region, the peripheral radio relic, as well as individual powerful cluster
+emission: the core region, the peripheral radio relic, and individual powerful cluster
 member galaxies. VERITAS has a large enough field of view to allow investigation of several of
-these scenarios. In this work the focus has been on the core region and three cluster members. The
+these scenarios. In this work, the focus has been on the core region and three cluster members. The
 core region is treated as either a point
@@
 is evidence of a recent merger event between the two central galaxies NGC 4889 and NGC 4874
-\citep{article:Tribble:1993}. There is also evidence for an excess of non-thermal X-ray emission
-from these galaxies as well as the galaxy NGC 4921 \citep{article:Neumann_etal:2003}. Therefore,
-searches for point-like VHE gamma-ray emission have been conducted at the locations of these
-galaxies. The regions of interest considered in this work are summarized in Table \ref{table:roi}.
-
-The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background
+\citep{article:Tribble:1993}. There is also evidence for an excess of nonthermal X-ray emission
+from these galaxies as well as from the galaxy NGC 4921 \citep{article:Neumann_etal:2003}.
+Therefore, searches for point-like VHE gamma-ray emission have been conducted at the locations of
+these galaxies. The regions of interest considered in this work are summarized in Table
+\ref{table:roi}.
+
+The ring-background model \citep{article:Aharonian_etal:2001} is used to estimate the background
 due to CRs misinterpreted as gamma rays (the cuts described above reject more than 99\% of all
@@
 background from the off-source region scaled by the ratio of the solid angles to produce a final
-excess. The VHE gamma-ray significance is then calculated according to Formula 17 in
+excess or defecit. The VHE gamma-ray significance is then calculated according to Formula 17 in
 \citet{article:LiMa:1983}. Significance skymaps over the VERITAS field of view produced with a
-$0.2^{\circ}$ sampling radius are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio
+$0.2^{\circ}$ integration radius are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio
 contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz
@@
 \subsection{VERITAS Results}
-No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as
+No significant excess of VHE gamma rays from the Coma cluster was detected with VERITAS, as
 illustrated by the $\theta^{2}$ distribution shown in Figure \ref{fig:thetasq}. The $\theta^{2}$
@@
 excess of gamma rays. A 99\% confidence level upper limit is calculated for each region of
-interest using the method described by \citet{article:Rolke_etal:2005} assuming a Gaussian
-background. A lower bound of zero is imposed on the signal rate to handle the negative excesses
-seen for several of the regions of interest. Figure \ref{fig:sigdist} shows the distribution of
-significances over the VERITAS skymap, which is well fit by a Gaussian with a mean close to zero and
-a standard deviation within a few percent of unity.
+interest using the method described by \citet{article:Rolke_etal:2005} assuming a
+Gaussian-distributred background. A lower bound of zero is imposed on the signal rate to handle the
+negative excesses seen for several of the regions of interest. Figure \ref{fig:sigdist} shows the
+distribution of significances over the VERITAS skymap, which is well fit by a Gaussian with a mean
+close to zero and a standard deviation within a few percent of unity.
 
@@
 Table \ref{table:roi}. These upper-limit calculations depend on the gamma-ray spectrum, which in
-this work is assumed to be a power law in energy, $F\propto E^{-\alpha}$, with a spectral index
-$\alpha=2.1, 2.3$, and $2.5$.
+this work is assumed to be a power law in energy, $F\propto E^{-\alpha}$, where the spectral index
+$\alpha$ was allowed to have a value of 2.1, 2.3, or 2.5.
 
@@
 \section{\Fermi-LAT Analysis and Results}
-The Large Area Telescope (LAT) on board the \Fermi Gamma-ray Space Telescope (\Fermi)
-has observed the Coma cluster in all-sky survey mode since its launch in June 2008. The
-\Fermi-LAT is sensitive to gamma rays in the 20 MeV to $\sim$300 GeV energy range and is
-very complimentary to the VERITAS observations. \citet{article:Ackermann_etal:2010} reported on the
-search for gamma-ray emission from thirty-three galaxy clusters in the data from the first 18
-months, including the Coma cluster, for which an upper limit of $4.58\times 10^{-9}$ ph. cm$^{-2}$
-s$^{-1}$ in the 0.2 to 100 GeV energy band was reported. This limit is expected to improve as the
-exposure is increased. In this work an updated analysis which includes additional data taken during
-the period 2010 February 5 to 2011 June 10 is presented as a compliment to the VERITAS results.
-
-The analysis of this work follows the same procedure as described in detail in
-\citet{article:Abdo_etal:2009}. To eliminate albedo gamma rays from the Earth limb, a zenith angle
-cut of 105$^{\circ}$ is applied. The \Fermi Science Tools version v9r23p1 and Instrumental
-Response Functions (IRFs) P6\_V11\_Diffuse were used throughout this work. Only photons above 1 GeV
-are considered, where the constraints on the flux are most meaningful. The \Fermi-LAT collaboration
+The Large Area Telescope (LAT) on board the Fermi Gamma-ray Space Telescope (Fermi) has observed
+the Coma cluster in all-sky survey mode since its launch in June 2008. The Fermi-LAT is sensitive
+to gamma rays in the 20 MeV to $\sim300$ GeV energy range and is very complementary to the VERITAS
+observations. Ackermann et al. (2010) reported on the search for gamma-ray emission from
+thirty-three galaxy clusters in the data from the first 18 months, including the Coma cluster, for
+which an upper limit of $4.58\times10^{-9}$ ph. cm$^{-2}$ s$^{-1}$ in the 0.2 to 100 GeV energy band was reported. This limit is expected to improve as the exposure is increased. In this work an
+updated analysis which includes additional data taken during the period 2010 February 5 to 2011 
+June 10 is presented as a complement to the VERITAS results.
+
+The analysis of this work follows the same procedure as described in detail in Abdo et al (2009).
+The data analysis was performed using the Fermi Science Tools version 9.23.1. To select high
+quality photon events, the \textit{Diffuse} event class data and the corresponding P6\_V11\_Diffuse
+Instrument Response Functions (IRFs) were used throughout this work.
+
+A zenith-angle cut of 105$^\circ$ was applied to eliminate albedo gamma rays from the Earth limb,
+excluding time intervals where any part of the region of interest (ROI) is outside the field of
+view. In addition, time intervals during which the observatory was transiting the Southern Atlantic Anomaly or the rocking angle exceeded 52$^\circ$ were also removed.
+
+The binned likelihood analysis is performed on a map with $0.1^{\circ}$ pixel size in gnomonic (TAN)
+projection, measuring $14^{\circ}$ on a side and centered on $\alpha_{J2000}=194.953$ and
+$\delta_{J2000}=27.9806$, the nominal position of the Coma cluster. Only photons above 1 GeV are
+considered, where the constraints on the flux are most meaningful. The Fermi-LAT collaboration
 estimates the systematic uncertainties on the effective area at 10 GeV to be around
-20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper
-limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both an unresolved,
-point-like or spatially extended emission, are shown in Table \ref{table:fermi}. The gamma-ray
-emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and
-$2.5$.
+20\%\footnote{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}.
+
+The remaining background includes twenty-eight sources listed in the 11 months catalog of Fermi-LAT
+data (Abdo et al. 2010), and the LAT standard Galactic diffuse emission component
+\verb+gll_iem_v02.fit+ along with the corresponding isotropic template
+\verb+isotropic_iem_v02.txt+ that accounts for extragalactic emission and residual instrumental
+background. All of the twenty-eight sources are modeled as point sources with power-law energy
+spectra. Fourteen of them lie outside the ROI and their spatial and spectral parameters were being
+kept fixed at the values given in the catalog. The parameters of the remaining sources, being
+inside the ROI, and the normalization of the diffuse components were left to freely vary. The
+gamma-ray emission from the Coma cluster is assumed to follow a power-law distribution with a
+spectral index $\alpha$, which is allowed to have a value of 2.1, 2.3, or 2.5.
+
+No significant gamma-ray signal was detected. Values of the significance greater than one were only
+obtained for the higher energy bin, where the test statistic (TS) is $\sim2$ for the point source
+model, $\sim4$ for the disk model with r$=0.2^{\circ}$ and $\sim6$ for the disk model with
+r$=0.4^{\circ}$.
+
+Flux upper limits at the 99\% confidence level in the energy range $1-30$ GeV, assuming both an
+unresolved, point-like or spatially extended emission, are shown in Table \ref{table:fermi}.
 
@@
 \section{Gamma Ray Emission from Cosmic Rays}
-We decided to adopt a multi-faceted approach to constrain the CR-to-thermal pressure distribution in
-the Coma cluster using the upper limits derived from VERITAS and \Fermi-LAT data in this work. This
-approach includes (1) a simplified multi-frequency analytical approach that assumes a constant
+We decided to adopt a multifaceted approach to constrain the CR-to-thermal pressure distribution in
+the Coma cluster using the upper limits derived from the VERITAS and \Fermi-LAT data in this work.
+This approach includes (1) a simplified multifrequency analytical model that assumes a constant
 CR-to-thermal energy density and a power-law spectrum in momentum, (2) an analytic model derived
 from cosmological hydrodynamical simulations of the formation of galaxy clusters, and (3) an
-approach that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on
-the expected $\gamma$-ray flux in the hadronic model -- where the radio-emitting electrons are
+model that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on
+the expected gamma-ray flux in the hadronic model -- where the radio-emitting electrons are
 secondaries from CR interactions and which is independent of the magnetic field distribution.  This
 last approach translates into a minimum CR pressure which, if challenged by tight gamma-ray
-limits/detections, enables scrutinizing the hadronic interaction model of the formation of giant
+limits/detections, permits scrutiny of the hadronic interaction model of the formation of giant
 radio halos. Alternatively, realizing a spatial CR distribution that is consistent with the flux
-upper limits and requiring the model to match the observed radio data, enables us to derive a
+upper limits, and requiring the model to match the observed radio data, enables us to derive a
 lower limit on the magnetic field distribution. We stress again that this approach assumes the
@@
 techniques enables us to bracket our lack of understanding about the underlying plasma physics that
-shape the CR distribution and hence reflect the Bayesian priors that are imposed on the modeling
+shapes the CR distribution hence to reflect the Bayesian priors that are imposed on the modeling
 \citep[see][for a discussion]{article:PinzkePfrommerBergstrom}.
@@
 We start by adopting a simplified analytical model that assumes a power-law CR spectrum and a
-constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs} following the approach
+constant relative CR pressure, i.e., we adopt the isobaric model of CRs following the approach
 of \citet{article:PfrommerEnsslin:2004b}. To be independent of additional assumptions and in line
 with earlier work in the literature, we do not impose a low-momentum cutoff, $q$, on the CR
-distribution function, i.e., we adopt $q=0$. Since {\em a priori}, the CR spectral index is
+distribution function, i.e., we adopt $q=0$. Since, {\em a priori}, the CR spectral index is
 unconstrained,\footnote{The hadronic interaction physics guarantees that the CR spectral index
@@
 GeV energies (that dominate the CR pressure, provided $\alpha>2$ and the CR population has a
-non-relativistic low-momentum cutoff, i.e., $q<m_p c$) to energies at 220 GeV, where our quality
+nonrelativistic low-momentum cutoff, i.e., $q<m_{p}c$, where $m_{p}$ is the proton mass) to
+energies at 220 GeV, where our quality
 selection criteria imposed the energy threshold. These gamma-ray energies correspond to 1.6 TeV
-CRs -- an energy ratio of more than 3 orders of magnitudes which explains the sensitivity to small
+CRs -- an energy ratio of more than 3 orders of magnitudes, which explains the sensitivity to small
 changes in $\alpha$. The flux measurements within 0.2$^{\circ}$ are the most constraining due to
-a competition between integrated signal and background for an increasing size of the radius of
-integration. This yields limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1
-and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted
-by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV). Constraints on $X_\CR$
-with \Fermi limits (99\%\ CL) depend only weakly on $\alpha$ since the energy range at GeV
-energies probed by \Fermi are influenced by the pion-decay bump which is characterized by a shape
+a competition between the integrated signal and the background as the integration radius increases.
+This yields limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between
+2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index
+predicted by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV). Constraints on
+$X_\CR$ with \Fermi limits (99\%\ CL) depend only weakly on $\alpha$ because the energy range at GeV
+energies probed by \Fermi is influenced by the pion-decay bump which is characterized by a shape
 parameter that depends inversely on the CR spectral index \citep{article:PfrommerEnsslin:2004b},
@@
 gamma-ray luminosity due to the increasing volume in this model. The best limit of $X_\CR< 0.017$
-is achieved for $\alpha=2.3$ and only slightly worse for $\alpha\simeq 2.1$ yielding $X_\CR<0.025$.
+is achieved for $\alpha=2.3$, while the limit for $\alpha=2.1$ is only slightly worse
+$(X_\CR<0.025)$.
 
@@
 gamma-ray model developed by \citet{article:PinzkePfrommer:2010} to estimate the emission from
-decaying neutral pions which in clusters dominates over the inverse Compton (IC) emission above
-100 MeV. Given a density profile as, e.g., inferred by
+decaying neutral pions which in clusters dominates over the inverse-Compton (IC) emission above
+100 MeV. Given a density profile as, e.g., as inferred by
 cosmological simulations or X-ray observations, the analytic approach models the CR distribution and
@@
 derived from high-resolution simulations of clusters of galaxies that included radiative
-hydrodynamics,
-star formation, supernova feedback, and followed CR physics by tracing the most important injection
-and loss processes self-consistently while accounting for the CR pressure in the equation of motion
+hydrodynamics, star formation and supernova feedback, and it followed the CR physics by tracing the
+most important injection and loss processes self-consistently while accounting for the CR pressure
+in the equation of motion
 \citep{article:PfrommerSpringelEnsslinJubelgas, article:EnsslinPfrommerSpringelJubelgas:2007,
@@
 
-The overall normalization of the CR and gamma-ray distribution scales non-linearly with the
-acceleration efficiency at structure formation shocks. Following recent observations at supernova
+The overall normalization of the CR and gamma-ray distribution scales nonlinearly with the
+acceleration efficiency at structure formation shocks. Following recent observations of supernova
 remnants \citep{article:Helder_etal:2009} as well as theoretical studies
 \citep{article:KangJones:2005}, we adopt an optimistic but nevertheless realistic value of this
-parameter and assume that 50\% of the dissipated energy at strong shocks is injected into CRs while
-this efficiency rapidly decreases for weaker shocks. Since the vast majority of internal formation
+parameter and assume that 50\% of the dissipated energy at strong shocks is injected into CRs, with
+this efficiency decreasing rapidly for weaker shocks. Since the vast majority of internal formation
 shocks (merger and flow shocks) are weak shocks with Mach numbers $M\lesssim3$
-\citep[e.g.,][]{article:Ryu_etal:2003}, they do not significantly contribute to the CR population in
+\citep[e.g.,][]{article:Ryu_etal:2003}, they do not contribute significantly to the CR population in
 clusters. Instead, strong shocks during the formation epoch of clusters and strong accretion shocks
-at the present time (at the boundary of voids and filaments/super-cluster regions) dominate the
+at the present time (at the boundary of voids and filaments/supercluster regions) dominate the
 acceleration of CRs which are adiabatically transported through the cluster. Hence, the
@@
 These cosmological simulations only consider advective transport of CRs by turbulent gas motions
-which lead to centrally enhanced density profiles.  However, other means of CR transport such as
+which lead to centrally-enhanced density profiles. However, other means of CR transport such as
 diffusion and streaming may flatten the CR radial profiles. It has been suggested that advection is
-dominant only during mergers, in which case relaxed clusters could have a reduced gamma-ray
-luminosity by up to a factor of five compared with merging clusters
+dominant only during mergers, in which case relaxed clusters could have a gamma-ray luminosity 
+reduced by up to a factor of five compared with merging clusters
 \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}. Hence, tight upper limits on the gamma-ray
-emission are able to constrain a combination of acceleration physics and transport properties of
-CRs.
+emission can constrain a combination of acceleration physics and transport properties of CRs.
 
@@
 the virial radius (dotted lines). This suggests a spectral index of $\alpha=2.1$ in the energy
-interval of 1--3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV). Additionally
+interval 1-3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV). Also
 shown are integrals of the differential spectrum for finite energy intervals across the angular
 apertures tested in this study (solid lines). These model fluxes (summarized in Table
-\ref{table:constraints_simple}) are compared to \Fermi and VERITAS flux upper limits of the same
+\ref{table:constraints_simple}) are compared to \Fermi and VERITAS flux upper limits for the same
 energy intervals. Constraints on $X_\CR$ with the gamma-ray flux limit of \Fermi in the energy
-interval of 1--3 GeV ($<0.4^\circ$) are most constraining but still above the model predictions that
-assume an optimistically large shock acceleration efficiency and CR transport parameters as laid out
-above. In our further analysis, we use the most constraining \Fermi flux limits in the energy
-interval of 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220
-GeV.
+interval 1-3 GeV ($<0.4^\circ$) are most constraining, but are still above the model predictions
+that assume an optimistically large shock-acceleration efficiency and CR transport parameters as
+laid out above. In our further analysis, we use the most constraining \Fermi flux limits in the
+energy interval 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above
+220 GeV.
 
 Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} =
-\expval{P_{\CR}}/\expval{P_\rmn{th}}$ as a function of radial distance, $R$, from the Coma cluster
+\expval{P_{\CR}}/\expval{P_\rmn{th}}$, as a function of radial distance, $R$, from the Coma cluster
 center and contained within $R$. All radii are shown in units of the virial radius,
 $R_\rmn{vir}=2.2$~Mpc. To compute the CR pressure, we assume a low-momentum cutoff of the CR
-distribution at $q = 0.8\,m_p c$ to reflect the high cooling rates at low CR energies. The relative
+distribution at $q = 0.8\,m_{p}c$, where $m_{p}$ is the proton mass, to reflect the high cooling
+rates at low CR energies. The relative
 CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at
@@
 $X_\CR<0.1$. This difference is explained by the concavity of the simulated spectrum which therefore
-carries more pressure at GeV energies than a pure power-law spectrum of $\alpha=2.3$.
-
-Equivalently, the most constraining \Fermi upper limit in the energy interval of 1-3 GeV
+carries more pressure at GeV energies than a pure power-law spectrum with $\alpha=2.3$.
+
+Equivalently, the most constraining \Fermi upper limit in the energy interval 1-3 GeV
 ($<0.4^\circ$) is a factor of 1.1 larger than our model predictions (assuming $\alpha=2.1$ which is
-very close to the simulated spectral index for the energy range of 1-3 GeV). Scaling our integrated
-relative CR pressure profile yields the constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that
+very close to the simulated spectral index for the energy range 1-3 GeV). Scaling our integrated
+relative CR pressure profile yields a constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that
 translates to a limit within the cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure
-\ref{fig:xcr}). The $X_\CR$-constraint evaluated within the cluster virial radius is comparable to
-the constraint in our simplified model of $X_\CR<0.025$. Naturally, with the \Fermi limits we probe
-the region around GeV-energies that dominate the CR pressure and we do not expect any differences in
-comparison to the simplified power-law model in comparison to the universal CR spectrum with its
+\ref{fig:xcr}). The $X_\CR$ constraint evaluated within the cluster virial radius is comparable to
+the constraint of $X_\CR<0.025$ in our simplified model. Naturally, with the \Fermi limits we probe
+the region around GeV energies that dominate the CR pressure, and we do not expect any differences
+in comparison to the simplified power-law model in comparison to the universal CR spectrum with its
 concave CR spectrum found in the simulations.
@@
 
-For clusters that host radio halos we can derive a minimum gamma-ray flux in the hadronic model of
+For clusters that host radio halos, we can derive a minimum gamma-ray flux in the hadronic model of
 radio halos -- where the radio-emitting electrons are secondaries from CR interactions.  Hadronic
@@
 where $L_{\nu}$ is the observed luminosity of the radio mini-halo, $D_{\rmn{lum}}$ denotes the
-luminosity distance to the respective cluster, $A_\gamma$ and $A_\nu$ are dimensional constants
+luminosity distance to the respective cluster, and $A_\gamma$ and $A_\nu$ are dimensional constants
 that depend on the hadronic physics of the interaction \citep{article:Pfrommer:2008,
@@
 To derive a minimum gamma-ray flux that is comparable to the upper limits, we need to determine the
-radio flux within the corresponding angular regions. To this end, we fit the point-source
-subtracted, azimuthally averaged radio halo profile at 1.38 GHz \citep{article:Deiss_etal:1997}
-with a $\beta$-model,
+radio flux within the corresponding angular regions. To this end, we fit the
+point-source-subtracted, azimuthally-averaged radio-halo profile at 1.38 GHz
+\citep{article:Deiss_etal:1997} with a $\beta$-model,
 \begin{equation}
@@
 The results for the minimum gamma-ray flux $F_{\gamma,\rmn{min}}(>220~\rmn{GeV})$ and the minimum
-relative CR pressure, $X_{\CR,\,\rmn{min}} = X_\CR F_{\gamma,\rmn{min}}/F_{\gamma,\rmn{iso}}$ are
+relative CR pressure $X_{\CR,\,\rmn{min}} = X_\CR F_{\gamma,\rmn{min}}/F_{\gamma,\rmn{iso}}$ are
 shown in Table \ref{table:constraints}, where $F_{\gamma,\rmn{iso}}$ is the gamma-ray flux in the
-simplified model introduced in \S\ref{sec:simple}. \C{Even in the most constraining cases and
+simplified model introduced in \S\ref{sec:simple}. \C{Even in the most constraining cases, and
 assuming $\alpha\leq 2.3$, these are a factor of $\sim 60$ below the VERITAS upper limits (for
 $\alpha=2.1$, $<0.2^{\circ}$) and a factor of $\sim 20$ below the \Fermi upper limits (for
-$\alpha=2.3$, $<0.4^{\circ}$)}. Note that these minimum gamma-ray fluxes are sensitive to a
-running of the CR proton spectral index with energy as a result of, e.g., momentum-dependent
+$\alpha=2.3$, $<0.4^{\circ}$)}. Note that these minimum gamma-ray fluxes are sensitive to the
+variation of the CR proton spectral index with energy as a result of, e.g., momentum-dependent
 diffusion: assuming a plausible value for the central magnetic field of Coma of 5~$\mu$G
-\citep{article:Bonafede_etal:2010}, the radio halo emission at GHz frequencies is dominated by the
-electrons with an energy $E_\rmn{e} \sim 2.5$ GeV (which corresponds to proton energies $E_\rmn{p}
+\citep{article:Bonafede_etal:2010}, the radio-halo emission at GHz frequencies is dominated by
+electrons with energy $E_\rmn{e} \sim 2.5$ GeV (which corresponds to proton energies $E_\rmn{p}
 \sim 40$ GeV). Gamma rays with an energy of $200$ GeV are produced by CR protons with an energy of
@@
 \label{sec:B}
-In the previous section we have obtained an absolute lower limit on the gamma-ray emission in
+In the previous section, we have obtained an absolute lower limit on the gamma-ray emission in
 the hadronic model by assuming high magnetic fields, $B\gg B_\rmn{CMB}$. We can turn the
@@
 measurements by other methods, e.g., Faraday rotation measure (RM),\footnote{Generally,
-Faraday RM analysis of the magnetic field strength by, e.g., background sources through
-clusters are degenerate with the magnetic coherence scale and may be biased by the unknown
+Faraday RM analyses of the magnetic field strength by, e.g., background sources observed through
+clusters, are degenerate with the magnetic coherence scale and may be biased by the unknown
 correlation between magnetic and density fluctuations.} the hadronic model of radio halos would
@@
 \end{equation}
-as suggested by Faraday RM studies and numerical magneto-hydrodynamical (MHD) simulations
+as suggested by Faraday RM studies and numerical magnetohydrodynamical (MHD) simulations
 \citep[][and references therein]{article:Bonafede_etal:2010, article:Bonafede_etal:2011}. Here
@@
 In fact, the magnetic field in the Coma cluster is among the best constrained, because its proximity
-permits RM observations of seven radio-sources located at projected distances of 50 to 1500 kpc from
+permits RM observations of seven radio sources located at projected distances of 50 to 1500 kpc from
 the cluster center. The best-fit model yields $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and $\alpha_{B} =
-0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim for constraining the central field
-strength, $B_{0}$, and permit the magnetic decline, $\alpha_{B}$, to vary within a reasonable range
-of $\Delta\alpha_{B}=0.2$ as suggested by the Faraday RM studies.  We proceed as follows:
+0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim toconstrain the central field
+strength, $B_{0}$, and we permit the magnetic decline, $\alpha_{B}$, to vary within a reasonable
+range of $\Delta\alpha_{B}=0.2$ as suggested by the Faraday RM studies. We proceed as follows:
 
@@
 Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we determine
-the profile of the relative CR pressure, $X_{\CR}(r)$, by matching the hadronically produced
-synchrotron emission to the observed radio halo emission over the entire extent. To 
-this end, we de-project the fit to the surface brightness profile of Eq. \ref{beta} (using an Abel
+the profile of the relative CR pressure, $X_{\CR}(r)$, by matching the hadronically-produced
+synchrotron emission to the observed radio-halo emission over the entire extent. To 
+this end, we deproject the fit to the surface-brightness profile of Eq. \ref{beta} (using an Abel
 integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio
@@
 ($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$
-(where $X_B$ denotes the magnetic-to-thermal energy density) has to increase by a factor of about
-100 toward the radio halo periphery to account for the observed extent. If we were to adopt a
+(where $X_B$ denotes the magnetic-to-thermal energy density ratio) has to increase by a factor of
+about 100 toward the radio-halo periphery to account for the observed extent. If we were to adopt a
 steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative CR
@@
 \item
-Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface brightness
+Given this realization for $X_{\CR}$, we compute the pion-decay gamma-ray surface-brightness
 profile, integrate the flux within a radius of $(0.13, 0.2, 0.4)$ degree, and scale the CR profile
@@
 
-\item Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
-  $B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as
+\item Inverse-Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
+  $B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a nonlinearity on the synchrotron emissivity as
   a function of magnetic field strength (see Eq. (\ref{eq:Lnu})). Hence we have to iterate through
-  the previous steps until our solution for the minimum magnetic field $B_{0}$ is converged.
+  the previous steps until our solution for the minimum magnetic field $B_{0}$ converges.
 \end{enumerate}
 
-Table \ref{table:Bmin} shows the resulting lower limit of the central magnetic field that range from
+Table \ref{table:Bmin} shows the resulting lower limit of the central magnetic field ranging from
 $B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from $B_{0} = 1.1$ to $4.6\,\mu$G in the
@@
 magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the
-observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits
+observed radio-emission profiles, which would yield a higher gamma-ray flux so that the upper limits
 are more constraining. This implies tighter lower limits for $B_{0}$. (3) Interestingly, in all
 cases, the 0.4$^{\circ}$-aperture limits are the most constraining. For a given magnetic
-realization a substantially increasing relative CR pressure profile is needed to match the
+realization, a substantially increasing relative CR pressure profile is needed to match the
 observed radio profiles, and therefore that CR realization produces a larger flux within 
@@
 relative CR pressure (at the largest emission radius at 1~Mpc) such that the model reproduces the
-observed radio surface brightness profile.\footnote{Note that in this section, we determine the
+observed radio surface-brightness profile.\footnote{Note that in this section, we determine the
 radial behavior of $X_\CR$ by adopting a specific model for the magnetic field and requiring the
-modeled synchrotron surface brightness profile to match the observed data of the Coma radio
-halo. This is in contrast to the simplified analytical CR model where $X_\CR=\rmn{const.}$
+modeled synchrotron surface-brightness profile to match the observed data of the Coma radio
+halo. This is in contrast to the simplified analytical CR model where $X_\CR$ is constant
 (\S~\ref{sec:simple}) and to the simulation-based model where $X_\CR(r)$ is derived from
@@
 limits since they are derived from flux upper limits. For the \Fermi upper limits, they range
-from 0.1 to 0.4; hence the $X_{\CR}$-profiles always obey the energy condition, i.e., $P_{\CR} <
-P_{\mathrm{th}}$ over the entire range of the radio halo emission ($< 1$ Mpc).\footnote{See Figure 3
+from 0.1 to 0.4; hence the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} <
+P_{\mathrm{th}}$, over the entire range of the radio-halo emission ($< 1$ Mpc).\footnote{See Figure 3
 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
-conditions and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parameterization as adopted in
-this study. We caution, however, that the minimum-energy condition is violated at the outer radio
-halo boundary for the range of minimum magnetic-field values inferred by this study.} The
+conditions, and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parameterization as adopted in
+this study. We caution, however, that the minimum-energy condition is violated at the outer
+radio-halo boundary for the range of minimum magnetic-field values inferred by this study.} The
 corresponding values for $X_\CR$ in the cluster center are smaller than 0.01 for the entire
 parameter space probed in this study. We conclude that the hadronic model is not challenged by
-current Faraday RM data and a perfectly viable possibility in explaining the Coma radio halo
+current Faraday RM data and is a perfectly viable possibility in explaining the Coma radio-halo
 emission.
@@
 DM. While the nature of DM remains unknown, the most compelling theoretical candidate is a
-WIMP. The self-annihilation of WIMPs can either produce monoenergetic gamma ray lines or a
+WIMP. The self-annihilation of WIMPs can produce either monoenergetic gamma-ray lines or a
 continuum of secondary gamma rays that deviates significantly from the power-law spectra observed
@@
 
-The expected gamma-ray flux due to self-annihilations of WIMPs is given by
+The expected gamma-ray flux due to self-annihilation of WIMPs is given by
 \begin{equation}
@@
 differential gamma-ray yield per annihilation\footnote{In this work, we have calculated the
-differential gamma-ray yield per annihilation using the Pythia Monte-Carlo simulator.},
+differential gamma-ray yield per annihilation using the Pythia Monte Carlo simulator.},
 $\Delta\Omega$ is the observed solid angle, and $J$ is the astrophysical factor - a dimensionless
@@
 \end{equation}
-where $\lambda$ represents the line-of-sight. In this work, we have modeled the Coma DM
-distribution with a Navarro, Frenk and White (NFW) profile,
-\citet{article:NavarroFrenkWhite:1997},
+where $\lambda$ represents the line of sight. In this work, we have modeled the Coma DM
+distribution with a Navarro, Frenk and White (NFW) profile \citet{article:NavarroFrenkWhite:1997},
 \begin{equation}
@@
 \end{equation}
-where $r_{s}$ is the scale radius and $\rho_{s}$ isthe scale density. Using weak weak-lensing
+where $r_{s}$ is the scale radius and $\rho_{s}$ is the scale density. Using weak-lensing
 measurements of the virial mass in the Coma cluster \citep{article:Gavazzi_etal:2009} and the DM
-halo mass-concentration relation derived from N-body simulation of structure formation 
+halo mass-concentration relation derived from $N$-body simulation of structure formation 
 \citep{article:Bullock_etal:2001}, we find for these parameters $r_{s}=0.654$ Mpc and
@@
 astrophysical factors calculated for the different VERITAS apertures considered in this work.
-It also lists the astrophysical factor calculated for the background region, which is used
-to estimate the gamma-ray contamination from DM annihilation in the background region.
+Table \ref{table:astrofactor} also lists the astrophysical factor calculated for the background
+region, which is used to estimate the gamma-ray contamination from DM annihilation in the
+background region.
 
@@
 \ref{table:DMlimits}. We note that these limits are derived with conservative estimates of the
-astrophysical factor J. They do not include any boost to the annihilation rate possibly due to DM
+astrophysical factor $J$. They do not include any boost to the annihilation rate possibly due to DM
 substructures populating the Coma halo, which could scale down the present limits by a factor
-O(100) in the most optimistic cases.
+$O(100)$ in the most optimistic cases.
 
@@
 radius, the astrophysical factors no longer compensate for the increased number of background
-events, and the signal-to-noise deteriorates.
+events, and the signal-to-noise ratio deteriorates.
 
@@
 galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008. No
-significant excess of gamma-rays above an energy threshold of about 220 GeV was detected. The
+significant excess of gamma rays was detected above an energy threshold of $\sim 220$ GeV. The
 \emph{Fermi}-LAT has observed the Coma cluster in all-sky survey mode since its launch in June
@@
 was detected. We have used the VERITAS and \emph{Fermi}-LAT data to calculate flux upper limits at
-the 99\% confidence level for the cluster core, considered as both a point-like and spatially
-extended source, and three member galaxies. The flux upper limits obtained were then used to
-constrain properties of the cluster.
+the 99\% confidence level for the cluster core (considered as both a point-like source and a
+spatially-extended emission region) and for three member galaxies. The flux upper limits obtained
+were then used to constrain properties of the cluster.
 
 We have employed various approaches to constrain the CR population and magnetic field distribution
-that are complementary in their assumptions and hence well suited in assessing underlying Bayesian
-priors in the models. (1) We used a simplified ``isobaric CR model'' that is characterized by a
-constant CR-to-thermal pressure fraction and has a power-law momentum spectrum. While this model
-is physically not justified {\em a priori}, it is simple and widely used in the literature and
+that are complementary in their assumptions and hence well suited to assessment of the underlying
+Bayesian priors in the models. (1) We used a simplified ``isobaric CR model'' that is characterized
+by a constant CR-to-thermal pressure fraction and has a power-law momentum spectrum. While this
+model is not physically justified {\em a priori}, it is simple and widely used in the literature and
 captures some aspects of more elaborate models such as (2) the simulation-based analytical approach 
-of \citet{article:PinzkePfrommer:2010}. This is a ``first principle approach'' that predicts the CR
-distribution spectrally and spatially for a given set of assumptions (namely the physics that was
-simulated). It is powerful since it only requires the density profile as input due to the
-approximate universality of the CR distribution (when neglecting CR diffusion and streaming which
-appears necessary to explain the radio halo bimodality). (3) We finally used a pragmatic
-approach which models the CR and magnetic distribution in order to reproduce the observed emission
-profile of the Coma radio halo. While this approach is also physically not justified, it is
-powerful as it shows what the ``correct'' model has to achieve and can point into the direction of
-the relevant physics.
-
-Within this pragmatic approach we employ two different methods. First, adopting a high magnetic
+of \citet{article:PinzkePfrommer:2010}. The latter is a ``first-principle approach'' that predicts
+the CR distribution spectrally and spatially for a given set of assumptions (namely the physics
+that was simulated). It is powerful since it only requires the density profile as input due to the
+approximate universality of the CR distribution ({\bf when neglecting CR diffusion and streaming which
+appears necessary to explain the radio-halo bimodality}). (3) We finally used a pragmatic
+approach which models the CR and magnetic distributions in order to reproduce the observed emission
+profile of the Coma radio halo. While this approach is also not physically justified, it is
+powerful because it shows what the ``correct'' model has to achieve and can point in the
+direction of the relevant physics.
+
+Within this pragmatic approach, we employ two different methods. Firstly, adopting a high magnetic
 field everywhere in the cluster ($B\gg B_\rmn{CMB}$) yields the minimum gamma-ray flux in the
 hadronic model of radio halos which we find to be a factor of 20 (60) below the most constraining
-flux upper limits of \Fermi (VERITAS). Second, by matching the radio emission profile (i.e.,
+flux upper limits of \Fermi (VERITAS). Secondly, by matching the radio-emission profile (i.e.,
 fixing the radial CR profile for a given magnetic field model) and by requiring the pion-decay
 gamma-ray flux to match the flux upper limits (i.e., fixing the normalization of the CR
-distribution) we obtain lower limits on the magnetic field distribution under consideration. Our
-limits of the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS  flux
+distribution), we obtain lower limits on the magnetic field distribution under consideration. Our
+limits for the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS  flux
 limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for \Fermi flux limits). Since all these lower
@@
 Applying our simplified ``isobaric CR model'' to the most constraining VERITAS limits, we can
-constrain the CR-to-thermal pressure, $X_\CR$, to be below 0.048 and 0.43 (for a CR or gamma-ray
-spectral index, $\alpha$, varying between 2.1 and 2.5). We obtain a constraint of $X_\CR<0.1$ for
-$\alpha=2.3$, the spectral index predicted by simulations at energies around 220 GeV.  This limit is
-more constraining by a factor of 1.6 in comparison to the simulation-based model which gives
+constrain the CR-to-thermal pressure ratio, $X_\CR$, to be below 0.048 and 0.43 (for a CR or
+gamma-ray spectral index, $\alpha$, varying between 2.1 and 2.5). We obtain a constraint of
+$X_\CR<0.1$ for $\alpha=2.3$, the spectral index predicted by simulations at energies around 220
+GeV. This limit is
+more constraining by a factor of 1.6 than that of the simulation-based model which gives
 $X_\CR<0.16$. This difference is due to the concave form of the simulated spectrum which provides
@@
 The \Fermi flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying
-between 2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$
-which is very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain an
-almost coincident constraint with our simulation-based model within the virial radius of
-$X_\CR<0.024$. That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$
+between 2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$,
+which is very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain 
+a constraint which is almost identical to that from our simulation-based model within the virial
+radius of $X_\CR<0.024$. That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$
 corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc. These are encouraging
 results in that we constrain the CR pressure (of a phase that is fully mixed with the ICM) to be at
-most a small fraction of the overall pressure, $<0.025$. As a result, hydrostatic cluster masses
-and the total Comptonization parameter due to the Sunyaev-Zel'dovich effect attain at most a very
+most a small fraction ($<0.025$) of the overall pressure. As a result, hydrostatic cluster masses
+and the total Comptonization parameter due to the Sunyaev-Zel'dovich effect suffer at most a very
 small bias due to CRs.
 
-We have also used the flux upper limits obtained with VERITAS to constrain the thermally averaged
-product of the total self-annihilation cross section and the relative velocity of the dark matter
+We have also used the flux upper limits obtained with VERITAS to constrain the thermally-averaged
+product of the total self-annihilation cross section and the relative velocity of DM
 particles. Modeling the Coma cluster DM halo with a NFW profile we derived limits on
 $\expval{\sigma v}$ to be on the order of $10^{-20}$ to $10^{-21}$ cm$^{-3}$ s$^{-1}$ depending on
-the chosen aperture. These limits are based on conservative estimates of the astrophysical factor
+the chosen aperture. These limits are based on conservative estimates of the astrophysical factor,
 where a possible boost to the annihilation rate due to DM substructures in the cluster halo has
@@
 source. Three central galaxies are also considered in point-source searches. The choice is based on
-evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the
+evidence of an excess of nonthermal X-ray emission \citep{article:Neumann_etal:2003} at the
 location of these galaxies.}
@@
 \colhead{Source} & 
-\colhead{RoI\tablenotemark{a} [deg]} & 
+\colhead{R\tablenotemark{a} [deg]} & 
 \colhead{$N_{S}$\tablenotemark{b}} & 
@@
 Point source & 0.30 & 0 & 1.3 & 1.73 & 4.87 & 0.627 \\
-Disk, $r=0.2^{\circ}$ & 0.65 & 0.22 & 2.0 & 2.03 & 0.691 & 0.783 \\
-Disk, $r=0.4^{\circ}$ & 0.77 & 0.18 & 2.3 & 2.39 & 0.757 & 0.847 \\
+Disk, $R=0.2^{\circ}$ & 0.65 & 0.22 & 2.0 & 2.03 & 0.691 & 0.783 \\
+Disk, $R=0.4^{\circ}$ & 0.77 & 0.18 & 2.3 & 2.39 & 0.757 & 0.847 \\
 \cutinhead{Spectral index $\alpha=2.5$ (fixed)}
 Point source & 0.33 & 0 & 1.42 & 1.81 & 0.526 & 0.635 \\
-Disk, $r=0.2^{\circ}$ & 0.66 & 0.35 & 2.1 & 2.12 & 0.748 & 0.785 \\
-Disk, $r=0.4^{\circ}$ & 0.80 & 0.36 & 2.4 & 2.50 & 0.833 & 0.849 \\
+Disk, $R=0.2^{\circ}$ & 0.66 & 0.35 & 2.1 & 2.12 & 0.748 & 0.785 \\
+Disk, $R=0.4^{\circ}$ & 0.80 & 0.36 & 2.4 & 2.50 & 0.833 & 0.849 \\
 \enddata
@@
 \tablehead{
-\colhead{RoI\tablenotemark{a} [deg]} 
+\colhead{R\tablenotemark{a} [deg]} 
 & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
@@
 \tablehead{
-\colhead{RoI\tablenotemark{a} [deg]} 
+\colhead{R\tablenotemark{a} [deg]} 
 & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{b}} 
@@
 $B(r) = B_{0}\,[n_\rmn{e}(r) / n_{\rmn{e}}(0)]^{\alpha_B}$. In all cases we used the most constraining
-$\rmn{RoI}=0.4^\circ$, see \S~\ref{sec:B} for details.}  
+$\rmn{R}=0.4^\circ$, see \S~\ref{sec:B} for details.}  
 \label{table:Bmin}
@@
 \tablehead{
-\colhead{RoI [deg]} &
+\colhead{R [deg]} &
 \colhead{$\expval{J}_{\rmn{signal}}$ [GeV$^{2}$ cm$^{-5}$ sr]} & 
@@
 \tablehead{
-\colhead{Channel} & RoI [deg] & $m_{\chi}$ [GeV] & $\expval{\sigma v}$ [cm$^{3}$ s$^{-1}$]
+\colhead{Channel} & R [deg] & $m_{\chi}$ [GeV] & $\expval{\sigma v}$ [cm$^{3}$ s$^{-1}$]
 }

### 2012-02-03 ms.tex
More of Pat's comments added in

@@
 $\alpha=2.3$, $<0.4^{\circ}$)}. Note that these minimum gamma-ray fluxes are sensitive to the
-variation of the CR proton spectral index with energy as a result of, e.g., momentum-dependent
-diffusion: assuming a plausible value for the central magnetic field of Coma of 5~$\mu$G
-\citep{article:Bonafede_etal:2010}, the radio-halo emission at GHz frequencies is dominated by
-electrons with energy $E_\rmn{e} \sim 2.5$ GeV (which corresponds to proton energies $E_\rmn{p}
-\sim 40$ GeV). Gamma rays with an energy of $200$ GeV are produced by CR protons with an energy of
-$E_\rmn{p} \sim 1.6$ TeV -- a factor of 50 higher than those probed by radio halo observations. A
-steepening of the CR proton spectral index of 0.2 between 40 GeV and 1.6 TeV would imply a decrease
-in the minimum gamma-ray flux by a factor of two.
+variation of the CR proton spectral index with energy as a result of, for example,
+momentum-dependent diffusion. Assuming a plausible value for the central magnetic field of Coma of
+5~$\mu$G \citep{article:Bonafede_etal:2010}, the radio-halo emission at GHz frequencies is
+dominated by electrons with energy $E_\rmn{e} \sim 2.5$ GeV (which corresponds to proton energies
+$E_\rmn{p} \sim 40$ GeV). Gamma rays with an energy of $200$ GeV are produced by CR protons with an
+energy of $E_\rmn{p} \sim 1.6$ TeV -- a factor of 50 higher than those probed by radio halo
+observations. A steepening of the CR proton spectral index of 0.2 between 40 GeV and 1.6 TeV would
+imply a decrease in the minimum gamma-ray flux by a factor of two.
 

### 2012-02-03 ms.tex
More of Pat's comments added in

@@
 \citep{article:Strigari_etal:2007, article:Acciari_etal:2010, article:Aliu_etal:2009} or the
-Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
+Galactic Center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
 article:Aharonian_etal:2009b, article:Abramowski_etal:2011}.

### 2012-02-03 ms.tex
More edits

@@
 article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images
-\citep{inproc:Hillas:1985}. The gamma-hadron separation cuts used in this analysis were optimized
-{\em a priori} for a weak point source (3\% Crab Nebula flux level) and a differential spectral
-index of 2.4, using data taken on the Crab Nebula during the same epoch. Because the VHE gamma-ray
-spectrum for the Coma cluster is expected to be a power-law function with an index of about 2.3
-\citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma cluster
-data set. It is noted that slightly varying the spectral index
-($\pm$ 0.2) does not significantly impact the cuts used for quality selection and gamma-hadron
-separation in this work.
+\citep{inproc:Hillas:1985}. In this analysis, events with a mean-scaled length in the range 
+0.05-1.19 and a mean-scaled width in the range 0.05-1.08 are selected as gamma-ray-like events.
+These ranges for the gamma-hadron separation cuts were optimized {\em a priori} for a weak point
+source (3\% Crab Nebula flux level) and a differential spectral index of 2.4, using data taken on
+the Crab Nebula during the same epoch. Because the VHE gamma-ray spectrum for the Coma cluster is
+expected to be a power-law function with an index of about 2.3 \citep{article:PinzkePfrommer:2010},
+these cuts are suitable for the analysis of the Coma cluster data set. It is noted that slightly
+varying the spectral index ($\pm$ 0.2) does not significantly impact the cuts used for quality
+selection and gamma-hadron separation in this work.
 
@@
 \end{center}
-\caption{\emph{Left}: Smoothed significance map of the Coma cluster calculated from the observed
-excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view. The excess counts
-were derived using a ring background model \citep{article:Aharonian_etal:2001}. White contours show
-the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey
-\citep{article:BrielHenryBohringer:1992}. \emph{Right}: Same as above but with overlaid contours
-from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where strong point sources
-have been subtracted. Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan)
-considered for the extended source analyses presented here.}
+\caption{\emph{Left}: Smoothed significance map of the Coma cluster calculated from the excess VHE
+gamma-ray events observed with VERITAS over a $4.5^{\circ}\times 4.5^{\circ}$ field of view.
+The color scale indicates significance in units of standard deviations. The excess counts were
+derived using a ring background model \citep{article:Aharonian_etal:2001}.
+White contours show the X-ray counts per second () in the 0.1 to 2.4 keV energy band from the ROSAT
+all-sky survey \citep{article:BrielHenryBohringer:1992}. \emph{Right}: Same as above but with
+overlaid contours (20-180 mJ in 20 mJ steps) from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where
+strong point sources have been subtracted. Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii
+(dashed cyan) considered for the extended source analyses presented here.}
 \label{fig:skymaps}
@@
 \end{center}
-\caption{Distribution of significance for Figure \ref{fig:skymaps} and a sampling radius of
-$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean close to zero and almost unit
-standard deviation.}
+\caption{Distribution of significances for Figure \ref{fig:skymaps} and a sampling radius of
+$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean of -0.11 (close to zero) and
+almost unit standard deviation.}
 \label{fig:sigdist}

### 2012-02-03 ms.tex
Updated figure 3 caption

@@
 \caption{Distribution of significances for Figure \ref{fig:skymaps} and a sampling radius of
-$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean of -0.11 (close to zero) and
-almost unit standard deviation.}
+$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean $\mu=-0.11\pm 0.0059$ and
+standard deviation $\sigma=1.01\pm 0.003$.}
 \label{fig:sigdist}
@@
 \end{center}
-\caption{Integral flux upper limits for Coma (this work, Tables~\ref{table:results} and
-\ref{table:fermi}) for different integration radii (arrows with different grey scales), assuming
+\caption{Integral gamma-ray flux upper limits for \Fermi and VERITAS observations of the Coma
+cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii
+(arrows with different grey scales), assuming
 that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is adopted. These are

### 2012-02-03 ms.tex
Updated figure 4 and 5 captions

@@
 cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii
-(arrows with different grey scales), assuming
-that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is adopted. These are
-compared to integrated spectra of the same energy interval and aperture, assuming the universal
-gamma-ray spectrum of clusters \citep[lines with different grey
+(arrows with different grey scales), assuming that $\alpha=2.3$ except in the 1--3 GeV energy
+interval where $\alpha=2.1$ is adopted. $R_{\rmn{vir}}$ is the virial radius of the Coma cluster.
+These are compared to integrated spectra of the same energy interval and aperture, assuming the
+universal gamma-ray spectrum of clusters \citep[lines with different grey
 scales,][]{article:PinzkePfrommer:2010}.To guide the eye, we show the underlying universal integral
@@
 \end{center}
-\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a
-function of radial distance from the center of the Coma. Model predictions are shown by dashed
-lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining
-VERITAS upper limits within 0.2$^\circ$ (solid) and \Fermi upper limits within 0.4$^\circ$
-(dashed). We compare differential $X_\CR$-profiles (grey) to integrated profiles
+\caption{CR-to-thermal pressure ratio, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as
+a function of radial distance from the center of the Coma cluster. Model predictions are shown by
+dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most
+constraining VERITAS upper limits within 0.2$^\circ$ (solid) and \Fermi upper limits within
+0.4$^\circ$ (dashed). We compare differential $X_\CR$-profiles (grey) to integrated profiles
 $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (black) which we use to

### 2012-02-03 ms.tex
Updated figure 4 and 5 captions

@@
 \end{center}
-\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ as a function of the DM
-particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits ($0.2^{\circ}$
-aperture) presented in this work.}
+\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ from VERITAS observations
+of the Coma cluster as a function of the DM particle mass $m_{\chi}$ derived from the VERITAS
+gamma-ray flux upper limits ($0.2^{\circ}$ aperture) presented in this work.}
 \label{fig:dm}

### 2012-02-03 ms.tex
More edits

@@
 points with error bars represent the ON-source data sample and the filled area is the background estimation in the OFF-source regions. Each bin represents an annulus around the Coma cluster core
-position. The data were derived from the ring background model using a $0.2^{\circ}$ sampling
+position. The data were derived from the ring background model using a $0.2^{\circ}$ integration
 radius.}
@@
 \end{center}
-\caption{Distribution of significances for Figure \ref{fig:skymaps} and a sampling radius of
+\caption{Distribution of significances for Figure \ref{fig:skymaps} and an integration radius of
 $0.2^{\circ}$. The line is a Gaussian fit to the data, with mean $\mu=-0.11\pm 0.0059$ and
@@
 \colhead{Source} &
-\colhead{RA} &
-\colhead{Dec}
+\colhead{RA (J2000)} &
+\colhead{Dec (J2000)}
 }
@@
 \tablewidth{0pc}
-\tablecaption{VERITAS flux upper limits for different regions of interest in the Coma cluster of
-galaxies and surroundings}
+\tablecaption{VERITAS VHE gamma-ray flux upper limits for different regions of interest in the
+Coma cluster of galaxies and surroundings}
 \rotate
@@
 \tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
-gamma-ray PSF.}
-\tablenotetext{b}{Event counts in the source region.}
+gamma-ray point-spread function.}
+\tablenotetext{b}{Net event counts in the source region.}
 \tablenotetext{c}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
@@
 calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with
-corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
+corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis, for different
+values of the spectral index, $\alpha$.}
 \label{table:results}
@@
 \tablewidth{0pc}
-\tablecaption{\Fermi-LAT upper limits for the Coma cluster core}
+\tablecaption{\Fermi-LAT HE gamma-ray flux upper limits for the Coma cluster core}
 \tablehead{
@@
 \enddata
-\tablenotetext{a}{99\% confidence level upper limit in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$.}
+\tablenotetext{a}{99\% confidence level flux upper limit in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$.}
 \label{table:fermi}
@@
 %
-
-\del{
-\begin{deluxetable}{lcccccc}
-\tablecolumns{7}
-\tablewidth{0pc}
-\tablecaption{\Fermi-LAT upper limits for the Coma cluster core}
-\tablehead{
-\colhead{Spatial model} & 
-\multicolumn{3}{c}{S[$\sigma$]\tablenotemark{a}} & 
-\multicolumn{3}{c}{Flux U.L.\tablenotemark{b}} \\
-\colhead{} & 
-\colhead{1-3 GeV} & 
-\colhead{3-10 GeV} & 
-\colhead{10-30 GeV} & 
-\colhead{1-3 GeV} & 
-\colhead{3-10 GeV} & 
-\colhead{10-30 GeV} \\
-\hline
-\multicolumn{7}{c}{Spectral index $\alpha=2.1$ (fixed)}
-}
-\startdata
-Point source & 0.30 & 0 & 1.3 & 1.73 & 4.87 & 0.627 \\
-Disk, $R=0.2^{\circ}$ & 0.65 & 0.22 & 2.0 & 2.03 & 0.691 & 0.783 \\
-Disk, $R=0.4^{\circ}$ & 0.77 & 0.18 & 2.3 & 2.39 & 0.757 & 0.847 \\
-\cutinhead{Spectral index $\alpha=2.5$ (fixed)}
-Point source & 0.33 & 0 & 1.42 & 1.81 & 0.526 & 0.635 \\
-Disk, $R=0.2^{\circ}$ & 0.66 & 0.35 & 2.1 & 2.12 & 0.748 & 0.785 \\
-Disk, $R=0.4^{\circ}$ & 0.80 & 0.36 & 2.4 & 2.50 & 0.833 & 0.849 \\
-\enddata
-\tablenotetext{a}{Statistical significance.}
-\tablenotetext{b}{95\% confidence level upper limit in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$.}
-\label{table:fermi}
-\end{deluxetable}
-}
 
@@
 \tablewidth{0pc}
-\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified, isobaric
-analytic model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV
-and $>220$~GeV (simulation-based model).}
+\tablecaption{Constraints on the CR-to-thermal pressure ratio in the Coma cluster core (simplified,
+isobaric analytic model) for different spatial extensions and predicted fluxes for the energy bands
+1-3 GeV and $>220$~GeV (simulation-based model).}
 \rotate
@@
 gamma-ray PSF.}
-\tablenotetext{b}{Constraint on the relative CR pressure,
+\tablenotetext{b}{Constraint on the CR-to-thermal pressure ratio,
 $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the
@@
 \tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background
-region (ring method) and is used to estimate the level of gamma-ray contamination from DM. $\alpha$
-is the size ratio of the ON vs OFF source regions.}
+region (ring method) and is used to estimate the level of gamma-ray contamination from DM
+annihilation. $\alpha$ is the size ratio of the ON vs OFF source regions.}
 \label{table:astrofactor}
@@
 \tablewidth{0pc}
-\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$}
+\tablecaption{Limits on the DM annihilation cross section times velocity $\expval{\sigma v}$
+from VERITAS observations of the Coma cluster.}
 \tablehead{

### 2012-02-03 ms.tex
More edits

@@
 The color scale indicates significance in units of standard deviations. The excess counts were
-derived using a ring background model \citep{article:Aharonian_etal:2001}.
+derived using a ring-background model \citep{article:Aharonian_etal:2001}.
 White contours show the X-ray counts per second () in the 0.1 to 2.4 keV energy band from the ROSAT
 all-sky survey \citep{article:BrielHenryBohringer:1992}. \emph{Right}: Same as above but with
-overlaid contours (20-180 mJ in 20 mJ steps) from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where
-strong point sources have been subtracted. Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii
-(dashed cyan) considered for the extended source analyses presented here.}
+overlaid contours (20-180 mJ in 20 mJ steps) from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010}, where
+strong point sources have been subtracted. Also shown are the $0.2^{\circ}$ and $0.4^{\circ}$ radii
+(dashed cyan) considered for the extended-source analyses presented here.}
 \label{fig:skymaps}
@@
 \caption{$\theta^{2}$ distribution from VERITAS observations of the Coma cluster of galaxies. The
-points with error bars represent the ON-source data sample and the filled area is the background estimation in the OFF-source regions. Each bin represents an annulus around the Coma cluster core
-position. The data were derived from the ring background model using a $0.2^{\circ}$ integration
-radius.}
+points with error bars represent the ON-source data sample and the filled area is the background
+estimation based on the OFF-source regions. Each bin represents an annulus around the Coma cluster
+core position and the annuli are all of equal area. The data were derived from the ring-background
+model using a $0.2^{\circ}$ integration radius.}
 \label{fig:thetasq}
@@
 \caption{Distribution of significances for Figure \ref{fig:skymaps} and an integration radius of
-$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean $\mu=-0.11\pm 0.0059$ and
-standard deviation $\sigma=1.01\pm 0.003$.}
+$0.2^{\circ}$. The curve is a Gaussian fit to the data, with mean $\mu=-0.11\pm 0.0059$ and
+standard deviation $\sigma=1.01\pm 0.003$, which is consistent with the abscence of gamma-ray
+sources in the field of view.}
 \label{fig:sigdist}
@@
 weighted with the smallest energy in each interval. Note that the \Fermi limit for the energy
-interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.}
+interval of 1--3 GeV within the aperture of 0.4$^\circ$ is the most constraining.}
 \label{fig:spectrum}
@@
 \caption{CR-to-thermal pressure ratio, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as
-a function of radial distance from the center of the Coma cluster. Model predictions are shown by
-dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most
+a function of radial distance from the center of the Coma cluster. The model predictions, shown by
+dashed curves \citep{article:PinzkePfrommer:2010}, have been scaled to match the most
 constraining VERITAS upper limits within 0.2$^\circ$ (solid) and \Fermi upper limits within
-0.4$^\circ$ (dashed). We compare differential $X_\CR$-profiles (grey) to integrated profiles
+0.4$^\circ$ (dashed). We compare differential $X_\CR$ profiles (grey) to integrated profiles
 $X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (black) which we use to
@@
 source. Three central galaxies are also considered in point-source searches. The choice is based on
-evidence of an excess of nonthermal X-ray emission \citep{article:Neumann_etal:2003} at the
+evidence for an excess of nonthermal X-ray emission \citep{article:Neumann_etal:2003} at the
 location of these galaxies.}
@@
 isobaric analytic model) for different spatial extensions and predicted fluxes for the energy bands
-1-3 GeV and $>220$~GeV (simulation-based model).}
+1-3 GeV and $>220$~GeV (simulation-based model)}
 \rotate
@@
 \startdata
-\multicolumn{6}{c}{VERITAS constraints:}\\
+\multicolumn{6}{c}{VERITAS constraints}\\
 \hline
@@
 0.4 & 6.7 & 15 & 62 & 4.4 & 10.8\\
-\cutinhead{\Fermi constraints:}
+\cutinhead{\Fermi constraints}
 0 & 5.2 & 3.5 & 4.7 & 1.4 & 1.96\\
@@
 \tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
-gamma-ray PSF.}
+gamma-ray point-spread function.}
 \tablenotetext{b}{Constraint on the CR-to-thermal pressure ratio,
-$X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the
+$X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant throughout the
 cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
@@
 \citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$
-s$^{-1}$ for VERITAS and between $E=1-3~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
+s$^{-1}$ for VERITAS and for $E=1-3~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
 Fermi.} 
-\tablenotetext{d}{Ratio of flux upper limits ($F_{\rmn{UL}}$) to the integrated gamma-ray flux
-from the simulation-based analytic model: in VERITAS band above $E=220~\rmn{GeV}$ an $\alpha=2.3$
-is assumed for the U.L., and in \Fermi band between $E=1-3$ GeV an $\alpha=2.1$ is assumed for the
-U.L.}
+\tablenotetext{d}{Ratio of flux upper limit ($F_{\rmn{UL}}$) to integrated gamma-ray flux
+from the simulation-based analytic model, with the U.L. based on spectral index $\alpha=2.3$ in
+the VERITAS band ($E>220~\rmn{GeV}$) and $\alpha=2.1$ in the \Fermi band ($E=1-3~\rmn{GeV}$).}
 \label{table:constraints_simple}
@@
 \tablecaption{Minimum gamma-ray fluxes in the hadronic model of radio halos, where the
-radio-emitting electrons are secondaries from CR interactions and corresponding minimum relative
+radio-emitting electrons are secondaries from CR interactions, and corresponding minimum relative
 CR pressures for Coma}
@@
 \startdata
-\multicolumn{7}{c}{VERITAS energy range, $E>220$~GeV:}\\
+\multicolumn{7}{c}{VERITAS energy range, $E>220$~GeV}\\
 \hline
@@
 0.4  & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
-\cutinhead{\Fermi energy range, 1--3~GeV:}
+\cutinhead{\Fermi energy range, 1--3~GeV}
 0.13 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
@@
 \tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
-gamma-ray PSF.}
-\tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in \S~\ref{sec:Fmin}. 
-Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph.
-m$^{-2}$ s$^{-1}$ (\Fermi energy range).}
+gamma-ray point-spread function.}
+\tablenotetext{b}{Minimum gamma-ray flux derived from the hadronic model described in
+\S~\ref{sec:Fmin}. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ for the VERITAS energy
+range and $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ for \Fermi energy range.}
 \tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the hadronic model
@@
 corresponding relative CR pressure (at the largest emission radius of 1 Mpc) such that the model
-reproduces the observed radio surface brightness profile.}
+reproduces the observed radio surface-brightness profile}
 \tablehead{ &
 \multicolumn{6}{c}{Minimum magnetic field, $B_{0,\rmn{min}}~[\mu\rmn{G}]$\tablenotemark{a}:}\\
-& \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{\Fermi constraints:} \\
+& \multicolumn{3}{c}{VERITAS constraints} & \multicolumn{3}{c}{\Fermi constraints} \\
 \colhead{$\alpha_{B}$} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} &
@@
 the central field strength, $B_{0}$, which are defined by
-$B(r) = B_{0}\,[n_\rmn{e}(r) / n_{\rmn{e}}(0)]^{\alpha_B}$. In all cases we used the most constraining
-$\rmn{R}=0.4^\circ$, see \S~\ref{sec:B} for details.}  
+$B(r) = B_{0}\,[n_\rmn{e}(r) / n_{\rmn{e}}(0)]^{\alpha_B}$. In all cases, we used the most constraining
+$\rmn{R}=0.4^\circ$; see \S~\ref{sec:B} for details.}  
 \label{table:Bmin}
@@
 region (ring method) and is used to estimate the level of gamma-ray contamination from DM
-annihilation. $\alpha$ is the size ratio of the ON vs OFF source regions.}
+annihilation. $\alpha$ is the size ratio of the ON and OFF source regions.}
 \label{table:astrofactor}
@@
 \tablewidth{0pc}
-\tablecaption{Limits on the DM annihilation cross section times velocity $\expval{\sigma v}$
+\tablecaption{Upper limits on the DM annihilation cross section times velocity $\expval{\sigma v}$
 from VERITAS observations of the Coma cluster.}
@@
 \enddata
-\tablecomments{Upper limits are for different integration regions and DM particle mass $m_{\chi}$
-derived from the VERITAS gamma-ray flux upper limits presented in this work.}
+\tablecomments{Upper limits are shown for different integration regions and DM particle mass
+$m_{\chi}$, and are derived from the VERITAS gamma-ray flux upper limits presented in this work.}
 \label{table:DMlimits}

### 2012-02-03 ms.tex
VERITAS comments addressed

@@
 \begin{abstract}
-\linenumbers
-Observations of radio halos and relics in galaxy clusters indicate efficient electron acceleration
-processes; the same processes are even more efficient for protons. Since protons have a cooling
-time which exceeds the Hubble time in clusters, they can accumulate suggesting that clusters may
-also be sources of very high-energy (VHE; $E>100$ GeV) gamma-ray emission resulting from the
-interactions of highly relativistic cosmic-ray (CR) hadrons with the intracluster gas. We report
-here on VHE gamma-ray observations of the Coma galaxy cluster with the VERITAS array of imaging
-Cherenkov telescopes, with complementing \Fermi Gamma-ray Space Telescope observations at GeV
-energies. No significant gamma-ray emission from the Coma cluster was detected. Integral flux upper
-limits at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$ ph.
-m$^{-2}$ s$^{-1}$ (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$ (\Fermi, 1-3
-GeV), respectively. For VERITAS (\Fermi), the limits are a factor of 60 (20) higher than
-model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons of the Coma
-radio halo are all secondaries from cosmic-ray interactions. We use the gamma-ray flux upper
+  \linenumbers Observations of radio halos and relics in galaxy clusters indicate efficient electron
+  acceleration processes; the same processes are even more efficient for protons. Since protons have
+  a cooling time which exceeds the Hubble time in clusters, they can accumulate suggesting that
+  clusters may also be sources of very high-energy (VHE; $E>100$ GeV) gamma-ray emission resulting
+  from the interactions of highly relativistic cosmic-ray (CR) hadrons with the intracluster gas. We
+  report here on VHE gamma-ray observations of the Coma galaxy cluster with the VERITAS array of
+  imaging Cherenkov telescopes, with complementing \Fermi Gamma-ray Space Telescope observations at
+  GeV energies. No significant gamma-ray emission from the Coma cluster was detected. Integral flux
+  upper limits at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$
+  ph.  m$^{-2}$ s$^{-1}$ (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$
+  (\Fermi, 1-3 GeV), respectively. For VERITAS (\Fermi), the limits are a factor of 60 (20) higher
+  than model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons of the
+  Coma radio halo are all secondaries from cosmic-ray interactions. We use the gamma-ray flux upper
   limits to constrain the populations of CRs and magnetic fields in Coma. Using an analytical
-approach motivated by cosmological cluster simulations, the CR-to-thermal pressure is constrained
-to be $< 16\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the virial
-radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic CR
-interactions, the observations imply a lower limit on the central magnetic field in Coma of
+  approach motivated by cosmological cluster simulations, the CR-to-thermal pressure ratio is
+  constrained to be $< 16\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the
+  virial radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic
+  CR interactions, the observations imply a lower limit on the central magnetic field in Coma of
   $1$--$3\mu$G, depending on how the magnetic field declines with radius and on the gamma-ray
@@
   been used to place constraints on the thermally averaged product of the total self-annihilation
-cross section and the relative velocity of the DM particles, $\expval{\sigma v}$. This is found
-to be about $10^{-20} - 10^{-21}$ cm$^{3}$ s$^{-1}$ for a DM particle mass $m_{\chi} = 300$
+  cross section and the relative velocity of the DM particles, $\expval{\sigma v}$. This is found to
+  be about $10^{-20} - 10^{-21}$ cm$^{3}$ s$^{-1}$ for a DM particle mass $m_{\chi} = 300$
   GeV/c$^{2}$.
@@
 The decay of neutral pions produces gamma rays and the decay of charged pions produces muons, which
-then decay to electrons and positrons. Due to the low density of the ICM
-($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large size and the volume-filling magnetic fields in
-the ICM, CR hadrons will be confined in the cluster on timescales comparable to, or longer than,
-the Hubble time \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} and they can
-therefore accumulate. For a given CR distribution function, the hadronically induced gamma-ray
-flux is directly proportional to the CR-to-thermal pressure fraction,
-$X_\CR=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$ \citep[see, e.g.,][]{article:Ensslin_etal:2007},
-where the brackets indicates volume averages. A very modest $X_{\CR}$ of a few percent implies an
+then decay to electrons and positrons. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim
+10^{-3}$ cm$^{-3}$), the large size and the volume-filling magnetic fields in the ICM, CR hadrons
+will be confined in the cluster on timescales comparable to, or longer than, the Hubble time
+\citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} and they can therefore
+accumulate. For a given CR distribution function, the hadronically induced gamma-ray flux is
+directly proportional to the CR-to-thermal pressure fraction, $X_\CR=\expval{P_{\CR}}/
+\expval{P_{\mathrm{th}}}$ \citep[see, e.g.,][]{article:EnsslinPfrommerSpringelJubelgas:2007}, where
+the brackets indicates volume averages. A very modest $X_{\CR}$ of a few percent implies an
 observable flux of gamma rays \citep[e.g.,][]{article:PfrommerEnsslin:2004b}.
@@
 force and the gravitational force, are biased low by the presence of any substantial nonthermal
-pressure component, including a CR pressure contribution. Similarly, a substantial relative CR
+pressure component, including a CR pressure contribution. Similarly, a substantial CR
 pressure can bias the temperature decrement of the cosmic microwave background (CMB) due to the
@@
 the mean-scaled length and width parameters \citep{article:Aharonian_etal:1997,
-article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images
+article:Krawczynski_etal:2006} calculated from a parametrized moment analysis of the shower images
 \citep{inproc:Hillas:1985}. In this analysis, events with a mean-scaled length in the range 
@@
 background from the off-source region scaled by the ratio of the solid angles to produce a final
-excess or defecit. The VHE gamma-ray significance is then calculated according to Formula 17 in
+excess or deficit. The VHE gamma-ray significance is then calculated according to Formula 17 in
 \citet{article:LiMa:1983}. Significance skymaps over the VERITAS field of view produced with a
@@
 interest using the method described by \citet{article:Rolke_etal:2005} assuming a
-Gaussian-distributred background. A lower bound of zero is imposed on the signal rate to handle the
+Gaussian-distributed background. A lower bound of zero is imposed on the signal rate to handle the
 negative excesses seen for several of the regions of interest. Figure \ref{fig:sigdist} shows the
@@
 the Coma cluster using the upper limits derived from the VERITAS and \Fermi-LAT data in this work.
-This approach includes (1) a simplified multifrequency analytical model that assumes a constant
+This approach includes (1) a simplified multi-frequency analytical model that assumes a constant
 CR-to-thermal energy density and a power-law spectrum in momentum, (2) an analytic model derived
@@
 We start by adopting a simplified analytical model that assumes a power-law CR spectrum and a
-constant relative CR pressure, i.e., we adopt the isobaric model of CRs following the approach
-of \citet{article:PfrommerEnsslin:2004b}. To be independent of additional assumptions and in line
-with earlier work in the literature, we do not impose a low-momentum cutoff, $q$, on the CR
-distribution function, i.e., we adopt $q=0$. Since, {\em a priori}, the CR spectral index is
+constant CR-to-thermal pressure ratio, i.e., we adopt the isobaric model of CRs following
+the approach of \citet{article:PfrommerEnsslin:2004b}. To be independent of additional assumptions
+and in line with earlier work in the literature, we do not impose a low-momentum cutoff, $q$, on the
+CR distribution function, i.e., we adopt $q=0$. Since, {\em a priori}, the CR spectral index is
 unconstrained,\footnote{The hadronic interaction physics guarantees that the CR spectral index
-coincides with that of the resulting pion-decay gamma-ray emission
-\citep[see discussion in][]{article:PfrommerEnsslin:2004b}.} we vary it in the range
-$2.1<\alpha<2.5$, which is compatible with the radio spectral index of the giant radio halo of the
-Coma cluster after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to
-the Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
+  coincides with that of the resulting pion-decay gamma-ray emission \citep[see discussion
+  in][]{article:PfrommerEnsslin:2004b}.} we vary it in the range $2.1<\alpha<2.5$, which is
+compatible with the radio spectral index of the giant radio halo of the Coma cluster after
+accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the
+Sunyaev-Zel'dovich effect \citep{article:Ensslin:2002,
   article:PfrommerEnsslin:2004b}.\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
@@
 
-Table \ref{table:constraints_simple} shows the resulting constraints on the relative CR pressure,
-$X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$, averaged within the virial radius,
+Table \ref{table:constraints_simple} shows the resulting constraints on the CR-to-thermal
+pressure ratio, $X_{\CR} = \expval{P_{\CR}}/\expval{P_\rmn{th}}$, averaged within the virial radius,
 $R_\rmn{vir}=2.2$~Mpc, that we define as the radius of a sphere enclosing a mean density that is 200
 times the critical density of the Universe. Constraints on $X_\CR$ with VERITAS flux upper limits
-(99\% CL) strongly depend on $\alpha$.This is due to the comparably large energy range from
-GeV energies (that dominate the CR pressure, provided $\alpha>2$ and the CR population has a
-nonrelativistic low-momentum cutoff, i.e., $q<m_{p}c$, where $m_{p}$ is the proton mass) to
-energies at 220 GeV, where our quality
-selection criteria imposed the energy threshold. These gamma-ray energies correspond to 1.6 TeV
-CRs -- an energy ratio of more than 3 orders of magnitudes, which explains the sensitivity to small
-changes in $\alpha$. The flux measurements within 0.2$^{\circ}$ are the most constraining due to
-a competition between the integrated signal and the background as the integration radius increases.
-This yields limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between
-2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index
-predicted by the simulations of \citet{article:PinzkePfrommer:2010} around 220 GeV). Constraints on
-$X_\CR$ with \Fermi limits (99\%\ CL) depend only weakly on $\alpha$ because the energy range at GeV
-energies probed by \Fermi is influenced by the pion-decay bump which is characterized by a shape
-parameter that depends inversely on the CR spectral index \citep{article:PfrommerEnsslin:2004b},
-partly absorbing the pressure ratios of different energy ranges. $X_\CR$-constraints with \Fermi
-limits are most constraining for an aperture of 0.4$^{\circ}$; despite the slightly weaker flux
-upper limits in comparison to the smaller radii of integration, we expect a considerably larger
-gamma-ray luminosity due to the increasing volume in this model. The best limit of $X_\CR< 0.017$
-is achieved for $\alpha=2.3$, while the limit for $\alpha=2.1$ is only slightly worse
-$(X_\CR<0.025)$.
+(99\% CL) strongly depend on $\alpha$.This is due to the comparably large energy range from GeV
+energies (that dominate the CR pressure, provided $\alpha>2$ and the CR population has a
+nonrelativistic low-momentum cutoff, i.e., $q<m_{p}c$, where $m_{p}$ is the proton mass) to energies
+at 220 GeV, where our quality selection criteria imposed the energy threshold. These gamma-ray
+energies correspond to 1.6 TeV CRs -- an energy ratio of more than 3 orders of magnitudes, which
+explains the sensitivity to small changes in $\alpha$. The flux measurements within 0.2$^{\circ}$
+are the most constraining due to a competition between the integrated signal and the background as
+the integration radius increases.  This yields limits on $X_\CR$ between 0.048 and 0.43 (for
+$\alpha$ varying between 2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to
+the spectral index predicted by the simulations of \citet{article:PinzkePfrommer:2010} around 220
+GeV). Constraints on $X_\CR$ with \Fermi limits (99\%\ CL) depend only weakly on $\alpha$ because
+the energy range at GeV energies probed by \Fermi is influenced by the pion-decay bump which is
+characterized by a shape parameter that depends inversely on the CR spectral index
+\citep{article:PfrommerEnsslin:2004b}, partly absorbing the pressure ratios of different energy
+ranges. $X_\CR$-constraints with \Fermi limits are most constraining for an aperture of
+0.4$^{\circ}$; despite the slightly weaker flux upper limits in comparison to the smaller radii of
+integration, we expect a considerably larger gamma-ray luminosity due to the increasing volume in
+this model. The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$, while the limit for
+$\alpha=2.1$ is only slightly worse $(X_\CR<0.025)$.
 
@@
 
-Figure \ref{fig:xcr} shows the relative CR pressure, $X_{\CR} =
+Figure \ref{fig:xcr} shows the CR-to-thermal pressure ratio, $X_{\CR} =
 \expval{P_{\CR}}/\expval{P_\rmn{th}}$, as a function of radial distance, $R$, from the Coma cluster
@@
 distribution at $q = 0.8\,m_{p}c$, where $m_{p}$ is the proton mass, to reflect the high cooling
-rates at low CR energies. The relative
-CR pressure rises toward the outer regions on account of the higher efficiency of CR acceleration at
-the peripheral accretion shocks compared to the weak central flow shocks. Adiabatic compression of a
-mixture of CRs and thermal gas disfavors the CR pressure relative to the thermal pressure on
-account of the softer equation of state of CRs. The weak increase of $X_{\CR}$ toward the core is
-due to the comparably fast thermal cooling of gas.
+rates at low CR energies. The CR-to-thermal pressure ratio rises toward the outer regions
+on account of the higher efficiency of CR acceleration at the peripheral accretion shocks compared
+to the weak central flow shocks. Adiabatic compression of a mixture of CRs and thermal gas disfavors
+the CR pressure relative to the thermal pressure on account of the softer equation of state of
+CRs. The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of
+gas.
 
@@
 the simulated one at energies $E_\gamma=200$ GeV). To first order, we can scale the averaged
-relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated
-limit of the relative CR pressure of $X_{\CR}<0.112$ within 0.2$^{\circ}$ that translates to a limit
-within the cluster virial radius of $X_\CR<0.162$ (solid lines of Figure \ref{fig:xcr}). This limit
-is less constraining by 50\% in comparison to the simplified analytical model, which gives
-$X_\CR<0.1$. This difference is explained by the concavity of the simulated spectrum which therefore
-carries more pressure at GeV energies than a pure power-law spectrum with $\alpha=2.3$.
-
-Equivalently, the most constraining \Fermi upper limit in the energy interval 1-3 GeV
-($<0.4^\circ$) is a factor of 1.1 larger than our model predictions (assuming $\alpha=2.1$ which is
-very close to the simulated spectral index for the energy range 1-3 GeV). Scaling our integrated
-relative CR pressure profile yields a constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that
-translates to a limit within the cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure
-\ref{fig:xcr}). The $X_\CR$ constraint evaluated within the cluster virial radius is comparable to
-the constraint of $X_\CR<0.025$ in our simplified model. Naturally, with the \Fermi limits we probe
-the region around GeV energies that dominate the CR pressure, and we do not expect any differences
-in comparison to the simplified power-law model in comparison to the universal CR spectrum with its
-concave CR spectrum found in the simulations.
+CR-to-thermal pressure ratio of our model by that factor, keep the spatial behavior and obtain an
+integrated limit of the CR-to-thermal pressure ratio of $X_{\CR}<0.112$ within 0.2$^{\circ}$ that
+translates to a limit within the cluster virial radius of $X_\CR<0.162$ (solid lines of Figure
+\ref{fig:xcr}). This limit is less constraining by 50\% in comparison to the simplified analytical
+model, which gives $X_\CR<0.1$. This difference is explained by the concavity of the simulated
+spectrum which therefore carries more pressure at GeV energies than a pure power-law spectrum with
+$\alpha=2.3$.
+
+Equivalently, the most constraining \Fermi upper limit in the energy interval 1-3 GeV ($<0.4^\circ$)
+is a factor of 1.1 larger than our model predictions (assuming $\alpha=2.1$ which is very close to
+the simulated spectral index for the energy range 1-3 GeV). Scaling our integrated CR-to-thermal
+pressure profile yields a constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a
+limit within the cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}). The
+$X_\CR$ constraint evaluated within the cluster virial radius is comparable to the constraint of
+$X_\CR<0.025$ in our simplified model. Naturally, with the \Fermi limits we probe the region around
+GeV energies that dominate the CR pressure, and we do not expect any differences in comparison to
+the simplified power-law model in comparison to the universal CR spectrum with its concave CR
+spectrum found in the simulations.
 
@@
 The results for the minimum gamma-ray flux $F_{\gamma,\rmn{min}}(>220~\rmn{GeV})$ and the minimum
-relative CR pressure $X_{\CR,\,\rmn{min}} = X_\CR F_{\gamma,\rmn{min}}/F_{\gamma,\rmn{iso}}$ are
-shown in Table \ref{table:constraints}, where $F_{\gamma,\rmn{iso}}$ is the gamma-ray flux in the
-simplified model introduced in \S\ref{sec:simple}. \C{Even in the most constraining cases, and
+CR-to-thermal pressure ratio $X_{\CR,\,\rmn{min}} = X_\CR F_{\gamma,\rmn{min}}/F_{\gamma,\rmn{iso}}$
+are shown in Table \ref{table:constraints}, where $F_{\gamma,\rmn{iso}}$ is the gamma-ray flux in
+the simplified model introduced in \S\ref{sec:simple}. \C{Even in the most constraining cases, and
   assuming $\alpha\leq 2.3$, these are a factor of $\sim 60$ below the VERITAS upper limits (for
@@
 momentum-dependent diffusion. Assuming a plausible value for the central magnetic field of Coma of
-5~$\mu$G \citep{article:Bonafede_etal:2010}, the radio-halo emission at GHz frequencies is
-dominated by electrons with energy $E_\rmn{e} \sim 2.5$ GeV (which corresponds to proton energies
-$E_\rmn{p} \sim 40$ GeV). Gamma rays with an energy of $200$ GeV are produced by CR protons with an
-energy of $E_\rmn{p} \sim 1.6$ TeV -- a factor of 50 higher than those probed by radio halo
-observations. A steepening of the CR proton spectral index of 0.2 between 40 GeV and 1.6 TeV would
-imply a decrease in the minimum gamma-ray flux by a factor of two.
+5~$\mu$G \citep{article:Bonafede_etal:2010}, the radio-halo emission at GHz frequencies is dominated
+by electrons with energy $E_\rmn{e} \sim 2.5$ GeV (which corresponds to proton energies $E_\rmn{p}
+\sim 40$ GeV). Gamma rays with an energy of $200$ GeV are produced by CR protons with an energy of
+$E_\rmn{p} \sim 1.6$ TeV -- a factor of 50 higher than those probed by radio halo observations. A
+steepening of the CR proton spectral index of 0.2 between 40 GeV and 1.6 TeV would imply a decrease
+in the minimum gamma-ray flux by a factor of two.
 
@@
 the cluster center. The best-fit model yields $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G and $\alpha_{B} =
-0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim toconstrain the central field
+0.5^{+0.2}_{-0.1}$ \citep{article:Bonafede_etal:2010}. We aim to constrain the central field
 strength, $B_{0}$, and we permit the magnetic decline, $\alpha_{B}$, to vary within a reasonable
@@
 Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we determine
-the profile of the relative CR pressure, $X_{\CR}(r)$, by matching the hadronically-produced
+the profile of the CR-to-thermal pressure ratio, $X_{\CR}(r)$, by matching the hadronically-produced
 synchrotron emission to the observed radio-halo emission over the entire extent. To 
@@
 where $\mathcal{B}$ denotes the beta function. It is generically true for weak magnetic fields
-($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$
-(where $X_B$ denotes the magnetic-to-thermal energy density ratio) has to increase by a factor of
-about 100 toward the radio-halo periphery to account for the observed extent. If we were to adopt a
-steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative CR
-pressure would have to rise accordingly by a factor of 100.
+($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$ (where
+$X_B$ denotes the magnetic-to-thermal energy density ratio) has to increase by a factor of about 100
+toward the radio-halo periphery to account for the observed extent. If we were to adopt a steeper
+magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the CR-to-thermal
+pressure ratio would have to rise accordingly by a factor of 100.
 
@@
 $B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from $B_{0} = 1.1$ to $4.6\,\mu$G in the
-case of \Fermi.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the
-Coma cluster to a relative magnetic energy density of $X_B=0.005$.} Since these lower limits on
+case of \Fermi.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the Coma
+  cluster to a magnetic-to-thermal energy density ratio of $X_B=0.005$.} Since these lower limits on
 $B_{0}$ are below the values favored by Faraday RM for the entire parameter space spanned by
@@
 cases, the 0.4$^{\circ}$-aperture limits are the most constraining. For a given magnetic
-realization, a substantially increasing relative CR pressure profile is needed to match the
+realization, a substantially increasing CR-to-thermal pressure profile is needed to match the
 observed radio profiles, and therefore that CR realization produces a larger flux within 
@@
 As a final word, in Table~\ref{table:Bmin} we additionally show the corresponding values for the
-relative CR pressure (at the largest emission radius at 1~Mpc) such that the model reproduces the
-observed radio surface-brightness profile.\footnote{Note that in this section, we determine the
-radial behavior of $X_\CR$ by adopting a specific model for the magnetic field and requiring the
-modeled synchrotron surface-brightness profile to match the observed data of the Coma radio
-halo. This is in contrast to the simplified analytical CR model where $X_\CR$ is constant
-(\S~\ref{sec:simple}) and to the simulation-based model where $X_\CR(r)$ is derived from
+CR-to-thermal pressure ratio (at the largest emission radius at 1~Mpc) such that the model
+reproduces the observed radio surface-brightness profile.\footnote{Note that in this section, we
+  determine the radial behavior of $X_\CR$ by adopting a specific model for the magnetic field and
+  requiring the modeled synchrotron surface-brightness profile to match the observed data of the
+  Coma radio halo. This is in contrast to the simplified analytical CR model where $X_\CR$ is
+  constant (\S~\ref{sec:simple}) and to the simulation-based model where $X_\CR(r)$ is derived from
   cosmological cluster simulations (\S~\ref{sec:simulation}).} They should be interpreted as upper
-limits since they are derived from flux upper limits. For the \Fermi upper limits, they range
-from 0.1 to 0.4; hence the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} <
-P_{\mathrm{th}}$, over the entire range of the radio-halo emission ($< 1$ Mpc).\footnote{See Figure 3
-in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
-conditions, and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parameterization as adopted in
-this study. We caution, however, that the minimum-energy condition is violated at the outer
+limits since they are derived from flux upper limits. For the \Fermi upper limits, they range from
+0.1 to 0.4; hence the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} <
+P_{\mathrm{th}}$, over the entire range of the radio-halo emission ($< 1$ Mpc).\footnote{See Figure
+  3 in \citet{article:PfrommerEnsslin:2004a} for the entire parameter range assuming minimum energy
+  conditions, and \citet{article:PfrommerEnsslin:2004b}, Figure 7 for a parametrization as adopted
+  in this study. We caution, however, that the minimum-energy condition is violated at the outer
   radio-halo boundary for the range of minimum magnetic-field values inferred by this study.} The
@@
 where $\lambda$ represents the line of sight. In this work, we have modeled the Coma DM
-distribution with a Navarro, Frenk and White (NFW) profile \citet{article:NavarroFrenkWhite:1997},
+distribution with a Navarro, Frenk and White (NFW) profile \citep{article:NavarroFrenkWhite:1997},
 \begin{equation}
@@
 \citep{article:Bullock_etal:2001}, we find for these parameters $r_{s}=0.654$ Mpc and
-$\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
-astrophysical factors calculated for the different VERITAS apertures considered in this work.
-Table \ref{table:astrofactor} also lists the astrophysical factor calculated for the background
-region, which is used to estimate the gamma-ray contamination from DM annihilation in the
-background region.
+$\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. According to the latest high-resolution DM-only
+simulations of nine rich galaxy clusters, the inner regions of the smooth density profiles are quite
+well approximated by the NFW formula \citep{article:Gao_etal:2012}. However, gravitational
+interactions of DM with baryons may modify these predictions. This could give rise to either an
+increasing inner density slope due to adiabatic contraction of the DM component in response to
+cooling baryons in the central regions or a decreasing density slope due to violent baryonic
+feedback processes pushing gas out of the center by, e.g., energy injection through AGNs. However,
+on scales $r>0.2\,R_{200}$ (which are of relevance for the present work), different assumptions
+about the inner slope of the smooth DM density profile only translate to small uncertainties in the
+resulting DM annihilation flux which are small in comparison to expected boost due to substructures
+\citep[see Fig.~2 of][]{article:PinzkePfrommerBergstrom}. Table \ref{table:astrofactor} lists the
+astrophysical factors calculated for the different VERITAS apertures considered in this work.  Table
+\ref{table:astrofactor} also lists the astrophysical factor calculated for the background region,
+which is used to estimate the gamma-ray contamination from DM annihilation in the background region.
 
@@
 of \citet{article:PinzkePfrommer:2010}. The latter is a ``first-principle approach'' that predicts
-the CR distribution spectrally and spatially for a given set of assumptions (namely the physics
-that was simulated). It is powerful since it only requires the density profile as input due to the
-approximate universality of the CR distribution ({\bf when neglecting CR diffusion and streaming which
-appears necessary to explain the radio-halo bimodality}). (3) We finally used a pragmatic
-approach which models the CR and magnetic distributions in order to reproduce the observed emission
-profile of the Coma radio halo. While this approach is also not physically justified, it is
-powerful because it shows what the ``correct'' model has to achieve and can point in the
-direction of the relevant physics.
+the CR distribution spectrally and spatially for a given set of assumptions (namely the physics that
+was simulated). It is powerful since it only requires the density profile as input due to the
+approximate universality of the CR distribution (when neglecting CR diffusion and streaming). Note,
+however, that inclusion of these CR transport processes may be necessary to explain the radio-halo
+bimodality. (3) We finally used a pragmatic approach which models the CR and magnetic distributions
+in order to reproduce the observed emission profile of the Coma radio halo. While this approach is
+also not physically justified, it is powerful because it shows what the ``correct'' model has to
+achieve and can point in the direction of the relevant physics.
 
@@
 $0.2^{\circ}$. The curve is a Gaussian fit to the data, with mean $\mu=-0.11\pm 0.0059$ and
-standard deviation $\sigma=1.01\pm 0.003$, which is consistent with the abscence of gamma-ray
+standard deviation $\sigma=1.01\pm 0.003$, which is consistent with the absence of gamma-ray
 sources in the field of view.}
@@
 \caption{Integral gamma-ray flux upper limits for \Fermi and VERITAS observations of the Coma
-cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii
-(arrows with different grey scales), assuming that $\alpha=2.3$ except in the 1--3 GeV energy
-interval where $\alpha=2.1$ is adopted. $R_{\rmn{vir}}$ is the virial radius of the Coma cluster.
-These are compared to integrated spectra of the same energy interval and aperture, assuming the
-universal gamma-ray spectrum of clusters \citep[lines with different grey
-scales,][]{article:PinzkePfrommer:2010}.To guide the eye, we show the underlying universal integral
-energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic
-interactions of CRs and ICM protons (dotted). For visualization purposes all photon fluxes are
-weighted with the smallest energy in each interval. Note that the \Fermi limit for the energy
-interval of 1--3 GeV within the aperture of 0.4$^\circ$ is the most constraining.}
+  cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration
+  radii (arrows with different grey scales), assuming that $\alpha=2.3$ except in the 1--3 GeV
+  energy interval where $\alpha=2.1$ is adopted. $R_{\rmn{vir}}$ is the virial radius of the Coma
+  cluster.  These are compared to integrated spectra of the same energy interval and aperture,
+  assuming the universal gamma-ray spectrum of clusters \citep[lines with different grey
+  scales,][]{article:PinzkePfrommer:2010}. To guide the eye, we show the underlying universal
+  integral energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting
+  from hadronic interactions of CRs and ICM protons (CR-$\pi^0$, dotted). For visualization purposes
+  all photon fluxes are weighted with the smallest energy in each interval. Note that the \Fermi
+  limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is the most
+  constraining.}
 \label{fig:spectrum}
@@
 \colhead{R\tablenotemark{a} [deg]} 
-& \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
+& \multicolumn{3}{c}{analytic model: $X_{\CR}~[\%]$\tablenotemark{b} }
 & \colhead{$F_{\gamma,\rmn{sim}}(E)$\tablenotemark{c}}
@@
 \tablecaption{Minimum gamma-ray fluxes in the hadronic model of radio halos, where the
-radio-emitting electrons are secondaries from CR interactions, and corresponding minimum relative
-CR pressures for Coma}
+radio-emitting electrons are secondaries from CR interactions, and corresponding minimum 
+CR-to-thermal pressure ratios for Coma}
 \rotate
@@
 range and $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ for \Fermi energy range.}
-\tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the hadronic model
+\tablenotetext{c}{Minimum CR-to-thermal pressure ratio, $X_{\CR,\,\rmn{min}}$, in the hadronic model
 described in \S~\ref{sec:Fmin}. For simplicity, we duplicate $X_{\CR,\,\rmn{min}}$ for the VERITAS
@@
 \tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo and the
-corresponding relative CR pressure (at the largest emission radius of 1 Mpc) such that the model
+corresponding CR-to-thermal pressure ratio (at the largest emission radius of 1 Mpc) such that the model
 reproduces the observed radio surface-brightness profile}

### 2012-02-27 ms.tex
Martin's edits before submission

@@
 
-\linenumbers
+%\linenumbers
 
@@
 \author{
-T. Arlen\altaffilmark{1},
-M. Beilicke\altaffilmark{2},
-W. Benbow\altaffilmark{3},
-V. Bugaev\altaffilmark{2},
-K. Byrum\altaffilmark{4},
-A. Cannon\altaffilmark{5},
-A. Cesarini\altaffilmark{6},
-L. Ciupik\altaffilmark{7},
-E. Collins-Hughes\altaffilmark{5},
-W. Cui\altaffilmark{8},
-R. Dickherber\altaffilmark{2},
-J. Dumm\altaffilmark{9},
-Q. Feng\altaffilmark{8},
-G. Finnegan\altaffilmark{10},
-L. Fortson\altaffilmark{9},
-A. Furniss\altaffilmark{11},
-N. Galante\altaffilmark{3},
-J. Grube\altaffilmark{7},
-G. Gyuk\altaffilmark{7},
-H. Huan\altaffilmark{12},
-G. Hughes\altaffilmark{13},
-T. B. Humensky\altaffilmark{14},
-P. Kaaret\altaffilmark{15},
-N. Karlsson\altaffilmark{9,27},
-Y. Khassen\altaffilmark{5},
-D. Kieda\altaffilmark{10},
-H. Krawczynski\altaffilmark{2},
-G. Maier\altaffilmark{13},
-P. Majumdar\altaffilmark{1},
-S. McArthur\altaffilmark{2},
-A. McCann\altaffilmark{16},
-P. Moriarty\altaffilmark{17},
-M. Orr\altaffilmark{18},
-A. N. Otte\altaffilmark{19},
-J. S. Perkins\altaffilmark{20,21},
-M. Pohl\altaffilmark{22,13},
-H. Prokoph\altaffilmark{13},
-P. T. Reynolds\altaffilmark{23},
-E. Roache\altaffilmark{3},
-J. Ruppel\altaffilmark{22,13},
-D. B. Saxon\altaffilmark{24},
-G. H. Sembroski\altaffilmark{8},
-C. Skole\altaffilmark{13},
-A. W. Smith\altaffilmark{10},
-I. Telezhinsky\altaffilmark{22,13},
-G. Te\v{s}i\'{c}\altaffilmark{16},
-S. Thibadeau\altaffilmark{2},
-M. Vivier\altaffilmark{24},
-J. E. Ward\altaffilmark{5},
-R. Welsing\altaffilmark{13}
+T.~Arlen\altaffilmark{1},
+T.~Aune\altaffilmark{2},
+M.~Beilicke\altaffilmark{3},
+W.~Benbow\altaffilmark{4},
+A.~Bouvier\altaffilmark{2},
+J.~H.~Buckley\altaffilmark{3},
+V.~Bugaev\altaffilmark{3},
+K.~Byrum\altaffilmark{5},
+A.~Cannon\altaffilmark{6},
+A.~Cesarini\altaffilmark{7},
+L.~Ciupik\altaffilmark{8},
+E.~Collins-Hughes\altaffilmark{6},
+M.~P.~Connolly\altaffilmark{7},
+W.~Cui\altaffilmark{9},
+R.~Dickherber\altaffilmark{3},
+J.~Dumm\altaffilmark{10},
+A.~Falcone\altaffilmark{11},
+S.~Federici\altaffilmark{12,13},
+Q.~Feng\altaffilmark{9},
+J.~P.~Finley\altaffilmark{9},
+G.~Finnegan\altaffilmark{14},
+L.~Fortson\altaffilmark{10},
+A.~Furniss\altaffilmark{2},
+N.~Galante\altaffilmark{4},
+D.~Gall\altaffilmark{15},
+S.~Godambe\altaffilmark{14},
+S.~Griffin\altaffilmark{16},
+J.~Grube\altaffilmark{8},
+G.~Gyuk\altaffilmark{8},
+J.~Holder\altaffilmark{17},
+H.~Huan\altaffilmark{18},
+G.~Hughes\altaffilmark{12},
+T.~B.~Humensky\altaffilmark{19},
+A.~Imran\altaffilmark{20},
+P.~Kaaret\altaffilmark{15},
+N.~Karlsson\altaffilmark{10},
+M.~Kertzman\altaffilmark{21},
+Y.~Khassen\altaffilmark{6},
+D.~Kieda\altaffilmark{14},
+H.~Krawczynski\altaffilmark{3},
+F.~Krennrich\altaffilmark{20},
+K.~Lee\altaffilmark{3},
+A.~S~Madhavan\altaffilmark{20},
+G.~Maier\altaffilmark{12},
+P.~Majumdar\altaffilmark{1},
+S.~McArthur\altaffilmark{3},
+A.~McCann\altaffilmark{16},
+P.~Moriarty\altaffilmark{22},
+R.~Mukherjee\altaffilmark{23},
+T.~Nelson\altaffilmark{10},
+A.~O'Faol\'{a}in de Bhr\'{o}ithe\altaffilmark{6},
+R.~A.~Ong\altaffilmark{1},
+M.~Orr\altaffilmark{20},
+A.~N.~Otte\altaffilmark{24},
+N.~Park\altaffilmark{18},
+J.~S.~Perkins\altaffilmark{25,26},
+M.~Pohl\altaffilmark{13,12,31}
+H.~Prokoph\altaffilmark{12},
+J.~Quinn\altaffilmark{6},
+K.~Ragan\altaffilmark{16},
+L.~C.~Reyes\altaffilmark{27},
+P.~T.~Reynolds\altaffilmark{28},
+E.~Roache\altaffilmark{4},
+J.~Ruppel\altaffilmark{13,12},
+D.~B.~Saxon\altaffilmark{17},
+M.~Schroedter\altaffilmark{4},
+G.~H.~Sembroski\altaffilmark{9},
+C.~Skole\altaffilmark{12},
+A.~W.~Smith\altaffilmark{14},
+I.~Telezhinsky\altaffilmark{13,12},
+G.~Te\v{s}i\'{c}\altaffilmark{16},
+M.~Theiling\altaffilmark{9},
+S.~Thibadeau\altaffilmark{3},
+K.~Tsurusaki\altaffilmark{15},
+A.~Varlotta\altaffilmark{9},
+M.~Vivier\altaffilmark{17},
+S.~P.~Wakely\altaffilmark{18},
+J.~E.~Ward\altaffilmark{3},
+A.~Weinstein\altaffilmark{20},
+R.~Welsing\altaffilmark{12},
+D.~A.~Williams\altaffilmark{2},
+B.~Zitzer\altaffilmark{5}
 }
@@
 \and
-\author{S. Federici\altaffilmark{13,22}, C. Pfrommer\altaffilmark{25,27},
-A. Pinzke\altaffilmark{26}}
+\author{C. Pfrommer\altaffilmark{29,31},
+A. Pinzke\altaffilmark{30}}
 
 \altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA 90095, USA}
-\altaffiltext{2}{Department of Physics, Washington University, St. Louis, MO 63130, USA}
-\altaffiltext{3}{Fred Lawrence Whipple Observatory, Harvard-Smithsonian Center for Astrophysics, Amado, AZ 85645, USA}
-\altaffiltext{4}{Argonne National Laboratory, 9700 S. Cass Avenue, Argonne, IL 60439, USA}
-\altaffiltext{5}{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
-\altaffiltext{6}{School of Physics, National University of Ireland Galway, University Road, Galway, Ireland}
-\altaffiltext{7}{Astronomy Department, Adler Planetarium and Astronomy Museum, Chicago, IL 60605, USA}
-\altaffiltext{8}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
-\altaffiltext{9}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
-\altaffiltext{10}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
-\altaffiltext{11}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
-\altaffiltext{12}{Enrico Fermi Institute, University of Chicago, Chicago, IL 60637, USA}
-\altaffiltext{13}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
-\altaffiltext{14}{Physics Department, Columbia University, New York, NY 10027, USA}
+\altaffiltext{2}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
+\altaffiltext{3}{Department of Physics, Washington University, St. Louis, MO 63130, USA}
+\altaffiltext{4}{Fred Lawrence Whipple Observatory, Harvard-Smithsonian Center for Astrophysics, Amado, AZ 85645, USA}
+\altaffiltext{5}{Argonne National Laboratory, 9700 S. Cass Avenue, Argonne, IL 60439, USA}
+\altaffiltext{6}{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
+\altaffiltext{7}{School of Physics, National University of Ireland Galway, University Road, Galway, Ireland}
+\altaffiltext{8}{Astronomy Department, Adler Planetarium and Astronomy Museum, Chicago, IL 60605, USA}
+\altaffiltext{9}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
+\altaffiltext{10}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
+\altaffiltext{11}{Department of Astronomy and Astrophysics, 525 Davey Lab, Pennsylvania State University, University Park, PA 16802, USA}
+\altaffiltext{12}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
+\altaffiltext{13}{Institut für Physik und Astronomie, Universität Potsdam, 14476 Potsdam-Golm,Germany}
+\altaffiltext{14}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
 \altaffiltext{15}{Department of Physics and Astronomy, University of Iowa, Van Allen Hall, Iowa City, IA 52242, USA}
 \altaffiltext{16}{Physics Department, McGill University, Montreal, QC H3A 2T8, Canada}
-\altaffiltext{17}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
-\altaffiltext{18}{Department of Physics and Astronomy, Iowa State University, Ames, IA 50011, USA}
-\altaffiltext{19}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
-\altaffiltext{20}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
-\altaffiltext{21}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
-\altaffiltext{22}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm,Germany}
-\altaffiltext{23}{Department of Applied Physics and Instrumentation, Cork Institute of Technology, Bishopstown, Cork, Ireland}
-\altaffiltext{24}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}
-
+\altaffiltext{17}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}
+\altaffiltext{18}{Enrico Fermi Institute, University of Chicago, Chicago, IL 60637, USA}
+\altaffiltext{19}{Physics Department, Columbia University, New York, NY 10027, USA}
+\altaffiltext{20}{Department of Physics and Astronomy, Iowa State University, Ames, IA 50011, USA}
+\altaffiltext{21}{Department of Physics and Astronomy, DePauw University, Greencastle, IN 46135-0037, USA}
+\altaffiltext{22}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
+\altaffiltext{23}{Department of Physics and Astronomy, Barnard College, Columbia University, NY 10027, USA}
+\altaffiltext{24}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
+\altaffiltext{25}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
+\altaffiltext{26}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
+\altaffiltext{27}{Physics Department, California Polytechnic State University, San Luis Obispo, CA 94307, USA}
+\altaffiltext{28}{Department of Applied Physics and Instrumentation, Cork Institute of Technology, Bishopstown, Cork, Ireland}
 % Christoph, Anders and Simone:
-\altaffiltext{25}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
-\altaffiltext{26}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
-\altaffiltext{27}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
+\altaffiltext{29}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
+\altaffiltext{30}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
+\altaffiltext{31}{Corresponding authors: M. Pohl, pohlmadq@gmail.com \& C. Pfrommer, christoph.pfrommer@h-its.org}
 
@@
 \begin{abstract}
-  \linenumbers Observations of radio halos and relics in galaxy clusters indicate efficient electron
-  acceleration processes; the same processes are even more efficient for protons. Since protons have
-  a cooling time which exceeds the Hubble time in clusters, they can accumulate suggesting that
-  clusters may also be sources of very high-energy (VHE; $E>100$ GeV) gamma-ray emission resulting
-  from the interactions of highly relativistic cosmic-ray (CR) hadrons with the intracluster gas. We
-  report here on VHE gamma-ray observations of the Coma galaxy cluster with the VERITAS array of
-  imaging Cherenkov telescopes, with complementing \Fermi Gamma-ray Space Telescope observations at
+Observations of radio halos and relics in galaxy clusters indicate efficient electron
+acceleration. Protons should likewise be accelerated and, on account of
+weak energy losses, can accumulate, suggesting that
+clusters may also be sources of very high-energy (VHE; $E>100$ GeV) gamma-ray
+emission. We
+report here on VHE gamma-ray observations of the Coma galaxy cluster
+with the VERITAS array of
+imaging Cherenkov telescopes, with complementing \Fermi-LAT observations at
 GeV energies. No significant gamma-ray emission from the Coma cluster was detected. Integral flux
-  upper limits at the 99\% confidence level were measured to be on the order of $2-5\times 10^{-8}$
-  ph.  m$^{-2}$ s$^{-1}$ (VERITAS, $>$220 GeV) and $\sim 3\times 10^{-6}$ ph. m$^{-2}$ s$^{-1}$
-  (\Fermi, 1-3 GeV), respectively. For VERITAS (\Fermi), the limits are a factor of 60 (20) higher
-  than model-predicted minimum gamma-ray fluxes, which assume the radio-emitting electrons of the
-  Coma radio halo are all secondaries from cosmic-ray interactions. We use the gamma-ray flux upper
-  limits to constrain the populations of CRs and magnetic fields in Coma. Using an analytical
-  approach motivated by cosmological cluster simulations, the CR-to-thermal pressure ratio is
+upper limits at the 99\% confidence level were measured to be on the
+order of $(2-5)\times 10^{-8}\ {\rm ph.\,m^{-2}\,s^{-1}}$ (VERITAS, $>220\ {\rm GeV}$) and $\sim 3\times 10^{-6}\ {\rm ph.\,m^{-2}\, s^{-1}}$
+(\Fermi, $1-3\ {\rm GeV}$), respectively. We use the gamma-ray upper
+limits to constrain CRs and magnetic fields in Coma. Using an analytical
+approach, the CR-to-thermal pressure ratio is
 constrained to be $< 16\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the
@@
 CR interactions, the observations imply a lower limit on the central magnetic field in Coma of
-  $1$--$3\mu$G, depending on how the magnetic field declines with radius and on the gamma-ray
+$1-3\,\mu{\rm G}$, depending on the radial magnetic-field profile and on the gamma-ray
 spectral index. Since these values are well below those inferred by Faraday rotation measurements
 in Coma, this makes the hadronic model a very plausible explanation of the Coma radio
-  halo. Finally, since galaxy clusters are dark matter (DM) dominated, the VERITAS upper limits have
-  been used to place constraints on the thermally averaged product of the total self-annihilation
-  cross section and the relative velocity of the DM particles, $\expval{\sigma v}$. This is found to
-  be about $10^{-20} - 10^{-21}$ cm$^{3}$ s$^{-1}$ for a DM particle mass $m_{\chi} = 300$
-  GeV/c$^{2}$.
+halo. Finally, since galaxy clusters are dark-matter (DM) dominated, the VERITAS upper limits have
+been used to place constraints on the thermally-averaged product of the total 
+self-annihilation
+cross section and the relative velocity of the DM particles, $\expval{\sigma v}$.
 \end{abstract}
@@
 e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters feature megaparsec
-scale halos of nonthermal radio emission, indicative of a population of relativistic electrons and
-positrons\footnote{From here on electrons and positrons are collectively referred to as electrons.}
+scale halos of nonthermal radio emission, indicative of a population of relativistic electrons
 and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. There are two competing
 theories to explain radio halos. In the ``hadronic model'', the radio-emitting
-electrons are produced in inelastic collisions of cosmic-ray (CR) ions with the thermal gas of the
+electrons and positrons are produced in inelastic collisions of cosmic-ray (CR) ions with the thermal gas of the
 ICM \citep{article:Dennison:1980, article:EnsslinPfrommerMiniatiSubramanian:2011}. In the
@@
 CMB photons, on ultra-relativistic electrons. Those electrons can either be secondaries from the
-above mentioned CR interactions or injected into the ICM by powerful cluster members and
+CR interactions mentioned above,or injected into the ICM by powerful cluster members and
 further accelerated by diffusive shock acceleration or turbulent reacceleration processes
@@
 
-\section{VERITAS Observations and Analysis}
+\section{VERITAS Observations, Analysis, and Results}
 The VERITAS gamma-ray detector \citep{article:Weekes_etal:2002} is an array of four 12 m-diameter
@@
 
-%
-%
-
-\subsection{VERITAS Results}
 No significant excess of VHE gamma rays from the Coma cluster was detected with VERITAS, as
@@
 interest using the method described by \citet{article:Rolke_etal:2005} assuming a
-Gaussian-distributed background. A lower bound of zero is imposed on the signal rate to handle the
-negative excesses seen for several of the regions of interest. Figure \ref{fig:sigdist} shows the
+Gaussian-distributed background.
+A lower bound of zero is imposed on the gamma-ray flux from the Coma cluster, which prevents artificially low flux upper limits in the case that the best-fit source flux is formally negative.
+Figure \ref{fig:sigdist} shows the
 distribution of significances over the VERITAS skymap, which is well fit by a Gaussian with a mean
@@
 Table \ref{table:roi}. These upper-limit calculations depend on the gamma-ray spectrum, which in
-this work is assumed to be a power law in energy, $F\propto E^{-\alpha}$, where the spectral index
+this work is assumed to be a power law in energy, $dN/dE\propto E^{-\alpha}$, where the spectral index
 $\alpha$ was allowed to have a value of 2.1, 2.3, or 2.5.
@@
 the Coma cluster in all-sky survey mode since its launch in June 2008. The Fermi-LAT is sensitive
-to gamma rays in the 20 MeV to $\sim300$ GeV energy range and is very complementary to the VERITAS
-observations. Ackermann et al. (2010) reported on the search for gamma-ray emission from
+to gamma rays in the 20 MeV to $\sim300$ GeV energy range and is very complementary to 
+VERITAS. Ackermann et al. (2010) reported on the search for gamma-ray emission from
 thirty-three galaxy clusters in the data from the first 18 months, including the Coma cluster, for
@@
 
-The remaining background includes twenty-eight sources listed in the 11 months catalog of Fermi-LAT
+The remaining background includes twenty-eight sources listed in the 11-month catalog of Fermi-LAT
 data (Abdo et al. 2010), and the LAT standard Galactic diffuse emission component
@@
 background. All of the twenty-eight sources are modeled as point sources with power-law energy
-spectra. Fourteen of them lie outside the ROI and their spatial and spectral parameters were being
+spectra. Fourteen of them lie outside the ROI and their spatial and spectral parameters were
 kept fixed at the values given in the catalog. The parameters of the remaining sources, being
@@
 No significant gamma-ray signal was detected. Values of the significance greater than one were only
-obtained for the higher energy bin, where the test statistic (TS) is $\sim2$ for the point source
+obtained for the high-energy bin, where the test statistic (TS) is $\sim2$ for the point source
 model, $\sim4$ for the disk model with r$=0.2^{\circ}$ and $\sim6$ for the disk model with
@@
 CR-to-thermal energy density and a power-law spectrum in momentum, (2) an analytic model derived
-from cosmological hydrodynamical simulations of the formation of galaxy clusters, and (3) an
-model that uses the observed luminosity of the giant radio halo in Coma to place a lower limit on
+from cosmological hydrodynamical simulations of the formation of galaxy clusters, and (3) a
+model that uses the observed intensity profile
+of the giant radio halo in Coma to place a lower limit on
 the expected gamma-ray flux in the hadronic model -- where the radio-emitting electrons are
@@
 $R_\rmn{vir}=2.2$~Mpc, that we define as the radius of a sphere enclosing a mean density that is 200
-times the critical density of the Universe. Constraints on $X_\CR$ with VERITAS flux upper limits
-(99\% CL) strongly depend on $\alpha$.This is due to the comparably large energy range from GeV
+times the critical density of the Universe. Constraints on $X_\CR$ with 
+VERITAS flux upper limits (99\% CL) strongly depend on $\alpha$.
+This is due to the comparably large energy range from GeV
 energies (that dominate the CR pressure, provided $\alpha>2$ and the CR population has a
@@
 at 220 GeV, where our quality selection criteria imposed the energy threshold. These gamma-ray
-energies correspond to 1.6 TeV CRs -- an energy ratio of more than 3 orders of magnitudes, which
+energies correspond to 1.6 TeV CRs -- an energy ratio of more than 3 orders of magnitude, which
 explains the sensitivity to small changes in $\alpha$. The flux measurements within 0.2$^{\circ}$
@@
 the spectral index predicted by the simulations of \citet{article:PinzkePfrommer:2010} around 220
-GeV). Constraints on $X_\CR$ with \Fermi limits (99\%\ CL) depend only weakly on $\alpha$ because
-the energy range at GeV energies probed by \Fermi is influenced by the pion-decay bump which is
-characterized by a shape parameter that depends inversely on the CR spectral index
-\citep{article:PfrommerEnsslin:2004b}, partly absorbing the pressure ratios of different energy
-ranges. $X_\CR$-constraints with \Fermi limits are most constraining for an aperture of
+GeV).
+Constraints on $X_\CR$ with \Fermi limits (99\%\ CL) depend only weakly on $\alpha$ because GeV-band gamma rays are produced by CRs with energies near the relativistic transition, that dominantly contribute to the CR pressure.
+$X_\CR$-constraints with \Fermi limits are most constraining for an aperture of
 0.4$^{\circ}$; despite the slightly weaker flux upper limits in comparison to the smaller radii of
@@
 $\alpha=2.1$ is only slightly worse $(X_\CR<0.025)$.
-
-%
-%
 
@@
 decaying neutral pions which in clusters dominates over the inverse-Compton (IC) emission above
-100 MeV. Given a density profile as, e.g., as inferred by
+100 MeV. Given a density profile as, e.g., inferred by
 cosmological simulations or X-ray observations, the analytic approach models the CR distribution and
@@
 \citep{article:Vikhlinin_etal:2005}. This enables us to adopt the spatial and spectral distribution
-of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution
+of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of supernova remnants, AGN,
 of cluster galaxies.
@@
 Figure \ref{fig:spectrum} shows the expected integral spectral energy distribution of Coma within
-the virial radius (dotted lines). This suggests a spectral index of $\alpha=2.1$ in the energy
+the virial radius (dotted line). This suggests a spectral index of $\alpha=2.1$ in the energy
 interval 1-3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV). Also
@@
 stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong
-magnetic fields ($B \gg B_\rmn{CMB} \simeq 3.2 \mu$G, where $B_\rmn{CMB}$ is the equivalent magnetic
+magnetic fields ($B \gg B_\rmn{CMB} \simeq (1+z)^2\,(3.2 \mu{\rm G})$, 
+where $B_\rmn{CMB}$ is the equivalent magnetic
 field strength of the CMB so that $B_\rmn{CMB}^2/8\pi$ equals the CMB energy density). Thus the
@@
 
-To derive a minimum gamma-ray flux that is comparable to the upper limits, we need to determine the
+To derive a minimum gamma-ray flux that can be compared to the upper limits, we need to determine the
 radio flux within the corresponding angular regions. To this end, we fit the
@@
 emission. This, again, assumes the validity of the hadronic model of radio halos, in which the
-radio-emitting electrons are secondaries from CR interactions. Lowering the gamma-ray
-constraint will tighten the magnetic field limit. In case of a conflict with magnetic field
+radio-emitting electrons are secondaries from CR interactions. A stronger gamma-ray
+constraint will tighten the magnetic-field limit. In case of a conflict with magnetic field
 measurements by other methods, e.g., Faraday rotation measure (RM),\footnote{Generally,
@@
 
-The expected gamma-ray flux due to self-annihilation of WIMPs is given by
+The expected gamma-ray flux due to self-annihilation of WIMPs in a
+dark-matter halo is given by \citep{2004PhRvD..69l3501E,2008ApJ...678..594W,2010ApJ...720.1174A}
 \begin{equation}
 \frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=
-\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\,\frac{N_{\gamma}}{dE}\, J(\Delta\Omega),
+\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\,\frac{dN_{\gamma}}{dE}\, J(\Delta\Omega),
 \label{eqn:WIMPflux}
@@
 where $\expval{\sigma v}$ is the thermally-averaged product of the total self-annihilation cross
-section and the relative WIMP velocity, $m_{\chi}$ is the WIMP mass, $\frac{N_{\gamma}}{dE}$ is the
+section and the relative WIMP velocity, $m_{\chi}$ is the WIMP mass, $\frac{dN_{\gamma}}{dE}$ is the
 differential gamma-ray yield per annihilation\footnote{In this work, we have calculated the
 differential gamma-ray yield per annihilation using the Pythia Monte Carlo simulator.},
-$\Delta\Omega$ is the observed solid angle, and $J$ is the astrophysical factor - a dimensionless
+$\Delta\Omega$ is the observed solid angle, and $J$ is the so-called
+astrophysical factor -- a 
 factor which determines the DM annihilation rate and depends on the DM distribution.
 
-Given the upper limit on the observed gamma-ray rate,
+Given the upper limit on the observed gamma-ray rate, defined as the ratio of the event number detected within the observing time $T_{\mathrm{obs}}$,
 $R_{\gamma}(99\%\ \mathrm{CL}) = N_{\gamma}(99\%\ \mathrm{CL}) / T_{\mathrm{obs}}$, we can place
@@
 R_{\gamma}(99\%\ \mathrm{CL})\, \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\,
-\frac{1}{\int^{m_{\chi}}_{0} dE\ A_{\mathrm{eff}}\,N_\gamma (E)},
+\left[\int^{m_{\chi}}_{0} dE\ A_{\mathrm{eff}}\,\frac{dN_\gamma (E)}{dE}\right]^{-1},
 \end{equation}
@@
 \begin{equation}
-J(\Delta\Omega)=\int_{\Delta\Omega}d\Omega\int d\lambda\ \rho_{\chi}(\lambda)^{2}(\lambda,\Omega),
+J(\Delta\Omega)=\int_{\Delta\Omega}d\Omega\int d\lambda\ \rho_{\chi}^{2}(\lambda,\Omega),
 \end{equation}
@@
 on scales $r>0.2\,R_{200}$ (which are of relevance for the present work), different assumptions
-about the inner slope of the smooth DM density profile only translate to small uncertainties in the
-resulting DM annihilation flux which are small in comparison to expected boost due to substructures
-\citep[see Fig.~2 of][]{article:PinzkePfrommerBergstrom}. Table \ref{table:astrofactor} lists the
+about the inner slope of the smooth DM density profile translate to 
+uncertainties in the
+resulting astrophysical factor. Table \ref{table:astrofactor} lists the
 astrophysical factors calculated for the different VERITAS apertures considered in this work.  Table
@@
 
-The resulting exclusion regions in the $(\expval{\sigma v}, m_{\chi})$ parameter space are shown in
+The resulting exclusion curves in the $(\expval{\sigma v}, m_{\chi})$ parameter space are shown in
 Figure \ref{fig:dm} for three different DM self-annihilation channels, W$^{+}$W$^{-}$,
-b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$, independently of any WIMP models. Depending on the
-chosen aperture, the limits are on the order of $10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The
+b$\bar{\mathrm{b}}$, and $\tau^{+}\tau^{-}$. Depending on the
+DM annihilation channel, the limits are on the order of
+$10^{-20}$ to $10^{-21}$ cm$^{3}$ s$^{-1}$. The
 minimum for each exclusion curve and corresponding DM particle mass is listed in Table
-\ref{table:DMlimits}. We note that these limits are derived with conservative estimates of the
+\ref{table:DMlimits}. We stress that these limits are derived with conservative estimates of the
 astrophysical factor $J$. They do not include any boost to the annihilation rate possibly due to DM
 substructures populating the Coma halo, which could scale down the present limits by a factor
-$O(100)$ in the most optimistic cases.
+$O(1000)$ in the most optimistic cases
+\citep{article:PinzkePfrommerBergstrom,article:Gao_etal:2012}.
 
@@
 events, and the signal-to-noise ratio deteriorates.
-
-%
-%
 
@@
 \emph{Fermi}-LAT has observed the Coma cluster in all-sky survey mode since its launch in June
-2008. We have used all data available from launch to June 2011 for an updated analysis over already
+2008. We have used all data available from launch to June 2011 for an updated analysis
+compared to
 published results \citep{article:Ackermann_etal:2010}. Again, no significant excess of gamma rays
@@
 of \citet{article:PinzkePfrommer:2010}. The latter is a ``first-principle approach'' that predicts
-the CR distribution spectrally and spatially for a given set of assumptions (namely the physics that
-was simulated). It is powerful since it only requires the density profile as input due to the
+the CR distribution spectrally and spatially for a given set of assumptions.
+It is powerful since it only requires the density profile as input due to the
 approximate universality of the CR distribution (when neglecting CR diffusion and streaming). Note,
 however, that inclusion of these CR transport processes may be necessary to explain the radio-halo
-bimodality. (3) We finally used a pragmatic approach which models the CR and magnetic distributions
+bimodality. (3) Finally, we used a pragmatic approach which models the CR and magnetic distributions
 in order to reproduce the observed emission profile of the Coma radio halo. While this approach is
@@
 Applying our simplified ``isobaric CR model'' to the most constraining VERITAS limits, we can
-constrain the CR-to-thermal pressure ratio, $X_\CR$, to be below 0.048 and 0.43 (for a CR or
+constrain the CR-to-thermal pressure ratio, $X_\CR$, to be below 0.048--0.43 (for a CR or
 gamma-ray spectral index, $\alpha$, varying between 2.1 and 2.5). We obtain a constraint of
@@
 where a possible boost to the annihilation rate due to DM substructures in the cluster halo has
-been neglected. Including such a boost could scale down the present limits by a factor $O(100)$ in
+been neglected. Including such a boost could scale down the present limits by a factor $O(1000)$ in
 the most optimistic cases.
@@
 institutions in the construction and operation of the instrument. C.P. gratefully acknowledges 
-financial support of the Klaus Tschira Foundation.
+financial support of the Klaus Tschira Foundation. A.P. acknowledges 
+NSF grant AST-0908480 for support.
 
@@
 derived using a ring-background model \citep{article:Aharonian_etal:2001}.
-White contours show the X-ray counts per second () in the 0.1 to 2.4 keV energy band from the ROSAT
+White contours show the X-ray counts per second in the 0.1 to 2 keV energy band
+(8 levels from 1 to 16 cts s$^{-1}$ after 3-pixel Gaussian smoothing) from the ROSAT
 all-sky survey \citep{article:BrielHenryBohringer:1992}. \emph{Right}: Same as above but with
@@
 \end{center}
-\caption{Integral gamma-ray flux upper limits for \Fermi and VERITAS observations of the Coma
+\caption{Integral gamma-ray flux upper limits in narrow energy bands $[E_0;E_1]$ 
+for \Fermi and VERITAS observations of the Coma
 cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration
-  radii (arrows with different grey scales), assuming that $\alpha=2.3$ except in the 1--3 GeV
-  energy interval where $\alpha=2.1$ is adopted. $R_{\rmn{vir}}$ is the virial radius of the Coma
-  cluster.  These are compared to integrated spectra of the same energy interval and aperture,
+radii (arrows with different grey intensities), assuming that $\alpha=2.3$ except 
+in the 1--3 GeV
+energy interval where $\alpha=2.1$ is adopted. $R_{\rmn{vir}}$ is the virial
+radius of the Coma
+cluster, corresponding to $1.25^\circ$. These are compared to integrated spectra of the same energy interval and aperture,
 assuming the universal gamma-ray spectrum of clusters \citep[lines with different grey
-  scales,][]{article:PinzkePfrommer:2010}. To guide the eye, we show the underlying universal
+intensities,][]{article:PinzkePfrommer:2010}. To guide the eye, we show the underlying universal
 integral energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting
@@
 \startdata
-\small{Point Source} & 2.745 (0.302) & 0.965 (0.000) & 1.002 (1.313)\\
-\small{Disk: r = 0.2$^\circ$} & 3.066 (0.648) & 1.193 (0.218) & 1.165 (2.031)\\
-\small{Disk: r = 0.4$^\circ$} & 3.515 (0.768) & 1.297 (0.177) & 1.234 (2.349)\\
+\small{Point Source} & 2.7 (0.30) & 0.97 (0.000) & 1.00 (1.3)\\
+\small{Disk: r = 0.2$^\circ$} & 3.1 (0.65) & 1.2 (0.22) & 1.2 (2.0)\\
+\small{Disk: r = 0.4$^\circ$} & 3.5 (0.77) & 1.3 (0.18) & 1.2 (2.4)\\
 \cutinhead{\small{Spectral index $\alpha=2.3$}}
-\small{Point Source} & 2.803 (0.317) & 0.992 (0.000) & 1.006 (1.371)\\
-\small{Disk: r = 0.2$^\circ$} & 3.130 (0.654) & 1.227 (0.286) & 1.166 (2.072)\\
-\small{Disk: r = 0.4$^\circ$} & 3.586 (0.787) & 1.341 (0.273) & 1.236 (2.380)\\
+\small{Point Source} & 2.8 (0.32) & 0.99 (0.000) & 1.0 (1.4)\\
+\small{Disk: r = 0.2$^\circ$} & 3.1 (0.65) & 1.2 (0.29) & 1.2 (2.1)\\
+\small{Disk: r = 0.4$^\circ$} & 3.6 (0.79) & 1.3 (0.27) & 1.2 (2.4)\\
 \cutinhead{\small{Spectral index $\alpha=2.5$}}
-\small{Point Source} & 2.854 (0.333) & 1.016 (0.000) & 1.009 (1.424)\\
-\small{Disk: r = 0.2$^\circ$} & 3.184 (0.658) & 1.259 (0.349) & 1.167 (2.112)\\
-\small{Disk: r = 0.4$^\circ$} & 3.647 (0.804) & 1.381 (0.362) & 1.237 (2.408)\\
+\small{Point Source} & 2.9 (0.33) & 1.0 (0.000) & 1.0 (1.4)\\
+\small{Disk: r = 0.2$^\circ$} & 3.2 (0.66) & 1.3 (0.35) & 1.2 (2.1)\\
+\small{Disk: r = 0.4$^\circ$} & 3.7 (0.80) & 1.4 (0.36) & 1.2 (2.48)\\
 \enddata
@@
 \colhead{R\tablenotemark{a} [deg]} 
-& \multicolumn{3}{c}{analytic model: $X_{\CR}~[\%]$\tablenotemark{b} }
+& \multicolumn{3}{c}{analytic model: $X_{\CR}$\tablenotemark{b} }
 & \colhead{$F_{\gamma,\rmn{sim}}(E)$\tablenotemark{c}}
@@
 \hline
-0 & 10 & 23 & 97 & 1.9 & 14.8\\
-0.2 & 4.8 & 10 & 43 & 2.9 & 7.2\\
-0.4 & 6.7 & 15 & 62 & 4.4 & 10.8\\
+0 & 0.1 & 0.23 & 0.97 & 1.9 & 14.8\\
+0.2 & 0.048 & 0.10 & 0.43 & 2.9 & 7.2\\
+0.4 & 0.067 & 0.15 & 0.62 & 4.4 & 10.8\\
 \cutinhead{\Fermi constraints}
-0 & 5.2 & 3.5 & 4.7 & 1.4 & 1.96\\
-0.2 & 3.5 & 2.4 & 3.1 & 2.1 & 1.46\\
-0.4 & 2.5 & 1.7 & 2.3 & 3.2 & 1.10\\
+0 & 0.052 & 0.035 & 0.047 & 1.4 & 1.96\\
+0.2 & 0.035 & 0.024 & 0.031 & 2.1 & 1.46\\
+0.4 & 0.025 & 0.017 & 0.023 & 3.2 & 1.10\\
 \enddata
@@
 & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{b}} 
-& \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{c} } \\
+& \multicolumn{3}{c}{$10^{4}\times X_{\CR,\,\rmn{min}}$\tablenotemark{c} } \\
 & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
@@
 \hline
-0.13 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
-0.2  & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
-0.4  & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
+0 & 1.6 & 0.7 & 0.3 & 6.7 & 6.1 & 11 \\
+0.2  & 3.1 & 1.4 & 0.6 & 7.8 & 7.2 & 13 \\
+0.4  & 6.3 & 2.8 & 1.3 & 9.8 & 9.0 & 16 \\
 \cutinhead{\Fermi energy range, 1--3~GeV}
-0.13 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
-0.2  & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
-0.4  &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
+0 & ~~3.5 & ~~4.8 & ~~6.4 & 6.7 & 6.1 & 11 \\
+0.2  & ~~6.8 & ~~9.3 &  12.5 & 7.8 & 7.2 & 13 \\
+0.4  &  13.5 & 18.6  &  25.0 & 9.8 & 9.0 & 16 \\
 \enddata

### 2012-05-31 ms-rev.tex
revision of CR part finished

--- 2012-02-27 ms.tex
@@
   Observations of radio halos and relics in galaxy clusters indicate efficient electron
-acceleration. Protons should likewise be accelerated and, on account of
-weak energy losses, can accumulate, suggesting that
-clusters may also be sources of very high-energy (VHE; $E>100$ GeV) gamma-ray
-emission. We
-report here on VHE gamma-ray observations of the Coma galaxy cluster
-with the VERITAS array of
-imaging Cherenkov telescopes, with complementing \Fermi-LAT observations at
+  acceleration. Protons should likewise be accelerated and, on account of weak energy losses, can
+  accumulate, suggesting that clusters may also be sources of very high-energy (VHE; $E>100$ GeV)
+  gamma-ray emission. We report here on VHE gamma-ray observations of the Coma galaxy cluster with
+  the VERITAS array of imaging Cherenkov telescopes, with complementing \Fermi-LAT observations at
   GeV energies. No significant gamma-ray emission from the Coma cluster was detected. Integral flux
-upper limits at the 99\% confidence level were measured to be on the
-order of $(2-5)\times 10^{-8}\ {\rm ph.\,m^{-2}\,s^{-1}}$ (VERITAS, $>220\ {\rm GeV}$) and $\sim 3\times 10^{-6}\ {\rm ph.\,m^{-2}\, s^{-1}}$
-(\Fermi, $1-3\ {\rm GeV}$), respectively. We use the gamma-ray upper
-limits to constrain CRs and magnetic fields in Coma. Using an analytical
-approach, the CR-to-thermal pressure ratio is
-constrained to be $< 16\%$ from VERITAS data and $< 2.5\%$ from \Fermi data (averaged within the
-virial radius). Assuming that the radio-emitting electrons of the Coma halo result from hadronic
-CR interactions, the observations imply a lower limit on the central magnetic field in Coma of
-$1-3\,\mu{\rm G}$, depending on the radial magnetic-field profile and on the gamma-ray
-spectral index. Since these values are well below those inferred by Faraday rotation measurements
-in Coma, this makes the hadronic model a very plausible explanation of the Coma radio
-halo. Finally, since galaxy clusters are dark-matter (DM) dominated, the VERITAS upper limits have
-been used to place constraints on the thermally-averaged product of the total 
-self-annihilation
-cross section and the relative velocity of the DM particles, $\expval{\sigma v}$.
+  upper limits at the 99\% confidence level were measured to be on the order of $(2-5)\times
+  10^{-8}\ {\rm ph.\,m^{-2}\,s^{-1}}$ (VERITAS, $>220\ {\rm GeV}$) and $\sim 2\times 10^{-6}\ {\rm
+    ph.\,m^{-2}\, s^{-1}}$ (\Fermi, $1-3\ {\rm GeV}$), respectively. We use the gamma-ray upper
+  limits to constrain CRs and magnetic fields in Coma. Using an analytical approach, the
+  CR-to-thermal pressure ratio is constrained to be $< 16\%$ from VERITAS data and $< 1.7\%$ from
+  \Fermi data (averaged within the virial radius). {\bf These upper limits are now starting to
+    constrain the CR physics in self-consistent cosmological cluster simulations and cap the maximum
+    CR acceleration efficiency at structure formation shocks to be $<50\%$. Alternatively, this may
+    argue for non-negligible CR transport processes such as CR streaming and diffusion into the
+    outer cluster regions. } Assuming that the radio-emitting electrons of the Coma halo result from
+  hadronic CR interactions, the observations imply a lower limit on the central magnetic field in
+  Coma of $\sim (2 - 5.5)\,\mu{\rm G}$, depending on the radial magnetic-field profile and on the
+  gamma-ray spectral index. Since these values are {\bf (for most of the parameter space)} below
+  those inferred by Faraday rotation measurements in Coma, this {\bf renders} the hadronic model a
+  very plausible explanation of the Coma radio halo. Finally, since galaxy clusters are dark-matter
+  (DM) dominated, the VERITAS upper limits have been used to place constraints on the
+  thermally-averaged product of the total self-annihilation cross section and the relative velocity
+  of the DM particles, $\expval{\sigma v}$.
 \end{abstract}
@@
 \citep[IACTs;][]{article:Perkins_etal:2006, inproc:Perkins_etal:2008, article:Aharonian_etal:2009a,
-article:Aleksic_etal:2010}.
+article:Aleksic_etal:2010,article:Aleksic_etal:2012}.
 
@@
 integration, we expect a considerably larger gamma-ray luminosity due to the increasing volume in
-this model. The best limit of $X_\CR< 0.017$ is achieved for $\alpha=2.3$, while the limit for
-$\alpha=2.1$ is only slightly worse $(X_\CR<0.025)$.
+this model. The best limit of $X_\CR< 0.012$ is achieved for $\alpha=2.3$, while the limit for
+$\alpha=2.1$ is only slightly worse $(X_\CR<0.017)$.
 
@@
 
-These cosmological simulations only consider advective transport of CRs by turbulent gas motions
-which lead to centrally-enhanced density profiles. However, other means of CR transport such as
-diffusion and streaming may flatten the CR radial profiles. It has been suggested that advection is
-dominant only during mergers, in which case relaxed clusters could have a gamma-ray luminosity 
-reduced by up to a factor of five compared with merging clusters
-\citep{article:EnsslinPfrommerMiniatiSubramanian:2011}. Hence, tight upper limits on the gamma-ray
-emission can constrain a combination of acceleration physics and transport properties of CRs.
+These cosmological simulations only consider advective transport of CRs by {\bf bulk gas flows that
+  inject a turbulent cascade, leading to} centrally-enhanced density profiles. However, other means
+of CR transport such as diffusion and streaming may flatten the CR radial profiles. {\bf The CRs
+  stream along magnetic field lines in the opposite direction of the CR number density gradient (at
+  any energy). In the stratified cluster atmosphere, this implies a net flux of CRs towards larger
+  radii, equalizing the CR number density with time if not counteracted by advective transport. It
+  has been suggested that advection velocities only dominate over the CR streaming velocities for
+  periods with trans- and supersonic cluster turbulence during a cluster merger and drop below the
+  CR streaming velocities for relaxing clusters.  As a consequence, a bimodality of the CR spatial
+  distribution is expected to result; with merging (relaxed) clusters showing a centrally
+  concentrated (flat) CR energy density profile
+  \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}. This translates into a bimodality of the
+  expected diffuse radio and gamma-ray emission of clusters, since more centrally concentrated CRs
+  will find higher target densities for hadronic CR proton interactions. As a result of this,
+  relaxed clusters could have a reduced gamma-ray luminosity by up to a factor of five
+  \citep{article:EnsslinPfrommerMiniatiSubramanian:2011}.}  Hence, tight upper limits on the
+gamma-ray emission can constrain a combination of acceleration physics and transport properties of
+CRs.
 
@@
 of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of supernova remnants, AGN,
-of cluster galaxies.
+and cluster galaxies.
 
@@
 the virial radius (dotted line). This suggests a spectral index of $\alpha=2.1$ in the energy
-interval 1-3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV). Also
-shown are integrals of the differential spectrum for finite energy intervals across the angular
-apertures tested in this study (solid lines). These model fluxes (summarized in Table
+interval 1-3 GeV and $\alpha=2.3$ for energies probed by VERITAS ($>220$~GeV). Also shown are
+integrals of the differential spectrum for finite energy intervals across the angular apertures
+tested in this study ({\bf dashed} lines). These model fluxes (summarized in Table
 \ref{table:constraints_simple}) are compared to \Fermi and VERITAS flux upper limits for the same
 energy intervals. Constraints on $X_\CR$ with the gamma-ray flux limit of \Fermi in the energy
-interval 1-3 GeV ($<0.4^\circ$) are most constraining, but are still above the model predictions
-that assume an optimistically large shock-acceleration efficiency and CR transport parameters as
-laid out above. In our further analysis, we use the most constraining \Fermi flux limits in the
+interval 1-3 GeV ($<0.4^\circ$) are most constraining, {\bf since that combination of a specific
+  energy interval and aperture minimizes the ratio of the upper limit to the expected model flux. In
+  particular, this upper limit is 24\% below} the model predictions that assume an optimistically
+large shock-acceleration efficiency and CR transport parameters as laid out above. {\bf Hence this
+  enables us to constrain a combination of maximum shock acceleration efficiency and CR transport
+  parameters.}  In our further analysis, we use the most constraining \Fermi flux limits in the
 energy interval 1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above
@@
 $R_\rmn{vir}=2.2$~Mpc. To compute the CR pressure, we assume a low-momentum cutoff of the CR
-distribution at $q = 0.8\,m_{p}c$, where $m_{p}$ is the proton mass, to reflect the high cooling
-rates at low CR energies. The CR-to-thermal pressure ratio rises toward the outer regions
-on account of the higher efficiency of CR acceleration at the peripheral accretion shocks compared
-to the weak central flow shocks. Adiabatic compression of a mixture of CRs and thermal gas disfavors
-the CR pressure relative to the thermal pressure on account of the softer equation of state of
-CRs. The weak increase of $X_{\CR}$ toward the core is due to the comparably fast thermal cooling of
-gas.
+distribution at $q = 0.8\,m_{p}c$, where $m_{p}$ is the proton mass. {\bf This is suggested by
+  cosmological cluster simulations and reflects} the high {\bf Coulomb} cooling rates at low CR
+energies. The CR-to-thermal pressure ratio rises toward the outer regions on account of the higher
+efficiency of CR acceleration at the peripheral accretion shocks compared to the weak central flow
+shocks. Adiabatic compression of a mixture of CRs and thermal gas disfavors the CR pressure relative
+to the thermal pressure on account of the softer equation of state of CRs. The weak increase of
+$X_{\CR}$ toward the core is due to the comparably fast thermal cooling of gas.
 
@@
 
-Equivalently, the most constraining \Fermi upper limit in the energy interval 1-3 GeV ($<0.4^\circ$)
-is a factor of 1.1 larger than our model predictions (assuming $\alpha=2.1$ which is very close to
-the simulated spectral index for the energy range 1-3 GeV). Scaling our integrated CR-to-thermal
-pressure profile yields a constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a
-limit within the cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}). The
-$X_\CR$ constraint evaluated within the cluster virial radius is comparable to the constraint of
-$X_\CR<0.025$ in our simplified model. Naturally, with the \Fermi limits we probe the region around
-GeV energies that dominate the CR pressure, and we do not expect any differences in comparison to
-the simplified power-law model in comparison to the universal CR spectrum with its concave CR
-spectrum found in the simulations.
+{\bf As already eluded,} the most constraining \Fermi upper limit in the energy interval 1-3 GeV
+($<0.4^\circ$) is a factor of {\bf 0.76 smaller} than our model predictions (assuming $\alpha=2.1$
+which is very close to the simulated spectral index for the energy range 1-3 GeV). Scaling our
+integrated CR-to-thermal pressure profile yields a constraint of $X_{\CR}<0.012$ within
+0.4$^{\circ}$ that translates to a limit within the cluster virial radius of $X_\CR<0.017$ (dashed
+lines of Figure \ref{fig:xcr}). The $X_\CR$ constraint evaluated within the cluster virial radius is
+comparable to the constraint of $X_\CR<0.017$ in our simplified model. Naturally, with the \Fermi
+limits we probe the region around GeV energies that dominate the CR pressure, and we do not expect
+any differences in comparison to the simplified power-law model in comparison to the universal CR
+spectrum with its concave CR spectrum found in the simulations.
 
@@
 stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong
-magnetic fields ($B \gg B_\rmn{CMB} \simeq (1+z)^2\,(3.2 \mu{\rm G})$, 
+magnetic fields ($B \gg B_\rmn{CMB} \simeq (1+z)^2\,3.2 \mu{\rm G}$, 
 where $B_\rmn{CMB}$ is the equivalent magnetic
@@
 strength, $B_{0}$, and we permit the magnetic decline, $\alpha_{B}$, to vary within a reasonable
-range of $\Delta\alpha_{B}=0.2$ as suggested by the Faraday RM studies. We proceed as follows:
+range of $\Delta\alpha_{B}=0.2$ as suggested by {\bf those} Faraday RM studies. We proceed as follows:
 
@@
 Table \ref{table:Bmin} shows the resulting lower limit of the central magnetic field ranging from
-$B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from $B_{0} = 1.1$ to $4.6\,\mu$G in the
+$B_{0} = 0.5$ to $1.4\,\mu$G in case the of VERITAS and from $B_{0} = 1.4$ to $5.5\,\mu$G in the
 case of \Fermi.\footnote{Note that a central magnetic field of $3\,\mu$G corresponds in the Coma
   cluster to a magnetic-to-thermal energy density ratio of $X_B=0.005$.} Since these lower limits on
-$B_{0}$ are below the values favored by Faraday RM for the entire parameter space spanned by
-$\alpha_{B}$ and $\alpha$, the hadronic model is a viable explanation of the Coma radio halo. Future
-gamma-ray observations of the Coma cluster may put more stringent constraints on the parameters of
-the hadronic model.
+$B_{0}$ are below the values favored by Faraday RM for {\bf most of the} parameter space spanned by
+$\alpha_{B}$ and $\alpha$ {\bf (and never exceed the values for the phenomenological Faraday
+  RM-inferred $B$-model)}, the hadronic model is a viable explanation of the Coma radio halo. {\bf
+  In fact, the \Fermi upper limits start to rule out the parameter combination of
+  $\alpha_{B}\gtrsim 0.7$ and $\alpha \gtrsim 2.5$ for the hadronic model of the Coma radio halo.}
+Future gamma-ray observations of the Coma cluster may put more stringent constraints on the
+parameters of the hadronic model.
 
@@
 limits since they are derived from flux upper limits. For the \Fermi upper limits, they range from
-0.1 to 0.4; hence the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} <
+0.08 to 0.27; hence the $X_{\CR}$ profiles always obey the energy condition, i.e., $P_{\CR} <
 P_{\mathrm{th}}$, over the entire range of the radio-halo emission ($< 1$ Mpc).\footnote{See Figure
@@
 As already mentioned in the introduction, most of the mass in a galaxy cluster is in the form of
-DM. While the nature of DM remains unknown, the most compelling theoretical candidate is a
+DM. While the nature of DM remains unknown, a compelling theoretical candidate is a
 WIMP. The self-annihilation of WIMPs can produce either monoenergetic gamma-ray lines or a
@@
 The expected gamma-ray flux due to self-annihilation of WIMPs in a
-dark-matter halo is given by \citep{2004PhRvD..69l3501E,2008ApJ...678..594W,2010ApJ...720.1174A}
+dark-matter halo is given by 
 \begin{equation}
@@
 halo mass-concentration relation derived from $N$-body simulation of structure formation
-\citep{article:Bullock_etal:2001}, we find for these parameters $r_{s}=0.654$ Mpc and
-$\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. According to the latest high-resolution DM-only
+\citep{article:Bullock_etal:2001}, $M_{\rm vir} =9.7(+6.1/-3.5)\cdot 10^{14}\,
+h^{-1}\ {\rm M_\odot}$ and $C_{\rm vir}=3.5(+1.1/-0.9)$,
+we find 
+for these parameters $r_{s}=0.654$ Mpc and
+$\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. 
+According to the latest high-resolution DM-only
 simulations of nine rich galaxy clusters, the inner regions of the smooth density profiles are quite
@@
 feedback processes pushing gas out of the center by, e.g., energy injection through AGNs. However,
-on scales $r>0.2\,R_{200}$ (which are of relevance for the present work), different assumptions
+on scales $r\gtrsim 0.45$~Mpc or more than 20\% of $R_{\rm vir}$ (which are of relevance for the present work), different assumptions
 about the inner slope of the smooth DM density profile translate to 
@@
 which is used to estimate the gamma-ray contamination from DM annihilation in the background region.
+The analysis uses a ring region to estimate the background in a ON region.
+We have to compute the expected level of gamma-ray emission from DM annihilation in the ring region in order to check that it is negligible with respect to the level of gamma-ray emission from DM annihilation in the ON region.
+This is equivalent to compute the astrophysical factor of the ON and OFF source region since this quantity is related to the rate of DM annihilations.
 
@@
 \emph{Fermi}-LAT has observed the Coma cluster in all-sky survey mode since its launch in June
-2008. We have used all data available from launch to June 2011 for an updated analysis
+2008. We have used all data available from launch to June 2011 {\bf [UPDATE!]} for an updated analysis
 compared to
@@
 limits for the central magnetic field range from $B_{0} = 0.5$ to $1.4\,\mu$G (for VERITAS flux
-limits) and from $B_{0} = 1.1$ to $4.6\,\mu$G (for \Fermi flux limits). Since all these lower
-limits on $B_0$ are below the values favored by Faraday RM, $B_{0} = 4.7^{+0.7}_{-0.8}\,\mu$G
-\citep{article:Bonafede_etal:2010}, the hadronic model is a very attractive explanation of the Coma
-radio halo.
+limits) and from $B_{0} = 1.4$ to $5.5\,\mu$G (for \Fermi flux limits). Since all {\em (but one) of}
+these lower limits on $B_0$ are below the values favored by Faraday RM, $B_{0} =
+4.7^{+0.7}_{-0.8}\,\mu$G \citep{article:Bonafede_etal:2010}, the hadronic model is a very attractive
+explanation of the Coma radio halo.  {\bf The \Fermi upper limits start to rule out the parameter
+  combination of $\alpha_{B}\gtrsim 0.7$ and $\alpha \gtrsim 2.5$ for the hadronic model of the Coma
+  radio halo.}
 
@@
 
-The \Fermi flux limits constrain $X_\CR$ to be below 0.017--0.025 (for $\alpha$ varying
-between 2.3 and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$,
-which is very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain 
-a constraint which is almost identical to that from our simulation-based model within the virial
-radius of $X_\CR<0.024$. That constraint improves to $X_{\CR}<0.018$ for an aperture of 0.4$^\circ$
-corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc. These are encouraging
-results in that we constrain the CR pressure (of a phase that is fully mixed with the ICM) to be at
-most a small fraction ($<0.025$) of the overall pressure. As a result, hydrostatic cluster masses
-and the total Comptonization parameter due to the Sunyaev-Zel'dovich effect suffer at most a very
-small bias due to CRs.
+The \Fermi flux limits constrain $X_\CR$ to be below 0.012--0.017 (for $\alpha$ varying between 2.3
+and 2.1), only weakly depending on the assumed CR spectral index. Assuming $\alpha=2.1$, which is
+very close to the simulated spectral index for the energy range of 1--3 GeV, we obtain a constraint
+which is identical to that from our simulation-based model within the virial radius of
+$X_\CR<0.017$. That constraint improves to $X_{\CR}<0.012$ for an aperture of 0.4$^\circ$
+corresponding to a physical scale of $R \simeq R_{200}/3 \simeq 660$~kpc.  {\bf These upper limits
+  are now starting to constrain the CR physics in self-consistent cosmological cluster simulations
+  and cap the maximum CR acceleration efficiency at structure formation shocks to be
+  $<50\%$. Alternatively, this may argue for non-negligible CR transport processes such as CR
+  streaming and diffusion into the outer cluster regions \citep{article:Aleksic_etal:2012}.} These
+are encouraging results in that we constrain the CR pressure (of a phase that is fully mixed with
+the ICM) to be at most a small fraction ($<0.017$) of the overall pressure. As a result, hydrostatic
+cluster masses and the total Comptonization parameter due to the Sunyaev-Zel'dovich effect suffer at
+most a very small bias due to CRs.
 
@@
 \cutinhead{\Fermi constraints}
-0 & 0.052 & 0.035 & 0.047 & 1.4 & 1.96\\
-0.2 & 0.035 & 0.024 & 0.031 & 2.1 & 1.46\\
-0.4 & 0.025 & 0.017 & 0.023 & 3.2 & 1.10\\
+0   & 0.035 & 0.024 & 0.033 & 1.4 & 1.34\\
+0.2 & 0.024 & 0.017 & 0.022 & 2.1 & 1.00\\
+0.4 & 0.017 & 0.012 & 0.016 & 3.2 & 0.76\\
 \enddata
@@
 \colhead{$\alpha=2.5$} } \startdata
-0.3 & 0.69 & 0.57 & 0.48 & 1.14 & 1.63 & 2.25 \\
-0.5 & 0.97 & 0.80 & 0.68 & 1.60 & 2.28 & 3.17 \\
-0.7 & 1.40 & 1.17 & 0.99 & 2.32 & 3.32 & 4.61 \\
+0.3 & 0.69 & 0.57 & 0.48 & 1.38 & 1.95 & 2.68 \\
+0.5 & 0.97 & 0.80 & 0.68 & 1.94 & 2.74 & 3.78 \\
+0.7 & 1.40 & 1.17 & 0.99 & 2.80 & 3.97 & 5.50 \\
 \hline
@@
 \hline
-0.3 & 0.46 & 1.05 & ~~4.55 & 0.17 & 0.11 & 0.15 \\
-0.5 & 0.74 & 1.70 & ~~7.47 & 0.27 & 0.18 & 0.25 \\
-0.7 & 1.09 & 2.59 &  11.55 & 0.41 & 0.28 & 0.37 \\
+0.3 & 0.46 & 1.05 & ~~4.55 & 0.11 & 0.08 & 0.11 \\
+0.5 & 0.74 & 1.70 & ~~7.47 & 0.18 & 0.13 & 0.17 \\
+0.7 & 1.09 & 2.59 &  11.55 & 0.27 & 0.19 & 0.26 \\
 \enddata
